### 2022-10-25 JASA-template.tex
Initial Overleaf Import

\documentclass{amsart}
\usepackage[foot]{amsaddr} % put addresses on first page

\usepackage{geometry}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsmath}
\allowdisplaybreaks
\usepackage{longtable}
\usepackage{bigints}
\usepackage{siunitx}
\usepackage{amsthm}
\usepackage{soul}
\usepackage{tikz}
\usepackage{color}
\usepackage{easyReview} % for \comment, \alert, etc.

\newcommand{\addition}[1]{#1}

\usepackage{hyperref}
\usepackage[capitalise]{cleveref}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
%

\usepackage[numbers]{natbib}
\usepackage{url} % not crucial - just used below for the URL 
\usepackage{doi}

\newcommand{\x}{\boldsymbol{X}}
\renewcommand{\b}{\hat{\beta}}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\normal}{\mathcal{N}}
\newcommand{\lexp}{\underline{\text{E}}}
\newcommand{\uexp}{\overline{\text{E}}}

\keywords{high dimensional data; variable selection; Bayesian analysis; imprecise probability}

\begin{document}

\title{Robust Bayesian Analysis of Causal Inference Problems}
\author{Tathagata Basu$^1$}
\email{tathagatabasumaths@gmail.com}
\author{Matthias C.~M.~Troffaes$^2$}
\email{matthias.troffaes@durham.ac.uk}
\author{Jochen Einbeck$^{2,3}$}
\email{jochen.einbeck@durham.ac.uk}
\address{$^1$UMR CNRS 7253 Heudiasyc, Universit\'{e} de Technologie de
Compi\`{e}gne}
\address{$^2$Department of Mathematical Sciences, Durham University}
\address{$^3$Durham Research Methods Centre}

\begin{abstract}
Causal inference using observational data is an important aspect in
many fields such as epidemiology, social science, economics, etc. In
particular, our goal is to find the treatment effect on the subjects
along with the causal links between the variables and the outcome.
However, estimation for such problems are extremely 
difficult as the treatment effects may vary from subject 
to subject and modelling the underlying heterogeneity explicitly makes the 
problem practically unsolvable. Another issue we face is the 
dimensionality of the problem and we may wish to find a subset of 
explanatory variables. However, standard variable selection methods
tend to maximise the predictive performance of the outcome model only and
can also be sensitive with respect to the choice of priors, particularly 
in the case of limited information. So, in this paper, we suggest a 
robust Bayesian analysis of causal inferential methods for 
high-dimensional problems in a regressional framework. We consider
a set of spike and slab priors to obtain robust estimates for
both the treatment and outcome model. We are specifically interested 
in the importance of priors in the high dimensional causal inference
as well as the identifying the confounder variables. However, indicator
based confounder selection can be deceptive in some cases. Especially, 
when the predictor is strongly associated with either the treatment or 
the outcome. This increases the posterior expectation of the selection
indicators. To avoid that we also apply a post-hoc selection scheme
which successfully remove negligible non-zero effects from the model
attaining a sparser model. Finally, we illustrate
our result using synthetic \alert{and real} dataset.

\end{abstract}

\maketitle

\section{Introduction}\label{sec:intro}

In causal inference, we are interested in estimating the causal
effect of independent variables on a dependent variable. Ideally,
randomised trials are the most efficient way to perform this task.
However, this is not very practical for several reasons; ethical 
concerns, design cost, population size, to name a few. This
leaves us with observational studies which are usually obtained
by means collecting data though surveys or record keeping.

Let an observational study give us the outcomes $Y=(Y_1$, \dots, $Y_n)$ along with 
corresponding treatment indicators $T=(T_1$, \dots, $T_n)$. Then the
individual causal
effect of the treatment $T_i$ on outcome $Y_i$ is given by:
\begin{align}
\delta \coloneqq E(Y\mid T=1) - E(Y\mid T=0).
\end{align}
However, we can not observe $(Y_i\mid T_i=1)$ and $(Y_i\mid T_i=0)$
simultaneously for the $i$-th individual. Instead, we can estimate
average causal effect of the treatment $T$ so that
\begin{align}
\hat{\delta} \coloneqq 
\frac{\sum_{i=1}^n(Y_i\mid T_i=1) - (Y_i\mid T_i=0)}{n}.
\end{align}
Now, let $X\coloneqq$ $[X_1$, \dots, $X_n]^T$ 
denote the $p$-dimensional covariates present in the studies and $\beta \coloneqq (\beta_1$, \dots, $\beta_p)$ denotes the vector of regression
coefficients. Then we can define a linear model for the outcome
so that
\begin{equation}
    Y_i = \beta_{T} T_i + \beta_0 + X\beta + \epsilon_i
\end{equation}
where $\epsilon_i\sim \mathcal{N}(0, \sigma^2)$. Clearly, when
the underlying true outcome model is linear,
\begin{equation}
    \delta = \beta_{T}\quad\text{and hence } 
    \hat{\delta} - \delta = \hat{\beta}_T - \beta_T.
\end{equation}

\begin{figure}
    \centering
    \begin{tikzpicture}[roundnode/.style={circle, draw=green!60, fill=green!5, very thick, minimum size=7mm},
squarednode/.style={rectangle, draw=red!60, fill=red!5, very thick, minimum size=5mm}]
    \node (1) at (0,0) {Treatment ($T$)};
    \node (2) [right = of 1] {Outcome ($Y$)};
    \node (4) [below = of 1] {Input ($X$)};

    \path (1) edge[->]  (2);
    \path (1) edge[<-]  (4);
    \path (2) edge[<-] (4);
\end{tikzpicture}
\caption{Confounding in causal models.}
    \label{fig:my_label}
\end{figure}

\citet{koch2020} suggested the use of a probit model to specify the conditional probability that
subject $i$ receives the treatment. That is,
\begin{align}
    P(T_i=1\mid X_i) = \Phi(X_i^T\gamma).
\end{align}
Therefore, we can define intermediate variables $T_i^*$ so that, $T_i=1$ if $T_i^*>0$ and
$T_i=0$ if $T_i^*\le0$. Now, following the approach of \citet{koch2018}, we define an adjusted
output vector $W\coloneqq(Y, T^*)^T$ and corresponding $2n\times(2p+1)$ dimensional design matrix
\begin{align}
    \boldsymbol{Z} &=
    \begin{bmatrix}
     X_O & 0 \\
     0 & X
    \end{bmatrix},
\end{align}
where, $X_0 = [T, X]$. Then, assuming Gaussian error term, we have the following likelihood function
\begin{align}
W\mid Z, \alpha, \beta, \gamma, \sigma^2 \sim\normal\left(Z\nu, \sigma^2\mathbf{I}_{2n}\right),
\end{align}
where $\nu = (\alpha, \beta, \gamma)^T$.

\section{Robust Bayesian Analysis}
\subsection{Hierarchical model}
We perform a robust Bayesian analysis to obtain robust estimates. To do so, we propose the
following spike and slab priors \cite{ishwaran2005} to specify $\beta$ and $\gamma$.
For $1\le j\le p$,
\begin{align}
    \beta_j \mid \pi_{\beta}, \sigma^2 &\sim 
    \pi_{\beta}\normal\left(0, \tau_1^2\sigma^2\right) 
    + (1-\pi_{\beta}) \normal\left(0, \tau_0^2\sigma^2\right)\\
    \gamma_j \mid \pi_{\gamma} &\sim 
    \pi_{\gamma}\normal\left(0, \tau_1^2\right) 
    + (1-\pi_{\gamma}) \normal\left(0, \tau_0^2\right)\\
    \alpha\mid \sigma^2 &\sim \normal(0, \sigma^2)\\
    \sigma^2&\sim \text{InvGamma}(a, b)\\
    \pi_{\beta}, \pi_{\gamma}&\sim\text{Beta}\left(sq, s(1-q)\right).
\end{align}
We fix sufficiently small $\tau^2_0$
$(1\gg\tau_0^2>0)$ so that  $(\beta_j, \gamma_j) = (0,0)$ has its probability mass 
concentrated around zero. Therefore, this represents the spike component of our prior specification. 
To construct the slab component, we consider $\tau_1^2$ to be large so that 
$\tau_1^2\gg\tau_0^2$. This allows the prior for $(\beta_j, \gamma_j)\not=(0,0)$ to be flat.

We use a set beta priors to specify the selection probability
$\pi_j$ of the $j$-th group where  $q_j$ represents our prior expectation of the 
selection probability ($\pi_j$) and `$s$' represents a concentration parameter. We perform our
robust Bayesian analysis on $q\coloneqq(q_1$, \dots, $q_p)\in\mathcal{P}$, where
\begin{equation}
    \mathcal{P} \coloneqq \mathcal{P}_1\times\cdots\times\mathcal{P}_p\subseteq \left(0, 1\right)^{p}.
\end{equation}

\subsection{Co-variate selection}
For the co-variate selection, we look into the posterior expectation of $\pi_j$. 
We consider the $j$-th group to be active, if
\begin{align}
    \lexp (\pi_j\mid W)\coloneqq \inf_{q_j\in \mathcal{P}_j} \text{E}(\pi_j\mid W) > 1/2
\end{align}
and inactive, if
\begin{align}
    \uexp(\pi_j\mid W) \coloneqq \sup_{q_j\in \mathcal{P}_j} \text{E}(\pi_j\mid W)< 1/2.
\end{align}
We consider the rest to be indecisive.

This way, we get a robust group selection routine. However, this type of variable 
selection includes both treatment and outcome effects at the same time. This may not be the
case in some cases especially when either treatment effect or the outcome effect is zero or
weak. To deal with such problems, we suggest the following ad-hoc method to obtain 
adjusted sparse estimate of the zero effect in a selected group.
Let $\mathcal{S}$ denote the set of active co-variates present in the model. That is,
\begin{equation}
    \mathcal{S}\coloneqq
    \left\{j : \lexp(\pi_j\mid W) > 1/2\right\}.
\end{equation}
Let $\hat{\beta}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression
coefficients for the non-zero outcome effects and
$\hat{\gamma}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression
coefficients for the non-zero treatment effects. We apply the 
``decoupled shrinkage and selection'' method proposed by \citet{hahn2015}, to obtain
the sparse estimate. To do so, we solve the following adaptive LASSO-type \cite{Zou2006}
problems

\begin{align}
    \hat{\beta}^*_{\mathcal{S}}(q_{\mathcal{S}}) &= 
    \arg\min_{\beta_{\mathcal{S}}} \frac{1}{n}\|\x_{\mathcal{S}}\hat{\beta}_{\mathcal{S}}(q_{\mathcal{S}})
    - \x_{\mathcal{S}} \beta_{\mathcal{S}}\|_2^2 + \lambda_1\sum_{j\in\mathcal{S}} 
    \frac{|\beta_j|}{|\hat{\beta}_j(q_j)|}
\end{align}
and
\begin{align}
    \hat{\gamma}^*_{\mathcal{S}}(q_{\mathcal{S}}) &= 
    \arg\min_{\gamma_{\mathcal{S}}} \frac{1}{n}\|\x_{\mathcal{S}}\hat{\gamma}_{\mathcal{S}}(q_{\mathcal{S}})
    - \x_{\mathcal{S}} \gamma_{\mathcal{S}}\|_2^2 + \lambda_1\sum_{j\in\mathcal{S}} 
    \frac{|\gamma_j|}{|\hat{\gamma}_j(q_j)|}
\end{align}
where $q_{\mathcal{S}}\in \mathcal{P}_{\mathcal{S}}$.

\bibliographystyle{agsm}
\bibliography{basu22}
\end{document}

### 2022-10-27 JASA-template.tex
some update

@@
 leaves us with observational studies which are usually obtained
-by means collecting data though surveys or record keeping.
+by means collecting data though surveys or record keeping. But this
+can be problematic in the presence of confounders. That is when
+the variables are associated with both the treatment and the outcome.
+In such cases, we need to be extra cautious as otherwise it will
+lead to unwanted bias in the treatment effect estimator \cite{rosenbaum83}.
+
+Several works have been done in order to tackle the presence of
+confounder variables. One such work in the topic was 
+by \citet{Robins1986ANA} where the author used  a graphical
+approach for the identification of the causal parameters.
+\citet{rosenbaum1985} suggested the use of a link model to estimate
+the propensity scores for all individuals. Later on several other
+methods have been proposed based on propensity score matching.
+A brief review on such methods can be found in \cite{winship99, stuart10}.
+
+Bayesian approach in causal effect estimation has become a popular
+topic in recent days. However, one of the earlier works on this can be
+found in \cite{rubin1978}. Lately with the notion of variable selection
+of high dimensional problems, Bayesian methodologies have become
+more significant.
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[params/.style={circle, draw=green!60, fill=green!5, very thick, minimum size=7mm}]
+	\node (1) at (0,0) {Treatment ($T$)};
+	\node (2) [right = of 1] {Outcome ($Y$)};
+	\node (4) [below = of 1] {Input ($X$)};
+
+	\path (1) edge[->]  (2);
+	\path (1) edge[<-]  (4);
+	\path (2) edge[<-] (4);
+	\end{tikzpicture}
+	\caption{Confounding in causal models.}
+	\label{fig:confounding}
+\end{figure}
 
@@
 \end{align}
+This relies on an important assumption that the treatment effect
+on the $i$-th subject given that they received the treatment is
+equal to the treatment effect when they remain as the control
+\cite{winship99}.
+
 Now, let $X\coloneqq$ $[X_1$, \dots, $X_n]^T$ 
@@
 \end{equation}
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}[roundnode/.style={circle, draw=green!60, fill=green!5, very thick, minimum size=7mm},
-squarednode/.style={rectangle, draw=red!60, fill=red!5, very thick, minimum size=5mm}]
-    \node (1) at (0,0) {Treatment ($T$)};
-    \node (2) [right = of 1] {Outcome ($Y$)};
-    \node (4) [below = of 1] {Input ($X$)};
-
-    \path (1) edge[->]  (2);
-    \path (1) edge[<-]  (4);
-    \path (2) edge[<-] (4);
-\end{tikzpicture}
-\caption{Confounding in causal models.}
-    \label{fig:my_label}
-\end{figure}
 
@@
 \subsection{Hierarchical model}
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[params/.style={circle, draw=black!60, very thick, minimum size=7mm},
+	hyper/.style={circle, draw=black!60, fill=black!20, thick, minimum size=7mm},
+	latent/.style={rectangle, draw=black!60, fill=black!10, dashed, minimum size=7mm},
+	data/.style={rectangle, draw=black!60, thick, minimum size=8mm}]
+	\node[params] (1) at (0,0) {$\pi$};
+	\node[data] (2) at (3,0) {$X$};
+	\node[data] (3) at (6,0) {$T$};
+	\node[params] (4) at (1.5,1.5) {$\gamma$};
+	\node[latent] (5) at (4.5,1.5) {$T^*$};
+	\node[params] (6) at (1.5,-1.5) {$\beta$};
+	\node[data] (7) at (3.5,-1.5) {$Y$};
+	\node[hyper] (8) at (-1.5,-3) {$\sigma^2$};
+	\node[params] (9) at (3,-3) {$\beta_0$};
+	\node[params] (10) at (5.5,-1.5) {$\beta_T$};
+	\node[hyper] (11) at (-1.5,-1) {$s$};
+	\node[hyper] (12) at (-1.5,1) {$\alpha$};
+	\draw[black, dashed] (-0.75,-3.75) rectangle (7,2.5);
+
+	\path (1) edge[->]  (6);
+	\path (1) edge[->]  (4);
+	\path (8) edge[->]  (6);
+	\path (6) edge[->]  (7);
+	\path (2) edge[->]  (7);
+	\path (2) edge[->]  (5);
+	\path (5) edge[<-] (4);
+	\path (5) edge[->] (3);
+	\path (3) edge[->]  (7);
+	\path (9) edge[->]  (7);
+	\path (10) edge[->]  (7);
+	\path (2) edge[dashed][->] (3);
+	\path (8) edge[bend right = 60][->]  (10);
+	\path (8) edge[->]  (9);
+	\path (11) edge[->]  (1);
+	\path (12) edge[->]  (1);
+
+	\end{tikzpicture}
+	\caption{Probabilistic graphical representation for causal inference with Bayesian hierarchical model.}
+	\label{fig:regress}
+\end{figure}
+
 We perform a robust Bayesian analysis to obtain robust estimates. To do so, we propose the

### 2022-10-27 JASA-template.tex
some more update

@@
 topic in recent days. However, one of the earlier works on this can be
-found in \cite{rubin1978}. Lately with the notion of variable selection
-of high dimensional problems, Bayesian methodologies have become
-more significant.
+found in \cite{rubin1978}. Lately with the notion of high dimensional problems, Bayesian methodologies have become
+more appealing. \citet{Crainiceanu2008} proposed a bi-level 
+Bayesian model averaging based method for estimating the causal 
+effect. \citet{wang2015} suggested BAC (or, Bayesian adjustment for
+confounding) where they use an informative prior obtained from
+the treatment model and apply them on the outcome model for
+estimating causal effect. Several other methods were also
+proposed to tackle confounders from the point of view of Bayesian
+variable selection such as: \citet{Zigler2014}, \citet{Hahn2018} etc.
+
+In this paper we closely follow the approach of \citet{koch2020}, where
+they proposed a bilevel spike and slab prior for causal effect 
+estimation. They considered a data-driven adaptive approach to
+reduce the variance of the causal estimate. Instead of that,
+we suggest a robust Bayesian analysis based approach where instead
+of using a single prior, we consider a set of priors \cite{BERGER1990303}. This is particularly interesting as in
+many cases, causal effect estimation can be performed through a 
+meta analysis and hence having a single prior can be problematic.
+Moreover, for some problems we have to rely on very limited data to
+perform our Bayesian analysis and choosing a data-driven prior
+can lead to overfitting.
 

### 2022-10-28 JASA-template.tex
intro done

@@
 lead to unwanted bias in the treatment effect estimator \cite{rosenbaum83}.
-
 Several works have been done in order to tackle the presence of
@@
 
-In this paper we closely follow the approach of \citet{koch2020}, where
+In this paper we take inspiration from the approach of \citet{koch2020}, where
 they proposed a bilevel spike and slab prior for causal effect 
 estimation. They considered a data-driven adaptive approach to
-reduce the variance of the causal estimate. Instead of that,
-we suggest a robust Bayesian analysis based approach where instead
+propose their prior which reduce the variance of the causal estimate. 
+In our approach,
+we suggest a sensitivity analysis based approach where instead
 of using a single prior, we consider a set of priors \cite{BERGER1990303}. This is particularly interesting as in
 many cases, causal effect estimation can be performed through a 
-meta analysis and hence having a single prior can be problematic.
+meta analysis and hence robust Bayesian analysis can be beneficial
+\cite{raices_cruz22} under severe uncertainty.
 Moreover, for some problems we have to rely on very limited data to
 perform our Bayesian analysis and choosing a data-driven prior
-can lead to overfitting.
+can lead to overfitting. Therefore, as to propose our
+robust Bayesian framework,
+we consider a set of continuous spike and slab priors \cite{ishwaran2005}
+for confounder selection and construct a Bayesian group LASSO
+\cite{xu2015}. To perform the sensitivity analysis, we consider
+a set of beta priors on the covariate selection probability
+of the spike and slab priors. This sensitivity analysis allows us
+to investigate the regression coefficients with respect to a different
+level of sparsity of the model. Following that, we consider a post-hoc
+variable selection method as suggested by \citet{hahn2015}. This
+ensures that we can efficiently separate the confounder variables
+with others and reduce the bias of treatment effect estimation.
 
-\begin{figure}
-	\centering
-	\begin{tikzpicture}[params/.style={circle, draw=green!60, fill=green!5, very thick, minimum size=7mm}]
-	\node (1) at (0,0) {Treatment ($T$)};
-	\node (2) [right = of 1] {Outcome ($Y$)};
-	\node (4) [below = of 1] {Input ($X$)};
+The rest of the paper is organised as follows. In \cref{sec:causal}
+we give a formal description of causal estimation problem in the
+context of linear regression. \cref{sec:bayes} is focused on the
+Bayesian analysis of causal inference problems, followed by the
+motivation of a robust Bayesian analysis. In \cref{sec:sim}, we
+provide our result of simulation studies under different 
+scenarios and in data analysis with real data in \cref{sec:data:analysis}. Finally we discuss our findings and 
+conclude this paper in \cref{sec:conc}.
 
-	\path (1) edge[->]  (2);
-	\path (1) edge[<-]  (4);
-	\path (2) edge[<-] (4);
-	\end{tikzpicture}
-	\caption{Confounding in causal models.}
-	\label{fig:confounding}
-\end{figure}
+\section{Causal Estimation}\label{sec:causal}
 
@@
 \end{equation}
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[params/.style={circle, draw=green!60, fill=green!5, very thick, minimum size=7mm}]
+	\node (1) at (0,0) {Treatment ($T$)};
+	\node (2) [right = of 1] {Outcome ($Y$)};
+	\node (4) [below = of 1] {Input ($X$)};
+
+	\path (1) edge[->]  (2);
+	\path (1) edge[<-]  (4);
+	\path (2) edge[<-] (4);
+	\end{tikzpicture}
+	\caption{Confounding in causal models.}
+	\label{fig:confounding}
+\end{figure}
 
@@
 
-\section{Robust Bayesian Analysis}
+\section{Bayesian Hierarchical model}\label{sec:bayes}
 \subsection{Hierarchical model}
@@
 
+\section{Simulation Studies}\label{sec:sim}
+
+\section{Data Analysis}\label{sec:data:analysis}
+
+\section{Conclusion}\label{sec:conc}
+
 \bibliographystyle{agsm}

### 2022-10-28 JASA-template.tex
causal

@@
 \begin{align}
-\delta \coloneqq E(Y\mid T=1) - E(Y\mid T=0).
+\delta_i \coloneqq (Y_i\mid T_i=1) - (Y_i\mid T_i=0).
 \end{align}
+That is, the difference between the outcome when $i$-th subject receives
+the treatment and when $i$-th subject remain as a control. Similarly, treatment 
+effect of the population is given by the expectation of difference
+in outcome between the treatment and controls. 
+\begin{align}
+	\delta = \mathbb{E}(Y\mid T =1) - E(Y\mid T=0).
+\end{align}
+
+In theory, both of these quantities exist.
 However, we can not observe $(Y_i\mid T_i=1)$ and $(Y_i\mid T_i=0)$
 simultaneously for the $i$-th individual. Instead, we can estimate
-average causal effect of the treatment $T$ so that
+average causal effect of the treatment $T$ by calculating the averaged
+outcome of all the subjects those received the treatment and
+all the subjects those remained as control.
 \begin{align}
 \hat{\delta} \coloneqq 
-\frac{\sum_{i=1}^n(Y_i\mid T_i=1) - (Y_i\mid T_i=0)}{n}.
+\frac{\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=1) - 
+	\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=0)}{n}.
 \end{align}
-This relies on an important assumption that the treatment effect
+However, this relies on an important assumption that the treatment effect
 on the $i$-th subject given that they received the treatment is

### 2022-10-29 JASA-template.tex
causal effect update

@@
+% !TeX spellcheck = en_GB
+
 \documentclass{amsart}
 \usepackage[foot]{amsaddr} % put addresses on first page
-
+\usepackage[british]{babel}
 \usepackage{geometry}
@@
 \usepackage{bigints}
-\usepackage{siunitx}
+%\usepackage{siunitx}
 \usepackage{amsthm}
@@
 corresponding treatment indicators $T=(T_1$, \dots, $T_n)$. Then the
-individual causal
+treatment 
+effect in the population is given by the expectation of the difference
+in outcome between the treatment and controls. 
+\begin{align}
+\delta = \mathbb{E}(Y\mid T =1) - E(Y\mid T=0).
+\end{align}
+Similarly, individual causal
 effect of the treatment $T_i$ on outcome $Y_i$ is given by:
@@
 That is, the difference between the outcome when $i$-th subject receives
-the treatment and when $i$-th subject remain as a control. Similarly, treatment 
-effect of the population is given by the expectation of difference
-in outcome between the treatment and controls. 
-\begin{align}
-	\delta = \mathbb{E}(Y\mid T =1) - E(Y\mid T=0).
-\end{align}
+the treatment and when $i$-th subject remain as a control.
 
@@
 
-Now, let $X\coloneqq$ $[X_1$, \dots, $X_n]^T$ 
-denote the $p$-dimensional covariates present in the studies and $\beta \coloneqq (\beta_1$, \dots, $\beta_p)$ denotes the vector of regression
+\subsection{Regression Model}
+Regression methods are widely used in causal effect estimation. The
+main idea behind these regression methods is to remove the
+correlation between the treatment indicator and the error term
+\cite{winship99,HECKMAN1985}. To do so, we rely on $p$ different observed quantities
+or predictors denoted by $X\coloneqq$ $[X_1$, \dots, $X_n]^T$. Now, let
+$\beta \coloneqq (\beta_1$, \dots, $\beta_p)$ denotes the vector of regression
 coefficients. Then we can define a linear model for the outcome
@@
 \begin{align}
-    \boldsymbol{Z} &=
+    Z &=
     \begin{bmatrix}
@@
 \end{align}
-where, $X_0 = [T, X]$. Then, assuming Gaussian error term, we have the following likelihood function
+where, $X_O = [T, X]$. Then, assuming Gaussian error term, we have the following likelihood function
 \begin{align}

### 2022-10-29 JASA-template.tex
more cleaning

@@
 \begin{equation}
-    Y_i = \beta_{T} T_i + \beta_0 + X\beta + \epsilon_i
+    Y_i = \beta_{T} T_i + \beta_0 + X_i\beta + \epsilon_i
 \end{equation}
@@
 	\node (2) [right = of 1] {Outcome ($Y$)};
-	\node (4) [below = of 1] {Input ($X$)};
+	\node (4) [below = of 1] {Predictors ($X$)};
 
@@
 
-\citet{koch2020} suggested the use of a probit model to specify the conditional probability that
-subject $i$ receives the treatment. That is,
+In the presence of confounders we also need to consider the
+association between the treatment indicators and the predictors.
+\citet{koch2020} suggested the use of a probit link function to 
+construct the regression model. This way, we can
+specify the conditional probability that subject $i$ receives the treatment through a linear model. 
+That is, for another vector of regression coefficients 
+$\gamma\coloneqq(\gamma_1, \cdots, \gamma_p)$ we define
 \begin{align}
-    P(T_i=1\mid X_i) = \Phi(X_i^T\gamma).
+    P(T_i=1\mid X_i) \coloneqq \Phi(\gamma_0+X_i\gamma)
 \end{align}
-Therefore, we can define intermediate variables $T_i^*$ so that, $T_i=1$ if $T_i^*>0$ and
-$T_i=0$ if $T_i^*\le0$. Now, following the approach of \citet{koch2018}, we define an adjusted
+where $\Phi(\cdot)$ denotes the cumulative distribution function
+of a standard normal distribution.
+
+This allows us to define intermediate latent variables 
+\begin{equation}
+	T_i^* = \gamma_0 + X_i\gamma +u_i
+\end{equation}
+where, $u_i\sim\mathcal{N}(0,1)$. Therefore, $T_i=1$ if $T_i^*>0$ and
+$T_i=0$ if $T_i^*\le0$.
+
+Now, following the approach of \citet{koch2018}, we define an adjusted
 output vector $W\coloneqq(Y, T^*)^T$ and corresponding $2n\times(2p+1)$ dimensional design matrix

### 2022-10-31 JASA-template.tex
bayes

@@
 
-This allows us to define intermediate latent variables 
+This allows us to define intermediate latent variables as suggested
+by \citet{albert93}
 \begin{equation}
@@
 Now, following the approach of \citet{koch2018}, we define an adjusted
-output vector $W\coloneqq(Y, T^*)^T$ and corresponding $2n\times(2p+1)$ dimensional design matrix
+output vector $W\coloneqq(Y, T^*)^T$ and corresponding $2n\times(2p+3)$ dimensional design matrix
 \begin{align}
@@
      X_O & 0 \\
-     0 & X
+     0 & X_T
     \end{bmatrix},
 \end{align}
-where, $X_O = [T, X]$. Then, assuming Gaussian error term, we have the following likelihood function
+where, $X_O = [T, 1_n, X]$ and $X_T = [1_n, X]$. Then, assuming a
+Gaussian error term, we have the following likelihood distribution
 \begin{align}
-W\mid Z, \alpha, \beta, \gamma, \sigma^2 \sim\normal\left(Z\nu, \sigma^2\mathbf{I}_{2n}\right),
+W\mid Z, \alpha, \beta, \gamma, \sigma^2 \sim\normal\left(Z\nu, \Sigma\right)\label{eq:like:group},
 \end{align}
-where $\nu = (\alpha, \beta, \gamma)^T$.
+where $\nu = (\beta_T, \beta_0, \beta, \gamma_0, \gamma)^T$ and
+\begin{align}
+\Sigma &=
+\begin{bmatrix}
+\sigma^2{I}_n & 0 \\
+0 & {I}_n
+\end{bmatrix}.
+\end{align}
 
-\section{Bayesian Hierarchical model}\label{sec:bayes}
+\section{Bayesian Causal Estimation}\label{sec:bayes}
+
+The likelihood formation given by \cref{eq:like:group} gives us
+a foundation for Bayesian group LASSO 
+\cite{xu2015} type model and look into the posterior selection
+probability associated with the $j$-th predictor. There are several
+ways to construct spike and slab priors which achieve 
+variable selection. In our case, we consider a continuous type
+\cite{ishwaran2005} prior for faster posterior
+computation.
+
 \subsection{Hierarchical model}
+
+Let, $\pi_j$ denote the prior probability that the $j$-th
+predictor is not associated with either the outcome or the 
+treatment. That is, 
+\begin{equation}
+	\pi_j = P\left((\beta_j,\gamma_j)=(0,0)\right).
+\end{equation}
+Then we can define a spike and slab group LASSO so that:
+for $1\le j\le p$,
+\begin{align}
+(\beta_j,\gamma_j)^T \mid \pi_{j}, \sigma^2 &\sim 
+(1-\pi_{j})\normal\left( (0,0)^T, 
+\tau_1^2\begin{bmatrix}
+\sigma^2 & 0 \\
+0 & 1
+\end{bmatrix}\right)
++ \pi_{j} \normal\left(0, 
+\tau_0^2\begin{bmatrix}
+\sigma^2 & 0 \\
+0 & 1
+\end{bmatrix}\right)\\
+%\beta_T, \beta_0\mid \sigma^2 &\sim \normal(0, \sigma^2)\\
+%\gamma_0 &\sim \normal(0,1)\\
+\sigma^2&\sim \text{InvGamma}(a, b)\\
+\pi_{j} &\sim\text{Beta}\left(sq_j, s(1-q_j)\right).
+\end{align}
+
+We fix sufficiently small $\tau^2_0$
+$(1\gg\tau_0^2>0)$ so that  $(\beta_j, \gamma_j) = (0,0)$ has its probability mass 
+concentrated around zero. Therefore, this represents the spike component of our prior specification. 
+To construct the slab component, we consider $\tau_1^2$ to be large so that 
+$\tau_1^2\ge 1$. This allows the prior for $(\beta_j, \gamma_j)\not=(0,0)$ to be flat.
+
+As mentioned earlier, $\pi_j$ is used as the rejection probability
+of the $j$-th predictor and we use a set beta priors to specify 
+these rejection probabilities where  $q_j$ represents our prior expectation of the rejection probability ($\pi_j$) and `$s$' acts as 
+a concentration parameter.
+For the intercept terms of the outcome model and the causal effect, 
+we consider a sufficiently flat prior so that 
+$\beta_0. \beta_T\sim \normal(0,\sigma^2)$. Similarly, for the
+intercept term in the treatment model, we consider 
+$\gamma_0\sim \normal(0,1)$.
 
@@
 	hyper/.style={circle, draw=black!60, fill=black!20, thick, minimum size=7mm},
+	post/.style={circle, draw=black!60, fill=green!20, thick, minimum size=7mm},
 	latent/.style={rectangle, draw=black!60, fill=black!10, dashed, minimum size=7mm},
@@
 	\node[data] (7) at (3.5,-1.5) {$Y$};
-	\node[hyper] (8) at (-1.5,-3) {$\sigma^2$};
+	\node[params] (8) at (0,-3) {$\sigma^2$};
 	\node[params] (9) at (3,-3) {$\beta_0$};
-	\node[params] (10) at (5.5,-1.5) {$\beta_T$};
-	\node[hyper] (11) at (-1.5,-1) {$s$};
-	\node[hyper] (12) at (-1.5,1) {$\alpha$};
-	\draw[black, dashed] (-0.75,-3.75) rectangle (7,2.5);
+	\node[params] (10) at (6,-1.5) {$\beta_T$};
+	\node[hyper] (11) at (-1.5,-.8) {$s$};
+	\node[hyper] (12) at (-1.5,.8) {$q$};
+	\node[hyper] (13) at (-1.5,-2.2) {$a$};
+	\node[hyper] (14) at (-1.5,-3.8) {$b$};
+	\draw[black, dashed] (0.75,-3.7) rectangle (7,2.1);
 
@@
 	\path (12) edge[->]  (1);
+	\path (13) edge[->]  (8);
+	\path (14) edge[->]  (8);
 
@@
 \end{figure}
-
-We perform a robust Bayesian analysis to obtain robust estimates. To do so, we propose the
-following spike and slab priors \cite{ishwaran2005} to specify $\beta$ and $\gamma$.
-For $1\le j\le p$,
-\begin{align}
-    \beta_j \mid \pi_{\beta}, \sigma^2 &\sim 
-    \pi_{\beta}\normal\left(0, \tau_1^2\sigma^2\right) 
-    + (1-\pi_{\beta}) \normal\left(0, \tau_0^2\sigma^2\right)\\
-    \gamma_j \mid \pi_{\gamma} &\sim 
-    \pi_{\gamma}\normal\left(0, \tau_1^2\right) 
-    + (1-\pi_{\gamma}) \normal\left(0, \tau_0^2\right)\\
-    \alpha\mid \sigma^2 &\sim \normal(0, \sigma^2)\\
-    \sigma^2&\sim \text{InvGamma}(a, b)\\
-    \pi_{\beta}, \pi_{\gamma}&\sim\text{Beta}\left(sq, s(1-q)\right).
-\end{align}
-We fix sufficiently small $\tau^2_0$
-$(1\gg\tau_0^2>0)$ so that  $(\beta_j, \gamma_j) = (0,0)$ has its probability mass 
-concentrated around zero. Therefore, this represents the spike component of our prior specification. 
-To construct the slab component, we consider $\tau_1^2$ to be large so that 
-$\tau_1^2\gg\tau_0^2$. This allows the prior for $(\beta_j, \gamma_j)\not=(0,0)$ to be flat.
-
-We use a set beta priors to specify the selection probability
-$\pi_j$ of the $j$-th group where  $q_j$ represents our prior expectation of the 
-selection probability ($\pi_j$) and `$s$' represents a concentration parameter. We perform our
-robust Bayesian analysis on $q\coloneqq(q_1$, \dots, $q_p)\in\mathcal{P}$, where
-\begin{equation}
-    \mathcal{P} \coloneqq \mathcal{P}_1\times\cdots\times\mathcal{P}_p\subseteq \left(0, 1\right)^{p}.
-\end{equation}
 
@@
 
+\subsection{Robust Bayesian Analysis}
+We perform our
+robust Bayesian analysis on $q\coloneqq(q_1$, \dots, $q_p)\in\mathcal{P}$, where
+\begin{equation}
+\mathcal{P} \coloneqq \mathcal{P}_1\times\cdots\times\mathcal{P}_p\subseteq \left(0, 1\right)^{p}.
+\end{equation}
+
 \section{Simulation Studies}\label{sec:sim}

### 2022-10-31 JASA-template.tex
some corrections

@@
 concentrated around zero. Therefore, this represents the spike component of our prior specification. 
-To construct the slab component, we consider $\tau_1^2$ to be large so that 
-$\tau_1^2\ge 1$. This allows the prior for $(\beta_j, \gamma_j)\not=(0,0)$ to be flat.
+To construct the slab component, we consider $\tau_1^2$ to be large so that $\tau_1^2\ge 1$. This allows the prior for $(\beta_j, \gamma_j)\not=(0,0)$ to be flat. Inverse-Gamma is a natural choice
+for the variance of the Gaussian noise because of conjugacy. To
+make the prior flat, we consider $1\gg a, b >0$.
 
-As mentioned earlier, $\pi_j$ is used as the rejection probability
-of the $j$-th predictor and we use a set beta priors to specify 
+As indicated earlier, $\pi_j$ is used as the rejection probability
+of the $j$-th predictor and we use a beta prior to specify 
 these rejection probabilities where  $q_j$ represents our prior expectation of the rejection probability ($\pi_j$) and `$s$' acts as 
@@
 $\gamma_0\sim \normal(0,1)$.
+
+In \cref{fig:regress}, we show a probabilistic graphical representation
+of our hierarchical model. In the figure, grey circular nodes represent the
+prior hyper-parameters which will be used for sensitivity analysis
+of the model. The transparent circular nodes are used to denote
+the modelling parameters which are our quantities of interest. 
+The observed quantities are denoted with transparent rectangular
+nodes. We also use a grey rectangular node to denote the intermediate
+latent variable $T^*$. We use directed edges to denote the
+relationship between different nodes. However, we use a dashed
+edge between $X$ and $T$ as we they are related through the latent
+variable $T^*$. This dashed edge also establish the notion of
+confounding as shown in \cref{fig:confounding}.
 

### 2022-11-01 JASA-template.tex
dss addition

@@
 
-\subsection{Co-variate selection}
+\subsection{Variable selection and coefficient adjustment}
 For the co-variate selection, we look into the posterior expectation of $\pi_j$. 
-We consider the $j$-th group to be active, if
+We consider the $j$-th predictor to be removed from both the
+treatment and outcome model, if
 \begin{align}
-    \lexp (\pi_j\mid W)\coloneqq \inf_{q_j\in \mathcal{P}_j} \text{E}(\pi_j\mid W) > 1/2
+    \lexp (\pi_j\mid W)\coloneqq \inf_{q_j\in \mathcal{P}_j} \text{E}(\pi_j\mid W) > 1/2.
 \end{align}
-and inactive, if
-\begin{align}
-    \uexp(\pi_j\mid W) \coloneqq \sup_{q_j\in \mathcal{P}_j} \text{E}(\pi_j\mid W)< 1/2.
-\end{align}
-We consider the rest to be indecisive.
 
-This way, we get a robust group selection routine. However, this type of variable 
-selection includes both treatment and outcome effects at the same time. This may not be the
-case in some cases especially when either treatment effect or the outcome effect is zero or
-weak. To deal with such problems, we suggest the following ad-hoc method to obtain 
-adjusted sparse estimate of the zero effect in a selected group.
-Let $\mathcal{S}$ denote the set of active co-variates present in the model. That is,
+For the rest of the variables, some of them will be present
+in the model as confounders and some will only be associated with
+either the treatment. Let $\mathcal{S}$ denote the set of
+predictors such that,
 \begin{equation}
     \mathcal{S}\coloneqq
-    \left\{j : \lexp(\pi_j\mid W) > 1/2\right\}.
+    \left\{j : \lexp(\pi_j\mid W) < 1/2\right\}.
 \end{equation}
-Let $\hat{\beta}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression
-coefficients for the non-zero outcome effects and
+That is the set that contains all the variables which are not
+removed from both treatment and outcome model. Now, for
+each fixed value of $q$,
+let $\hat{\beta}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression coefficients of the outcome model with respect to
+the predictors that belong to $\mathcal{S}$. Similarly,
 $\hat{\gamma}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression
-coefficients for the non-zero treatment effects. We apply the 
-``decoupled shrinkage and selection'' method proposed by \citet{hahn2015}, to obtain
-the sparse estimate. To do so, we solve the following adaptive LASSO-type \cite{Zou2006}
+coefficients for the treatment effects. Since, we use a continuous type
+selection prior, these regression coefficients are non-zero in nature.
+Therefore, to adjust the sparsity, we apply the 
+``decoupled shrinkage and selection'' method proposed by \citet{hahn2015}. To do so, we solve the following adaptive LASSO-type \cite{Zou2006}
 problems
@@
 \begin{align}
-    \hat{\beta}^*_{\mathcal{S}}(q_{\mathcal{S}}) &= 
-    \arg\min_{\beta_{\mathcal{S}}} \frac{1}{n}\|\x_{\mathcal{S}}\hat{\beta}_{\mathcal{S}}(q_{\mathcal{S}})
-    - \x_{\mathcal{S}} \beta_{\mathcal{S}}\|_2^2 + \lambda_1\sum_{j\in\mathcal{S}} 
+    \hat{\beta}^*_{\mathcal{S}}(q) &= 
+    \arg\min_{\beta_{\mathcal{S}}} \frac{1}{n}\|X_{\mathcal{S}}\hat{\beta}_{\mathcal{S}}(q)
+    - X_{\mathcal{S}} \beta_{\mathcal{S}}\|_2^2 + \lambda\sum_{j\in\mathcal{S}} 
     \frac{|\beta_j|}{|\hat{\beta}_j(q_j)|}
@@
 \begin{align}
-    \hat{\gamma}^*_{\mathcal{S}}(q_{\mathcal{S}}) &= 
-    \arg\min_{\gamma_{\mathcal{S}}} \frac{1}{n}\|\x_{\mathcal{S}}\hat{\gamma}_{\mathcal{S}}(q_{\mathcal{S}})
-    - \x_{\mathcal{S}} \gamma_{\mathcal{S}}\|_2^2 + \lambda_1\sum_{j\in\mathcal{S}} 
+    \hat{\gamma}^*_{\mathcal{S}}(q) &= 
+    \arg\min_{\gamma_{\mathcal{S}}} \frac{1}{n}\|X_{\mathcal{S}}\hat{\gamma}_{\mathcal{S}}(q)
+    - X_{\mathcal{S}} \gamma_{\mathcal{S}}\|_2^2 + \lambda\sum_{j\in\mathcal{S}} 
     \frac{|\gamma_j|}{|\hat{\gamma}_j(q_j)|}
 \end{align}
-where $q_{\mathcal{S}}\in \mathcal{P}_{\mathcal{S}}$.
+where $q_{j}\in \mathcal{P}_{j}$ for all $j\in\mathcal{S}$.
 
+\iffalse
+\subsection{Causal effect adjustment} The DSS method explained
+above give us adjusted coefficient estimates for the treatment
+and outcome model. However, as result the causal effect estimate
+remains the same and modelling with such adjusted sparse effect 
+will contribute to the prediction error. Therefore, we need to 
+adjust the causal effect estimate as well. We do that in three steps
+similar to double residual regression procedure as suggested by
+\citet{robinson1988}.
+
+First we compute the predicted values of $Y$ with respect to
+the adjusted regression coefficients so that,
+\begin{equation}
+\hat{Y}(q) 
+= \hat{\beta}_0(q) + X_{\mathcal{S}}\hat{\beta}^*_{\mathcal{S}}(q)
+\end{equation}
+and the values of $T$ with respect to the adjusted
+regression coefficients so that
+\begin{equation}
+\hat{T}(q) 
+= \Phi\left(\hat{\gamma}_0(q) + X_{\mathcal{S}}\hat{\gamma}^*_{\mathcal{S}}(q)\right).
+\end{equation}
+Then we estimate the adjusted causal effect using the following linear
+model
+\begin{equation}
+\left(Y-\hat{Y}(q)\right) = \left(T - \hat{T}(q)\right)\beta_{T} + \epsilon^*_i.
+\end{equation}
+That is 
+\begin{equation}
+\beta_{T}^* = \left(\left(T - \hat{T}(q)\right)^T\left(T - \hat{T}(q)\right)\right)^{-1}\left(T - \hat{T}(q)\right)^T\left(Y-\hat{Y}(q)\right)
+\end{equation}
+
+\fi
 \subsection{Robust Bayesian Analysis}

### 2022-11-01 causal.R

@@ -1,0 +1,162 @@
+library(mvtnorm)
+library(rjags)
+library(SSLASSO)
+library(monomvn)
+library(spikeslab)
+library(horseshoe)
+library(glmnet)
+library(ncvreg)
+library(xtable)
+
+sig1 = diag(100)
+
+x = rmvnorm(50, sigma = sig1)
+
+beta1 = c(runif(5, -4, -1), runif(5, 1, 4))
+gamma1 = c(runif(5, -4, -1), runif(5, 1, 4))
+
+a1_dum = 1/(1 + exp(-x[,1:length(beta1)] %*% gamma1))
+a1 = sapply(1:50, function(j)rbinom(1,1,a1_dum[j]))
+
+
+y1 = 4*a1 + x[,1:length(beta1)] %*% beta1 + rnorm(50, sd = .5)
+
+
+ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 1e-2, n.iter = 500, n.adapt = 500, n.sample = 5000){
+  MCMC = list()
+  
+  string = "
+  model {
+  
+    ## Likelihood
+    
+    for (i in 1:N) 
+    {
+      mean[i] = b_T * a[i] + inprod(x[i,], b)
+      y[i] ~ dnorm(mean[i], inv.var)
+      
+      a[i] ~ dinterval(a_dumm[i], 0)
+      
+      a_dumm[i] ~ dnorm(inprod(x[i,], g), 1)
+    }
+    
+    # Prior on the mean
+    
+    b_T ~ dnorm(0,inv.var)
+    b0 ~ dnorm(0,inv.var)
+    g0 ~ dnorm(0,1)
+    
+    # prior on the precision
+    
+    inv.var ~ dgamma(gam_a, gam_b)
+    
+    sigma2 = 1 / inv.var
+    
+    ## Prior on the regression parameters 
+    
+    for (j in 1:p) 
+    {
+      # prior on the selection probability
+      w[j] ~ dbeta(2*alpha[j], 2*(1-alpha[j]))I(0.001,0.999)
+      
+      
+      # Prior on beta
+      
+      spike[j] ~ dnorm(0, (inv.var / tau_0^2))
+      slab[j] ~ dnorm(0, (inv.var / tau_1^2))
+      
+      spikeg[j] ~ dnorm(0, (1 / tau_0^2))
+      slabg[j] ~ dnorm(0, (1 / tau_1^2))
+      
[…]

### 2022-11-02 causal.R
some changes

@@ -22,7 +22,7 @@ a1 = sapply(1:50, function(j)rbinom(1,1,a1_dum[j]))
 y1 = 4*a1 + x[,1:length(beta1)] %*% beta1 + rnorm(50, sd = .5)
 
 
-ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 1e-2, n.iter = 500, n.adapt = 500, n.sample = 5000){
+ISVS = function(x, y, a, alphas, tau_0 = 1e-10, tau_1 = 1, gam_a = 1e-2, gam_b = 1e-2, n.iter = 500, n.adapt = 500, n.sample = 5000){
   MCMC = list()
   
   string = "
@@ -32,12 +32,12 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 
     
     for (i in 1:N) 
     {
-      mean[i] = b_T * a[i] + inprod(x[i,], b)
+      mean[i] = b0 + b_T * a[i] + inprod(x[i,], b)
       y[i] ~ dnorm(mean[i], inv.var)
       
-      a[i] ~ dinterval(a_dumm[i], 0)
+      a[i] ~ dbern(a_dumm[i])
       
-      a_dumm[i] ~ dnorm(inprod(x[i,], g), 1)
+      a_dumm[i] = phi(inprod(x[i,], g) + g0)
     }
     
     # Prior on the mean
@@ -52,6 +52,11 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 
     
     sigma2 = 1 / inv.var
     
+    sig[1,1] = inv.var
+    sig[1,2] = 0
+    sig[2,1] = 0
+    sig[2,2] = 1
+      
     ## Prior on the regression parameters 
     
     for (j in 1:p) 
@@ -61,15 +66,17 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 
       
       
       # Prior on beta
+
+      spike[j, 1:2] ~ dmnorm(c(0,0),  1/tau_0^2 * sig[1:2,1:2])
+      slab[j, 1:2] ~ dmnorm(c(0,0),  1/tau_1^2 * sig[1:2,1:2])
       
[…]

### 2022-11-03 causal.R
cleaning

@@ -19,10 +19,10 @@ a1_dum = 1/(1 + exp(-x[,1:length(beta1)] %*% gamma1))
 a1 = sapply(1:50, function(j)rbinom(1,1,a1_dum[j]))
 
 
-y1 = 4*a1 + x[,1:length(beta1)] %*% beta1 + rnorm(50, sd = .5)
+y1 = 2+ 4*a1 + x[,1:length(beta1)] %*% beta1 + rnorm(50, sd = .1)
 
 
-ISVS = function(x, y, a, alphas, tau_0 = 1e-10, tau_1 = 1, gam_a = 1e-2, gam_b = 1e-2, n.iter = 500, n.adapt = 500, n.sample = 5000){
+ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 1e-2, n.iter = 5000, n.adapt = 2000, n.sample = 5000){
   MCMC = list()
   
   string = "
@@ -32,7 +32,7 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-10, tau_1 = 1, gam_a = 1e-2, gam_b =
     
     for (i in 1:N) 
     {
-      mean[i] = b0 + b_T * a[i] + inprod(x[i,], b)
+      mean[i] = b_T * a[i] + inprod(x[i,], b) + b0
       y[i] ~ dnorm(mean[i], inv.var)
       
       a[i] ~ dbern(a_dumm[i])
@@ -52,11 +52,6 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-10, tau_1 = 1, gam_a = 1e-2, gam_b =
     
     sigma2 = 1 / inv.var
     
-    sig[1,1] = inv.var
-    sig[1,2] = 0
-    sig[2,1] = 0
-    sig[2,2] = 1
-      
     ## Prior on the regression parameters 
     
     for (j in 1:p) 
@@ -66,17 +61,15 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-10, tau_1 = 1, gam_a = 1e-2, gam_b =
       
       
       # Prior on beta
-
-      spike[j, 1:2] ~ dmnorm(c(0,0),  1/tau_0^2 * sig[1:2,1:2])
-      slab[j, 1:2] ~ dmnorm(c(0,0),  1/tau_1^2 * sig[1:2,1:2])
       
[…]

### 2022-11-04 causal.R
change code

@@ -19,10 +19,10 @@ a1_dum = 1/(1 + exp(-x[,1:length(beta1)] %*% gamma1))
 a1 = sapply(1:50, function(j)rbinom(1,1,a1_dum[j]))
 
 
-y1 = 2+ 4*a1 + x[,1:length(beta1)] %*% beta1 + rnorm(50, sd = .1)
+y1 = 4*a1 + x[,1:length(beta1)] %*% beta1 + rnorm(50, sd = .1)
 
 
-ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 1e-2, n.iter = 5000, n.adapt = 2000, n.sample = 5000){
+ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 1e-2, n.iter = 10000, n.adapt = 5000, n.sample = 10000){
   MCMC = list()
   
   string = "
@@ -32,12 +32,12 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 
     
     for (i in 1:N) 
     {
-      mean[i] = b_T * a[i] + inprod(x[i,], b) + b0
+      mean[i] = b_T * a[i] + inprod(x[i,], b)
       y[i] ~ dnorm(mean[i], inv.var)
       
-      a[i] ~ dbern(a_dumm[i])
+      a[i] ~ dinterval(a_dumm[i], 0)
       
-      a_dumm[i] = phi(inprod(x[i,], g) + g0)
+      a_dumm[i] ~ dnorm(inprod(x[i,], g), 1)
     }
     
     # Prior on the mean
@@ -57,7 +57,7 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 
     for (j in 1:p) 
     {
       # prior on the selection probability
-      w[j] ~ dbeta(2*alpha[j], 2*(1-alpha[j]))I(0.001,0.999)
+      w[j] ~ dbeta(2*alpha, 2*(1-alpha))I(0.001,0.999)
       
       
       # Prior on beta
@@ -78,7 +78,7 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 
   
   for (i in 1:length(alphas)) {
     
[…]

### 2023-03-20 JASA-template.tex
just before meeting

@@
 \email{jochen.einbeck@durham.ac.uk}
-\address{$^1$UMR CNRS 7253 Heudiasyc, Universit\'{e} de Technologie de
-Compi\`{e}gne}
+\address{$^1$Civil and Environmental Engineering, University of Strathclyde}
 \address{$^2$Department of Mathematical Sciences, Durham University}
@@
 to subject and modelling the underlying heterogeneity explicitly makes the 
-problem practically unsolvable. Another issue we face is the 
-dimensionality of the problem and we may wish to find a subset of 
-explanatory variables. However, standard variable selection methods
-tend to maximise the predictive performance of the outcome model only and
-can also be sensitive with respect to the choice of priors, particularly 
-in the case of limited information. So, in this paper, we suggest a 
-robust Bayesian analysis of causal inferential methods for 
-high-dimensional problems in a regressional framework. We consider
-a set of spike and slab priors to obtain robust estimates for
+problem practically unsolvable. Another issue we often face is the 
+dimensionality of the problem and we need to find a subset of 
+explanatory variables to initiate the treatment. However, currently variable selection methods
+tend to maximise the predictive performance of the outcome model only. This can be problematic in the case of limited information. 
+As the consequence of mistreatment can be harmful. 
+So, in this paper, we suggest a general framework with
+robust Bayesian analysis which accounts for abstention in deciding
+an explanatory variable in the high dimensional regression model. 
+To achieve that, we consider a set of spike and slab priors 
+through prior elicitation to obtain robust estimates for
 both the treatment and outcome model. We are specifically interested 
-in the importance of priors in the high dimensional causal inference
-as well as the identifying the confounder variables. However, indicator
+in the sensitivity of the treatment effect in the high dimensional causal inference
+as well as the identifying the confounder variables by means of variable selection. However, indicator
 based confounder selection can be deceptive in some cases. Especially, 
@@
 the outcome. This increases the posterior expectation of the selection
-indicators. To avoid that we also apply a post-hoc selection scheme
+indicators. To avoid that we apply a post-hoc selection scheme
 which successfully remove negligible non-zero effects from the model
-attaining a sparser model. Finally, we illustrate
+attaining a smaller set of confounders. Finally, we illustrate
 our result using synthetic \alert{and real} dataset.
@@
 Bayesian approach in causal effect estimation has become a popular
-topic in recent days. However, one of the earlier works on this can be
+topic in recent days. However, it has been a topic of interest for about 50 
+years and one of the earlier works on this can be
 found in \cite{rubin1978}. Lately with the notion of high dimensional problems, Bayesian methodologies have become
@@
 In this paper we take inspiration from the approach of \citet{koch2020}, where
-they proposed a bilevel spike and slab prior for causal effect 
+they proposed a bi-level spike and slab prior for causal effect 
 estimation. They considered a data-driven adaptive approach to
 propose their prior which reduce the variance of the causal estimate. 
-In our approach,
-we suggest a sensitivity analysis based approach where instead
-of using a single prior, we consider a set of priors \cite{BERGER1990303}. This is particularly interesting as in
-many cases, causal effect estimation can be performed through a 
-meta analysis and hence robust Bayesian analysis can be beneficial
-\cite{raices_cruz22} under severe uncertainty.
-Moreover, for some problems we have to rely on very limited data to
-perform our Bayesian analysis and choosing a data-driven prior
-can lead to overfitting. Therefore, as to propose our
-robust Bayesian framework,
-we consider a set of continuous spike and slab priors \cite{ishwaran2005}
-for confounder selection and construct a Bayesian group LASSO
-\cite{xu2015}. To perform the sensitivity analysis, we consider
-a set of beta priors on the covariate selection probability
-of the spike and slab priors. This sensitivity analysis allows us
-to investigate the regression coefficients with respect to a different
-level of sparsity of the model. Following that, we consider a post-hoc
-variable selection method as suggested by \citet{hahn2015}. This
-ensures that we can efficiently separate the confounder variables
-with others and reduce the bias of treatment effect estimation.
+In our approach, we are interested in the decision theoretic notion of 
+variable selection and its effect in causal estimation. We suggest a 
+sensitivity analysis based approach where instead of using a single prior, 
+we consider a set of priors \cite{BERGER1990303}. This is particularly 
+interesting as in many cases, causal effect estimation can be performed 
+through a meta analysis and hence robust Bayesian analysis can be beneficial
+\cite{raices_cruz22} under severe uncertainty. Moreover, for some problems 
+we have to rely on very limited data to perform our Bayesian analysis and 
+choosing a data-driven prior can lead to overfitting. Instead we can 
+benefit from expert opinion and elicit prior based on empirical evidence.
+This also allows us to construct the problem of confounder selection 
+in a framework where abstention has a positive gain. To propose our 
+framework, we consider a set of continuous spike and slab priors 
+\cite{ishwaran2005} for confounder selection and construct a Bayesian 
+group LASSO \cite{xu2015} type problem. To perform the prior sensitivity 
+analyses, we consider a set of beta priors on the covariate selection 
+probability of the spike and slab priors. We use the posteriors of these
+covariate selection probability for identifying the confounders. Finally, 
+we consider a post-hoc coefficient adjustment method \citet{hahn2015}
+to recover sparse estimates. This post hoc treatment also helps us to 
+reduce the bias of treatment effect estimation.
 
@@
 Bayesian analysis of causal inference problems, followed by the
-motivation of a robust Bayesian analysis. In \cref{sec:sim}, we
-provide our result of simulation studies under different 
-scenarios and in data analysis with real data in \cref{sec:data:analysis}. Finally we discuss our findings and 
-conclude this paper in \cref{sec:conc}.
+motivation of a robust Bayesian analysis along with our proposed decision 
+theoretic framework for confounder (variable) selection. In \cref{sec:sim}, 
+we provide our result of simulation studies under different scenarios 
+and data analysis with \alert{real data} in \cref{sec:data:analysis}. Finally 
+we discuss our findings and conclude this paper in \cref{sec:conc}.
 
@@
 
+\subsection{Robust Bayesian Analysis}
+We perform our
+robust Bayesian analysis on $q\coloneqq(q_1$, \dots, $q_p)\in\mathcal{P}$, where
+\begin{equation}
+	\mathcal{P} \coloneqq \mathcal{P}_1\times\cdots\times\mathcal{P}_p\subseteq \left(0, 1\right)^{p}.
+\end{equation}
+
 \subsection{Variable selection and coefficient adjustment}
@@
 
-\iffalse
+\iftrue
 \subsection{Causal effect adjustment} The DSS method explained
@@
 \fi
-\subsection{Robust Bayesian Analysis}
-We perform our
-robust Bayesian analysis on $q\coloneqq(q_1$, \dots, $q_p)\in\mathcal{P}$, where
-\begin{equation}
-\mathcal{P} \coloneqq \mathcal{P}_1\times\cdots\times\mathcal{P}_p\subseteq \left(0, 1\right)^{p}.
-\end{equation}
 

### 2023-03-20 causal.R

@@ -22,7 +22,7 @@ a1 = sapply(1:50, function(j)rbinom(1,1,a1_dum[j]))
 y1 = 4*a1 + x[,1:length(beta1)] %*% beta1 + rnorm(50, sd = .1)
 
 
-ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 1e-2, n.iter = 10000, n.adapt = 5000, n.sample = 10000){
+ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 10, gam_a = 1e-2, gam_b = 1e-2, n.iter = 1000, n.adapt = 500, n.sample = 1000){
   MCMC = list()
   
   string = "
@@ -130,40 +130,46 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 1, gam_a = 1e-2, gam_b = 
   
 }
 
-sim1_rbvs1 = ISVS(x, y1, a1, alphas = seq(0.8,0.9, length.out = 2), tau_1 = 1)
+sim1_rbvs1 = ISVS(x, y1, a1, alphas = seq(0.2,0.9, length.out = 5), tau_1 = 10)
 
-prob_exp = matrix(unlist(lapply(sim1_rbvs1$probs, function(x)colMeans(as.matrix(x)))), nrow = 2, byrow = T)
+prob_exp = matrix(unlist(lapply(sim1_rbvs1$probs, function(x)colMeans(as.matrix(x)))), nrow = 5, byrow = T)
 
-active = c(1:100)[-c(which(apply(prob_exp, 2, min)>0.5))] 
+active = t(sapply(1:5, function(i) (prob_exp[i,] >0.5)))
+  #c(1:100)[-c(which(apply(prob_exp, 2, min)>0.5))] 
 
-beta_exp = matrix(unlist(lapply(sim1_rbvs1$Betas, function(x)colMeans(as.matrix(x)))), nrow = 2, byrow = T)
+beta_exp = matrix(unlist(lapply(sim1_rbvs1$Betas, function(x)colMeans(as.matrix(x)))), nrow = 5, byrow = T)
 
-gamma_exp = matrix(unlist(lapply(sim1_rbvs1$Gammas, function(x)colMeans(as.matrix(x)))), nrow = 2, byrow = T)
[…]

### 2023-05-17 basu23c.tex
lncs and others

--- 2023-03-20 JASA-template.tex
@@
-% !TeX spellcheck = en_GB
-
-\documentclass{amsart}
-\usepackage[foot]{amsaddr} % put addresses on first page
+% This is samplepaper.tex, a sample chapter demonstrating the
+% LLNCS macro package for Springer Computer Science proceedings;
+% Version 2.20 of 2017/10/04
+%
+\documentclass[oribibl]{llncs}
+%
+\usepackage{graphicx}
+\usepackage{enumitem}
+\usepackage{bm}
+\usepackage{amsfonts}
+\usepackage{mathtools}
+\usepackage{blindtext}
+\usepackage[capitalise]{cleveref}
 \usepackage[british]{babel}
@@
 \usepackage{enumitem}
-\usepackage{amsfonts}
-\usepackage{mathtools}
 \usepackage{amssymb}
 \usepackage{amsmath}
-\allowdisplaybreaks
 \usepackage{longtable}
@@
 %\usepackage{siunitx}
-\usepackage{amsthm}
 \usepackage{soul}
@@
 \usepackage{easyReview} % for \comment, \alert, etc.
-
-\newcommand{\addition}[1]{#1}
-
-\usepackage{hyperref}
-\usepackage[capitalise]{cleveref}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[theorem]
-\newtheorem{lemma}[theorem]{Lemma}
-%
-
-\usepackage[numbers]{natbib}
-\usepackage{url} % not crucial - just used below for the URL 
-\usepackage{doi}
 
@@
 
-\keywords{high dimensional data; variable selection; Bayesian analysis; imprecise probability}
-
 \begin{document}
 
-\title{Robust Bayesian Analysis of Causal Inference Problems}
-\author{Tathagata Basu$^1$}
-\email{tathagatabasumaths@gmail.com}
-\author{Matthias C.~M.~Troffaes$^2$}
-\email{matthias.troffaes@durham.ac.uk}
-\author{Jochen Einbeck$^{2,3}$}
-\email{jochen.einbeck@durham.ac.uk}
-\address{$^1$Civil and Environmental Engineering, University of Strathclyde}
-\address{$^2$Department of Mathematical Sciences, Durham University}
-\address{$^3$Durham Research Methods Centre}
-
+\title{A Robust Bayesian Approach for Causal Inference Problems
+%\thanks{}
+}
+%
+\author{Tathagata Basu\inst{1}\orcidID{0000-0002-6851-154X} \and
+Matthias C.~M.~Troffaes\inst{2}\orcidID{0000-0002-1294-600X} \and
+Jochen Einbeck\inst{2,3}\orcidID{0000-0002-9457-2020}}
+%
+\authorrunning{Basu et al.}
+%
+\institute{Civil and Environmental Engineering, University of Strathclyde, UK \
+Department of Mathematical Sciences, Durham University, UK \
+Durham Research Methods Centre, UK}
+%
+\maketitle              
+%
 \begin{abstract}
@@
 dimensionality of the problem and we need to find a subset of
-explanatory variables to initiate the treatment. However, currently variable selection methods
-tend to maximise the predictive performance of the outcome model only. This can be problematic in the case of limited information. 
-As the consequence of mistreatment can be harmful. 
-So, in this paper, we suggest a general framework with
-robust Bayesian analysis which accounts for abstention in deciding
+explanatory variables to understand the treatment effect.
+However, currently variable selection methods tend to maximise the
+predictive performance of the underlying model. This can be problematic
+in the case of limited information. As in many cases, the consequence of
+mistreatment can be harmful. So, in this paper, we considering for a
+robust Bayesian analysis which accounts for abstention in selecting
 an explanatory variable in the high dimensional regression model.
 To achieve that, we consider a set of spike and slab priors
-through prior elicitation to obtain robust estimates for
+through prior elicitation to obtain set of posteriors for
 both the treatment and outcome model. We are specifically interested
-in the sensitivity of the treatment effect in the high dimensional causal inference
-as well as the identifying the confounder variables by means of variable selection. However, indicator
-based confounder selection can be deceptive in some cases. Especially, 
-when the predictor is strongly associated with either the treatment or 
-the outcome. This increases the posterior expectation of the selection
-indicators. To avoid that we apply a post-hoc selection scheme
+in the sensitivity of the treatment effect in the high dimensional causal
+inference as well as the identifying the confounder variables by means
+of variable selection. However, confounder selection can be deceptive
+in this setting. Especially, when a predictor is strongly associated
+with either the treatment or the outcome. This will increase the posterior
+expectation of the selection probability and might abstain from rejecting
+this variable as a confounder. To avoid that we apply a post-hoc selection scheme
 which successfully remove negligible non-zero effects from the model
-attaining a smaller set of confounders. Finally, we illustrate
-our result using synthetic \alert{and real} dataset.
+attaining a smaller set of confounders as well as seperate sets of variables
+which are only related to treatment or outcome model. Finally, we illustrate
+our method to show it's applicability in real life scenarios.
 
+\keywords{high dimensional data \and variable selection \and Bayesian analysis \and imprecise probability.}
 \end{abstract}
-
-\maketitle
 
@@
 confounder variables. One such work in the topic was 
-by \citet{Robins1986ANA} where the author used  a graphical
+by Robins \cite{Robins1986ANA} where the author used  a graphical
 approach for the identification of the causal parameters.
-\citet{rosenbaum1985} suggested the use of a link model to estimate
+Rosenbaum and Robin \cite{rosenbaum1985} suggested the use of a link model to estimate
 the propensity scores for all individuals. Later on several other
@@
 
-Bayesian approach in causal effect estimation has become a popular
-topic in recent days. However, it has been a topic of interest for about 50 
-years and one of the earlier works on this can be
-found in \cite{rubin1978}. Lately with the notion of high dimensional problems, Bayesian methodologies have become
-more appealing. \citet{Crainiceanu2008} proposed a bi-level 
+Bayesian approaches in causal effect estimation is a popular
+strategy in the field and one of the earlier works on this can be
+found in \cite{rubin1978}. Lately, with the rise of high dimensional 
+data, Bayesian methodologies have become
+more appealing. Crainiceanu \text{et al.~}\cite{Crainiceanu2008} proposed a bi-level 
 Bayesian model averaging based method for estimating the causal 
-effect. \citet{wang2015} suggested BAC (or, Bayesian adjustment for
+effect. Wang \text{et al.~}\cite{wang2015} suggested BAC (or, Bayesian adjustment for
 confounding) where they use an informative prior obtained from
@@
 proposed to tackle confounders from the point of view of Bayesian
-variable selection such as: \citet{Zigler2014}, \citet{Hahn2018} etc.
+variable selection such as: \cite{Zigler2014}, \cite{Hahn2018} etc.
 
-In this paper we take inspiration from the approach of \citet{koch2020}, where
+In this paper we take inspiration from the approach of Koch \text{et al.~}\cite{koch2020}, where
 they proposed a bi-level spike and slab prior for causal effect 
@@
 propose their prior which reduce the variance of the causal estimate. 
-In our approach, we are interested in the decision theoretic notion of 
-variable selection and its effect in causal estimation. We suggest a 
+In our approach, we perform a 
 sensitivity analysis based approach where instead of using a single prior, 
@@
 interesting as in many cases, causal effect estimation can be performed 
-through a meta analysis and hence robust Bayesian analysis can be beneficial
-\cite{raices_cruz22} under severe uncertainty. Moreover, for some problems 
+through a meta analysis and hence robust Bayesian analysis \cite{raices_cruz22} 
+can be beneficial under severe uncertainty. Moreover, for some problems 
 we have to rely on very limited data to perform our Bayesian analysis and 
-choosing a data-driven prior can lead to overfitting. Instead we can 
-benefit from expert opinion and elicit prior based on empirical evidence.
-This also allows us to construct the problem of confounder selection 
-in a framework where abstention has a positive gain. To propose our 
+inference may not be reliable in presence of hetaroskedasticity within
+the data. Instead, we use expert opinion and elicit a set of priors 
+based on empirical evidence. 
+This also allows us to construct the problem of confounder identification 
+in a framework where abstention has a relatively positive gain ie.~
+the cost of further tests/data collection is cheaper than
+mistreating a subject. To propose our 
 framework, we consider a set of continuous spike and slab priors 
-\cite{ishwaran2005} for confounder selection and construct a Bayesian 
+\cite{ishwaran2005} for confounder identification and construct a Bayesian 
 group LASSO \cite{xu2015} type problem. To perform the prior sensitivity 
@@
 covariate selection probability for identifying the confounders. Finally, 
-we consider a post-hoc coefficient adjustment method \citet{hahn2015}
-to recover sparse estimates. This post hoc treatment also helps us to 
-reduce the bias of treatment effect estimation.
+we consider a post-hoc coefficient adjustment method \cite{hahn2015}
+to recover sparse estimates associated with either the outcome or the
+treatment model.
 
@@
 we provide our result of simulation studies under different scenarios 
-and data analysis with \alert{real data} in \cref{sec:data:analysis}. Finally 
+and to show the applicability in real life problems. Finally, 
 we discuss our findings and conclude this paper in \cref{sec:conc}.
@@
 where $\epsilon_i\sim \mathcal{N}(0, \sigma^2)$. Clearly, when
-the underlying true outcome model is linear,
+the underlying true outcome model is linear with respect to the treatment,
 \begin{equation}
-    \delta = \beta_{T}\quad\text{and hence } 
-    \hat{\delta} - \delta = \hat{\beta}_T - \beta_T.
+	\delta = \mathbb{E}(Y\mid T =1) - E(Y\mid T=0) = \beta_{T}.
 \end{equation}
-\begin{figure}
-	\centering
-	\begin{tikzpicture}[params/.style={circle, draw=green!60, fill=green!5, very thick, minimum size=7mm}]
-	\node (1) at (0,0) {Treatment ($T$)};
-	\node (2) [right = of 1] {Outcome ($Y$)};
-	\node (4) [below = of 1] {Predictors ($X$)};
-
-	\path (1) edge[->]  (2);
-	\path (1) edge[<-]  (4);
-	\path (2) edge[<-] (4);
-	\end{tikzpicture}
-	\caption{Confounding in causal models.}
-	\label{fig:confounding}
-\end{figure}
-
 In the presence of confounders we also need to consider the
 association between the treatment indicators and the predictors.
-\citet{koch2020} suggested the use of a probit link function to 
+In literature, authors often suggested the use of a probit link function to 
 construct the regression model. This way, we can
@@
 where $\Phi(\cdot)$ denotes the cumulative distribution function
-of a standard normal distribution.
-
-This allows us to define intermediate latent variables as suggested
-by \citet{albert93}
+of a standard normal distribution. To incorporate this probit
+link function, we define intermediate latent variables as suggested
+by \cite{albert93}
 \begin{equation}
@@
 \end{equation}
-where, $u_i\sim\mathcal{N}(0,1)$. Therefore, $T_i=1$ if $T_i^*>0$ and
-$T_i=0$ if $T_i^*\le0$.
+where, $u_i\sim\mathcal{N}(0,1)$. Therefore, $T_i=1$ if $\Phi(\gamma_0+X_i\gamma)
+>1/2$ and hence $T_i^*>0$. Similarly, $T_i=0$ if $T_i^*\le0$.
 
-Now, following the approach of \citet{koch2018}, we define an adjusted
+Now, to construct the joint likelihood function, we define an appended
 output vector $W\coloneqq(Y, T^*)^T$ and corresponding $2n\times(2p+3)$ dimensional design matrix
@@
 \end{align}
-where, $X_O = [T, 1_n, X]$ and $X_T = [1_n, X]$. Then, assuming a
-Gaussian error term, we have the following likelihood distribution
+where, $X_O = [T, 1_n, X]$ and $X_T = [1_n, X]$. Then, considering the assumption of
+Gaussian error terms, we have the following likelihood distribution
 \begin{align}
@@
 Let, $\pi_j$ denote the prior probability that the $j$-th
-predictor is not associated with either the outcome or the 
+predictor is associated to either the outcome or the 
 treatment. That is, 
 \begin{equation}
-	\pi_j = P\left((\beta_j,\gamma_j)=(0,0)\right).
+	\pi_j = P\left((\beta_j,\gamma_j)\not=(0,0)\right).
 \end{equation}
-Then we can define a spike and slab group LASSO so that:
+Then we can define the following hierarchical model for spike and 
+slab group LASSO so that,
 for $1\le j\le p$,
@@
 	(\beta_j,\gamma_j)^T \mid \pi_{j}, \sigma^2 &\sim 
-(1-\pi_{j})\normal\left( (0,0)^T, 
+	\pi_{j}\normal\left( \begin{bmatrix}
+		0 \\
+		0
+	\end{bmatrix}, 
 	\tau_1^2\begin{bmatrix}
@@
 	\end{bmatrix}\right)
-+ \pi_{j} \normal\left(0, 
+	+ (1-\pi_{j}) \normal\left(\begin{bmatrix}
+		0 \\
+		0
+	\end{bmatrix}, 
 	\tau_0^2\begin{bmatrix}
@@
 	\end{bmatrix}\right)\\
-%\beta_T, \beta_0\mid \sigma^2 &\sim \normal(0, \sigma^2)\\
-%\gamma_0 &\sim \normal(0,1)\\
+	\beta_T, \beta_0\mid \sigma^2 &\sim \normal\left(0, \sigma^2\right)\\
+	\gamma_0 &\sim \normal(0,1)\\
 	\sigma^2&\sim \text{InvGamma}(a, b)\\
@@
 \end{align}
-
-We fix sufficiently small $\tau^2_0$
+In the hierarchical model, we fix sufficiently small $\tau^2_0$
 $(1\gg\tau_0^2>0)$ so that  $(\beta_j, \gamma_j) = (0,0)$ has its probability mass 
 concentrated around zero. Therefore, this represents the spike component of our prior specification. 
-To construct the slab component, we consider $\tau_1^2$ to be large so that $\tau_1^2\ge 1$. This allows the prior for $(\beta_j, \gamma_j)\not=(0,0)$ to be flat. Inverse-Gamma is a natural choice
-for the variance of the Gaussian noise because of conjugacy. To
-make the prior flat, we consider $1\gg a, b >0$.
+For the slab component, we consider $\tau_1^2$ to be large so that $\tau_1^2\ge 1$. This allows the prior for $(\beta_j, \gamma_j)\not=(0,0)$ to be flat. 
+We illustrate the components of a bivariate spike and slab prior in 
+\cref{fig:ssbl} (with fixed $\sigma=1$). We generate the spike component 
+with $\tau_0=0.001$ and the slab component with $\tau_1=5$.
 
-As indicated earlier, $\pi_j$ is used as the rejection probability
-of the $j$-th predictor and we use a beta prior to specify 
-these rejection probabilities where  $q_j$ represents our prior expectation of the rejection probability ($\pi_j$) and `$s$' acts as 
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[width = 0.95\linewidth]{spike_slab_bi.pdf}
+	\end{center}
+	\caption{Spike and slab components of a bi-variate distribution for $\tau_0 = 0.001$, $\tau_1$ = 5 and $\sigma=1$.}
+	\label{fig:ssbl}
+\end{figure}
+
+For the variance term $\sigma^2$, a natural choice of prior is inverse-Gamma 
+because of conjugacy properties with Gaussian distribution. To
+ensure that the prior is flat, we consider $1\ge a, b >0$.
+As defined earlier, $\pi_j$ is used as the selection probability
+of the $j$-th predictor in either of the models and we use a beta prior to specify 
+these selection probabilities where  $q_j$ represents our prior expectation of the selection probability ($\pi_j$) and `$s$' acts as 
 a concentration parameter.
-For the intercept terms of the outcome model and the causal effect, 
-we consider a sufficiently flat prior so that 
-$\beta_0. \beta_T\sim \normal(0,\sigma^2)$. Similarly, for the
-intercept term in the treatment model, we consider 
-$\gamma_0\sim \normal(0,1)$.
+For the intercept term of the outcome model and the causal effect, 
+we want to use a Gaussian distribution that matches the scale of the noise term.
+Therefore, we consider $\beta_0. \beta_T\sim \normal(0,\sigma^2)$. 
+Similarly, for the intercept term in the treatment model, we consider 
+$\gamma_0\sim \normal(0,1)$ as we use a probit link function.
 
@@
 relationship between different nodes. However, we use a dashed
-edge between $X$ and $T$ as we they are related through the latent
-variable $T^*$. This dashed edge also establish the notion of
-confounding as shown in \cref{fig:confounding}.
+edge between $X$ and $T$ as they are related through the latent
+variable $T^*$.
 
@@
 Therefore, to adjust the sparsity, we apply the 
-``decoupled shrinkage and selection'' method proposed by \citet{hahn2015}. To do so, we solve the following adaptive LASSO-type \cite{Zou2006}
+``decoupled shrinkage and selection'' method proposed by \cite{hahn2015}. To do so, we solve the following adaptive LASSO-type \cite{Zou2006}
 problems
@@
 similar to double residual regression procedure as suggested by
-\citet{robinson1988}.
+\cite{robinson1988}.
 
@@
 
-\section{Data Analysis}\label{sec:data:analysis}
-
 \section{Conclusion}\label{sec:conc}
 
-\bibliographystyle{agsm}
+\bibliographystyle{splncs04}
 \bibliography{basu22}
+
 \end{document}

### 2023-05-17 causal.R

@@ -8,6 +8,8 @@ library(glmnet)
 library(ncvreg)
 library(xtable)
 
+set.seed(1e3)
+
 sig1 = diag(100)
 
 x = rmvnorm(50, sigma = sig1)
@@ -22,7 +24,7 @@ a1 = sapply(1:50, function(j)rbinom(1,1,a1_dum[j]))
 y1 = 4*a1 + x[,1:length(beta1)] %*% beta1 + rnorm(50, sd = .1)
 
 
-ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 10, gam_a = 1e-2, gam_b = 1e-2, n.iter = 1000, n.adapt = 500, n.sample = 1000){
+ISVS = function(x, y, a, alphas, tau_0 = 1e-5, tau_1 = 10, gam_a = 1e-2, gam_b = 1e-2, n.iter = 1000, n.adapt = 500, n.sample = 1000){
   MCMC = list()
   
   string = "
@@ -130,11 +132,11 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-2, tau_1 = 10, gam_a = 1e-2, gam_b =
   
 }
 
-sim1_rbvs1 = ISVS(x, y1, a1, alphas = seq(0.2,0.9, length.out = 5), tau_1 = 10)
+sim1_rbvs1 = ISVS(x, y1, a1, alphas = seq(0.8,0.9, length.out = 5), tau_1 = 5)
 
 prob_exp = matrix(unlist(lapply(sim1_rbvs1$probs, function(x)colMeans(as.matrix(x)))), nrow = 5, byrow = T)
 
-active = t(sapply(1:5, function(i) (prob_exp[i,] >0.5)))
+active = t(sapply(1:5, function(i) (prob_exp[i,] <= 0.5)))
   #c(1:100)[-c(which(apply(prob_exp, 2, min)>0.5))] 
 
 beta_exp = matrix(unlist(lapply(sim1_rbvs1$Betas, function(x)colMeans(as.matrix(x)))), nrow = 5, byrow = T)
@@ -160,8 +162,7 @@ causal_corr = c()
 for (i in 1:5) {
   y_new = y1 - x[,which(active[i,] ==T)] %*% beta_dss[[i]] - beta0_exp[i]
   print(sum(y_new))
-  T_new = a1 - ((pnorm(x[,which(active[i,] ==T)] %*% gamma_dss[[i]] + gamma0_exp[i])))
[…]

### 2023-05-18 JASA-template.tex
update till simulation

@@
 \subsection{Robust Bayesian Analysis}
+The hierarchical model presented above is fairly common in
+Bayesian analysis and performs well when we have sufficient data to begin with. However, especially
+in the case of causal inference having sufficient data may not be practical. Moreover, since there’s
+an aspect of intervention in causal effect estimator, we also need to be cautious around the side
+effects of a treatment.
+Therefore, we are interested in having a more robust framework for selecting a variable. So
+that, once we are initiating our treatment, we can decide whether we require more data to conduct
+our analysis. For instance, we can assign a cost for false positives and false negatives and also for
+conducting more tests. This way we can have a more generalised utility based framework with
+which we can incorporate the notion of indeterminacy.
 We perform our

### 2023-05-18 basu23c.tex
update till simulation

@@
 \subsection{Robust Bayesian Analysis}
-We perform our
-robust Bayesian analysis on $q\coloneqq(q_1$, \dots, $q_p)\in\mathcal{P}$, where
+
+The hierarchical model presented above is a standard spike and slab model for
+variable selection and performs well when we have sufficient data to begin with. 
+However, especially in the case of causal inference having sufficient data may not 
+be practical. Moreover, since there’s an aspect of intervention in causal effect 
+estimator, we also need to be cautious about the side effects of a treatment.
+Therefore, we are particularly interested in constructing a robust Bayesian framework
+for variable selection. So that, once we are preparing a guideline for treatment, we 
+can decide whether we require more data to conduct our analysis. For instance, 
+we want to evaluate the problem based on the cost associated with different aspects
+of variable selection including the possibility of abstention that is
+conducting more tests. This way we can have a generalised utility based framework with
+which we can interpret the lack of evidence efficiently without having an adverse
+effect.
+
+In general, a possible outcome of mistreating a subject can have an outcome
+which can not be associated with a loss function for obvious reasons. Instead, we
+assume that we can always treat a subject to normality after an initial mistreatment.
+and we can associate a loss function with the cost of further treatments. This way, 
+for in simplest case, can associate two constant values for false positives and
+false negatives. Clearly, false positives will lead to unwanted side effects and
+false negatives will lead to mistreatment of the patient. Finally, we associate
+a loss value for abstention which can be interpreted as the cost of further tests.
+We present this notion in the following table.
+\begin{table}[h]
+    \centering
+    \begin{tabular}{l|ccc}
+       &  False Positive & False Negative & Abstention \\
+       \hline
+       Value  &  $\ell_1$ & $\ell_2$ & $\ell_3$
+    \end{tabular}
+    \caption{Losses with respect to different types of variable selection}
+    \label{tab:loss:vs}
+\end{table}
+Ideally, in most cases, $\ell_3\ll \ell_1,\ell_2$. However, in certain scenarios,
+this might not be the case. Especially when the condition of a subject deteriorates rapidly
+over time.
+
+Now, based on this notion of abstaining from selecting a variable, we can perform
+a sensitivity analysis over a set of priors on the prior selection probability.
+That is, we can consider a set of possible values for $q_j$ such that
+$q\coloneqq(q_1$, \dots, $q_p)\in\mathcal{P}$, where
 \begin{equation}
@@
 \end{equation}
+Here the equality occurs for the near vacuous case. However, in real-life
+situations, performing a robust Bayesian analysis for near vacuous case is 
+not practical. Instead, we incorporate expert elicitation to define our model.
+For instance, for the equiprobable case, we can consider $q = q_1=q_2=\cdots = q_p$
+and $q\in \left[\underline{q}, \overline{q}\right]$
+where $p\underline{q}$ and $p\overline{q}$ represent the bounds of the prior expectation on the
+total number of variables present in either of the models.
 
@@
 \begin{align}
-	\lexp (\pi_j\mid W)\coloneqq \inf_{q_j\in \mathcal{P}_j} \text{E}(\pi_j\mid W) > 1/2.
+	\uexp (\pi_j\mid W)\coloneqq \sup_{q_j\in \mathcal{P}_j} \text{E}(\pi_j\mid W) < 1/2.
+\end{align}
+Similarly, we consider the $j$-th predictor to be present in at least one of the models, if
+\begin{align}\label{eq:vs:sel}
+	\lexp (\pi_j\mid W)\coloneqq \sup_{q_j\in \mathcal{P}_j} \text{E}(\pi_j\mid W) > 1/2.
+\end{align}
+Otherwise, we consider the variable to be indeterminate and abstain from putting
+it in any of the models and reports lack of information.
+
+In general, this framework is self sufficient for variable selection. However, for
+model fitting and prediction, we need to evaluate the values 
+of the regression coefficients. For that we first need to find the set of active
+predictors with respect to our prior expectation of the selection probability $q$.
+We define the set $S(q)$ such that for any fixed $q$.
+\begin{equation}
+	S(q)\coloneqq
+	\left\{j : E(\pi_j\mid W) \ge 1/2\right\}.
+\end{equation}
+That is the set that contains all the variables which are active
+either in the treatment model and or in the outcome model for a fixed value of $q$. 
+Clearly, if we take intersection over all $q$ then it gives us back the set of
+active variables obtained through \cref{eq:vs:sel}. That is 
+\begin{align}
+    \mathcal{S}\coloneqq \left\{j:\lexp (\pi_j\mid W)>1/2\right\}
+    = \bigcap_{q\in \mathcal{P}}S(q)
 \end{align}
 
-For the rest of the variables, some of them will be present
-in the model as confounders and some will only be associated with
-either the treatment. Let $\mathcal{S}$ denote the set of
-predictors such that,
-\begin{equation}
-	\mathcal{S}\coloneqq
-	\left\{j : \lexp(\pi_j\mid W) < 1/2\right\}.
-\end{equation}
-That is the set that contains all the variables which are not
-removed from both treatment and outcome model. Now, for
-each fixed value of $q$,
-let $\hat{\beta}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression coefficients of the outcome model with respect to
-the predictors that belong to $\mathcal{S}$. Similarly,
-$\hat{\gamma}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression
-coefficients for the treatment effects. Since, we use a continuous type
-selection prior, these regression coefficients are non-zero in nature.
-Therefore, to adjust the sparsity, we apply the 
-``decoupled shrinkage and selection'' method proposed by \cite{hahn2015}. To do so, we solve the following adaptive LASSO-type \cite{Zou2006}
+Now, for each fixed value of $q$, let $\hat{\beta}_{S(q)}$ be the posterior means 
+of the regression coefficients of the outcome model with respect to
+the predictors that belong to $S(q)$. Similarly,
+$\hat{\gamma}_{S(q)}$ be the posterior means of the regression
+coefficients for the treatment effects. Since, we use continuous 
+spike and slab priors, these regression coefficients are not sparse.
+Moreover, with our variable selection we only determine whether the variable 
+is included in at least one of the models. But, we can not determine a specific 
+association. Therefore, to adjust the sparsity of the estimates and understand
+the specific association with the treatment/outcome/both, we apply the 
+``decoupled shrinkage and selection'' method proposed by \cite{hahn2015}. 
+For that, we solve the following adaptive LASSO-type \cite{Zou2006}
 problems
@@
 \begin{align}
-	\hat{\beta}^*_{\mathcal{S}}(q) &= 
-	\arg\min_{\beta_{\mathcal{S}}} \frac{1}{n}\|X_{\mathcal{S}}\hat{\beta}_{\mathcal{S}}(q)
-	- X_{\mathcal{S}} \beta_{\mathcal{S}}\|_2^2 + \lambda\sum_{j\in\mathcal{S}} 
-	\frac{|\beta_j|}{|\hat{\beta}_j(q_j)|}
+	\hat{\beta}^D_{S(q)} &= 
+	\arg\min_{\beta_{S(q)}} \frac{1}{n}\|X_{S(q)}\hat{\beta}_{S(q)}
+	- X_{S(q)} \beta_{S(q)}\|_2^2 + \lambda\sum_{j\in S(q)} 
+	\frac{|\beta_{j,S(q)}|}{|\hat{\beta}_{j,S(q)}|}
 \end{align}
@@
 \begin{align}
-	\hat{\gamma}^*_{\mathcal{S}}(q) &= 
-	\arg\min_{\gamma_{\mathcal{S}}} \frac{1}{n}\|X_{\mathcal{S}}\hat{\gamma}_{\mathcal{S}}(q)
-	- X_{\mathcal{S}} \gamma_{\mathcal{S}}\|_2^2 + \lambda\sum_{j\in\mathcal{S}} 
-	\frac{|\gamma_j|}{|\hat{\gamma}_j(q_j)|}
+	\hat{\gamma}^D_{S(q)} &= 
+	\arg\min_{\gamma_{S(q)}} \frac{1}{n}\|X_{S(q)}\hat{\gamma}_{S(q)}
+	- X_{S(q)} \gamma_{S(q)}\|_2^2 + \lambda\sum_{j\in S(q)} 
+	\frac{|\gamma_{j,S(q)}|}{|\hat{\gamma}_{j,S(q)}|}
 \end{align}
-where $q_{j}\in \mathcal{P}_{j}$ for all $j\in\mathcal{S}$.
+where $q\in \mathcal{P}$.
 
-\iftrue
-\subsection{Causal effect adjustment} The DSS method explained
+The DSS method explained
 above give us adjusted coefficient estimates for the treatment
@@
 will contribute to the prediction error. Therefore, we need to 
-adjust the causal effect estimate as well. We do that in three steps
+adjust the causal effect estimate as well. Let
+\begin{equation}
+    \hat{T}^D = \mathbb{I}\left(\hat{\gamma}_0+X_{S(q)}\hat{\gamma}^D_{S(q)} >0\right)
+    \quad\text{and}\quad
+    \hat{T} = \mathbb{I}\left(\hat{\gamma}_0+X\hat{\gamma}^q >0\right).
+\end{equation}
+and let $\beta_{T}^D(q)$
+be the causal effect after applying `DSS' and $\hat{\beta}_{T}(q)$ be the
+posterior estimate of the causal effect for any fixed $q\in\mathcal{P}$. Then
+the adjusted estimate is given by:
+\begin{equation}
+    \beta_{T}^D(q) = \left(\left(\hat{T}^D\right)^T \hat{T}^D\right)^{-1}
+    \left(\hat{T}^D\right)^T \left[\hat{\beta}_{T}(q)\hat{T} 
+    + X_{S(q)}\left(\hat{\beta}_{S(q)} - \hat{\beta}^D_{S(q)}\right) 
+    +X_{S^C(q)}\hat{\beta}_{S^C(q)}\right]
+\end{equation}
+where
+\begin{equation}
+    S^C(q)\coloneqq \left\{1,2,\cdots, p\right\} \neg S(q).
+\end{equation}
+
+\iffalse
+\subsection{Causal effect adjustment}  We do that in three steps
 similar to double residual regression procedure as suggested by

### 2023-05-19 causal.R
update code for par

@@ -7,8 +7,10 @@ library(horseshoe)
 library(glmnet)
 library(ncvreg)
 library(xtable)
+library(foreach)
+library(doParallel)
 
-set.seed(1e3)
+set.seed(1e8)
 
 sig1 = diag(100)
 
@@ -24,7 +26,7 @@ a1 = sapply(1:50, function(j)rbinom(1,1,a1_dum[j]))
 y1 = 4*a1 + x[,1:length(beta1)] %*% beta1 + rnorm(50, sd = .1)
 
 
-ISVS = function(x, y, a, alphas, tau_0 = 1e-5, tau_1 = 10, gam_a = 1e-2, gam_b = 1e-2, n.iter = 1000, n.adapt = 500, n.sample = 1000){
+ISVS = function(x, y, a, alphas, tau_0 = 1e-5, tau_1 = 10, gam_a = 1e-2, gam_b = 1e-2, n.iter = 10000, n.adapt = 5000, n.sample = 10000, n.cores = 5){
   MCMC = list()
   
   string = "
@@ -70,15 +72,18 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-5, tau_1 = 10, gam_a = 1e-2, gam_b =
       spikeg[j] ~ dnorm(0, (1 / tau_0^2))
       slabg[j] ~ dnorm(0, (1 / tau_1^2))
       
-      b[j] = (1 - w[j]) * slab[j]  + w[j] * spike[j]
-      g[j] = (1 - w[j]) * slabg[j]  + w[j] * spikeg[j]
+      b[j] = w[j] * slab[j]  + (1 - w[j]) * spike[j]
+      g[j] = w[j] * slabg[j]  + (1 - w[j]) * spikeg[j]
     }
     
   }
   "
   params = c("b", "b0", "b_T", "g", "g0", "w", "sigma2")
   
-  for (i in 1:length(alphas)) {
+  cl = makeCluster(n.cores) #not to overload your computer
+  registerDoParallel(cl)
+  
+  MCMC = foreach (i = 1:length(alphas), .packages = 'rjags') %dopar% {
     
     alpha = as.vector(alphas[i])
     
@@ -99,8 +104,10 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-5, tau_1 = 10, gam_a = 1e-2, gam_b =
     
[…]

### 2024-03-09 replies_reviews.txt
sync

----------------------- REVIEW 1 ---------------------

This paper introduces a robustification of a Bayesian approach to indentify 
whether a treatment has an influence on an outcome variable, including possible 
effects of external variables. The model is assumed to be linear (both between 
outcomes and treatments/variables, and between treatment and variables).

Overall, the paper is well written and I believe rigourous (my knowledge of this
particular approach is limited). I would say the technical extension is rather 
simple (considering sets of parameters and performing sampling experiments wihtin 
these sets, followed by a classical Bayesian analysis), and the experiments 
synthetic, hence the most interesting part of the paper appears to me as the one 
trying to identify why going imprecise/robust is good. However the analysis of 
the experiments is a bit cryptic to me. Still, the paper seems ok enough to me to 
be presented and discussed at ECSQARU, and it fits the scope of the conference.

-> Thank you very much for your positive feedbacks. We have modified the 
-> simulation studies to explain the methods in a better way.

Given my limited knowledge of the formal model, most of my relevant comments 
will concern the experiments:

* I do not really understand what is reported in Table 2: what is the quantity 
we read, what should be his ideal value (lower=better, higher=better, fitting a
particular estimate?). Form my understanding, this is the estimate of \beta_T 
once the Bayesian analysis has been achieved. This should be clearly stated. 
The results however seem to show that the Bayesian analysis is doing really fine 
in both cases, and it would also be interesting to report some credibility 
intervals for those. It would also probably be interesting to look what happens 
in case of model/prior misspescification, and how the two approaches would react 
in this case.

-> We propose a robust Bayesian analysis to show its benefits in situation
-> where we have limited data to perform our analysis. We now have modified
-> the text and the table to make it more interpretable.

* Table 3 is a bit frustrating, as 1. we also appear to be in a rebgime where 
classical approaches mostly do fine (maybe finding a regime where imprecision 
works better would be useful?), 2. it is not clear what are the origins/main
contributors to the loss when it is non-null (mostly false positives/false 
negatives or abstention?) and 3. what would give the classical Bayesian approaches 
if one used the proposed loss functions to take decisions, using a rather classical
appraoch of seeing abstention as a peculiar decision in competition with the 
others... albeit by choosing \ell_3=0.5 which is similar to discounted accuracy 
it is quite likely that such an otpion would never be considered by precise methods.

-> Thank you very much for this interesting feedback. As we mentioned earlier,
-> we are particularly focusing on the situations where we have limited data.
-> Since it is a regressional framework, the analyses tends to support
-> classical approaches for $n \ge 50$. We have modified the simulation
-> setting to show results for $25 \le n \le 75 $, to reflect a regime where
-> imprecision is more useful.

Minor comments:

* Equations (2) and (3): I am not sure what to do subject-specific random variable? 
How can we interpret a single individual experiment as a random quantity (I know 
this is classical in statistics and that "in theory" everything goes fine, but in
practice this seems weird).

-> The random variables for subject specific
-> quantities, such as Yi and Ti, denote quantities before they are observed.
-> Since these quantities, before observation, are uncertain, they must be treated
-> as random variables. For instance, the decision to treat or not, Ti, could be
-> based on some bio markers, which are inherently random due to noise.
-> The uncertainty about the response Yi could be more epistemic in nature,
-> although there could also be random factors that influence the response.
-> The resulting subject specific values of delta_i correspond then to a
-> mathematical formulation of treatment effect heterogeneity.

* I am not sure Table 1 information should be a table rather than in-line texts. 
It seems to me like its taking space without adding much structure/info.

-> We now have modified the table accordingly.

----------------------- REVIEW 2 ---------------------

The authors focus on causal inference, and the goal here is to enlarge the usual
Bayesian analysis so that a set of probability distributions is contemplated and 
so that robustness can be assessed. This is a relevant issue (even though it is
presented as if its relevant is obvious, and some words connecting with the bursting
literature on causal thinking in AI would be really valuable). And the paper is 
well written and easy to follow. The contribution is somewhat narrow as it basically
consists in taking an existing model and adding a set of probabilities to it, so 
as to examine robustness and sensitivity. This makes sense but the idea seems quite
natural and does not seem to bring technical insight (perhaps this should be 
discussed: is there any technical issue that is challenging in doing the extension
proposed in the paper?). The weak part is the validation, as it is based on apparently
simple simulations. It would be a lot more convincing to use real data; given the
amount of data available today, it would be strange not to find some dataset that 
is appropriate. Any thoughts?

-> Thank you for the comment. We agree it would be better to use real data.
-> Unfortunately we cannot fully implement this suggestion for the conference paper,
-> but we have acknowledged this issue in the conclusion, and we shall definitely take
-> your suggestion forward in future work.

Concerning the text, a few suggestions:
- The abstract is rather long and wordy; perhaps it could be shortened and made sharper.

-> We agree. We have made the abstract a bit shorter.

- A few places: "can not" instead of "cannot".
- Expressions (20) and (21) should have ending punctuation.
- Page 9: "under estimates" instead of "underestimates"; also, expression "the near
vacuous of set of" seems incorrect.
- References:  "Bayesian" instead of "bayesian".

-> Thank you very much for pointing out the typos. We have corrected those accordingly.

----------------------- REVIEW 3 ---------------------

This is paper focuses on Bayesian hierarchical methods for the estimation of causal effects. The authors adopt a standard regression model for causal estimation and a Bayesian hierarchical model based on that model. The goal is to cope with data scarcity, and a robust approach consisting of a sensitivity analysis wrt the priors is used. This gives a procedure for covariate selection.  A utility approach is also sketched to evaluate whether the available data are sufficient for a robust decision. The method is tested on a synthetic model, and the results compete with existing approaches.

I understand the work of the authors as an application of ideas from robust Bayes and imprecise probability theories to causal analysis. This looks very promising to me. Even if I regard the present work as a first attempt in this direction, the paper might trigger interesting discussions at the conference.

-> Thank you for your positive comments.

I miss some discussions about the optimisation method. I understand everything here is based on sampling, but the differences between standard approaches should also be emphasised. I also don't understand whether the bound approximation can be characterised (e.g., inner approx).

-> Thank you for the comment. We agree it would be better to investigate further theoretical
-> properties and obtain approximations of the posterior estimates.
-> Unfortunately we cannot finish the implementation for the conference paper,
-> but we have acknowledged this issue in the conclusion, and we shall definitely take
-> your suggestion forward in future work.

More generally speaking, the authors might also be interested in the works about the bounding of counterfactuals. Sampling methods have been proposed for that (see various recent works by Bareinboim and colleagues and also Zaffalon and colleagues).

-> Thank you for this interesting insight, currently this is beyond the scope of our
-> contribution but we will definitely take your suggestion for the extension of the
-> paper.

### 2024-03-09 ecsqaru.tex
sync

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[oribibl]{llncs}
%
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{mathtools}
\usepackage{blindtext}
\usepackage[capitalise]{cleveref}
\usepackage[british]{babel}
\usepackage{geometry}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage{bigints}
%\usepackage{siunitx}
\usepackage{soul}
\usepackage{tikz}
\usepackage{color}
\usepackage{easyReview} % for \comment, \alert, etc.
\usepackage{multicol}
\usepackage{multirow}
\newcommand{\x}{\boldsymbol{X}}
\renewcommand{\b}{\hat{\beta}}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\normal}{\mathcal{N}}
\newcommand{\lexp}{\underline{\text{E}}}
\newcommand{\uexp}{\overline{\text{E}}}

\begin{document}

\title{A Robust Bayesian Approach for Causal Inference Problems
%\thanks{}
}
%
\author{Tathagata Basu\inst{1}\orcidID{0000-0002-6851-154X} \and
Matthias C.~M.~Troffaes\inst{2}\orcidID{0000-0002-1294-600X} \and
Jochen Einbeck\inst{2,3}\orcidID{0000-0002-9457-2020}}
%
\authorrunning{Basu et al.}
%
\institute{Civil and Environmental Engineering, University of Strathclyde, UK \and
Department of Mathematical Sciences, Durham University, UK \and
Durham Research Methods Centre, UK}
%
\maketitle              
%
\begin{abstract}
Causal inference
%using observational data is an important problem in
%many fields such as epidemiology, social science, economics, etc.
%Our goal is to find
concerns finding
the treatment effect on subjects
along with causal links between the variables and the outcome.
However,
the underlying heterogeneity between subjects makes the
problem practically unsolvable. Additionally, we often
need to find a subset of
explanatory variables to understand the treatment effect.
Currently, variable selection methods tend to maximise the
predictive performance of the underlying model, and unfortunately,
under limited data, the predictive performance is hard to assess,
leading to
harmful consequences. To address these issues, in this paper, we consider a
robust Bayesian analysis which accounts for abstention in selecting
explanatory variables in the high dimensional regression model.
To achieve that, we consider a set of spike and slab priors
through prior elicitation to obtain a set of posteriors for
both the treatment and outcome model. We are specifically interested
in the sensitivity of the treatment effect in high dimensional causal
inference as well as identifying confounder variables.
However, confounder selection can be deceptive
in this setting, especially when a predictor is strongly associated
with either the treatment or the outcome.
To avoid that we apply a post-hoc selection scheme,
attaining a smaller set of confounders as well as separate sets of variables
which are only related to treatment or outcome model. Finally, we illustrate
our method to show its applicability.

\keywords{high dimensional data \and variable selection \and Bayesian analysis \and imprecise probability.}
\end{abstract}

\section{Introduction}\label{sec:intro}

In causal inference, we are interested in estimating the causal
effect of independent variables on a dependent variable. Ideally,
randomised trials are the most efficient way to perform this task.
However, this is not always practical for several reasons; ethical 
concerns, design cost, population size, to name a few. This
leaves us with observational studies which are usually obtained
by means of collecting data though surveys or record keeping. But this
can be problematic in the presence of confounders, which are variables associated with both the treatment and the outcome.
In such cases, we need to be extra cautious as otherwise it will
lead to unwanted bias in the treatment effect estimator \cite{rosenbaum83}.
Several works have been done in order to tackle the presence of
confounder variables. One such work in the topic was 
by Robins \cite{Robins1986ANA} where the author used  a graphical
approach for the identification of the causal parameters.
Rosenbaum and Robin \cite{rosenbaum1985} suggested the use of a link model to estimate
the propensity scores for all individuals. Later on several other
methods have been proposed based on propensity score matching.
A brief review on such methods can be found in \cite{winship99, stuart10}.

The Bayesian approach in causal effect estimation is a popular
strategy in the field and one of the earlier works on this can be
found in \cite{rubin1978}. Lately, with the rise of high dimensional 
data, Bayesian methodologies have become
more appealing. Crainiceanu \text{et al.~}\cite{Crainiceanu2008} proposed a bi-level 
Bayesian model averaging based method for estimating the causal 
effect. Wang \text{et al.~}\cite{wang2015} suggested BAC (or, Bayesian adjustment for
confounding) where they use an informative prior obtained from
the treatment model and apply them on the outcome model for
estimating causal effect. Several other methods were also
proposed to tackle confounders from the point of view of Bayesian
variable selection, see for instance \cite{Zigler2014,Hahn2018} among others.

In this paper we take inspiration from the approach of Koch \text{et al.~}\cite{koch2020}, who proposed a bi-level spike and slab prior for causal effect 
estimation. They considered a data-driven adaptive approach to
propose their prior which reduces the variance of the causal estimate. 
In our approach, we perform a 
sensitivity analysis based approach where instead of using a single prior, 
we consider a set of priors \cite{BERGER1990303}. This is particularly 
interesting as in many cases, causal effect estimation can be performed 
through a meta analysis and hence robust Bayesian analysis \cite{raices_cruz22} 
can be beneficial under severe uncertainty. Moreover, for some problems 
we have to rely on very limited data to perform our Bayesian analysis and 
inference may not be reliable in presence of heteroscedasticity within
the data. Instead, we use expert opinion and elicit a set of priors 
based on empirical evidence. 
This also allows us to construct the problem of confounder identification 
in a framework where abstention has a relatively positive gain i.e.~
when the cost of further tests/data collection is cheaper than
mistreating a subject. To propose our 
framework, we consider a set of continuous spike and slab priors 
\cite{ishwaran2005} for confounder identification and construct a Bayesian 
group LASSO \cite{xu2015} type problem. To perform the prior sensitivity 
analysis, we consider a set of beta priors on the covariate selection 
probability of the spike and slab priors. We use the posteriors of this
covariate selection probability for identifying the confounders. Finally, 
we consider a post-hoc coefficient adjustment method \cite{hahn2015}
to recover sparse estimates associated with either the outcome or the
treatment model.

The rest of the paper is organised as follows. In \cref{sec:causal}
we give a formal description of the causal estimation problem in the
context of linear regression. \Cref{sec:bayes} is focused on the
Bayesian analysis of causal inference problems, followed by the
motivation of a robust Bayesian analysis along with our proposed decision 
theoretic framework for confounder (variable) selection. In \cref{sec:sim}, 
we provide results of simulation studies under different scenarios 
and show the possible applications in real life problems. Finally, 
we discuss our findings and conclude this paper in \cref{sec:conc}.

\section{Causal Estimation}\label{sec:causal}

Let an observational study give us the outcomes $Y=(Y_1, \dots, Y_n)$ along with 
corresponding treatment indicators $T=(T_1, \dots, T_n)$. Then the
treatment 
effect in the population is given by the expectation of the difference
in outcomes between the treatment and controls:
\begin{align}
	\delta = \mathbb{E}(Y\mid T =1) - \mathbb{E}(Y\mid T=0).
\end{align}
Similarly, the individual causal
effect of treatment $T_i$ on outcome $Y_i$ is given by:
\begin{align}
	\delta_i \coloneqq \mathbb{E}(Y_i\mid T_i=1) - \mathbb{E}(Y_i\mid T_i=0).
\end{align}
That is, we are interested in the difference between the outcomes when the $i$-th subject receives
the treatment and when 
%$i$-th subject 
it remains as a control.

In theory, both of these quantities exist.
However, we cannot observe $\mathbb{E}(Y_i\mid T_i=1)$ and $\mathbb{E}(Y_i\mid T_i=0)$
the average causal effect of the treatment $T$ by calculating the averaged
outcome of all the subjects that received the treatment and
all the subjects that remained as control:
\begin{align}
	\hat{\delta} \coloneqq 
	\frac{\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=1) - 
		\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=0)}{n}.
\end{align}
However, this relies on an important assumption that the treatment effect
on the $i$-th subject given that they received the treatment is the same as the (counterfactual) treatment effect when they remain as control \cite{winship99}.

\subsection{Regression Model}
Regression methods are widely used in causal effect estimation. The
main idea behind these regression methods is to remove the
correlation between the treatment indicator and the error term
\cite{winship99,HECKMAN1985}. To do so, we rely on $p$ different observed quantities
or predictors denoted by $X\coloneqq$ $[X_1^T, \dots, X_n^T]^T$
where each $X_i\in\mathbb{R}^p$.
Each $X_i$ is treated as a $p$-dimensional row vector,
so $X$ is a $n\times p$ matrix.
Now, let
$\beta \coloneqq (\beta_1$, \dots, $\beta_p)^T$ denote the vector of regression
coefficients
related to the predictors, and $\beta_T$ denote a regression coefficient related to the treatment.
Then we can define a linear model for the outcome
so that
\begin{equation}
	Y_i =  T_i \beta_{T} + X_i\beta + \epsilon_i
\end{equation}
where $\epsilon_i\sim \mathcal{N}(0, \sigma^2)$. Clearly, when
the underlying true outcome model is linear with respect to the treatment,
\begin{equation}
	\delta_i = \mathbb{E}(Y_i\mid T_i =1) - \mathbb{E}(Y_i\mid T_i=0) = \beta_{T}.
\end{equation}
In the presence of confounders we also need to consider the
association between the treatment indicators and the predictors.
In literature, authors often suggest a probit link function to 
construct the regression model. This way, we can
specify the conditional probability that subject $i$ receives the treatment through a linear model. 
That is, for another vector of regression coefficients 
$\gamma\coloneqq(\gamma_1, \cdots, \gamma_p)^T$ we define
\begin{align}
	P(T_i=1\mid X_i) = \Phi(X_i\gamma)
\end{align}
where $\Phi(\cdot)$ denotes the cumulative distribution function
of a standard normal distribution. To incorporate this probit
link function, we assume that we can model the $T_i$ through the following \cite{albert93}:
\begin{align}
    T_i^* &= X_i\gamma +u_i \\
    T_i   &= \mathbb{I}(T_i^*>0)
    =
    \begin{cases}
    1 & \text{if }T_i^*>0 \\
    0 & \text{otherwise}
    \end{cases}
\end{align}
where $u_i\sim\mathcal{N}(0,1)$.

Now, to construct the joint likelihood function, we define an extended
output $2n\times 1$ column vector
$W\coloneqq\left(\begin{smallmatrix}Y \\ T^*\end{smallmatrix}\right)$
and corresponding $2n\times(2p+1)$ dimensional design matrix
\begin{align}
	Z &\coloneqq
        \begin{bmatrix}
           T_1 & X_1 & 0 \\
           \vdots & \vdots & 0 \\
           T_n & X_n & 0 \\
           0 & 0 & X_1 \\
           \vdots & \vdots & \vdots \\
           0 & 0 & X_n
        \end{bmatrix}
        =
	\begin{bmatrix}
		X_O & 0 \\
		0 & X_T
	\end{bmatrix}
\end{align}
where, $X_O = [T, X]$ and $X_T = X$. Then, considering the assumption of
Gaussian error terms, we have the following likelihood distribution
\begin{align}
	W\mid Z, \beta_T, \beta, \gamma, \sigma^2 \sim\normal\left(Z\nu, \Sigma\right)\label{eq:like:group},
\end{align}
where $\nu = (\beta_T, \beta^T, \gamma^T)^T$ and
\begin{align}
	\Sigma &=
	\begin{bmatrix}
		\sigma^2{I}_n & 0 \\
		0 & {I}_n
	\end{bmatrix}.
\end{align}

\section{Bayesian Causal Estimation}\label{sec:bayes}

The likelihood given by \cref{eq:like:group} gives us
a foundation for a Bayesian group LASSO 
\cite{xu2015} type model. This way, we can look into the posterior selection
probability associated with the $j$-th predictor. There are several
ways to construct spike and slab priors which achieve 
variable selection. In our case, we consider a continuous type
\cite{ishwaran2005} prior for faster posterior
computation.

\subsection{Hierarchical model}

Let $\pi_j$ denote the prior probability that the $j$-th
predictor is associated to the outcome or the 
treatment. That is, 
\begin{equation}
	\pi_j = P\left((\beta_j,\gamma_j)\not=(0,0)\right).
\end{equation}
Then we can define the following hierarchical model for spike and 
slab group LASSO so that,
for $1\le j\le p$,
\begin{align}
	(\beta_j,\gamma_j)^T \mid \pi_{j}, \sigma^2 &\sim 
	\pi_{j}\normal\left( \begin{bmatrix}
		0 \\
		0
	\end{bmatrix}, 
	\tau_1^2\begin{bmatrix}
		\sigma^2 & 0 \\
		0 & 1
	\end{bmatrix}\right)
	+ (1-\pi_{j}) \normal\left(\begin{bmatrix}
		0 \\
		0
	\end{bmatrix}, 
	\tau_0^2\begin{bmatrix}
		\sigma^2 & 0 \\
		0 & 1
	\end{bmatrix}\right)\\
	\beta_T\mid \sigma^2 &\sim \normal\left(0, \sigma^2\right)\\
	\frac{1}{\sigma^2}&\sim \text{Gamma}(a, b)\\
	\pi_{j} &\sim\text{Beta}\left(sq, s(1-q)\right).
\end{align}
In the hierarchical model, we fix sufficiently small $\tau_0$
$(1\gg\tau_0>0)$ so that  $(\beta_j, \gamma_j)$ has its probability mass 
concentrated around zero. Therefore, this represents the spike component of our prior specification. 
For the slab component, we consider $\tau_1$ to be large so that $\tau_1\ge 1$. This allows the prior for $(\beta_j,\gamma_j)$ to be flat, besides the spike component at the origin.. 
We illustrate the components of a bivariate spike and slab prior in 
\cref{fig:ssbl} (with fixed $\sigma=1$). We generate the spike component 
with $\tau_0=0.001$ and the slab component with $\tau_1=5$.

\begin{figure}[h]
	\begin{center}
		\includegraphics[width = 0.95\linewidth]{spike_slab_bi.pdf}
	\end{center}
	\caption{Spike (left) and slab (right) components of a bi-variate distribution for $\tau_0 = 0.001$, $\tau_1$ = 5 and $\sigma=1$.}
	\label{fig:ssbl}
\end{figure}

For the precision term $1/\sigma^2$, a natural choice of prior is the gamma distribution
as it allows the control of both the location and the scale of the precision. To
ensure that the prior is able to represent the data, we consider $b=1$ and 
fix $a$ so that it represents the prior mean of the precision. In cases where we have no prior information,
we can simply consider a large value for $a$ so that the interval
$[0, 2a]$ contains the true value of the precision.
As defined earlier, $\pi_j$ is used as the selection probability
of the $j$-th predictor in either of the models and we use a beta prior to specify 
these selection probabilities where  $q_j$ represents our prior expectation of the selection probability ($\pi_j$) and $s$ acts as 
a concentration parameter.
For the causal effect, we want to use a Gaussian distribution that 
matches the scale of the noise term. Therefore, we consider $\beta_T\sim \normal(0,\sigma^2)$.

In \cref{fig:regress}, we show a probabilistic graphical representation
of our hierarchical model. In the figure, grey circular nodes represent the
prior hyper-parameters which will be used for sensitivity analysis
of the model. The transparent circular nodes are used to denote
the modelling parameters which are our quantities of interest. 
The observed quantities are denoted with transparent rectangular
nodes. We also use a grey rectangular node to denote the intermediate
latent variable $T^*$. We use directed edges to denote the
relationship between different nodes. However, we use a dashed
edge between $X$ and $T$ as they are related through the latent
variable $T^*$.

\begin{figure}
	\centering
	\begin{tikzpicture}[params/.style={circle, draw=black!60, very thick, minimum size=7mm},
		hyper/.style={circle, draw=black!60, fill=black!20, thick, minimum size=7mm},
		post/.style={circle, draw=black!60, fill=green!20, thick, minimum size=7mm},
		latent/.style={rectangle, draw=black!60, fill=black!10, dashed, minimum size=7mm},
		data/.style={rectangle, draw=black!60, thick, minimum size=8mm}]
		\node[params] (1) at (0,0) {$\pi$};
		\node[data] (2) at (3,0) {$X$};
		\node[data] (3) at (6,0) {$T$};
		\node[params] (4) at (1.5,1.5) {$\gamma$};
		\node[latent] (5) at (4.5,1.5) {$T^*$};
		\node[params] (6) at (1.5,-1.5) {$\beta$};
		\node[data] (7) at (3.5,-1.5) {$Y$};
		\node[params] (8) at (0,-3) {$\sigma^2$};
		\node[params] (10) at (6,-1.5) {$\beta_T$};
		\node[hyper] (11) at (-1.5,-.8) {$s$};
		\node[hyper] (12) at (-1.5,.8) {$q$};
		\node[hyper] (13) at (-1.5,-2.2) {$a$};
		\node[hyper] (14) at (-1.5,-3.8) {$b$};
		\draw[black, dashed] (0.75,-3.7) rectangle (7,2.1);

		\path (1) edge[->]  (6);
		\path (1) edge[->]  (4);
		\path (8) edge[->]  (6);
		\path (6) edge[->]  (7);
		\path (2) edge[->]  (7);
		\path (2) edge[->]  (5);
		\path (5) edge[<-] (4);
		\path (5) edge[->] (3);
		\path (3) edge[->]  (7);
		\path (10) edge[->]  (7);
		\path (2) edge[dashed][->] (3);
		\path (8) edge[bend right = 60][->]  (10);
		\path (11) edge[->]  (1);
		\path (12) edge[->]  (1);
		\path (13) edge[->]  (8);
		\path (14) edge[->]  (8);

	\end{tikzpicture}
	\caption{Probabilistic graphical representation for causal inference with Bayesian hierarchical model.}
	\label{fig:regress}
\end{figure}

\subsection{Robust Bayesian Analysis}

The hierarchical model presented above is a standard spike and slab model for
variable selection and performs well when we have sufficient data to begin with. 
However, especially in the case of causal inference having sufficient data may not 
be feasible. Moreover, 
we also need to be cautious about the side effects of a treatment.
Therefore, we are particularly interested in constructing a robust Bayesian framework
for variable selection. This way, when we are preparing a guideline for treatment, we 
can have the option to ask for more data before reaching any conclusion. To achieve this,
we consider a utility based framework with three possible ways of determining a variable.

In general, an unsuccessful treatment of a subject can have severe consequences 
which cannot be associated with a suitable loss function. Instead, we
assume that we can always revert any initial mistreatment by further treatments, 
and we can associate a loss function with the cost of further treatments. This way, 
in the simplest case, we can associate two constant loss values $\ell_1,\ell_2$ 
with false positives and false negatives respectively. 
Clearly, false positives will lead to unwanted side effects and
false negatives will lead to mistreatment of the patient. Finally, we associate
a loss value $\ell_3$ for abstention which can be interpreted as the cost of further tests.
Ideally, in most cases, $\ell_3\ll \ell_1,\ell_2$. However, in certain scenarios,
this might not be the case, especially when the condition of a subject deteriorates rapidly
over time.
\iffalse
\begin{table}[h]
    \caption{Losses with respect to different types of variable selection}
    \label{tab:loss:vs}
    \centering
    \begin{tabular}{l||c|c|c}
       &  False Positive & False Negative & Abstention \\
       \hline
       \hline
       Value  &  $\ell_1$ & $\ell_2$ & $\ell_3$
    \end{tabular}
\end{table}
\fi

Now, based on this notion of abstaining from selecting a variable, we can perform
a sensitivity analysis over a set of priors on the prior selection probability.
That is, we can consider a set of possible values for $q$ such that
$q\in\mathcal{P}$, where $\mathcal{P} \subseteq \left(0, 1\right)^{p}$.
Here, the equality occurs for the near vacuous case. However, in real-life
situations, performing a robust Bayesian analysis for the near vacuous case is 
not practical. Instead, we incorporate expert elicitation to define our model.
For instance, we can consider $q\in \left[\underline{q}, \overline{q}\right]$
where $p\underline{q}$ and $p\overline{q}$ represent the bounds of the prior expectation on the
total number of variables present in either of the models.

\subsection{Variable selection and coefficient adjustment}
For the co-variate selection, we look into the posterior expectation of $\pi_j$. 
We consider the $j$-th predictor to be removed from both the
treatment and outcome model, if
\begin{align}\label{eq:vs:remove}
	\uexp (\pi_j\mid W)\coloneqq \sup_{q\in \mathcal{P}} \mathbb{E}(\pi_j\mid W) < 1/2.
\end{align}
Similarly, we consider the $j$-th predictor to be present in at least one of the models, if
\begin{align}\label{eq:vs:sel}
	\lexp (\pi_j\mid W)\coloneqq \inf_{q\in \mathcal{P}} \mathbb{E}(\pi_j\mid W) \ge 1/2.
\end{align}
Otherwise, we consider the variable to be indeterminate,  in which case we abstain from putting
it in any of the models but instead just report a lack of information.

In general, this framework is self sufficient for variable selection. However, for
model fitting and prediction, we need to evaluate the values 
of the regression coefficients. For that we first need to find the set of active
predictors with respect to our prior expectation of the selection probability $q$.
For any fixed $q$, we define the set $S(q)$ as the set of all variables which are active
in the treatment model or in the outcome model:
\begin{equation}
	S(q)\coloneqq
	\left\{j\colon E(\pi_j\mid W) \ge 1/2\right\}.
\end{equation}
For sensitivity analysis,
the intersection of $S(q)$ over all $q$ gives us the set of
active variables obtained through \cref{eq:vs:sel}.
Similarly, the union gives us the set of
variables that are not removed through \cref{eq:vs:remove}.
That is:
\begin{align}
    \mathcal{S}_*\coloneqq \left\{j:\lexp (\pi_j\mid W)\ge1/2\right\}
    = \bigcap_{q\in \mathcal{P}}S(q),
    \qquad \mathcal{S}^*\coloneqq \left\{j:\uexp (\pi_j\mid W)\ge1/2\right\}
    = \bigcup_{q\in \mathcal{P}}S(q).
\end{align}
Clearly, $\mathcal{S}_*\subseteq\mathcal{S}^*$.
$\mathcal{S}_*$ represents the set of variables that are sure to be selected,
$\{1,\dots,p\}\setminus\mathcal{S}^*$ represents the set of variables that are sure to be removed, and
$\mathcal{S}^*\setminus\mathcal{S}_*$ represents the set of variables about which we are undecided.
In this way, through sensitivity analysis, our approach incorporates robustness.

Now, for each fixed value of $q$, let $\hat{\beta}_{S(q)}$ be the posterior means 
of the regression coefficients of the outcome model with respect to
the predictors that belong to $S(q)$. Similarly,
$\hat{\gamma}_{S(q)}$ be the posterior means of the regression
coefficients for the treatment effects. Since we use continuous 
spike and slab priors, these regression coefficients are not sparse.
Moreover, with our variable selection we only determine whether the variable 
is included in at least one of the models. But, we cannot determine a specific 
association. Therefore, to adjust the sparsity of the estimates and understand
the specific association with the treatment/outcome/both, we apply the 
``decoupled shrinkage and selection'' method proposed by \cite{hahn2015}. 
For that, we solve the following adaptive LASSO-type \cite{Zou2006}
problems

\begin{align}
	\hat{\beta}^D_{S(q)} &= 
	\arg\min_{\beta_{S(q)}} \frac{1}{n}\|X_{S(q)}\hat{\beta}_{S(q)}
	- X_{S(q)} \beta_{S(q)}\|_2^2 + \lambda\sum_{j\in S(q)} 
	\frac{|\beta_{j,S(q)}|}{|\hat{\beta}_{j,S(q)}|}
\end{align}
and
\begin{align}
	\hat{\gamma}^D_{S(q)} &= 
	\arg\min_{\gamma_{S(q)}} \frac{1}{n}\|X_{S(q)}\hat{\gamma}_{S(q)}
	- X_{S(q)} \gamma_{S(q)}\|_2^2 + \lambda\sum_{j\in S(q)} 
	\frac{|\gamma_{j,S(q)}|}{|\hat{\gamma}_{j,S(q)}|}
\end{align}
where $q\in \mathcal{P}$.

\iffalse
The DSS method explained
above give us adjusted coefficient estimates for the treatment
and outcome model. However, as result the causal effect estimate
remains the same and modelling with such adjusted sparse effect 
will contribute to the prediction error. Therefore, we need to 
adjust the causal effect estimate as well. Let
\begin{equation}
    \hat{T}^D = \mathbb{I}\left(X_{S(q)}\hat{\gamma}^D_{S(q)} >0\right)
    \quad\text{and}\quad
    \hat{T} = \mathbb{I}\left(X\hat{\gamma}^q >0\right).
\end{equation}
and let $\beta_{T}^D(q)$
be the causal effect after applying `DSS' and $\hat{\beta}_{T}(q)$ be the
posterior estimate of the causal effect for any fixed $q\in\mathcal{P}$. Then
the adjusted estimate is given by:
\begin{equation}
    \beta_{T}^D(q) = \left(\left(\hat{T}^D\right)^T \hat{T}^D\right)^{-1}
    \left(\hat{T}^D\right)^T \left[\hat{\beta}_{T}(q)\hat{T} 
    + X_{S(q)}\left(\hat{\beta}_{S(q)} - \hat{\beta}^D_{S(q)}\right) 
    +X_{S^C(q)}\hat{\beta}_{S^C(q)}\right]
\end{equation}
where
\begin{equation}
    S^C(q)\coloneqq \left\{1,2,\cdots, p\right\} \neg S(q).
\end{equation}
\fi

\section{Simulation Studies}\label{sec:sim}

For the simulation studies, we consider 2 different settings. In each
case, we generate the design matrix $X$ such that $X_i\sim\mathcal{N}(0, \Sigma)$
for $1\le i\le n$ where $[\Sigma]_{ij} = 0.3^{|i-j|}$. This way, we 
generate 50 predictors for our model with mild correlations among them.
We then use the following generation schemes to generate the outcome and
treatment indicator: 
\begin{equation}
    T_i \sim \text{Bernoulli}\left(1/(1+\exp(-X_i\gamma))\right)
    \quad\text{and}\quad
    Y_i = 4T_i + X_i\beta.
\end{equation}
\begin{description}
    \item[Scenario 1] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
    \item[Scenario 2] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
\end{description}
For both
the cases, we consider different numbers of observations $n$ where
$n=25+ 5k$ for $k=0,1,2,\cdots,10$. %depends on finishing
%$n=25\times 2^k$ for $k=0,1,2,\cdots,5$.

We present our analyses in \cref{tab:causal} and \cref{tab:misspec}.
For the sake of clarity we use the following accronyms: RBCE for 
robust Bayesian causal estimation (our method); SSCE for spike and
slab causal estimation \cite{koch2020}; BSSCE for bi-level spike and slab causal
estimation \cite{koch2020}; and BSSL for Bayesian spike and slab lasso
\cite{xu2015}. As it can be
seen from both the tables, SSCE and BSSCE are formulated for problems
where $p\le n$ and therefore we do not have any results for $n<50$.

\paragraph{Elicitation} For the
elicitation of $\mathcal{P}$, we use marginal correlation between 
$Y$ and $X$ to determine the bounds on number of active variables. We 
set the thresholds to be $0.15$ and $0.35$ for the correlations. We compute the
number of variables with marginal correlation greater than 0.15
(say $p_1$) and number of variables with  marginal 
correlation greater than 0.35 (say $p_2$). 
We use these numbers to obtain the bounds on the number of active
variables so that $\mathcal{P}=[p_2/p , p_1/p]$.

\paragraph{Initialisation} 
To implement our method, we use \texttt{rjags} and for the other three
methods we use the code provided in the appendix of \cite{koch2020}.
For our method, we set $\tau_0=10^{-6}$ and $\tau_1=1$ to construct the
spike and slab prior. For the noise term, we set $a=10$ and $b=1$.  To perform 
our Bayesian analysis with \texttt{rjags}, we first consider an adaptive 
stage with 2000 iterations followed by discarding of 2000 burn in samples 
to refine the posteriors. We consider 5000 MCMC samples to compute the
posterior estimates. For the other methods we use the in-built settings 
to initiate the analyses.

\paragraph{Results}
We provide our result for causal estimate in \cref{tab:causal}. 
As we perform a sensitivity analysis,
our method gives an interval estimate for the causal effect and we show
that in two different rows where the first row gives the lower bound
and the second row gives the upper bound. We notice that our method is 
somewhat in agreement with the other methods but much more consistent
in terms of estimating the treatment effect. However, this is not the
case for other methods and sometimes those methods produce extreme 
values. This can be observed in \cref{fig:comp:trt} as well. Here, the true 
value is represented by the straight line for $\beta_T = 4$.

From the figure, we can notice that our method tends
to underestimate the causal effect. This suggests that
we may want to have a different value of $a$ for these sets of observations
instead of a fixed value of $a=10$ for all of our analyses.
We can also see that the lower bound tends to improve
with increasing number of observations which validates the assumption that as we accumulate
more information, the interval becomes smaller and converges towards
the true value.

% latex table generated in R 4.3.0 by xtable 1.8-4 package
% Tue May 23 18:29:20 2023
\begin{table}[ht]
\caption{Causal estimates obtained from different methods
for 6 different
numbers of observations.}\label{tab:causal}
\centering
\subcaption*{First scenario: $|\gamma_j|, |\beta_j|>0$ for $j\le 10$}
\begin{tabular}{l|rrrrrrrrrrr}
  \hline
 & 25 & 30 & 35 & 40 & 45 & 50 & 55 & 60 & 65 & 70 & 75 \\ 
  \hline
RBCE (low) & 3.22 & 3.54 & 3.30 & 3.66 & 3.77 & 3.80 & 3.85 & 3.89 & 3.90 & 3.91 & 3.89 \\ 
  RBCE (up) & 4.03 & 3.96 & 3.50 & 3.77 & 3.82 & 3.83 & 3.90 & 3.93 & 3.92 & 3.92 & 3.91 \\ 
  SSCE & -- & -- & -- & -- & -- & 4.24 & 4.11 & 3.99 & 4.00 & 4.00 & 3.99 \\ 
  BSSCE & -- & -- & -- & -- & -- & 4.02 & 4.01 & 4.01 & 4.01 & 4.01 & 4.01 \\ 
  BSSL & -0.23 & 4.07 & 6.80 & 4.05 & 4.00 & 4.00 & 4.01 & 3.98 & 3.99 & 3.99 & 3.99 \\ 
   \hline
\end{tabular}\subcaption*{Second scenario: $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$}
\begin{tabular}{l|rrrrrrrrrrr}
  \hline
 & 25 & 30 & 35 & 40 & 45 & 50 & 55 & 60 & 65 & 70 & 75 \\ 
  \hline
RBCE (low) & 2.79 & 3.70 & 3.77 & 3.56 & 3.69 & 3.70 & 3.81 & 3.78 & 3.81 & 3.82 & 3.85 \\ 
  RBCE (up) & 3.65 & 4.01 & 3.96 & 3.82 & 3.90 & 3.86 & 3.92 & 3.89 & 3.91 & 3.88 & 3.91 \\ 
  SSCE & -- & -- & -- & -- & -- & 4.80 & 4.05 & 4.06 & 6.02 & 4.04 & 4.04 \\ 
  BSSCE & -- & -- & -- & -- & -- & 10.34 & 8.12 & 4.17 & 4.04 & 4.06 & 4.05 \\ 
  BSSL & -6.68 & 3.62 & 4.06 & 4.07 & 4.06 & 4.02 & 4.05 & 4.07 & 4.03 & 4.05 & 4.04 \\ 
   \hline
\end{tabular}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width = 0.9\linewidth]{RBCE_comp.pdf}
    \caption{Comparison of different methods in estimating the treatment effect.}
    \label{fig:comp:trt}
\end{figure}

For the variable identification, we use the notion of
different losses as described earlier. We consider
$\ell_1=\ell_2 = 1$ and $\ell_3= 0.2$. This is a
simplified way of choosing the loss function, we can choose more 
sophisticated loss functions based on \cite{ZAFFALON20121282}. We use this associated loss
to obtain the total loss, which we present in \cref{tab:misspec}.
In the table we denote the misspecification by counting the number of
false positives (FP) and false negatives (FN). For RBCE, we have an
additional column `ID' which denotes the number of variables which remain as
indeterminate.
From the table it can be seen that for the first scenario, our method
abstains from identifying some variables for 
$n <50$. Especially for $n=25$, our method identifies 26 and 23 variables as indeterminate
for the first setting and second setting respectively. However,
later on our method gives more precise results in terms of variable
selection. We also notice that BSSL tends to perform poorly
in terms of variable selection for $n=25$, this can be seen
from the treatment effect estimation as well.
Moreover, we observe that for the second setting both SSCE
and BSSCE underperform in identifying the active variables, which can 
be explained from \cref{tab:causal} as well.

% latex table generated in R 4.3.0 by xtable 1.8-4 package
% Wed May 24 00:50:53 2023
\begin{table}[ht]
\caption{Loss based on misspecification of active variables in different
models.}\label{tab:misspec}
\centering
\subcaption*{First scenario: $|\gamma_j|, |\beta_j|>0$ for $j\le 10$}
\begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
  \hline
  &\multicolumn{4}{c||}{RBCE}&\multicolumn{3}{c||}{SSCE}
  &\multicolumn{3}{c||}{BSSCE}&\multicolumn{3}{c|}{BSSL}\\
  \cline{2-14}
 Samples & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
  \hline
25 &   0 &   0 &  26 & 5.2 & -- & -- & -- & -- & -- & -- &  12 &   2 & 14\\ 
  30 &   0 &   1 &   1 & 1.2 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
  35 &   0 &   0 &   1 & 0.2 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
  40 &   0 &   1 &   0 & 1.0 &-- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
  45 &   0 &   0 &   1 & 0.2 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
  50 &   0 &   0 &   0 & 0.0 &  0 &   0  & 0 &   0 &   0  & 0 &   0 &   0  & 0\\ 
  55 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0  & 0 &   0  & 0 &   0 &   0  & 0\\ 
  60 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0  & 0  & 0 &   0 &   0  & 0\\ 
  65 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0 &   0  & 0  & 0 &   0  & 0\\ 
  70 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0 &   0  & 0  & 0 &   0  & 0\\ 
  75 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0 &   0  & 0  & 0 &   0  & 0\\ 
   \hline
\end{tabular}
\subcaption*{Second scenario: $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$}
\begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
  \hline
  &\multicolumn{4}{c||}{RBCE}&\multicolumn{3}{c||}{SSCE}
  &\multicolumn{3}{c||}{BSSCE}&\multicolumn{3}{c|}{BSSL}\\
  \cline{2-14}
 Samples & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
  \hline
25 &   0 &   2 &  23 & 6.6 & -- & -- & -- & -- & -- & -- &   9 &   4 & 13\\ 
  30 &   0 &   2 &   9 & 3.8 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
  35 &   0 &   0 &  18 & 3.6 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
  40 &   0 &   0 &   5 & 1.0 &-- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
  45 &   0 &   0 &   3 & 0.6 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
  50 &   0 &   0 &   1 & 0.2 &  0 &   7 & 7 &   0 &  14 & 14 &   0 &   0 & 0 \\ 
  55 &   0 &   0 &   1 & 0.2 &  0 &   0 & 0 &  0 &  12 & 12 &  0 &   0 & 0 \\ 
  60 &   0 &   0 &   1 & 0.2 &  1 &   0 & 1 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
  65 &   0 &   0 &   0 & 0.0 &  0 &  12 & 12 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
  70 &   0 &   0 &   0 & 0.0 &  0 &   0 &  0 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
  75 &   0 &   0 &   0 & 0.0 &  0 &   0 &  0 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
   \hline
\end{tabular}
\end{table}

\section{Conclusion}\label{sec:conc}

Causal effect estimation is an important tool in statistical learning and needs to
be performed with utmost care as in many cases we may have severe consequence of poor estimation.
In this paper, we tackle this issue by proposing a robust Bayesian analysis of causal 
effect estimation problem for high dimensional data. Our 
framework is focused on the effect of prior elicitation on confounder selection
as well as causal effect estimation. We consider a spike and slab type
prior for confounder selection and discuss the possible sources of uncertainty that
need to be tackled carefully. We were particularly focused on the uncertainty associated
with prior selection probabilities for which we consider a set of beta priors to perform
sensitivity analysis. We showed that the sensitivity analysis on the prior selection probability
gives us a robust confounder selection scheme. In this way, we can abstain from selecting
a confounder when the available data is not sufficient. We also propose a generalised
utility based framework, where we associate a loss for abstaining which can be interpreted 
as the cost of further data collection. Finally, we illustrate our method with synthetic dataset
and compare with other state of the art Bayesian methods.

Currently, the paper proposes a robust Bayesian approach for causal effect estimation where
we rely on sampling strategies to obtain the posterior bounds as well as performing 
variable selection. In future, it will be interesting to derive inner approximation bounds
for the posterior estimates to reduce the computational cost. Moreover, for the sake of
illustration, we rely on simple loss functions and elicitation strategy. In future, we would
like to investigate different elicitation strategies for the method and explore alternative 
loss functions for formulating a decision theoretic framework. Last but not the least,
we noticed that our method
is in good agreement with other methods with an added level of robustness.
This confirms that our method has good potential for real-life problems,
and we intend to apply it on a real dataset in future work.

\bibliographystyle{splncs04}
\bibliography{basu_causal}

\end{document}

### 2024-03-09 causal.R

@@ -10,23 +10,14 @@ library(xtable)
 library(foreach)
 library(doParallel)
 
+source("other_causal.R")
+
 set.seed(1e8)
 
-sig1 = diag(100)
-
-x = rmvnorm(50, sigma = sig1)
-
-beta1 = c(runif(5, -4, -1), runif(5, 1, 4))
-gamma1 = c(runif(5, -4, -1), runif(5, 1, 4))
-
-a1_dum = 1/(1 + exp(-x[,1:length(beta1)] %*% gamma1))
-a1 = sapply(1:50, function(j)rbinom(1,1,a1_dum[j]))
+sig1 = diag(50)
 
 
-y1 = 4*a1 + x[,1:length(beta1)] %*% beta1 + rnorm(50, sd = .1)
-
-
-ISVS = function(x, y, a, alphas, tau_0 = 1e-5, tau_1 = 10, gam_a = 1e-2, gam_b = 1e-2, n.iter = 10000, n.adapt = 5000, n.sample = 10000, n.cores = 5){
+ISVS = function(x, y, a, alphas, tau_0 = 1e-3, tau_1 = 10, gam_a = 10, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 5){
   MCMC = list()
   
   string = "
@@ -47,8 +38,6 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-5, tau_1 = 10, gam_a = 1e-2, gam_b =
     # Prior on the mean
     
     b_T ~ dnorm(0,inv.var)
-    b0 ~ dnorm(0,inv.var)
-    g0 ~ dnorm(0,1)
     
     # prior on the precision
     
@@ -78,9 +67,13 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-5, tau_1 = 10, gam_a = 1e-2, gam_b =
     
   }
   "
-  params = c("b", "b0", "b_T", "g", "g0", "w", "sigma2")
+  params = c("b","b_T", "g", "sigma2", "w")
   
-  cl = makeCluster(n.cores) #not to overload your computer
+  if(n.cores>detectCores()){
+    n.cores = detectCores() - 2 #not to overload your computer
+  }
+  
+  cl = makeCluster(n.cores) 
   registerDoParallel(cl)
   
   MCMC = foreach (i = 1:length(alphas), .packages = 'rjags') %dopar% {
[…]

### 2024-03-09 other_causal.R

@@ -1,0 +1,397 @@
+library(truncnorm) 
+library(MCMCpack) 
+library(parcor)
+
+#Xorig: nxp matrix of covariates 
+#Yorig: nx1 vector of outcomes
+#Aorig: nx1 binary vector indicating treatment assignment
+#tau.2: shrinkage parameter (set to large value to remove shrinkage bias; default is 1000) 
+#M: number of MCMC iterations
+#burn: number of burn-in iterations
+SSCE <- function(Xorig, Yorig, Aorig, tau.2 = 1000, M = 5000, burn = 0, Bilevel = TRUE){
+  #this stores outcome coefficients at each MCMC iteration 
+  beta.sv <- list()
+  
+  #this stores treatment coefficients at each MCMC iteration 
+  gamma.sv <- list()
+  
+  #this stores pi_0 at each MCMC iteration
+  pi_0.sv <- list()
+  
+  #this stores sigma.2 at each MCMC iteration
+  sigma.2.sv <- list()
+  
+  #number of covariates
+  p <- ncol(Xorig)
+  
+  #sample size
+  n <- nrow(Xorig)
+  
+  #transform covariates to have mean zero and unit variance
+  Xstd <- cbind(t(t(Xorig - matrix(rep(apply(Xorig, 2, mean), nrow(Xorig)), 
+                                   nrow(Xorig),byrow=TRUE))*(1/apply(Xorig, 2, sd))), 1, Aorig)
+  
+  #initialize beta to zero
+  beta <- rep(0, p+2)
+  
+  #initialize gamma to zero
+  gamma <- rep(0, p+1)
+  
+  #initialize pi_0
+  pi_0 <- 0.5
+  
+  #initialize sigma.2
+  sigma.2 <- 1
+  
+  #these two variables are used in computations in the Gibbs sampler below
+  Sigma <- 1/(n - 1 + 1/tau.2)
+  D.tau.inv <-diag(rep(1/tau.2, p))
+  
+  #############################################################
+  ######This block is used to estimate parameters for Bilevel SSCE#############
+  ##################################################################
+  
+  #To use the lasso on the outcome model, we will transform the outcome so that
+  #we do not need to estimate an intercept or the main effect of treatment 
+  ##Such a transformation is not necessary but allows for all lasso software to be used
[…]

### 2024-03-21 causal (copy).R
sync

@@ -1,0 +1,752 @@
+library(mvtnorm)
+library(rjags)
+library(SSLASSO)
+library(monomvn)
+library(spikeslab)
+library(horseshoe)
+library(glmnet)
+library(ncvreg)
+library(xtable)
+library(foreach)
+library(doParallel)
+
+source("other_causal.R")
+
+
+set.seed(1e8)
+
+ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 10, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
+  MCMC = list()
+  x_scale = scale(x)
+  x_ctr = attr(x_scale,"scaled:center")
+  x_sd = attr(x_scale,"scaled:scale")
+  
+  string = "
+  model {
+  
+    ## Likelihood
+    
+    for (i in 1:N) 
+    {
+      mean[i] = b_T * a[i] + inprod(x[i,], b)
+      y[i] ~ dnorm(mean[i], inv.var)
+      
+      a[i] ~ dinterval(a_dumm[i], 0)
+      
+      a_dumm[i] ~ dnorm(inprod(x[i,], g), 1)
+    }
+    
+    # Prior on the mean
+    
+    b_T ~ dnorm(0,inv.var)
+    
+    # prior on the precision
+    
+    inv.var ~ dgamma(gam_a, gam_b)
+    
+    sigma2 = 1 / inv.var
+    
+    ## Prior on the regression parameters 
+    
+    for (j in 1:p) 
+    {
+      # prior on the selection probability
+      w[j] ~ dbeta(2*alpha, 2*(1-alpha))I(0.001,0.999)
+      
+      
+      # Prior on beta
+      
+      spike[j] ~ dnorm(0, (inv.var / tau_0^2))
+      slab[j] ~ dnorm(0, (inv.var / tau_1^2))
+      
+      spikeg[j] ~ dnorm(0, (1 / tau_0^2))
+      slabg[j] ~ dnorm(0, (1 / tau_1^2))
+      
+      b[j] = w[j] * slab[j]  + (1 - w[j]) * spike[j]
+      g[j] = w[j] * slabg[j]  + (1 - w[j]) * spikeg[j]
+    }
+    
+  }
+  "
+  params = c("b","b_T", "g", "sigma2", "w")
+  
[…]

### 2024-03-21 causal.R

@@ -12,13 +12,22 @@ library(doParallel)
 
 source("other_causal.R")
 
+
 set.seed(1e8)
 
-sig1 = diag(50)
+sig1 = matrix(nrow=50,ncol = 50)#diag(50)#
 
+for (i in 1:50) {
+  for (j in 1:50) {
+    sig1[i,j] = 0.3^abs(i-j)
+  }
+}
 
-ISVS = function(x, y, a, alphas, tau_0 = 1e-3, tau_1 = 10, gam_a = 10, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 5){
+ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 10, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
   MCMC = list()
+  x_scale = scale(x)
+  x_ctr = attr(x_scale,"scaled:center")
+  x_sd = attr(x_scale,"scaled:scale")
   
   string = "
   model {
@@ -109,11 +118,11 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-3, tau_1 = 10, gam_a = 10, gam_b = 1
   
   for (i in 1:length(alphas)) {
     
-    b_post[[i]] = as.matrix(MCMC[[i]][[1]])[,1:ncol(x)]
+    b_post[[i]] = as.matrix(MCMC[[i]][[1]])[,1:ncol(x)] / x_sd
     
     b_T_post[[i]] = as.matrix(MCMC[[i]][[1]])[,(1+ncol(x))]
     
-    g_post[[i]] = as.matrix(MCMC[[i]][[1]])[,(ncol(x)+2):(2*ncol(x)+1)]
+    g_post[[i]] = as.matrix(MCMC[[i]][[1]])[,(ncol(x)+2):(2*ncol(x)+1)] / x_sd
     
     w_post[[i]] = as.matrix(MCMC[[i]][[1]])[,(2*ncol(x)+3):(3*ncol(x)+2)]
     
@@ -131,33 +140,38 @@ coeff_adj = function(rbvs_obj){
 
 # setting1 
 
-# beta1 = c(runif(5, -4, -1), runif(5, 1, 4))
-# gamma1 = c(runif(5, -4, -1), runif(5, 1, 4))
+if(T){
+  x_all = rmvnorm(75, sigma = sig1)
[…]

### 2024-03-21 JASA-template.tex
Move Jochen to acknowledgements.

--- 2023-03-20 JASA-template.tex
@@
 \usepackage{doi}
+\usepackage{multicol}
+\usepackage{multirow}
+\usepackage{subcaption}
 
@@
 \email{matthias.troffaes@durham.ac.uk}
-\author{Jochen Einbeck$^{2,3}$}
-\email{jochen.einbeck@durham.ac.uk}
 \address{$^1$Civil and Environmental Engineering, University of Strathclyde}
 \address{$^2$Department of Mathematical Sciences, Durham University}
-\address{$^3$Durham Research Methods Centre}
 
@@
 attaining a smaller set of confounders. Finally, we illustrate
-our result using synthetic \alert{and real} dataset.
+our result using synthetic dataset.
 
@@
 \maketitle
-
 \section{Introduction}\label{sec:intro}
@@
 randomised trials are the most efficient way to perform this task.
-However, this is not very practical for several reasons; ethical 
+However, this is not always practical for several reasons; ethical 
 concerns, design cost, population size, to name a few. This
 leaves us with observational studies which are usually obtained
-by means collecting data though surveys or record keeping. But this
-can be problematic in the presence of confounders. That is when
-the variables are associated with both the treatment and the outcome.
+by means of collecting data though surveys or record keeping. But this
+can be problematic in the presence of confounders, which are variables associated with both the treatment and the outcome.
 In such cases, we need to be extra cautious as otherwise it will
@@
 
-Bayesian approach in causal effect estimation has become a popular
-topic in recent days. However, it has been a topic of interest for about 50 
-years and one of the earlier works on this can be
-found in \cite{rubin1978}. Lately with the notion of high dimensional problems, Bayesian methodologies have become
-more appealing. \citet{Crainiceanu2008} proposed a bi-level 
+The Bayesian approach in causal effect estimation is a popular
+strategy in the field and one of the earlier works on this can be
+found in \cite{rubin1978}. Lately, with the rise of high dimensional 
+data, Bayesian methodologies have become
+more appealing. Crainiceanu \text{et al.~}\cite{Crainiceanu2008} proposed a bi-level 
 Bayesian model averaging based method for estimating the causal 
-effect. \citet{wang2015} suggested BAC (or, Bayesian adjustment for
+effect. Wang \text{et al.~}\cite{wang2015} suggested BAC (or, Bayesian adjustment for
 confounding) where they use an informative prior obtained from
@@
 proposed to tackle confounders from the point of view of Bayesian
-variable selection such as: \citet{Zigler2014}, \citet{Hahn2018} etc.
+variable selection, see for instance \cite{Zigler2014,Hahn2018} among others.
 
-In this paper we take inspiration from the approach of \citet{koch2020}, where
-they proposed a bi-level spike and slab prior for causal effect 
+In this paper we take inspiration from the approach of Koch \text{et al.~}\cite{koch2020}, who proposed a bi-level spike and slab prior for causal effect 
 estimation. They considered a data-driven adaptive approach to
-propose their prior which reduce the variance of the causal estimate. 
-In our approach, we are interested in the decision theoretic notion of 
-variable selection and its effect in causal estimation. We suggest a 
+propose their prior which reduces the variance of the causal estimate. 
+In our approach, we perform a 
 sensitivity analysis based approach where instead of using a single prior, 
@@
 interesting as in many cases, causal effect estimation can be performed 
-through a meta analysis and hence robust Bayesian analysis can be beneficial
-\cite{raices_cruz22} under severe uncertainty. Moreover, for some problems 
+through a meta analysis and hence robust Bayesian analysis \cite{raices_cruz22} 
+can be beneficial under severe uncertainty. Moreover, for some problems 
 we have to rely on very limited data to perform our Bayesian analysis and 
-choosing a data-driven prior can lead to overfitting. Instead we can 
-benefit from expert opinion and elicit prior based on empirical evidence.
-This also allows us to construct the problem of confounder selection 
-in a framework where abstention has a positive gain. To propose our 
+inference may not be reliable in presence of heteroscedasticity within
+the data. Instead, we use expert opinion and elicit a set of priors 
+based on empirical evidence. 
+This also allows us to construct the problem of confounder identification 
+in a framework where abstention has a relatively positive gain i.e.~
+when the cost of further tests/data collection is cheaper than
+mistreating a subject. To propose our 
 framework, we consider a set of continuous spike and slab priors 
-\cite{ishwaran2005} for confounder selection and construct a Bayesian 
+\cite{ishwaran2005} for confounder identification and construct a Bayesian 
 group LASSO \cite{xu2015} type problem. To perform the prior sensitivity 
-analyses, we consider a set of beta priors on the covariate selection 
-probability of the spike and slab priors. We use the posteriors of these
+analysis, we consider a set of beta priors on the covariate selection 
+probability of the spike and slab priors. We use the posteriors of this
 covariate selection probability for identifying the confounders. Finally, 
-we consider a post-hoc coefficient adjustment method \citet{hahn2015}
-to recover sparse estimates. This post hoc treatment also helps us to 
-reduce the bias of treatment effect estimation.
+we consider a post-hoc coefficient adjustment method \cite{hahn2015}
+to recover sparse estimates associated with either the outcome or the
+treatment model.
 
 The rest of the paper is organised as follows. In \cref{sec:causal}
-we give a formal description of causal estimation problem in the
-context of linear regression. \cref{sec:bayes} is focused on the
+we give a formal description of the causal estimation problem in the
+context of linear regression. \Cref{sec:bayes} is focused on the
 Bayesian analysis of causal inference problems, followed by the
@@
 theoretic framework for confounder (variable) selection. In \cref{sec:sim}, 
-we provide our result of simulation studies under different scenarios 
-and data analysis with \alert{real data} in \cref{sec:data:analysis}. Finally 
+we provide results of simulation studies under different scenarios 
+and show the possible applications in real life problems. Finally, 
 we discuss our findings and conclude this paper in \cref{sec:conc}.
@@
 
-Let an observational study give us the outcomes $Y=(Y_1$, \dots, $Y_n)$ along with 
-corresponding treatment indicators $T=(T_1$, \dots, $T_n)$. Then the
+Let an observational study give us the outcomes $Y=(Y_1, \dots, Y_n)$ along with 
+corresponding treatment indicators $T=(T_1, \dots, T_n)$. Then the
 treatment 
 effect in the population is given by the expectation of the difference
-in outcome between the treatment and controls. 
+in outcomes between the treatment and controls:
 \begin{align}
-\delta = \mathbb{E}(Y\mid T =1) - E(Y\mid T=0).
+	\delta = \mathbb{E}(Y\mid T =1) - \mathbb{E}(Y\mid T=0).
 \end{align}
-Similarly, individual causal
-effect of the treatment $T_i$ on outcome $Y_i$ is given by:
+Similarly, the individual causal
+effect of treatment $T_i$ on outcome $Y_i$ is given by:
 \begin{align}
-\delta_i \coloneqq (Y_i\mid T_i=1) - (Y_i\mid T_i=0).
+	\delta_i \coloneqq \mathbb{E}(Y_i\mid T_i=1) - \mathbb{E}(Y_i\mid T_i=0).
 \end{align}
-That is, the difference between the outcome when $i$-th subject receives
-the treatment and when $i$-th subject remain as a control.
+That is, we are interested in the difference between the outcomes when the $i$-th subject receives
+the treatment and when 
+%$i$-th subject 
+it remains as a control.
 
 In theory, both of these quantities exist.
-However, we can not observe $(Y_i\mid T_i=1)$ and $(Y_i\mid T_i=0)$
-simultaneously for the $i$-th individual. Instead, we can estimate
-average causal effect of the treatment $T$ by calculating the averaged
-outcome of all the subjects those received the treatment and
-all the subjects those remained as control.
+However, we cannot observe $\mathbb{E}(Y_i\mid T_i=1)$ and $\mathbb{E}(Y_i\mid T_i=0)$
+the average causal effect of the treatment $T$ by calculating the averaged
+outcome of all the subjects that received the treatment and
+all the subjects that remained as control:
 \begin{align}
@@
 However, this relies on an important assumption that the treatment effect
-on the $i$-th subject given that they received the treatment is
-equal to the treatment effect when they remain as the control
-\cite{winship99}.
+on the $i$-th subject given that they received the treatment is the same as the (counterfactual) treatment effect when they remain as control \cite{winship99}.
 
@@
 \cite{winship99,HECKMAN1985}. To do so, we rely on $p$ different observed quantities
-or predictors denoted by $X\coloneqq$ $[X_1$, \dots, $X_n]^T$. Now, let
-$\beta \coloneqq (\beta_1$, \dots, $\beta_p)$ denotes the vector of regression
-coefficients. Then we can define a linear model for the outcome
+or predictors denoted by $X\coloneqq$ $[X_1^T, \dots, X_n^T]^T$
+where each $X_i\in\mathbb{R}^p$.
+Each $X_i$ is treated as a $p$-dimensional row vector,
+so $X$ is a $n\times p$ matrix.
+Now, let
+$\beta \coloneqq (\beta_1$, \dots, $\beta_p)^T$ denote the vector of regression
+coefficients
+related to the predictors, and $\beta_T$ denote a regression coefficient related to the treatment.
+Then we can define a linear model for the outcome
 so that
 \begin{equation}
-    Y_i = \beta_{T} T_i + \beta_0 + X_i\beta + \epsilon_i
+	Y_i =  T_i \beta_{T} + X_i\beta + \epsilon_i
 \end{equation}
 where $\epsilon_i\sim \mathcal{N}(0, \sigma^2)$. Clearly, when
-the underlying true outcome model is linear,
+the underlying true outcome model is linear with respect to the treatment,
 \begin{equation}
-    \delta = \beta_{T}\quad\text{and hence } 
-    \hat{\delta} - \delta = \hat{\beta}_T - \beta_T.
+	\delta_i = \mathbb{E}(Y_i\mid T_i =1) - \mathbb{E}(Y_i\mid T_i=0) = \beta_{T}.
 \end{equation}
-\begin{figure}
-	\centering
-	\begin{tikzpicture}[params/.style={circle, draw=green!60, fill=green!5, very thick, minimum size=7mm}]
-	\node (1) at (0,0) {Treatment ($T$)};
-	\node (2) [right = of 1] {Outcome ($Y$)};
-	\node (4) [below = of 1] {Predictors ($X$)};
-
-	\path (1) edge[->]  (2);
-	\path (1) edge[<-]  (4);
-	\path (2) edge[<-] (4);
-	\end{tikzpicture}
-	\caption{Confounding in causal models.}
-	\label{fig:confounding}
-\end{figure}
-
 In the presence of confounders we also need to consider the
 association between the treatment indicators and the predictors.
-\citet{koch2020} suggested the use of a probit link function to 
+In literature, authors often suggest a probit link function to 
 construct the regression model. This way, we can
@@
 That is, for another vector of regression coefficients 
-$\gamma\coloneqq(\gamma_1, \cdots, \gamma_p)$ we define
+$\gamma\coloneqq(\gamma_1, \cdots, \gamma_p)^T$ we define
 \begin{align}
-    P(T_i=1\mid X_i) \coloneqq \Phi(\gamma_0+X_i\gamma)
+	P(T_i=1\mid X_i) = \Phi(X_i\gamma)
 \end{align}
 where $\Phi(\cdot)$ denotes the cumulative distribution function
-of a standard normal distribution.
+of a standard normal distribution. To incorporate this probit
+link function, we assume that we can model the $T_i$ through the following \cite{albert93}:
+\begin{align}
+    T_i^* &= X_i\gamma +u_i \\
+    T_i   &= \mathbb{I}(T_i^*>0)
+    =
+    \begin{cases}
+    1 & \text{if }T_i^*>0 \\
+    0 & \text{otherwise}
+    \end{cases}
+\end{align}
+where $u_i\sim\mathcal{N}(0,1)$.
 
-This allows us to define intermediate latent variables as suggested
-by \citet{albert93}
-\begin{equation}
-	T_i^* = \gamma_0 + X_i\gamma +u_i
-\end{equation}
-where, $u_i\sim\mathcal{N}(0,1)$. Therefore, $T_i=1$ if $T_i^*>0$ and
-$T_i=0$ if $T_i^*\le0$.
-
-Now, following the approach of \citet{koch2018}, we define an adjusted
-output vector $W\coloneqq(Y, T^*)^T$ and corresponding $2n\times(2p+3)$ dimensional design matrix
+Now, to construct the joint likelihood function, we define an extended
+output $2n\times 1$ column vector
+$W\coloneqq\left(\begin{smallmatrix}Y \\ T^*\end{smallmatrix}\right)$
+and corresponding $2n\times(2p+1)$ dimensional design matrix
 \begin{align}
-    Z &=
+	Z &\coloneqq
+        \begin{bmatrix}
+           T_1 & X_1 & 0 \\
+           \vdots & \vdots & 0 \\
+           T_n & X_n & 0 \\
+           0 & 0 & X_1 \\
+           \vdots & \vdots & \vdots \\
+           0 & 0 & X_n
+        \end{bmatrix}
+        =
 	\begin{bmatrix}
@@
 		0 & X_T
-    \end{bmatrix},
+	\end{bmatrix}
 \end{align}
-where, $X_O = [T, 1_n, X]$ and $X_T = [1_n, X]$. Then, assuming a
-Gaussian error term, we have the following likelihood distribution
+where, $X_O = [T, X]$ and $X_T = X$. Then, considering the assumption of
+Gaussian error terms, we have the following likelihood distribution
 \begin{align}
-W\mid Z, \alpha, \beta, \gamma, \sigma^2 \sim\normal\left(Z\nu, \Sigma\right)\label{eq:like:group},
+	W\mid Z, \beta_T, \beta, \gamma, \sigma^2 \sim\normal\left(Z\nu, \Sigma\right)\label{eq:like:group},
 \end{align}
-where $\nu = (\beta_T, \beta_0, \beta, \gamma_0, \gamma)^T$ and
+where $\nu = (\beta_T, \beta^T, \gamma^T)^T$ and
 \begin{align}
@@
 
-The likelihood formation given by \cref{eq:like:group} gives us
-a foundation for Bayesian group LASSO 
-\cite{xu2015} type model and look into the posterior selection
+The likelihood given by \cref{eq:like:group} gives us
+a foundation for a Bayesian group LASSO 
+\cite{xu2015} type model. This way, we can look into the posterior selection
 probability associated with the $j$-th predictor. There are several
@@
 
-Let, $\pi_j$ denote the prior probability that the $j$-th
-predictor is not associated with either the outcome or the 
+Let $\pi_j$ denote the prior probability that the $j$-th
+predictor is associated to the outcome or the 
 treatment. That is, 
 \begin{equation}
-	\pi_j = P\left((\beta_j,\gamma_j)=(0,0)\right).
+	\pi_j = P\left((\beta_j,\gamma_j)\not=(0,0)\right).
 \end{equation}
-Then we can define a spike and slab group LASSO so that:
+Then we can define the following hierarchical model for spike and 
+slab group LASSO so that,
 for $1\le j\le p$,
@@
 	\end{bmatrix}\right)\\
-%\beta_T, \beta_0\mid \sigma^2 &\sim \normal(0, \sigma^2)\\
-%\gamma_0 &\sim \normal(0,1)\\
-\sigma^2&\sim \text{InvGamma}(a, b)\\
-\pi_{j} &\sim\text{Beta}\left(sq_j, s(1-q_j)\right).
+	\beta_T\mid \sigma^2 &\sim \normal\left(0, \sigma^2\right)\\
+	\frac{1}{\sigma^2}&\sim \text{Gamma}(a, b)\\
+	\pi_{j} &\sim\text{Beta}\left(sq, s(1-q)\right).
 \end{align}
+In the hierarchical model, we fix sufficiently small $\tau_0$
+$(1\gg\tau_0>0)$ so that  $(\beta_j, \gamma_j)$ has its probability mass 
+concentrated around zero. Therefore, this represents the spike component of our prior specification. 
+For the slab component, we consider $\tau_1$ to be large so that $\tau_1\ge 1$. This allows the prior for $(\beta_j,\gamma_j)$ to be flat, besides the spike component at the origin.. 
+We illustrate the components of a bivariate spike and slab prior in 
+\cref{fig:ssbl} (with fixed $\sigma=1$). We generate the spike component 
+with $\tau_0=0.001$ and the slab component with $\tau_1=5$.
 
-We fix sufficiently small $\tau^2_0$
-$(1\gg\tau_0^2>0)$ so that  $(\beta_j, \gamma_j) = (0,0)$ has its probability mass 
-concentrated around zero. Therefore, this represents the spike component of our prior specification. 
-To construct the slab component, we consider $\tau_1^2$ to be large so that $\tau_1^2\ge 1$. This allows the prior for $(\beta_j, \gamma_j)\not=(0,0)$ to be flat. Inverse-Gamma is a natural choice
-for the variance of the Gaussian noise because of conjugacy. To
-make the prior flat, we consider $1\gg a, b >0$.
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[width = 0.95\linewidth]{spike_slab_bi.pdf}
+	\end{center}
+	\caption{Spike (left) and slab (right) components of a bi-variate distribution for $\tau_0 = 0.001$, $\tau_1$ = 5 and $\sigma=1$.}
+	\label{fig:ssbl}
+\end{figure}
 
-As indicated earlier, $\pi_j$ is used as the rejection probability
-of the $j$-th predictor and we use a beta prior to specify 
-these rejection probabilities where  $q_j$ represents our prior expectation of the rejection probability ($\pi_j$) and `$s$' acts as 
+For the precision term $1/\sigma^2$, a natural choice of prior is the gamma distribution
+as it allows the control of both the location and the scale of the precision. To
+ensure that the prior is able to represent the data, we consider $b=1$ and 
+fix $a$ so that it represents the prior mean of the precision. In cases where we have no prior information,
+we can simply consider a large value for $a$ so that the interval
+$[0, 2a]$ contains the true value of the precision.
+As defined earlier, $\pi_j$ is used as the selection probability
+of the $j$-th predictor in either of the models and we use a beta prior to specify 
+these selection probabilities where  $q_j$ represents our prior expectation of the selection probability ($\pi_j$) and $s$ acts as 
 a concentration parameter.
-For the intercept terms of the outcome model and the causal effect, 
-we consider a sufficiently flat prior so that 
-$\beta_0. \beta_T\sim \normal(0,\sigma^2)$. Similarly, for the
-intercept term in the treatment model, we consider 
-$\gamma_0\sim \normal(0,1)$.
+For the causal effect, we want to use a Gaussian distribution that 
+matches the scale of the noise term. Therefore, we consider $\beta_T\sim \normal(0,\sigma^2)$.
 
@@
 		\node[params] (8) at (0,-3) {$\sigma^2$};
-	\node[params] (9) at (3,-3) {$\beta_0$};
 		\node[params] (10) at (6,-1.5) {$\beta_T$};
@@
 		\path (3) edge[->]  (7);
-	\path (9) edge[->]  (7);
 		\path (10) edge[->]  (7);
@@
 		\path (8) edge[bend right = 60][->]  (10);
-	\path (8) edge[->]  (9);
 		\path (11) edge[->]  (1);
@@
 \subsection{Robust Bayesian Analysis}
-We perform our
-robust Bayesian analysis on $q\coloneqq(q_1$, \dots, $q_p)\in\mathcal{P}$, where
-\begin{equation}
-	\mathcal{P} \coloneqq \mathcal{P}_1\times\cdots\times\mathcal{P}_p\subseteq \left(0, 1\right)^{p}.
-\end{equation}
+
+The hierarchical model presented above is a standard spike and slab model for
+variable selection and performs well when we have sufficient data to begin with. 
+However, especially in the case of causal inference having sufficient data may not 
+be feasible. Moreover, 
+we also need to be cautious about the side effects of a treatment.
+Therefore, we are particularly interested in constructing a robust Bayesian framework
+for variable selection. This way, when we are preparing a guideline for treatment, we 
+can have the option to ask for more data before reaching any conclusion. To achieve this,
+we consider a utility based framework with three possible ways of determining a variable.
+
+In general, an unsuccessful treatment of a subject can have severe consequences 
+which cannot be associated with a suitable loss function. Instead, we
+assume that we can always revert any initial mistreatment by further treatments, 
+and we can associate a loss function with the cost of further treatments. This way, 
+in the simplest case, we can associate two constant loss values $\ell_1,\ell_2$ 
+with false positives and false negatives respectively. 
+Clearly, false positives will lead to unwanted side effects and
+false negatives will lead to mistreatment of the patient. Finally, we associate
+a loss value $\ell_3$ for abstention which can be interpreted as the cost of further tests.
+Ideally, in most cases, $\ell_3\ll \ell_1,\ell_2$. However, in certain scenarios,
+this might not be the case, especially when the condition of a subject deteriorates rapidly
+over time.
+\iffalse
+\begin{table}[h]
+    \caption{Losses with respect to different types of variable selection}
+    \label{tab:loss:vs}
+    \centering
+    \begin{tabular}{l||c|c|c}
+       &  False Positive & False Negative & Abstention \\
+       \hline
+       \hline
+       Value  &  $\ell_1$ & $\ell_2$ & $\ell_3$
+    \end{tabular}
+\end{table}
+\fi
+
+Now, based on this notion of abstaining from selecting a variable, we can perform
+a sensitivity analysis over a set of priors on the prior selection probability.
+That is, we can consider a set of possible values for $q$ such that
+$q\in\mathcal{P}$, where $\mathcal{P} \subseteq \left(0, 1\right)^{p}$.
+Here, the equality occurs for the near vacuous case. However, in real-life
+situations, performing a robust Bayesian analysis for the near vacuous case is 
+not practical. Instead, we incorporate expert elicitation to define our model.
+For instance, we can consider $q\in \left[\underline{q}, \overline{q}\right]$
+where $p\underline{q}$ and $p\overline{q}$ represent the bounds of the prior expectation on the
+total number of variables present in either of the models.
 
@@
 treatment and outcome model, if
+\begin{align}\label{eq:vs:remove}
+	\uexp (\pi_j\mid W)\coloneqq \sup_{q\in \mathcal{P}} \mathbb{E}(\pi_j\mid W) < 1/2.
+\end{align}
+Similarly, we consider the $j$-th predictor to be present in at least one of the models, if
+\begin{align}\label{eq:vs:sel}
+	\lexp (\pi_j\mid W)\coloneqq \inf_{q\in \mathcal{P}} \mathbb{E}(\pi_j\mid W) \ge 1/2.
+\end{align}
+Otherwise, we consider the variable to be indeterminate,  in which case we abstain from putting
+it in any of the models but instead just report a lack of information.
+
+In general, this framework is self sufficient for variable selection. However, for
+model fitting and prediction, we need to evaluate the values 
+of the regression coefficients. For that we first need to find the set of active
+predictors with respect to our prior expectation of the selection probability $q$.
+For any fixed $q$, we define the set $S(q)$ as the set of all variables which are active
+in the treatment model or in the outcome model:
+\begin{equation}
+	S(q)\coloneqq
+	\left\{j\colon E(\pi_j\mid W) \ge 1/2\right\}.
+\end{equation}
+For sensitivity analysis,
+the intersection of $S(q)$ over all $q$ gives us the set of
+active variables obtained through \cref{eq:vs:sel}.
+Similarly, the union gives us the set of
+variables that are not removed through \cref{eq:vs:remove}.
+That is:
 \begin{align}
-    \lexp (\pi_j\mid W)\coloneqq \inf_{q_j\in \mathcal{P}_j} \text{E}(\pi_j\mid W) > 1/2.
+    \mathcal{S}_*\coloneqq \left\{j:\lexp (\pi_j\mid W)\ge1/2\right\}
+    = \bigcap_{q\in \mathcal{P}}S(q),
+    \qquad \mathcal{S}^*\coloneqq \left\{j:\uexp (\pi_j\mid W)\ge1/2\right\}
+    = \bigcup_{q\in \mathcal{P}}S(q).
 \end{align}
+Clearly, $\mathcal{S}_*\subseteq\mathcal{S}^*$.
+$\mathcal{S}_*$ represents the set of variables that are sure to be selected,
+$\{1,\dots,p\}\setminus\mathcal{S}^*$ represents the set of variables that are sure to be removed, and
+$\mathcal{S}^*\setminus\mathcal{S}_*$ represents the set of variables about which we are undecided.
+In this way, through sensitivity analysis, our approach incorporates robustness.
 
-For the rest of the variables, some of them will be present
-in the model as confounders and some will only be associated with
-either the treatment. Let $\mathcal{S}$ denote the set of
-predictors such that,
-\begin{equation}
-    \mathcal{S}\coloneqq
-    \left\{j : \lexp(\pi_j\mid W) < 1/2\right\}.
-\end{equation}
-That is the set that contains all the variables which are not
-removed from both treatment and outcome model. Now, for
-each fixed value of $q$,
-let $\hat{\beta}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression coefficients of the outcome model with respect to
-the predictors that belong to $\mathcal{S}$. Similarly,
-$\hat{\gamma}_{\mathcal{S}}(q_{\mathcal{S}})$ be the posterior means of the regression
-coefficients for the treatment effects. Since, we use a continuous type
-selection prior, these regression coefficients are non-zero in nature.
-Therefore, to adjust the sparsity, we apply the 
-``decoupled shrinkage and selection'' method proposed by \citet{hahn2015}. To do so, we solve the following adaptive LASSO-type \cite{Zou2006}
+Now, for each fixed value of $q$, let $\hat{\beta}_{S(q)}$ be the posterior means 
+of the regression coefficients of the outcome model with respect to
+the predictors that belong to $S(q)$. Similarly,
+$\hat{\gamma}_{S(q)}$ be the posterior means of the regression
+coefficients for the treatment effects. Since we use continuous 
+spike and slab priors, these regression coefficients are not sparse.
+Moreover, with our variable selection we only determine whether the variable 
+is included in at least one of the models. But, we cannot determine a specific 
+association. Therefore, to adjust the sparsity of the estimates and understand
+the specific association with the treatment/outcome/both, we apply the 
+``decoupled shrinkage and selection'' method proposed by \cite{hahn2015}. 
+For that, we solve the following adaptive LASSO-type \cite{Zou2006}
 problems
@@
 \begin{align}
-    \hat{\beta}^*_{\mathcal{S}}(q) &= 
-    \arg\min_{\beta_{\mathcal{S}}} \frac{1}{n}\|X_{\mathcal{S}}\hat{\beta}_{\mathcal{S}}(q)
-    - X_{\mathcal{S}} \beta_{\mathcal{S}}\|_2^2 + \lambda\sum_{j\in\mathcal{S}} 
-    \frac{|\beta_j|}{|\hat{\beta}_j(q_j)|}
+	\hat{\beta}^D_{S(q)} &= 
+	\arg\min_{\beta_{S(q)}} \frac{1}{n}\|X_{S(q)}\hat{\beta}_{S(q)}
+	- X_{S(q)} \beta_{S(q)}\|_2^2 + \lambda\sum_{j\in S(q)} 
+	\frac{|\beta_{j,S(q)}|}{|\hat{\beta}_{j,S(q)}|}
 \end{align}
@@
 \begin{align}
-    \hat{\gamma}^*_{\mathcal{S}}(q) &= 
-    \arg\min_{\gamma_{\mathcal{S}}} \frac{1}{n}\|X_{\mathcal{S}}\hat{\gamma}_{\mathcal{S}}(q)
-    - X_{\mathcal{S}} \gamma_{\mathcal{S}}\|_2^2 + \lambda\sum_{j\in\mathcal{S}} 
-    \frac{|\gamma_j|}{|\hat{\gamma}_j(q_j)|}
+	\hat{\gamma}^D_{S(q)} &= 
+	\arg\min_{\gamma_{S(q)}} \frac{1}{n}\|X_{S(q)}\hat{\gamma}_{S(q)}
+	- X_{S(q)} \gamma_{S(q)}\|_2^2 + \lambda\sum_{j\in S(q)} 
+	\frac{|\gamma_{j,S(q)}|}{|\hat{\gamma}_{j,S(q)}|}
 \end{align}
-where $q_{j}\in \mathcal{P}_{j}$ for all $j\in\mathcal{S}$.
+where $q\in \mathcal{P}$.
 
-\iftrue
-\subsection{Causal effect adjustment} The DSS method explained
+\iffalse
+The DSS method explained
 above give us adjusted coefficient estimates for the treatment
@@
 will contribute to the prediction error. Therefore, we need to 
-adjust the causal effect estimate as well. We do that in three steps
-similar to double residual regression procedure as suggested by
-\citet{robinson1988}.
-
-First we compute the predicted values of $Y$ with respect to
-the adjusted regression coefficients so that,
+adjust the causal effect estimate as well. Let
 \begin{equation}
-\hat{Y}(q) 
-= \hat{\beta}_0(q) + X_{\mathcal{S}}\hat{\beta}^*_{\mathcal{S}}(q)
+    \hat{T}^D = \mathbb{I}\left(X_{S(q)}\hat{\gamma}^D_{S(q)} >0\right)
+    \quad\text{and}\quad
+    \hat{T} = \mathbb{I}\left(X\hat{\gamma}^q >0\right).
 \end{equation}
-and the values of $T$ with respect to the adjusted
-regression coefficients so that
+and let $\beta_{T}^D(q)$
+be the causal effect after applying `DSS' and $\hat{\beta}_{T}(q)$ be the
+posterior estimate of the causal effect for any fixed $q\in\mathcal{P}$. Then
+the adjusted estimate is given by:
 \begin{equation}
-\hat{T}(q) 
-= \Phi\left(\hat{\gamma}_0(q) + X_{\mathcal{S}}\hat{\gamma}^*_{\mathcal{S}}(q)\right).
+    \beta_{T}^D(q) = \left(\left(\hat{T}^D\right)^T \hat{T}^D\right)^{-1}
+    \left(\hat{T}^D\right)^T \left[\hat{\beta}_{T}(q)\hat{T} 
+    + X_{S(q)}\left(\hat{\beta}_{S(q)} - \hat{\beta}^D_{S(q)}\right) 
+    +X_{S^C(q)}\hat{\beta}_{S^C(q)}\right]
 \end{equation}
-Then we estimate the adjusted causal effect using the following linear
-model
+where
 \begin{equation}
-\left(Y-\hat{Y}(q)\right) = \left(T - \hat{T}(q)\right)\beta_{T} + \epsilon^*_i.
+    S^C(q)\coloneqq \left\{1,2,\cdots, p\right\} \neg S(q).
 \end{equation}
-That is 
-\begin{equation}
-\beta_{T}^* = \left(\left(T - \hat{T}(q)\right)^T\left(T - \hat{T}(q)\right)\right)^{-1}\left(T - \hat{T}(q)\right)^T\left(Y-\hat{Y}(q)\right)
-\end{equation}
-
 \fi
@@
 
-\section{Data Analysis}\label{sec:data:analysis}
+For the simulation studies, we consider 2 different settings. In each
+case, we generate the design matrix $X$ such that $X_i\sim\mathcal{N}(0, \Sigma)$
+for $1\le i\le n$ where $[\Sigma]_{ij} = 0.3^{|i-j|}$. This way, we 
+generate 50 predictors for our model with mild correlations among them.
+We then use the following generation schemes to generate the outcome and
+treatment indicator: 
+\begin{equation}
+    T_i \sim \text{Bernoulli}\left(1/(1+\exp(-X_i\gamma))\right)
+    \quad\text{and}\quad
+    Y_i = 4T_i + X_i\beta.
+\end{equation}
+\begin{description}
+    \item[Scenario 1] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
+    \item[Scenario 2] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
+\end{description}
+For both
+the cases, we consider different numbers of observations $n$ where
+$n=25+ 5k$ for $k=0,1,2,\cdots,10$. %depends on finishing
+%$n=25\times 2^k$ for $k=0,1,2,\cdots,5$.
+
+We present our analyses in \cref{tab:causal} and \cref{tab:misspec}.
+For the sake of clarity we use the following accronyms: RBCE for 
+robust Bayesian causal estimation (our method); SSCE for spike and
+slab causal estimation \cite{koch2020}; BSSCE for bi-level spike and slab causal
+estimation \cite{koch2020}; and BSSL for Bayesian spike and slab lasso
+\cite{xu2015}. As it can be
+seen from both the tables, SSCE and BSSCE are formulated for problems
+where $p\le n$ and therefore we do not have any results for $n<50$.
+
+\paragraph{Elicitation} For the
+elicitation of $\mathcal{P}$, we use marginal correlation between 
+$Y$ and $X$ to determine the bounds on number of active variables. We 
+set the thresholds to be $0.15$ and $0.35$ for the correlations. We compute the
+number of variables with marginal correlation greater than 0.15
+(say $p_1$) and number of variables with  marginal 
+correlation greater than 0.35 (say $p_2$). 
+We use these numbers to obtain the bounds on the number of active
+variables so that $\mathcal{P}=[p_2/p , p_1/p]$.
+
+\paragraph{Initialisation} 
+To implement our method, we use \texttt{rjags} and for the other three
+methods we use the code provided in the appendix of \cite{koch2020}.
+For our method, we set $\tau_0=10^{-6}$ and $\tau_1=1$ to construct the
+spike and slab prior. For the noise term, we set $a=10$ and $b=1$.  To perform 
+our Bayesian analysis with \texttt{rjags}, we first consider an adaptive 
+stage with 2000 iterations followed by discarding of 2000 burn in samples 
+to refine the posteriors. We consider 5000 MCMC samples to compute the
+posterior estimates. For the other methods we use the in-built settings 
+to initiate the analyses.
+
+\paragraph{Results}
+We provide our result for causal estimate in \cref{tab:causal}. 
+As we perform a sensitivity analysis,
+our method gives an interval estimate for the causal effect and we show
+that in two different rows where the first row gives the lower bound
+and the second row gives the upper bound. We notice that our method is 
+somewhat in agreement with the other methods but much more consistent
+in terms of estimating the treatment effect. However, this is not the
+case for other methods and sometimes those methods produce extreme 
+values. This can be observed in \cref{fig:comp:trt} as well. Here, the true 
+value is represented by the straight line for $\beta_T = 4$.
+
+From the figure, we can notice that our method tends
+to underestimate the causal effect. This suggests that
+we may want to have a different value of $a$ for these sets of observations
+instead of a fixed value of $a=10$ for all of our analyses.
+We can also see that the lower bound tends to improve
+with increasing number of observations which validates the assumption that as we accumulate
+more information, the interval becomes smaller and converges towards
+the true value.
+
+% latex table generated in R 4.3.0 by xtable 1.8-4 package
+% Tue May 23 18:29:20 2023
+\begin{table}[ht]
+\caption{Causal estimates obtained from different methods
+for 6 different
+numbers of observations.}\label{tab:causal}
+\centering
+\subcaption*{First scenario: $|\gamma_j|, |\beta_j|>0$ for $j\le 10$}
+\begin{tabular}{l|rrrrrrrrrrr}
+  \hline
+ & 25 & 30 & 35 & 40 & 45 & 50 & 55 & 60 & 65 & 70 & 75 \\ 
+  \hline
+RBCE (low) & 3.22 & 3.54 & 3.30 & 3.66 & 3.77 & 3.80 & 3.85 & 3.89 & 3.90 & 3.91 & 3.89 \\ 
+  RBCE (up) & 4.03 & 3.96 & 3.50 & 3.77 & 3.82 & 3.83 & 3.90 & 3.93 & 3.92 & 3.92 & 3.91 \\ 
+  SSCE & -- & -- & -- & -- & -- & 4.24 & 4.11 & 3.99 & 4.00 & 4.00 & 3.99 \\ 
+  BSSCE & -- & -- & -- & -- & -- & 4.02 & 4.01 & 4.01 & 4.01 & 4.01 & 4.01 \\ 
+  BSSL & -0.23 & 4.07 & 6.80 & 4.05 & 4.00 & 4.00 & 4.01 & 3.98 & 3.99 & 3.99 & 3.99 \\ 
+   \hline
+\end{tabular}\subcaption*{Second scenario: $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$}
+\begin{tabular}{l|rrrrrrrrrrr}
+  \hline
+ & 25 & 30 & 35 & 40 & 45 & 50 & 55 & 60 & 65 & 70 & 75 \\ 
+  \hline
+RBCE (low) & 2.79 & 3.70 & 3.77 & 3.56 & 3.69 & 3.70 & 3.81 & 3.78 & 3.81 & 3.82 & 3.85 \\ 
+  RBCE (up) & 3.65 & 4.01 & 3.96 & 3.82 & 3.90 & 3.86 & 3.92 & 3.89 & 3.91 & 3.88 & 3.91 \\ 
+  SSCE & -- & -- & -- & -- & -- & 4.80 & 4.05 & 4.06 & 6.02 & 4.04 & 4.04 \\ 
+  BSSCE & -- & -- & -- & -- & -- & 10.34 & 8.12 & 4.17 & 4.04 & 4.06 & 4.05 \\ 
+  BSSL & -6.68 & 3.62 & 4.06 & 4.07 & 4.06 & 4.02 & 4.05 & 4.07 & 4.03 & 4.05 & 4.04 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\begin{figure}
+    \centering
+    \includegraphics[width = 0.9\linewidth]{RBCE_comp.pdf}
+    \caption{Comparison of different methods in estimating the treatment effect.}
+    \label{fig:comp:trt}
+\end{figure}
+
+For the variable identification, we use the notion of
+different losses as described earlier. We consider
+$\ell_1=\ell_2 = 1$ and $\ell_3= 0.2$. This is a
+simplified way of choosing the loss function, we can choose more 
+sophisticated loss functions based on \cite{ZAFFALON20121282}. We use this associated loss
+to obtain the total loss, which we present in \cref{tab:misspec}.
+In the table we denote the misspecification by counting the number of
+false positives (FP) and false negatives (FN). For RBCE, we have an
+additional column `ID' which denotes the number of variables which remain as
+indeterminate.
+From the table it can be seen that for the first scenario, our method
+abstains from identifying some variables for 
+$n <50$. Especially for $n=25$, our method identifies 26 and 23 variables as indeterminate
+for the first setting and second setting respectively. However,
+later on our method gives more precise results in terms of variable
+selection. We also notice that BSSL tends to perform poorly
+in terms of variable selection for $n=25$, this can be seen
+from the treatment effect estimation as well.
+Moreover, we observe that for the second setting both SSCE
+and BSSCE underperform in identifying the active variables, which can 
+be explained from \cref{tab:causal} as well.
+
+% latex table generated in R 4.3.0 by xtable 1.8-4 package
+% Wed May 24 00:50:53 2023
+\begin{table}[ht]
+\caption{Loss based on misspecification of active variables in different
+models.}\label{tab:misspec}
+\centering
+\subcaption*{First scenario: $|\gamma_j|, |\beta_j|>0$ for $j\le 10$}
+\begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
+  \hline
+  &\multicolumn{4}{c||}{RBCE}&\multicolumn{3}{c||}{SSCE}
+  &\multicolumn{3}{c||}{BSSCE}&\multicolumn{3}{c|}{BSSL}\\
+  \cline{2-14}
+ Samples & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
+  \hline
+25 &   0 &   0 &  26 & 5.2 & -- & -- & -- & -- & -- & -- &  12 &   2 & 14\\ 
+  30 &   0 &   1 &   1 & 1.2 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
+  35 &   0 &   0 &   1 & 0.2 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
+  40 &   0 &   1 &   0 & 1.0 &-- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
+  45 &   0 &   0 &   1 & 0.2 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
+  50 &   0 &   0 &   0 & 0.0 &  0 &   0  & 0 &   0 &   0  & 0 &   0 &   0  & 0\\ 
+  55 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0  & 0 &   0  & 0 &   0 &   0  & 0\\ 
+  60 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0  & 0  & 0 &   0 &   0  & 0\\ 
+  65 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0 &   0  & 0  & 0 &   0  & 0\\ 
+  70 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0 &   0  & 0  & 0 &   0  & 0\\ 
+  75 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0 &   0  & 0  & 0 &   0  & 0\\ 
+   \hline
+\end{tabular}
+\subcaption*{Second scenario: $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$}
+\begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
+  \hline
+  &\multicolumn{4}{c||}{RBCE}&\multicolumn{3}{c||}{SSCE}
+  &\multicolumn{3}{c||}{BSSCE}&\multicolumn{3}{c|}{BSSL}\\
+  \cline{2-14}
+ Samples & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
+  \hline
+25 &   0 &   2 &  23 & 6.6 & -- & -- & -- & -- & -- & -- &   9 &   4 & 13\\ 
+  30 &   0 &   2 &   9 & 3.8 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
+  35 &   0 &   0 &  18 & 3.6 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
+  40 &   0 &   0 &   5 & 1.0 &-- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
+  45 &   0 &   0 &   3 & 0.6 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
+  50 &   0 &   0 &   1 & 0.2 &  0 &   7 & 7 &   0 &  14 & 14 &   0 &   0 & 0 \\ 
+  55 &   0 &   0 &   1 & 0.2 &  0 &   0 & 0 &  0 &  12 & 12 &  0 &   0 & 0 \\ 
+  60 &   0 &   0 &   1 & 0.2 &  1 &   0 & 1 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
+  65 &   0 &   0 &   0 & 0.0 &  0 &  12 & 12 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
+  70 &   0 &   0 &   0 & 0.0 &  0 &   0 &  0 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
+  75 &   0 &   0 &   0 & 0.0 &  0 &   0 &  0 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
+   \hline
+\end{tabular}
+\end{table}
 
@@
 
+Causal effect estimation is an important tool in statistical learning and needs to
+be performed with utmost care as in many cases we may have severe consequence of poor estimation.
+In this paper, we tackle this issue by proposing a robust Bayesian analysis of causal 
+effect estimation problem for high dimensional data. Our 
+framework is focused on the effect of prior elicitation on confounder selection
+as well as causal effect estimation. We consider a spike and slab type
+prior for confounder selection and discuss the possible sources of uncertainty that
+need to be tackled carefully. We were particularly focused on the uncertainty associated
+with prior selection probabilities for which we consider a set of beta priors to perform
+sensitivity analysis. We showed that the sensitivity analysis on the prior selection probability
+gives us a robust confounder selection scheme. In this way, we can abstain from selecting
+a confounder when the available data is not sufficient. We also propose a generalised
+utility based framework, where we associate a loss for abstaining which can be interpreted 
+as the cost of further data collection. Finally, we illustrate our method with synthetic dataset
+and compare with other state of the art Bayesian methods.
+
+Currently, the paper proposes a robust Bayesian approach for causal effect estimation where
+we rely on sampling strategies to obtain the posterior bounds as well as performing 
+variable selection. In future, it will be interesting to derive inner approximation bounds
+for the posterior estimates to reduce the computational cost. Moreover, for the sake of
+illustration, we rely on simple loss functions and elicitation strategy. In future, we would
+like to investigate different elicitation strategies for the method and explore alternative 
+loss functions for formulating a decision theoretic framework. Last but not the least,
+we noticed that our method
+is in good agreement with other methods with an added level of robustness.
+This confirms that our method has good potential for real-life problems,
+and we intend to apply it on a real dataset in future work.
+
+\section*{Acknowledgements}
+
+We sincerely thank Jochen Einbeck for his contributions to an earlier version of this paper.
+
 \bibliographystyle{agsm}
-\bibliography{basu22}
+\bibliography{basu_causal}
 \end{document}

### 2024-03-21 JASA-template.tex
Small edit in abstract for clarity.
Another few small edits for abstract.

@@
 to subject and modelling the underlying heterogeneity explicitly makes the 
-problem practically unsolvable. Another issue we often face is the 
-dimensionality of the problem and we need to find a subset of 
-explanatory variables to initiate the treatment. However, currently variable selection methods
-tend to maximise the predictive performance of the outcome model only. This can be problematic in the case of limited information. 
-As the consequence of mistreatment can be harmful. 
-So, in this paper, we suggest a general framework with
-robust Bayesian analysis which accounts for abstention in deciding
-an explanatory variable in the high dimensional regression model. 
+problem practically unsolvable. Additionally, for high dimensional problems,
+we often need to find a subset of 
+explanatory variables to initiate the treatment. However, current variable selection methods
+tend to maximise the predictive performance of the outcome model only. This can be problematic under limited information,
+as the consequence of mistreatment can be harmful. 
+So, in this paper, we develop our model using
+robust Bayesian analysis, to allow for abstention when selecting
+explanatory variables.
 To achieve that, we consider a set of spike and slab priors 

### 2024-03-21 JASA-template.tex
More edits to abstract.

@@
 explanatory variables.
-To achieve that, we consider a set of spike and slab priors 
+Our robust Bayesian model uses a set of spike and slab priors 
 through prior elicitation to obtain robust estimates for
@@
 in the sensitivity of the treatment effect in the high dimensional causal inference
-as well as the identifying the confounder variables by means of variable selection. However, indicator
-based confounder selection can be deceptive in some cases. Especially, 
+as well as identifying confounder variables. However, indicator
+based confounder selection can be deceptive, especially
 when the predictor is strongly associated with either the treatment or 
-the outcome. This increases the posterior expectation of the selection
-indicators. To avoid that we apply a post-hoc selection scheme
-which successfully remove negligible non-zero effects from the model
+the outcom, as this increases the posterior expectation of the selection
+indicators. To avoid that, we apply a post-hoc selection scheme
+which successfully removes negligible non-zero effects from the model,
 attaining a smaller set of confounders. Finally, we illustrate
-our result using synthetic dataset.
+our method using a synthetic dataset.
 

### 2024-03-21 JASA-template.tex
Fix typo.

@@
 when the predictor is strongly associated with either the treatment or 
-the outcom, as this increases the posterior expectation of the selection
+the outcome, as this increases the posterior expectation of the selection
 indicators. To avoid that, we apply a post-hoc selection scheme

### 2024-03-21 JASA-template.tex
Last round of edits for abstract.

@@
 \begin{abstract}
-Causal inference using observational data is an important aspect in
-many fields such as epidemiology, social science, economics, etc. In
-particular, our goal is to find the treatment effect on the subjects
-along with the causal links between the variables and the outcome.
-However, estimation for such problems are extremely 
-difficult as the treatment effects may vary from subject 
-to subject and modelling the underlying heterogeneity explicitly makes the 
+Causal inference using observational data is important in
+many fields, including epidemiology, social science, economics, and many more.
+The goal of causal inference is to find the treatment effect on the subjects
+by identifying causal links between the variables and the outcome.
+However, estimation of such causal links is extremely 
+difficult because the treatment effects may vary from subject 
+to subject. Unfortunately, modelling the underlying heterogeneity explicitly makes the 
 problem practically unsolvable. Additionally, for high dimensional problems,
@@
 explanatory variables to initiate the treatment. However, current variable selection methods
-tend to maximise the predictive performance of the outcome model only. This can be problematic under limited information,
+simply tend to maximise the predictive performance of the outcome model. This can be problematic when information and data are limited,
 as the consequence of mistreatment can be harmful. 
-So, in this paper, we develop our model using
+So, in this paper, we develop a model for causal inference using
 robust Bayesian analysis, to allow for abstention when selecting
@@
 our method using a synthetic dataset.
-
 \end{abstract}
@@
 \maketitle
+
 \section{Introduction}\label{sec:intro}

### 2024-03-21 JASA-template.tex
Small edits.

@@
 
-In causal inference, we are interested in estimating the causal
+Causal inference concerns estimating the causal
 effect of independent variables on a dependent variable. Ideally,
 randomised trials are the most efficient way to perform this task.
-However, this is not always practical for several reasons; ethical 
+However, this is not always practical due to, for instance, ethical 
 concerns, design cost, population size, to name a few. This

### 2024-03-21 JASA-template.tex
Small edits.

@@
 concerns, design cost, population size, to name a few. This
-leaves us with observational studies which are usually obtained
-by means of collecting data though surveys or record keeping. But this
+leaves us with observational studies
+where data is collected though surveys or record keeping. But this
 can be problematic in the presence of confounders, which are variables associated with both the treatment and the outcome.
-In such cases, we need to be extra cautious as otherwise it will
-lead to unwanted bias in the treatment effect estimator \cite{rosenbaum83}.
+In such cases, we must be extra cautious as we risk
+unwanted bias in the treatment effect estimator \cite{rosenbaum83}.
 Several works have been done in order to tackle the presence of

### 2024-03-21 JASA-template.tex
Edits.

@@
 unwanted bias in the treatment effect estimator \cite{rosenbaum83}.
-Several works have been done in order to tackle the presence of
-confounder variables. One such work in the topic was 
-by Robins \cite{Robins1986ANA} where the author used  a graphical
-approach for the identification of the causal parameters.
-Rosenbaum and Robin \cite{rosenbaum1985} suggested the use of a link model to estimate
-the propensity scores for all individuals. Later on several other
-methods have been proposed based on propensity score matching.
-A brief review on such methods can be found in \cite{winship99, stuart10}.
+Several authors have tackled the presence of
+confounder variables. 
+Robins \cite{Robins1986ANA} used a graphical
+approach to identify the causal parameters.
+Rosenbaum and Robin \cite{rosenbaum1985} suggested a link model to estimate
+the propensity scores for all individuals. Subsequently, several other
+methods have been proposed based on propensity score matching;
+see \cite{winship99,stuart10} for a brief review.
 

### 2024-03-21 JASA-template.tex
More edits in intro.

@@
 
-The Bayesian approach in causal effect estimation is a popular
-strategy in the field and one of the earlier works on this can be
-found in \cite{rubin1978}. Lately, with the rise of high dimensional 
-data, Bayesian methodologies have become
-more appealing. Crainiceanu \text{et al.~}\cite{Crainiceanu2008} proposed a bi-level 
+One of the earlier Bayesian approaches to causal inference
+can be found in \cite{rubin1978}. More recently,
+with the rise of high dimensional data,
+Bayesian methodologies have grown in popularity.
+Crainiceanu \text{et al.~}\cite{Crainiceanu2008} proposed a bi-level 
 Bayesian model averaging based method for estimating the causal 
 effect. Wang \text{et al.~}\cite{wang2015} suggested BAC (or, Bayesian adjustment for
-confounding) where they use an informative prior obtained from
-the treatment model and apply them on the outcome model for
-estimating causal effect. Several other methods were also
-proposed to tackle confounders from the point of view of Bayesian
-variable selection, see for instance \cite{Zigler2014,Hahn2018} among others.
+confounding), where an informative prior obtained from
+the treatment model is applied on the outcome model for
+estimating the causal effect. Several other methods were
+proposed to tackle confounders from a Bayesian perspective,
+see for instance \cite{Zigler2014,Hahn2018} among others.
 

### 2024-03-21 JASA-template.tex
updates

@@
 effect. Wang \text{et al.~}\cite{wang2015} suggested BAC (or, Bayesian adjustment for
-confounding), where an informative prior obtained from
+confounding),
+%%% MT to TB: check next phrase
+where an informative prior obtained from
 the treatment model is applied on the outcome model for
@@
 propose their prior which reduces the variance of the causal estimate. 
-In our approach, we perform a 
-sensitivity analysis based approach where instead of using a single prior, 
+Our approach is based on
+sensitivity analysis, where instead of using a single prior, 
 we consider a set of priors \cite{BERGER1990303}. This is particularly 
 interesting as in many cases, causal effect estimation can be performed 
-through a meta analysis and hence robust Bayesian analysis \cite{raices_cruz22} 
-can be beneficial under severe uncertainty. Moreover, for some problems 
+through a meta analysis where robust Bayesian analysis 
+can be beneficial under severe uncertainty \cite{raices_cruz22}.
+Moreover, for some problems 
 we have to rely on very limited data to perform our Bayesian analysis and 
-inference may not be reliable in presence of heteroscedasticity within
-the data. Instead, we use expert opinion and elicit a set of priors 
+inference with a single prior may not be reliable.
+%%% MT to TB: I don't quite understand the heteroscedasticity argument;
+%%% I added "inference with a single prior" above instead
+% in presence of heteroscedasticity within the data.
+Instead, we use expert opinion and elicit a set of priors 
 based on empirical evidence. 

### 2024-03-21 JASA-template.tex
Update.

@@
 % in presence of heteroscedasticity within the data.
-Instead, we use expert opinion and elicit a set of priors 
+Instead, we use expert opinion to elicit a set of priors 
 based on empirical evidence. 
-This also allows us to construct the problem of confounder identification 
+This allows us to construct the problem of confounder identification 
 in a framework where abstention has a relatively positive gain i.e.~
 when the cost of further tests/data collection is cheaper than
-mistreating a subject. To propose our 
-framework, we consider a set of continuous spike and slab priors 
-\cite{ishwaran2005} for confounder identification and construct a Bayesian 
-group LASSO \cite{xu2015} type problem. To perform the prior sensitivity 
-analysis, we consider a set of beta priors on the covariate selection 
+mistreating a subject.
+
+Our framework considers a set of continuous spike and slab priors 
+\cite{ishwaran2005} for confounder identification.
+%%% MT to TB: check if you are happy with this next sentence
+We thereby construct a Bayesian group LASSO \cite{xu2015} type problem.
+To perform sensitivity analysis,
+we consider a set of beta priors on the covariate selection 
 probability of the spike and slab priors. We use the posteriors of this

### 2024-03-21 JASA-template.tex
Small updates, clarify n.

@@
 
-Let an observational study give us the outcomes $Y=(Y_1, \dots, Y_n)$ along with 
-corresponding treatment indicators $T=(T_1, \dots, T_n)$. Then the
+Let an observational study on $n$ individuals give us the outcomes $Y\coloneqq(Y_1, \dots, Y_n)$ along with 
+corresponding treatment indicators $T\coloneqq(T_1, \dots, T_n)$. Then the
 treatment 
@@
 in outcomes between the treatment and controls:
+%%% MT to TB: I don't understand this equation; since Y and T are vectors, is \delta simply \delta_1,\dots,\delta_n? I think something else is meant? or remove this equation?
 \begin{align}

### 2024-03-21 JASA-template.tex
Comment.
Comments and some edits.

@@
 \end{align}
+%%% MT to TB: are we interested in predicting the effect on an individual that is not yet observed, i.e. say $\delta_{n+1}$?
 That is, we are interested in the difference between the outcomes when the $i$-th subject receives
@@
 
-In theory, both of these quantities exist.
-However, we cannot observe $\mathbb{E}(Y_i\mid T_i=1)$ and $\mathbb{E}(Y_i\mid T_i=0)$
-the average causal effect of the treatment $T$ by calculating the averaged
+In theory, both $\mathbb{E}(Y_i\mid T_i=1)$ and $\mathbb{E}(Y_i\mid T_i=0)$ exist.
+However, we cannot observe them simultaneously, since we cannot `treat' and `not treat' the same individual at the same time.
+What we can observe is the average causal effect of the treatment,
+by calculating the averaged
 outcome of all the subjects that received the treatment and
@@
   \hat{\delta} \coloneqq 
-	\frac{\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=1) - 
-		\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=0)}{n}.
+  \frac{\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=1)-\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=0)}{n}.
 \end{align}

### 2024-03-21 JASA-template.tex
Another note.

@@
 by calculating the averaged
-outcome of all the subjects that received the treatment and
-all the subjects that remained as control:
+outcome of all the subjects that received the treatment
+minus that of all the subjects that remained as control:
 \begin{align}
   \hat{\delta} \coloneqq 
-  \frac{\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=1)-\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=0)}{n}.
+  %\frac{\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=1)-\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=0)}{n}
+  %%% MT to TB check if this is correct, it seems a bit simpler to write like this
+  \frac{\sum_{i=1}^n Y_iT_i-\sum_{i=1}^n Y_i(1-T_i)}{n}.
 \end{align}
+%%% MT to TB: is it assumed both groups have the same size, namely n/2? or not?
 However, this relies on an important assumption that the treatment effect

### 2024-03-21 JASA-template.tex
Comment for Tatha.
Small edit.
Some updates.

@@
 
+%%% MT to TB: there is a slight disjoint between this section and what
+%%% comes later: only \delta_i is ever being referred to, \hat{\delta}
+%%% is never referred to later on (also I find its definition
+%%% confusing); can we simply say that we try to estimate
+%%% $\delta_{n+1}$, the main difficulty being that $\delta_1$, \dots,
+%%% $\delta_n$ are not directly observable, instead we only observe
+%%% each $Y_i$ under either $T_i=0$ or $T_i=1$ but never both?
+
 Let an observational study on $n$ individuals give us the outcomes $Y\coloneqq(Y_1, \dots, Y_n)$ along with 
@@
 That is, we are interested in the difference between the outcomes when the $i$-th subject receives
-the treatment and when 
-%$i$-th subject 
-it remains as a control.
+the treatment and when they remain as a control.
 
@@
 the underlying true outcome model is linear with respect to the treatment,
+%%% MT to BT: should we say $\delta_{n+1}$ here (and Y_{n+1}, T_{n+1})?
 \begin{equation}
@@
 \end{equation}
-In the presence of confounders we also need to consider the
+To estimate $\beta_T$,
+especially in the presence of confounders,
+we also need to consider the
 association between the treatment indicators and the predictors.
 In literature, authors often suggest a probit link function to 
-construct the regression model. This way, we can
+construct the regression model.
+In this way, we can
 specify the conditional probability that subject $i$ receives the treatment through a linear model. 

### 2024-03-21 JASA-template.tex
Small edits.

@@
 \end{equation}
-To estimate $\beta_T$,
+To estimate $\beta_T$ from the data $X$, $Y$ and $T$,
 especially in the presence of confounders,
 we also need to consider the
-association between the treatment indicators and the predictors.
+association between the treatment indicators $T$ and the predictors $X$.
 In literature, authors often suggest a probit link function to 

### 2024-03-21 JASA-template.tex
Highlight potential issues with derivation of the treatment effect.

--- 2024-03-21 JASA-template.tex
@@
 \end{equation}
-To estimate $\beta_T$,
+*** MT to TB: trying to derive this\dots ***      
+\begin{align}
+  \delta_i
+  &=\mathbb{E}(Y_i\mid T_i =1) - \mathbb{E}(Y_i\mid T_i=0)\\
+  &=\beta_T+\mathbb{E}(X_i\beta+\epsilon_i\mid T_i =1) - \mathbb{E}(X_i\beta+\epsilon_i\mid T_i=0)\\
+  %%% MT to BT:
+  \intertext{*** I get why $\epsilon_i$ has expectation zero (assumed independent from $T_i$); but why do the $X_i\beta$ terms vanish, since $X_i$ and $T_i$ are not assumed independent?
+maybe this can only assumed to hold for $i=n+1$ i.e.
+for the `next' person, not for the person in the data\dots ***}
+  &=\beta_{T}.
+\end{align}
+To estimate $\beta_T$ from the data $X$, $Y$ and $T$,
 especially in the presence of confounders,
 we also need to consider the
-association between the treatment indicators and the predictors.
+association between the treatment indicators $T$ and the predictors $X$.
 In literature, authors often suggest a probit link function to 

### 2024-03-21 JASA-template.tex
Update.
Alternate derivation.

@@
 maybe this can only assumed to hold for $i=n+1$ i.e.
-for the `next' person, not for the person in the data\dots ***}
+for the `next' person, not for the person in the data\dots another even better solution is just to condition on $X_{n+1}$ since this is known, then the entire problem goes away ***}
   &=\beta_{T}.
 \end{align}
+*** MT to BT: derivation v2; this shows the causal effect does not depend on the value of $X_{n+1}$: ***
+\begin{align}
+  \delta(x_{n+1})
+  &=\mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) - \mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1}=0)\\
+  &=\beta_T+x_{n+1}\beta+\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) \\
+  &\quad - x_{n+1}\beta-\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =0)\\
+  %%% MT to BT:
+  \intertext{and because $\epsilon_{n+1}$ is independent from $X_{n+1}$ and $T_{n+1}$,}
+  &=\beta_{T}.
+\end{align}
+Note that, for this model, the causal effect $\delta(x_{n+1})$ does not depend on the value $x_{n+1}$ of $X_{n+1}$.
+
 To estimate $\beta_T$ from the data $X$, $Y$ and $T$,

### 2024-03-21 JASA-template.tex
Add probit proof.
Small edits.

@@
 association between the treatment indicators $T$ and the predictors $X$.
-In literature, authors often suggest a probit link function to 
-construct the regression model.
+A common choice in the literature is to use a probit link function.
 In this way, we can
@@
 where $u_i\sim\mathcal{N}(0,1)$.
+%%% MT to TB: not entirely trivial so I added a quick derivation
+With this model, indeed
+\begin{align}
+  P(T_i=1\mid X_i)
+  &=P(T_i^*>0)=P(u_i>-X_i\gamma)=1-P(u_i\le -X_i\gamma) \\
+  &=1-\Phi(-X_i\gamma)=\Phi(X_i\gamma)
+\end{align}
 
@@
 \cite{xu2015} type model. This way, we can look into the posterior selection
-probability associated with the $j$-th predictor. There are several
-ways to construct spike and slab priors which achieve 
-variable selection. In our case, we consider a continuous type
+probability of each predictor. There are several
+ways to construct spike and slab priors for
+variable selection. Here, we consider a continuous type
 \cite{ishwaran2005} prior for faster posterior

### 2024-03-21 JASA-template.tex
Notation for defs.
Some comments.

@@
 \end{align}
-where, $X_O = [T, X]$ and $X_T = X$. Then, considering the assumption of
+where, $X_O \coloneqq [T, X]$ and $X_T \coloneqq X$. Then, considering the assumption of
 Gaussian error terms, we have the following likelihood distribution
@@
 \end{align}
-where $\nu = (\beta_T, \beta^T, \gamma^T)^T$ and
+where $\nu \coloneqq (\beta_T, \beta^T, \gamma^T)^T$ and
 \begin{align}
-	\Sigma &=
+	\Sigma &\coloneqq
 	\begin{bmatrix}
@@
 Let $\pi_j$ denote the prior probability that the $j$-th
-predictor is associated to the outcome or the 
+predictor is associated with the outcome or the 
 treatment. That is, 
 \begin{equation}
-	\pi_j = P\left((\beta_j,\gamma_j)\not=(0,0)\right).
+	\pi_j \coloneqq P\left((\beta_j,\gamma_j)\not=(0,0)\right).
 \end{equation}
@@
 concentrated around zero. Therefore, this represents the spike component of our prior specification. 
-For the slab component, we consider $\tau_1$ to be large so that $\tau_1\ge 1$. This allows the prior for $(\beta_j,\gamma_j)$ to be flat, besides the spike component at the origin.. 
+For the slab component, we consider $\tau_1$ to be large so that $\tau_1\ge 1$. This allows the prior for $(\beta_j,\gamma_j)$ to be flat beyond the spike component at the origin. 
 We illustrate the components of a bivariate spike and slab prior in 
@@
 For the precision term $1/\sigma^2$, a natural choice of prior is the gamma distribution
-as it allows the control of both the location and the scale of the precision. To
-ensure that the prior is able to represent the data, we consider $b=1$ and 
-fix $a$ so that it represents the prior mean of the precision. In cases where we have no prior information,
-we can simply consider a large value for $a$ so that the interval
+as it allows the control of both the location and the scale of the precision.
+%%% MT to TB: why not simply say the prior is exponential?
+To ensure that the prior is able to represent the data, we consider $b=1$ and 
+fix $a$ so that it represents the prior mean of the precision.
+%%% MT to TB: "no prior information" seems a bit misleading here? I suggest removing
+% In cases where we have no prior information,
+We can simply consider a large enough value for $a$
+%%% MT to TB: the next phrase is confusing... do you mean to say "with probability ..." (not sure what that is for [0,2a]))
+so that the interval
 $[0, 2a]$ contains the true value of the precision.

### 2024-03-21 JASA-template.tex
Make suggestion.
Some fixes.

@@
         \frac{1}{\sigma^2}&\sim \text{Gamma}(a, b)\\
-	\pi_{j} &\sim\text{Beta}\left(sq, s(1-q)\right).
+        %%% MT to TB: text referred to q_j so I changed q -> q_j here
+	\pi_{j} &\sim\text{Beta}\left(sq_j, s(1-q_j)\right).
 \end{align}
@@
 We can simply consider a large enough value for $a$
-%%% MT to TB: the next phrase is confusing... do you mean to say "with probability ..." (not sure what that is for [0,2a]))
+%%% MT to TB: the next phrase is confusing...
+do you mean to say "with probability ..." (not sure what that is for [0,2a], but true value has probability of about 95% to be contained in [0,3a] for the exponential since 1-exp(-3) is about 95%))
 so that the interval
 $[0, 2a]$ contains the true value of the precision.
-As defined earlier, $\pi_j$ is used as the selection probability
-of the $j$-th predictor in either of the models and we use a beta prior to specify 
-these selection probabilities where  $q_j$ represents our prior expectation of the selection probability ($\pi_j$) and $s$ acts as 
+We use a beta prior to
+model our uncertainty about
+the selection probabilities $\pi_j$ where  $q_j$ represents our prior expectation of the selection probability ($\pi_j$) and $s$ acts as 
 a concentration parameter.

### 2024-03-21 JASA-template.tex
Small fix.

@@
 model our uncertainty about
-the selection probabilities $\pi_j$ where  $q_j$ represents our prior expectation of the selection probability ($\pi_j$) and $s$ acts as 
+the selection probabilities $\pi_j$ where  $q_j$ represents our prior expectation of $\pi_j$ and $s$ acts as 
 a concentration parameter.

### 2024-03-21 JASA-template.tex
Note.
Remove.
Edits.

@@
 predictor is associated with the outcome or the 
-treatment. That is, 
+treatment. That is, conceptually,
 \begin{equation}
@@
 \end{equation}
-Then we can define the following hierarchical model for spike and 
-slab group LASSO so that,
+Practically, we model this by defining the following hierarchical model
+%%% MT to TB do you mean "from" instead of "for"? for now removed as confusing
+% for spike and  slab group LASSO
+so that,
 for $1\le j\le p$,
@@
 The hierarchical model presented above is a standard spike and slab model for
-variable selection and performs well when we have sufficient data to begin with. 
-However, especially in the case of causal inference having sufficient data may not 
-be feasible. Moreover, 
-we also need to be cautious about the side effects of a treatment.
+variable selection and performs well when we have sufficient data. 
+However, especially in the case of causal inference, we do not always have sufficient data. Moreover, 
+we also must be cautious about the side effects of a treatment.
 Therefore, we are particularly interested in constructing a robust Bayesian framework
-for variable selection. This way, when we are preparing a guideline for treatment, we 
+for variable selection. In this way, when we are preparing guidelines for treatment, we 
 can have the option to ask for more data before reaching any conclusion. To achieve this,
-we consider a utility based framework with three possible ways of determining a variable.
+we consider a utility based framework with three possible ways of
+%%% MT to TB: not sure what is meant, subsequent text does not consider "determining a variable"
+determining a variable.
 
@@
 assume that we can always revert any initial mistreatment by further treatments, 
-and we can associate a loss function with the cost of further treatments. This way, 
-in the simplest case, we can associate two constant loss values $\ell_1,\ell_2$ 
+and we can associate a loss function with the cost of further treatments.
+So, we will associate two constant loss values $\ell_1$ and $\ell_2$ 
 with false positives and false negatives respectively. 

### 2024-03-21 JASA-template.tex
Try fix.
Note.
Notation fix.
Fix.

@@
 can have the option to ask for more data before reaching any conclusion. To achieve this,
-we consider a utility based framework with three possible ways of
-%%% MT to TB: not sure what is meant, subsequent text does not consider "determining a variable"
-determining a variable.
+we consider a utility based framework with three possible 
+%%% MT to TB: not sure what is meant, subsequent text does not consider "determining a variable"; replace with "scenarios"?
+% ways of determining a variable. 
+scenarios.
 
@@
 
+%%% MT to TB: text above talks about abstaining from treatment; this is quite different from abstaining from selecting a variable
 Now, based on this notion of abstaining from selecting a variable, we can perform
@@
 treatment and outcome model, if
+%%% MT to TB: should we add a subscript q to \mathbb{E} to emphasize the dependence?
 \begin{align}\label{eq:vs:remove}
@@
 
-In general, this framework is self sufficient for variable selection. However, for
+In general, this framework is
+%%% MT to TB: self-sufficient sounds a bit strange here, do you mean "sufficient"?
+self-sufficient
+for variable selection. However, for
 model fitting and prediction, we need to evaluate the values 
@@
 	S(q)\coloneqq
-	\left\{j\colon E(\pi_j\mid W) \ge 1/2\right\}.
+	\left\{j\colon \mathbb{E}(\pi_j\mid W) \ge 1/2\right\}.
 \end{equation}
@@
 the predictors that belong to $S(q)$. Similarly,
-$\hat{\gamma}_{S(q)}$ be the posterior means of the regression
+let $\hat{\gamma}_{S(q)}$ be the posterior means of the regression
 coefficients for the treatment effects. Since we use continuous 

### 2024-03-21 JASA-template.tex
Elsevier style.

@@
 
-\documentclass{amsart}
-\usepackage[foot]{amsaddr} % put addresses on first page
-\usepackage[british]{babel}
-\usepackage{geometry}
+\documentclass[preprint,12pt]{elsarticle}
 \usepackage{graphicx,psfrag,epsf}
-\usepackage{enumerate}
-\usepackage{enumitem}
 \usepackage{amsfonts}
@@
 \usepackage{amsmath}
-\allowdisplaybreaks
 \usepackage{longtable}
 \usepackage{bigints}
-%\usepackage{siunitx}
-\usepackage{amsthm}
 \usepackage{soul}
@@
 \usepackage{color}
-\usepackage{easyReview} % for \comment, \alert, etc.
-
-\newcommand{\addition}[1]{#1}
 
@@
 \usepackage[capitalise]{cleveref}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[theorem]
-\newtheorem{lemma}[theorem]{Lemma}
-%
-
-\usepackage[numbers]{natbib}
-\usepackage{url} % not crucial - just used below for the URL 
+\usepackage{url}
 \usepackage{doi}
@@
 
-\keywords{high dimensional data; variable selection; Bayesian analysis; imprecise probability}
+\usepackage{lineno}
 
@@
 
+\begin{frontmatter}
+
+%% Title, authors and addresses
 \title{Robust Bayesian Analysis of Causal Inference Problems}
-\author{Tathagata Basu$^1$}
-\email{tathagatabasumaths@gmail.com}
-\author{Matthias C.~M.~Troffaes$^2$}
-\email{matthias.troffaes@durham.ac.uk}
-\address{$^1$Civil and Environmental Engineering, University of Strathclyde}
-\address{$^2$Department of Mathematical Sciences, Durham University}
+\author[1]{Tathagata Basu\corref{cor1}}
+\ead{tathagatabasumaths@gmail.com}
+\cortext[cor1]{Corresponding author}
+\author[2]{Matthias C.~M.~Troffaes}
+\ead{matthias.troffaes@durham.ac.uk}
+\affiliation[1]{organization={Civil and Environmental Engineering, University of Strathclyde},
+            addressline={}, 
+            city={},
+            postcode={}, 
+            state={},
+            country={}}
+\affiliation[2]{organization={Department of Mathematical Sciences, Durham University},
+            addressline={South Road}, 
+            city={Durham},
+            postcode={DH13LE}, 
+            state={},
+            country={United Kingdom}}
 
 \begin{abstract}
+%%% MT to TB: will try reduce abstract length slightly        
 Causal inference using observational data is important in
@@
 
-\maketitle
+\begin{keyword}
+  high dimensional data\sep variable selection\sep Bayesian analysis\sep imprecise probability
+\end{keyword}
+
+\begin{highlights}
+\item *** TODO ***
+\item *** TODO ***
+\end{highlights}
+
+\end{frontmatter}
 
@@
 
-\bibliographystyle{agsm}
+\bibliographystyle{elsarticle-num} 
 \bibliography{basu_causal}
+
 \end{document}

### 2024-03-21 JASA-template.tex
Line numbers.

@@
 \usepackage{lineno}
+\linenumbers
 
@@
             postcode={DH13LE}, 
-            state={},
+            %state={},
             country={United Kingdom}}

### 2024-03-21 JASA-template.tex
Updates.

@@
 
-%%% MT to TB: there is a slight disjoint between this section and what
-%%% comes later: only \delta_i is ever being referred to, \hat{\delta}
-%%% is never referred to later on (also I find its definition
-%%% confusing); can we simply say that we try to estimate
-%%% $\delta_{n+1}$, the main difficulty being that $\delta_1$, \dots,
-%%% $\delta_n$ are not directly observable, instead we only observe
-%%% each $Y_i$ under either $T_i=0$ or $T_i=1$ but never both?
+\subsection{Regression Model}
 
-Let an observational study on $n$ individuals give us the outcomes $Y\coloneqq(Y_1, \dots, Y_n)$ along with 
-corresponding treatment indicators $T\coloneqq(T_1, \dots, T_n)$. Then the
-treatment 
-effect in the population is given by the expectation of the difference
-in outcomes between the treatment and controls:
-%%% MT to TB: I don't understand this equation; since Y and T are vectors, is \delta simply \delta_1,\dots,\delta_n? I think something else is meant? or remove this equation?
-\begin{align}
-	\delta = \mathbb{E}(Y\mid T =1) - \mathbb{E}(Y\mid T=0).
-\end{align}
-Similarly, the individual causal
-effect of treatment $T_i$ on outcome $Y_i$ is given by:
-\begin{align}
-	\delta_i \coloneqq \mathbb{E}(Y_i\mid T_i=1) - \mathbb{E}(Y_i\mid T_i=0).
-\end{align}
-%%% MT to TB: are we interested in predicting the effect on an individual that is not yet observed, i.e. say $\delta_{n+1}$?
-That is, we are interested in the difference between the outcomes when the $i$-th subject receives
-the treatment and when they remain as a control.
-
-In theory, both $\mathbb{E}(Y_i\mid T_i=1)$ and $\mathbb{E}(Y_i\mid T_i=0)$ exist.
-However, we cannot observe them simultaneously, since we cannot `treat' and `not treat' the same individual at the same time.
-What we can observe is the average causal effect of the treatment,
-by calculating the averaged
-outcome of all the subjects that received the treatment
-minus that of all the subjects that remained as control:
-\begin{align}
-  \hat{\delta} \coloneqq 
-  %\frac{\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=1)-\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=0)}{n}
-  %%% MT to TB check if this is correct, it seems a bit simpler to write like this
-  \frac{\sum_{i=1}^n Y_iT_i-\sum_{i=1}^n Y_i(1-T_i)}{n}.
-\end{align}
-%%% MT to TB: is it assumed both groups have the same size, namely n/2? or not?
-However, this relies on an important assumption that the treatment effect
-on the $i$-th subject given that they received the treatment is the same as the (counterfactual) treatment effect when they remain as control \cite{winship99}.
-
-\subsection{Regression Model}
+Let an observational study on $n$ individuals give us
+the outcomes $Y\coloneqq(Y_1, \dots, Y_n)$ along with 
+corresponding treatment indicators $T\coloneqq(T_1, \dots, T_n)$.
 Regression methods are widely used in causal effect estimation. The
@@
 correlation between the treatment indicator and the error term
-\cite{winship99,HECKMAN1985}. To do so, we rely on $p$ different observed quantities
+\cite{winship99,HECKMAN1985}.
+
+%%% MT to TB: not sure where this text needs to go, omitted for now...
+
+% In theory, both $\mathbb{E}(Y_i\mid T_i=1)$ and $\mathbb{E}(Y_i\mid T_i=0)$ exist.
+% However, we cannot observe them simultaneously, since we cannot `treat' and `not treat' the same individual at the same time.
+
+% We rely on the important assumption that the treatment effect
+% on the $i$-th subject given that they received the treatment is the same as the (counterfactual) treatment effect when they remain as control \cite{winship99}.
+
+To do so, we rely on $p$ different observed quantities
 or predictors denoted by $X\coloneqq$ $[X_1^T, \dots, X_n^T]^T$
@@
 \end{equation}
-where $\epsilon_i\sim \mathcal{N}(0, \sigma^2)$. Clearly, when
-the underlying true outcome model is linear with respect to the treatment,
-%%% MT to BT: should we say $\delta_{n+1}$ here (and Y_{n+1}, T_{n+1})?
-\begin{equation}
-	\delta_i = \mathbb{E}(Y_i\mid T_i =1) - \mathbb{E}(Y_i\mid T_i=0) = \beta_{T}.
-\end{equation}
-*** MT to TB: trying to derive this\dots ***      
-\begin{align}
-  \delta_i
-  &=\mathbb{E}(Y_i\mid T_i =1) - \mathbb{E}(Y_i\mid T_i=0)\\
-  &=\beta_T+\mathbb{E}(X_i\beta+\epsilon_i\mid T_i =1) - \mathbb{E}(X_i\beta+\epsilon_i\mid T_i=0)\\
-  %%% MT to BT:
-  \intertext{*** I get why $\epsilon_i$ has expectation zero (assumed independent from $T_i$); but why do the $X_i\beta$ terms vanish, since $X_i$ and $T_i$ are not assumed independent?
-maybe this can only assumed to hold for $i=n+1$ i.e.
-for the `next' person, not for the person in the data\dots another even better solution is just to condition on $X_{n+1}$ since this is known, then the entire problem goes away ***}
-  &=\beta_{T}.
-\end{align}
-*** MT to BT: derivation v2; this shows the causal effect does not depend on the value of $X_{n+1}$: ***
+where $\epsilon_i\sim \mathcal{N}(0, \sigma^2)$.
+
+%%% MT to TB: check if you're happy with this paragraph
+To decide whether or not to treat a new individual with given predictors,
+we are mainly interested in the effect of the treatment on the outcome.
+More precisely, the treatment effect of a new individual, indexed as $n+1$,
+whose outcome $Y_{n+1}$ is not yet observed, and with observed predictors $X_{n+1}=x_{n+1}$, is defined by:
 \begin{align}
   \delta(x_{n+1})
-  &=\mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) - \mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1}=0)\\
+  &\coloneqq\mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) - \mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1}=0)
+\end{align}
+For our model, due to linearity of expectation, we have that
+\begin{align}
+  \delta(x_{n+1})
   &=\beta_T+x_{n+1}\beta+\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) \\
   &\quad - x_{n+1}\beta-\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =0)\\
-  %%% MT to BT:
   \intertext{and because $\epsilon_{n+1}$ is independent from $X_{n+1}$ and $T_{n+1}$,}
@@
 \end{align}
-Note that, for this model, the causal effect $\delta(x_{n+1})$ does not depend on the value $x_{n+1}$ of $X_{n+1}$.
+Note that, for this model, the treatment effect $\delta(x_{n+1})$ does not depend on the value $x_{n+1}$ of $X_{n+1}$.
+So, to find the treatment effect, we simply need to estimate $\beta_T$.
 

### 2024-03-21 JASA-template.tex
Updates.

@@
 \end{align}
-Note that, for this model, the treatment effect $\delta(x_{n+1})$ does not depend on the value $x_{n+1}$ of $X_{n+1}$.
+Note that, for this model, the treatment effect $\delta(x_{n+1})$
+does not depend on the observed value $x_{n+1}$ of $X_{n+1}$.
 So, to find the treatment effect, we simply need to estimate $\beta_T$.
@@
 \end{align}
-where $\Phi(\cdot)$ denotes the cumulative distribution function
+where $\Phi$ denotes the cumulative distribution function
 of a standard normal distribution. To incorporate this probit
-link function, we assume that we can model the $T_i$ through the following \cite{albert93}:
+link function, we model the $T_i$ as follows \cite{albert93}:
 \begin{align}

### 2024-03-21 JASA-template.tex
Updates.

@@
 as it allows the control of both the location and the scale of the precision.
-%%% MT to TB: why not simply say the prior is exponential?
 To ensure that the prior is able to represent the data, we consider $b=1$ and 
 fix $a$ so that it represents the prior mean of the precision.
-%%% MT to TB: "no prior information" seems a bit misleading here? I suggest removing
-% In cases where we have no prior information,
-We can simply consider a large enough value for $a$
-%%% MT to TB: the next phrase is confusing...
-do you mean to say "with probability ..." (not sure what that is for [0,2a], but true value has probability of about 95% to be contained in [0,3a] for the exponential since 1-exp(-3) is about 95%))
-so that the interval
-$[0, 2a]$ contains the true value of the precision.
+%%% MT to TB: check if you are happy with this
+Alternatively, when $b=1$, we know that the interval
+$[0, 3a]$ contains the true value of the precision parameter with probability $0.95$.
+So, we can also use a prior judgement on the 95\% quantile to set $a$.
 We use a beta prior to

### 2024-03-22 JASA-template.tex
Terminology note.
Fix.
Formatting.
Formatting of lower and upper expectation in line with linear expectation.
Minor grammar things.

@@
 \newcommand{\normal}{\mathcal{N}}
-\newcommand{\lexp}{\underline{\text{E}}}
-\newcommand{\uexp}{\overline{\text{E}}}
+\newcommand{\lexp}{\underline{\mathbb{E}}}
+\newcommand{\uexp}{\overline{\mathbb{E}}}
 
@@
 \end{frontmatter}
+
+%%% MT to TB: do we say "treatment effect" or "causal effect"? later
+%%% in the text both are used; we should pick something and be
+%%% consistent to avoid confusion (if indeed they are the same...)
 
@@
 In general, this framework is
-%%% MT to TB: self-sufficient sounds a bit strange here, do you mean "sufficient"?
-self-sufficient
+%%% MT to TB: self-sufficient sounds a bit strange here, do you mean "sufficient"? [changed]
+sufficient
 for variable selection. However, for
@@
 \begin{align}
-    \mathcal{S}_*\coloneqq \left\{j:\lexp (\pi_j\mid W)\ge1/2\right\}
-    = \bigcap_{q\in \mathcal{P}}S(q),
-    \qquad \mathcal{S}^*\coloneqq \left\{j:\uexp (\pi_j\mid W)\ge1/2\right\}
+    \mathcal{S}_*&\coloneqq \left\{j:\lexp (\pi_j\mid W)\ge1/2\right\}
+    = \bigcap_{q\in \mathcal{P}}S(q), \\
+    \mathcal{S}^*&\coloneqq \left\{j:\uexp (\pi_j\mid W)\ge1/2\right\}
     = \bigcup_{q\in \mathcal{P}}S(q).
@@
 case, we generate the design matrix $X$ such that $X_i\sim\mathcal{N}(0, \Sigma)$
-for $1\le i\le n$ where $[\Sigma]_{ij} = 0.3^{|i-j|}$. This way, we 
+for $1\le i\le n$ where $\Sigma_{ij} = 0.3^{|i-j|}$. In this way, we 
 generate 50 predictors for our model with mild correlations among them.
-We then use the following generation schemes to generate the outcome and
-treatment indicator: 
+We then use the following distributions to generate the outcome and
+the treatment indicator: 
 \begin{equation}
@@
 the cases, we consider different numbers of observations $n$ where
-$n=25+ 5k$ for $k=0,1,2,\cdots,10$. %depends on finishing
-%$n=25\times 2^k$ for $k=0,1,2,\cdots,5$.
+$n=25+ 5k$ for $k=0,1,2,\dots,10$.
 

### 2024-03-22 JASA-template.tex
Small fixes.

@@
 
-We present our analyses in \cref{tab:causal} and \cref{tab:misspec}.
+We present our analyses in \cref{tab:causal,tab:misspec}.
 For the sake of clarity we use the following accronyms: RBCE for 
@@
 slab causal estimation \cite{koch2020}; BSSCE for bi-level spike and slab causal
-estimation \cite{koch2020}; and BSSL for Bayesian spike and slab lasso
+estimation \cite{koch2020}; and BSSL for Bayesian spike and slab LASSO
 \cite{xu2015}. As it can be

### 2024-03-22 JASA-template.tex
Small rephrasing.
Some updates, question about bounds for mathcal{P}.

@@
 \end{equation}
+%%% MT to BT: added this sentence for clarity later when discussing tables
+Note that the simulated causal effect $\beta_T$ is equal to $4$.
 \begin{description}
@@
 estimation \cite{koch2020}; and BSSL for Bayesian spike and slab LASSO
-\cite{xu2015}. As it can be
-seen from both the tables, SSCE and BSSCE are formulated for problems
-where $p\le n$ and therefore we do not have any results for $n<50$.
+\cite{xu2015}. Note that since SSCE and BSSCE are formulated for problems
+where $p\le n$, we do not have any results for $n<50$ for these cases.
 
-\paragraph{Elicitation} For the
-elicitation of $\mathcal{P}$, we use marginal correlation between 
-$Y$ and $X$ to determine the bounds on number of active variables. We 
-set the thresholds to be $0.15$ and $0.35$ for the correlations. We compute the
+\paragraph{Elicitation}
+For the
+elicitation of $\mathcal{P}$, we use the marginal correlation between 
+$Y$ and $X$ to determine bounds on the number of active variables.
+%%% MT to BT: I think we need to clarify what is going on here... What
+%%% were the marginal correlations? How are these values 0.15 and 0.35
+%%% informed from the marginal correlations? Also, why are marginal
+%%% correlations the best way to do this? Ideally, one would set this
+%%% without reference to the data... (since it is prior elicitation)
+We set the thresholds to be $0.15$ and $0.35$ for the correlations.
+We compute the
 number of variables with marginal correlation greater than 0.15
@@
 \paragraph{Results}
-We provide our result for causal estimate in \cref{tab:causal}. 
+\Cref{tab:causal} shows the results of estimating the causal effect $\beta_T$. 
 As we perform a sensitivity analysis,

### 2024-03-22 JASA-template.tex
Mention true value.
Small updates.

@@
 \paragraph{Results}
-\Cref{tab:causal} shows the results of estimating the causal effect $\beta_T$. 
+\Cref{tab:causal} shows the results of estimating the causal effect $\beta_T$
+For reference, recall the true value is $\beta_T=4$. 
 As we perform a sensitivity analysis,
-our method gives an interval estimate for the causal effect and we show
-that in two different rows where the first row gives the lower bound
+our method gives an interval estimate for the causal effect:
+the first row gives the lower bound
 and the second row gives the upper bound. We notice that our method is 
-somewhat in agreement with the other methods but much more consistent
+somewhat in agreement with the other methods but is more consistent
 in terms of estimating the treatment effect. However, this is not the

### 2024-03-22 JASA-template.tex
More notes.

@@
     \quad\text{and}\quad
+%%% MT to TB: did you forget to mention the error term in the next equation?
     Y_i = 4T_i + X_i\beta.
@@
 For our method, we set $\tau_0=10^{-6}$ and $\tau_1=1$ to construct the
-spike and slab prior. For the noise term, we set $a=10$ and $b=1$.  To perform 
+spike and slab prior.
+%%% MT to TB: where does a=10 come from? can we say something about that?
+For the noise term, we set $a=10$ and $b=1$.
+To perform 
 our Bayesian analysis with \texttt{rjags}, we first consider an adaptive 
@@
 
-From the figure, we can notice that our method tends
-to underestimate the causal effect. This suggests that
+In these simulations, our method tends
+to underestimate the causal effect.
+%%% MT to TB: why is the problem with a? can you explain a bit more?
+This suggests that
 we may want to have a different value of $a$ for these sets of observations
+%%% MT to TB: is the problem that it is "fixed"? this seems a bit misleading
 instead of a fixed value of $a=10$ for all of our analyses.

### 2024-03-22 JASA-template.tex
Updates.

@@
 We can also see that the lower bound tends to improve
-with increasing number of observations which validates the assumption that as we accumulate
+with increasing number of observations: as we accumulate
 more information, the interval becomes smaller and converges towards
@@
 
-For the variable identification, we use the notion of
-different losses as described earlier. We consider
-$\ell_1=\ell_2 = 1$ and $\ell_3= 0.2$. This is a
-simplified way of choosing the loss function, we can choose more 
-sophisticated loss functions based on \cite{ZAFFALON20121282}. We use this associated loss
-to obtain the total loss, which we present in \cref{tab:misspec}.
-In the table we denote the misspecification by counting the number of
+%%% MT to TB: I changed "identification" to "selection" (assuming that is meant?)
+For variable selection, we use a loss function as described earlier.
+Here, we consider
+$\ell_1=\ell_2=1$ and $\ell_3= 0.2$,
+%%% MT to TB: I've briefly recap what these losses mean; please check if correct
+i.e. we associate a loss of $1$ with false positive and false negative selections,
+and a loss of $0.2$ with indeterminate selections.
+Note that we could also choose more 
+sophisticated loss functions based on \cite{ZAFFALON20121282}.
+%%% MT to TB: I added "we sum these losses together across all preds"; check
+We sum these losses together across all predictors
+to obtain the total loss, presented in \cref{tab:misspec}.
+The table counts the number of
 false positives (FP) and false negatives (FN). For RBCE, we have an
-additional column `ID' which denotes the number of variables which remain as
-indeterminate.
+additional column (ID)
+which counts the number of indeterminate predictors.
 From the table it can be seen that for the first scenario, our method
@@
 selection. We also notice that BSSL tends to perform poorly
-in terms of variable selection for $n=25$, this can be seen
-from the treatment effect estimation as well.
+in terms of variable selection for $n=25$. This can be seen
+from the causal effect estimation as well.
 Moreover, we observe that for the second setting both SSCE

### 2024-03-22 JASA-template.tex
Comment on 'confounder'

@@
 
-Causal effect estimation is an important tool in statistical learning and needs to
-be performed with utmost care as in many cases we may have severe consequence of poor estimation.
-In this paper, we tackle this issue by proposing a robust Bayesian analysis of causal 
+Causal effect estimation is an important tool in statistical learning.
+Especially in risk-sensitive situations, such as medicine, it needs to
+be performed with utmost care as in many cases poor estimation can have severe adverse consequences.
+In this paper, we tackle this issue by proposing a robust Bayesian analysis of the causal 
 effect estimation problem for high dimensional data. Our 
-framework is focused on the effect of prior elicitation on confounder selection
+framework is focused on the effect of prior elicitation on
+%%% MT to TB: I don't understand "confounder selection" - do you mean
+%%% "predictor selection" or "variable selection"? (also see later,
+%%% "confounder selection" is repeated a few times; I'm not sure
+%%% "confounder" is the correct term here, some variables may be
+%%% confounding but some may not; if it is appropriate then earlier in
+%%% the paper we should talk a bit more to explain why these variables
+%%% are all confounders and be consistent with our terminology)
+confounder selection
 as well as causal effect estimation. We consider a spike and slab type

### 2024-03-25 JASA-template.tex
Small update (Matthias).
update analysis

@@
 \begin{abstract}
-%%% MT to TB: will try reduce abstract length slightly        
 Causal inference using observational data is important in
 many fields, including epidemiology, social science, economics, and many more.
-The goal of causal inference is to find the treatment effect on the subjects
+The goal of causal inference is to find the causal effect on the subjects
 by identifying causal links between the variables and the outcome.
 However, estimation of such causal links is extremely 
-difficult because the treatment effects may vary from subject 
+difficult because the causal effects may vary from subject 
 to subject. Unfortunately, modelling the underlying heterogeneity explicitly makes the 
@@
 both the treatment and outcome model. We are specifically interested 
-in the sensitivity of the treatment effect in the high dimensional causal inference
+in the sensitivity of the causal effect in the high dimensional causal inference
 as well as identifying confounder variables. However, indicator
@@
 
+%TB to MT: changed to causal effect now
+
 \section{Introduction}\label{sec:intro}
@@
 In such cases, we must be extra cautious as we risk
-unwanted bias in the treatment effect estimator \cite{rosenbaum83}.
+unwanted bias in the causal effect estimator \cite{rosenbaum83}.
 Several authors have tackled the presence of
@@
 we are mainly interested in the effect of the treatment on the outcome.
-More precisely, the treatment effect of a new individual, indexed as $n+1$,
+More precisely, the causal effect of a new individual, indexed as $n+1$,
 whose outcome $Y_{n+1}$ is not yet observed, and with observed predictors $X_{n+1}=x_{n+1}$, is defined by:
@@
 \end{align}
-Note that, for this model, the treatment effect $\delta(x_{n+1})$
+Note that, for this model, the causal effect $\delta(x_{n+1})$
 does not depend on the observed value $x_{n+1}$ of $X_{n+1}$.
-So, to find the treatment effect, we simply need to estimate $\beta_T$.
+So, to find the causal effect, we simply need to estimate $\beta_T$.
 
@@
 let $\hat{\gamma}_{S(q)}$ be the posterior means of the regression
-coefficients for the treatment effects. Since we use continuous 
+coefficients for the causal effects. Since we use continuous 
 spike and slab priors, these regression coefficients are not sparse.
@@
 
-For the simulation studies, we consider 2 different settings. In each
+For the simulation studies, we consider 4 different settings. In each
 case, we generate the design matrix $X$ such that $X_i\sim\mathcal{N}(0, \Sigma)$
 for $1\le i\le n$ where $\Sigma_{ij} = 0.3^{|i-j|}$. In this way, we 
-generate 50 predictors for our model with mild correlations among them.
+generate predictors for our model with mild correlations among (within?) them.
 We then use the following distributions to generate the outcome and
@@
 %%% MT to TB: did you forget to mention the error term in the next equation? 
-    Y_i = 4T_i + X_i\beta.
+%%% TB to MT: Thanks Matthias, yes I forgot to put that. 
+    Y_i = 4T_i + X_i\beta + \epsilon_i.
 \end{equation}
@@
 the cases, we consider different numbers of observations $n$ where
-$n=25+ 5k$ for $k=0,1,2,\dots,10$.
+$n=25+ 5k$ for $k=0,1,2,\dots,35$ and 50 ($p$)
+predictors. This way, we check the efficiency of our method with varying level of information.
+
+For the next two cases, we check our method for varying number of predictors (and hence sparsity level, ie the percentage of active variables present in the model)
+
+\begin{description}
+    \item[Scenario 3] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
+    \item[Scenario 4] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
+\end{description}
+For both
+the cases, we consider different numbers of predictors $p$ where
+$p=25+ 5k$ for $k=1,2,\dots,35$ and 100 ($n$)
+predictors.
 
@@
 %%% without reference to the data... (since it is prior elicitation)
+%%% TB to MT: To be honest it was just two random numbers I came up with, without any proper reason so that the this doesn't become an overfit
+
 We set the thresholds to be $0.15$ and $0.35$ for the correlations.
@@
 somewhat in agreement with the other methods but is more consistent
-in terms of estimating the treatment effect. However, this is not the
+in terms of estimating the causal effect. However, this is not the
 case for other methods and sometimes those methods produce extreme 
@@
 %%% MT to TB: is the problem that it is "fixed"? this seems a bit misleading
+%TB to MT: I was thinking of a differernt value to get a flatter prior
 instead of a fixed value of $a=10$ for all of our analyses.
@@
     \centering
-    \includegraphics[width = 0.9\linewidth]{RBCE_comp.pdf}
-    \caption{Comparison of different methods in estimating the treatment effect.}
+    \includegraphics[width = 0.9\linewidth]{treat_obs.pdf}
+    \caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
     \label{fig:comp:trt}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width = 0.9\linewidth]{treat_pred.pdf}
+    \caption{Comparison of different methods in estimating the causal effect for varying number of predictors.}
+    \label{fig:comp:trt:pred}
+\end{figure}
+
 %%% MT to TB: I changed "identification" to "selection" (assuming that is meant?)
+% TB to MT: yes, thanks
 For variable selection, we use a loss function as described earlier.
@@
 %%% MT to TB: I've briefly recap what these losses mean; please check if correct
+% TB to MT: yes, thanks
 i.e. we associate a loss of $1$ with false positive and false negative selections,
@@
 %%% MT to TB: I added "we sum these losses together across all preds"; check
+% TB to MT: yes, thanks
 We sum these losses together across all predictors
@@
   \hline
-25 &   0 &   0 &  26 & 5.2 & -- & -- & -- & -- & -- & -- &  12 &   2 & 14\\ 
-  30 &   0 &   1 &   1 & 1.2 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
-  35 &   0 &   0 &   1 & 0.2 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
-  40 &   0 &   1 &   0 & 1.0 &-- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
-  45 &   0 &   0 &   1 & 0.2 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
-  50 &   0 &   0 &   0 & 0.0 &  0 &   0  & 0 &   0 &   0  & 0 &   0 &   0  & 0\\ 
-  55 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0  & 0 &   0  & 0 &   0 &   0  & 0\\ 
-  60 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0  & 0  & 0 &   0 &   0  & 0\\ 
-  65 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0 &   0  & 0  & 0 &   0  & 0\\ 
-  70 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0 &   0  & 0  & 0 &   0  & 0\\ 
-  75 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0 &   0  & 0  & 0 &   0  & 0\\ 
+1 &   0 &   0 &  43 &  &  &  &  &   0 &   0 \\ 
+  2 &   0 &   0 &   5 &  &  &  &  &   0 &   0 \\ 
+  3 &   0 &   0 &   2 &  &  &  &  &   0 &   0 \\ 
+  4 &   0 &   0 &   0 &  &  &  &  &   0 &   0 \\ 
+  5 &   0 &   0 &   0 &  &  &  &  &   0 &   0 \\ 
+  6 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  7 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  8 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  9 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  10 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  11 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  12 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  13 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  14 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  15 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 &   0 \\ 
+  16 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 &   0 \\ 
+  17 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  18 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  19 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  20 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  21 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  22 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  23 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  24 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  25 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  26 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  27 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 &   0 \\ 
+  28 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  29 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  30 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  31 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  32 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  33 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  34 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  35 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  36 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
    \hline
 \end{tabular}
-\subcaption*{Second scenario: $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$}
+\end{table}
+\begin{table}
+\caption{Second scenario: $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$}
 \begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
@@
   \hline
-25 &   0 &   2 &  23 & 6.6 & -- & -- & -- & -- & -- & -- &   9 &   4 & 13\\ 
-  30 &   0 &   2 &   9 & 3.8 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
-  35 &   0 &   0 &  18 & 3.6 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
-  40 &   0 &   0 &   5 & 1.0 &-- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
-  45 &   0 &   0 &   3 & 0.6 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
-  50 &   0 &   0 &   1 & 0.2 &  0 &   7 & 7 &   0 &  14 & 14 &   0 &   0 & 0 \\ 
-  55 &   0 &   0 &   1 & 0.2 &  0 &   0 & 0 &  0 &  12 & 12 &  0 &   0 & 0 \\ 
-  60 &   0 &   0 &   1 & 0.2 &  1 &   0 & 1 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
-  65 &   0 &   0 &   0 & 0.0 &  0 &  12 & 12 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
-  70 &   0 &   0 &   0 & 0.0 &  0 &   0 &  0 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
-  75 &   0 &   0 &   0 & 0.0 &  0 &   0 &  0 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
+1 &   0 &   1 &  21 &  &  &  &  &   0 &   0 \\ 
+  2 &   0 &   0 &  44 &  &  &  &  &   0 &  13 \\ 
+  3 &   0 &   0 &  11 &  &  &  &  &   0 &  13 \\ 
+  4 &   0 &   0 &   4 &  &  &  &  &   0 &   0 \\ 
+  5 &   0 &   0 &   3 &  &  &  &  &   0 &   0 \\ 
+  6 &   0 &   0 &   2 &   0 &   0 &   0 &  15 &   0 &   0 \\ 
+  7 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  8 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  9 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  10 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  11 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  12 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  13 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  14 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  15 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  16 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  17 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  18 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  19 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  20 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  21 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  22 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  23 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  24 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  25 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  26 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  27 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  28 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  29 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  30 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  31 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  32 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  33 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  34 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  35 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  36 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
    \hline

### 2024-03-25 JASA-template.tex
Updates (remove resolved comments too).

@@
 \end{frontmatter}
-
-%%% MT to TB: do we say "treatment effect" or "causal effect"? later
-%%% in the text both are used; we should pick something and be
-%%% consistent to avoid confusion (if indeed they are the same...)
-
-%TB to MT: changed to causal effect now
 
@@
 for $1\le i\le n$ where $\Sigma_{ij} = 0.3^{|i-j|}$. In this way, we 
-generate predictors for our model with mild correlations among (within?) them.
+generate predictors for our model with mild correlations between them.
 We then use the following distributions to generate the outcome and
@@
     \quad\text{and}\quad
-%%% MT to TB: did you forget to mention the error term in the next equation? 
-%%% TB to MT: Thanks Matthias, yes I forgot to put that. 
     Y_i = 4T_i + X_i\beta + \epsilon_i.
 \end{equation}
-%%% MT to BT: added this sentence for clarity later when discussing tables
+%%% MT to TB: check if this is correct; I hope I got this correctly from the code
+where $\epsilon_i\sim\mathcal{N}(0,0.01)$ (i.e.\ a standard deviation of $0.1$).
+%%% MT to TB: added this sentence for clarity later when discussing tables
 Note that the simulated causal effect $\beta_T$ is equal to $4$.
+
+The first two cases that we consider are:
 \begin{description}
@@
 For both
-the cases, we consider different numbers of observations $n$ where
+cases, we consider different numbers of observations $n$ where
 $n=25+ 5k$ for $k=0,1,2,\dots,35$ and 50 ($p$)
@@
 
-For the next two cases, we check our method for varying number of predictors (and hence sparsity level, ie the percentage of active variables present in the model)
-
+For the next two cases, we check our method for varying number of predictors (and hence sparsity level, i.e.\ the percentage of active variables present in the model):
 \begin{description}
@@
 For both
-the cases, we consider different numbers of predictors $p$ where
+cases, we consider different numbers of predictors $p$ where
 $p=25+ 5k$ for $k=1,2,\dots,35$ and 100 ($n$)
@@
 
-%%% MT to TB: I changed "identification" to "selection" (assuming that is meant?)
-% TB to MT: yes, thanks
 For variable selection, we use a loss function as described earlier.
@@
 $\ell_1=\ell_2=1$ and $\ell_3= 0.2$,
-%%% MT to TB: I've briefly recap what these losses mean; please check if correct
-% TB to MT: yes, thanks
 i.e. we associate a loss of $1$ with false positive and false negative selections,
@@
 sophisticated loss functions based on \cite{ZAFFALON20121282}.
-%%% MT to TB: I added "we sum these losses together across all preds"; check
-% TB to MT: yes, thanks
 We sum these losses together across all predictors

### 2024-03-25 JASA-template.tex
Updates from Overleaf

--- 2024-03-25 JASA-template.tex
@@
 % Tue May 23 18:29:20 2023
+% latex table generated in R 4.3.2 by xtable 1.8-4 package
+% Mon Mar 25 09:52:08 2024
 \begin{table}[ht]
-\caption{Causal estimates obtained from different methods
-for 6 different
-numbers of observations.}\label{tab:causal}
 \centering
-\subcaption*{First scenario: $|\gamma_j|, |\beta_j|>0$ for $j\le 10$}
-\begin{tabular}{l|rrrrrrrrrrr}
+\small
+\begin{tabular}{r|ccccc|ccccc}
   \hline
- & 25 & 30 & 35 & 40 & 45 & 50 & 55 & 60 & 65 & 70 & 75 \\ 
+ Case&  &  & 1 &  &  &  &  & 2 &  &  \\ 
   \hline
-RBCE (low) & 3.22 & 3.54 & 3.30 & 3.66 & 3.77 & 3.80 & 3.85 & 3.89 & 3.90 & 3.91 & 3.89 \\ 
-  RBCE (up) & 4.03 & 3.96 & 3.50 & 3.77 & 3.82 & 3.83 & 3.90 & 3.93 & 3.92 & 3.92 & 3.91 \\ 
-  SSCE & -- & -- & -- & -- & -- & 4.24 & 4.11 & 3.99 & 4.00 & 4.00 & 3.99 \\ 
-  BSSCE & -- & -- & -- & -- & -- & 4.02 & 4.01 & 4.01 & 4.01 & 4.01 & 4.01 \\ 
-  BSSL & -0.23 & 4.07 & 6.80 & 4.05 & 4.00 & 4.00 & 4.01 & 3.98 & 3.99 & 3.99 & 3.99 \\ 
+ & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL \\ 
   \hline
-\end{tabular}\subcaption*{Second scenario: $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$}
-\begin{tabular}{l|rrrrrrrrrrr}
-  \hline
- & 25 & 30 & 35 & 40 & 45 & 50 & 55 & 60 & 65 & 70 & 75 \\ 
-  \hline
-RBCE (low) & 2.79 & 3.70 & 3.77 & 3.56 & 3.69 & 3.70 & 3.81 & 3.78 & 3.81 & 3.82 & 3.85 \\ 
-  RBCE (up) & 3.65 & 4.01 & 3.96 & 3.82 & 3.90 & 3.86 & 3.92 & 3.89 & 3.91 & 3.88 & 3.91 \\ 
-  SSCE & -- & -- & -- & -- & -- & 4.80 & 4.05 & 4.06 & 6.02 & 4.04 & 4.04 \\ 
-  BSSCE & -- & -- & -- & -- & -- & 10.34 & 8.12 & 4.17 & 4.04 & 4.06 & 4.05 \\ 
-  BSSL & -6.68 & 3.62 & 4.06 & 4.07 & 4.06 & 4.02 & 4.05 & 4.07 & 4.03 & 4.05 & 4.04 \\ 
+25 & 3.06 & 4.18 & -- & -- & 3.98 & 3.61 & 5.12 &  &  & 3.69 \\ 
+  30 & 3.47 & 4.31 & -- & -- & 4.01 & 3.42 & 5.40 &  &  & 9.54 \\ 
+  35 & 3.24 & 3.53 & -- & -- & 3.99 & 3.69 & 4.93 &  &  & 9.86 \\ 
+  40 & 3.61 & 3.83 & -- & -- & 3.99 & 3.77 & 4.42 &  &  & 3.95 \\ 
+  45 & 3.80 & 3.87 & -- & -- & 3.95 & 3.67 & 3.96 &  &  & 3.95 \\ 
+  50 & 3.81 & 3.87 & 3.99 & 4.01 & 3.99 & 3.77 & 3.86 & 3.72 & 4.93 & 3.94 \\ 
+  55 & 3.88 & 3.95 & 3.97 & 4.00 & 3.98 & 3.79 & 3.92 & 3.96 & 3.95 & 3.97 \\ 
+  60 & 3.97 & 3.99 & 3.99 & 4.00 & 3.98 & 3.86 & 3.90 & 3.93 & 3.91 & 3.94 \\ 
+  65 & 3.96 & 4.00 & 4.00 & 4.02 & 4.00 & 3.91 & 3.94 & 3.95 & 3.94 & 3.94 \\ 
+  70 & 3.96 & 3.99 & 4.01 & 4.05 & 4.00 & 3.84 & 3.89 & 3.94 & 3.95 & 3.95 \\ 
+  75 & 3.98 & 4.00 & 4.02 & 4.03 & 4.02 & 3.84 & 3.87 & 3.97 & 3.97 & 3.97 \\ 
+  80 & 3.98 & 4.00 & 4.02 & 4.05 & 4.01 & 3.87 & 3.89 & 3.95 & 3.96 & 3.96 \\ 
+  85 & 3.97 & 4.00 & 4.03 & 4.04 & 4.03 & 3.91 & 3.93 & 3.96 & 3.94 & 3.96 \\ 
+  90 & 3.98 & 4.00 & 4.05 & 4.07 & 4.04 & 3.91 & 3.94 & 3.95 & 3.95 & 3.95 \\ 
+  95 & 3.97 & 3.99 & 4.02 & 4.05 & 4.04 & 3.92 & 3.93 & 3.97 & 3.97 & 3.97 \\ 
+  100 & 3.96 & 3.98 & 4.03 & 4.05 & 4.04 & 3.92 & 3.94 & 3.96 & 3.96 & 3.96 \\ 
+  105 & 3.98 & 3.99 & 4.03 & 4.05 & 4.03 & 3.92 & 3.93 & 3.95 & 3.95 & 3.95 \\ 
+  110 & 3.98 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.97 \\ 
+  115 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.93 & 3.94 & 3.97 & 3.98 & 3.98 \\ 
+  120 & 3.99 & 4.00 & 4.04 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
+  125 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
+  130 & 3.99 & 3.99 & 4.02 & 4.04 & 4.02 & 3.92 & 3.94 & 3.97 & 3.97 & 3.97 \\ 
+  135 & 3.99 & 4.00 & 4.02 & 4.04 & 4.02 & 3.93 & 3.94 & 3.98 & 3.97 & 3.98 \\ 
+  140 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
+  145 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.94 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
+  150 & 3.99 & 4.00 & 4.02 & 4.02 & 4.02 & 3.93 & 3.95 & 3.98 & 3.98 & 3.98 \\ 
+  155 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.98 & 3.98 & 3.99 \\ 
+  160 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
+  165 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.98 & 3.98 \\ 
+  170 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.99 & 3.99 \\ 
+  175 & 3.99 & 4.00 & 4.03 & 4.05 & 4.04 & 3.95 & 3.95 & 4.00 & 4.00 & 4.00 \\ 
+  180 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
+  185 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
+  190 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
+  195 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
+  200 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
    \hline
@@
 \end{table}
-
 \begin{figure}

### 2024-03-25 JASA-template.tex
Small comment on intro (Matthias).
Comments on abstract/intro.

@@
 many fields, including epidemiology, social science, economics, and many more.
-The goal of causal inference is to find the causal effect on the subjects
-by identifying causal links between the variables and the outcome.
+The goal of causal inference is to find the causal effect on subjects
+by identifying causal links between
+%%% MT to TB: changed "the variables and the outcome" to "a (typically large) number of predictor variables and the outcome of a treatment"
+%%% please check if you're happy with this
+a (typically large) number of predictor variables and the outcome of a treatment.
+% the variables and the outcome.
 However, estimation of such causal links is extremely 
@@
 Causal inference concerns estimating the causal
-effect of independent variables on a dependent variable. Ideally,
+%%% MT to TB: I changed "dependent variable" to "outcome variable" (I think it's clearer for a general audience, and we talk a lot about the outcome later)
+%%% MT to TB: Why do we say "independent variables"? These need not be independent. I've changed this to "predictor variables", I hope that's ok.
+effect of predictor variables on an outcome variable,
+%%% MT to TB: I added this, please check
+as well as identifying which predictors truly affect the outcome.
+Ideally,
 randomised trials are the most efficient way to perform this task.
@@
 \small
-\begin{tabular}{r|ccccc|ccccc}
+\begin{tabular}{l|ccccc|ccccc}
   \hline
@@
 
+% latex table generated in R 4.3.2 by xtable 1.8-4 package
+% Mon Mar 25 10:08:22 2024
+\begin{table}[ht]
+\centering
+\small
+\begin{tabular}{r|ccccc|ccccc}
+  \hline
+ Case&  &  & 1 &  &  &  &  & 2 &  &  \\ 
+  \hline
+ & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL \\ 
+  \hline
+25.00 & 3.06 & 4.18 &  &  & 3.98 & 3.61 & 5.12 &  &  & 3.69 \\ 
+  30.00 & 3.47 & 4.31 &  &  & 4.01 & 3.42 & 5.40 &  &  & 9.54 \\ 
+  35.00 & 3.24 & 3.53 &  &  & 3.99 & 3.69 & 4.93 &  &  & 9.86 \\ 
+  40.00 & 3.61 & 3.83 &  &  & 3.99 & 3.77 & 4.42 &  &  & 3.95 \\ 
+  45.00 & 3.80 & 3.87 &  &  & 3.95 & 3.67 & 3.96 &  &  & 3.95 \\ 
+  50.00 & 3.81 & 3.87 & 3.99 & 4.01 & 3.99 & 3.77 & 3.86 & 3.72 & 4.93 & 3.94 \\ 
+  55.00 & 3.88 & 3.95 & 3.97 & 4.00 & 3.98 & 3.79 & 3.92 & 3.96 & 3.95 & 3.97 \\ 
+  60.00 & 3.97 & 3.99 & 3.99 & 4.00 & 3.98 & 3.86 & 3.90 & 3.93 & 3.91 & 3.94 \\ 
+  65.00 & 3.96 & 4.00 & 4.00 & 4.02 & 4.00 & 3.91 & 3.94 & 3.95 & 3.94 & 3.94 \\ 
+  70.00 & 3.96 & 3.99 & 4.01 & 4.05 & 4.00 & 3.84 & 3.89 & 3.94 & 3.95 & 3.95 \\ 
+  75.00 & 3.98 & 4.00 & 4.02 & 4.03 & 4.02 & 3.84 & 3.87 & 3.97 & 3.97 & 3.97 \\ 
+  80.00 & 3.98 & 4.00 & 4.02 & 4.05 & 4.01 & 3.87 & 3.89 & 3.95 & 3.96 & 3.96 \\ 
+  85.00 & 3.97 & 4.00 & 4.03 & 4.04 & 4.03 & 3.91 & 3.93 & 3.96 & 3.94 & 3.96 \\ 
+  90.00 & 3.98 & 4.00 & 4.05 & 4.07 & 4.04 & 3.91 & 3.94 & 3.95 & 3.95 & 3.95 \\ 
+  95.00 & 3.97 & 3.99 & 4.02 & 4.05 & 4.04 & 3.92 & 3.93 & 3.97 & 3.97 & 3.97 \\ 
+  100.00 & 3.96 & 3.98 & 4.03 & 4.05 & 4.04 & 3.92 & 3.94 & 3.96 & 3.96 & 3.96 \\ 
+  105.00 & 3.98 & 3.99 & 4.03 & 4.05 & 4.03 & 3.92 & 3.93 & 3.95 & 3.95 & 3.95 \\ 
+  110.00 & 3.98 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.97 \\ 
+  115.00 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.93 & 3.94 & 3.97 & 3.98 & 3.98 \\ 
+  120.00 & 3.99 & 4.00 & 4.04 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
+  125.00 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
+  130.00 & 3.99 & 3.99 & 4.02 & 4.04 & 4.02 & 3.92 & 3.94 & 3.97 & 3.97 & 3.97 \\ 
+  135.00 & 3.99 & 4.00 & 4.02 & 4.04 & 4.02 & 3.93 & 3.94 & 3.98 & 3.97 & 3.98 \\ 
+  140.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
+  145.00 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.94 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
+  150.00 & 3.99 & 4.00 & 4.02 & 4.02 & 4.02 & 3.93 & 3.95 & 3.98 & 3.98 & 3.98 \\ 
+  155.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.98 & 3.98 & 3.99 \\ 
+  160.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
+  165.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.98 & 3.98 \\ 
+  170.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.99 & 3.99 \\ 
+  175.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.04 & 3.95 & 3.95 & 4.00 & 4.00 & 4.00 \\ 
+  180.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
+  185.00 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
+  190.00 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
+  195.00 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
+  200.00 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
+   \hline
+\end{tabular}
+\end{table}
 \begin{figure}
@@
 \centering
-\subcaption*{First scenario: $|\gamma_j|, |\beta_j|>0$ for $j\le 10$}
+\small
 \begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
@@
   \hline
-1 &   0 &   0 &  43 &  &  &  &  &   0 &   0 \\ 
-  2 &   0 &   0 &   5 &  &  &  &  &   0 &   0 \\ 
-  3 &   0 &   0 &   2 &  &  &  &  &   0 &   0 \\ 
-  4 &   0 &   0 &   0 &  &  &  &  &   0 &   0 \\ 
-  5 &   0 &   0 &   0 &  &  &  &  &   0 &   0 \\ 
-  6 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  7 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  8 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  9 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  10 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  11 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  12 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  13 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  14 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  15 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 &   0 \\ 
-  16 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 &   0 \\ 
-  17 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  18 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  19 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  20 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  21 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  22 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  23 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  24 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  25 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  26 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  27 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 &   0 \\ 
-  28 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  29 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  30 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  31 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  32 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  33 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  34 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  35 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  36 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+25 &   0 &   0 &  43 & 8.6 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0&   0  \\ 
+  30 &   0 &   0 &   5 & 1 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0 \\ 
+  35 &   0 &   0 &   2 & .4 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0 \\ 
+  40 &   0 &   0 &   0 & 0 &  -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0 \\ 
+  45 &   0 &   0 &   0 & 0 & -- &  --  &  -- &  --  &  -- &  --  &    0 &   0 &   0 \\ 
+  50 &   0 &   0 &   0 & 0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  55 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  60 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  65 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  70 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  75 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  80 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  85 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  90 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  95 &   0 &   0 &   0 &  0 &  1 &   0 & 1 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  100 &   0 &   0 &   0 &  0 &  1 &   0 & 1 &  0 &   0 &   0 &   0 &   0 &   0 \\ 
+  105 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  110 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0&   0 &   0 &   0  &   0 \\ 
+  115 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  120 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  125 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  130 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  135 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  140 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  145 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  150 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  155 &   0 &   0 &   0 &  0 &  1 &   0 & 1 &  0 &   0 &   0 &   0 &   0 &   0 \\ 
+  160 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  165 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  170 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  175 &   0 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  180 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  185 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  190 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  195 &   0 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+  200 &   0 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
    \hline

### 2024-03-25 JASA-template.tex
Edits abstract (Matthias).

@@
 \begin{abstract}
-Causal inference using observational data is important in
-many fields, including epidemiology, social science, economics, and many more.
 The goal of causal inference is to find the causal effect on subjects
 by identifying causal links between
-%%% MT to TB: changed "the variables and the outcome" to "a (typically large) number of predictor variables and the outcome of a treatment"
+%%% MT to TB: changed "the variables and the outcome" to "a typically large number of predictor variables and the outcome of a treatment"
 %%% please check if you're happy with this
-a (typically large) number of predictor variables and the outcome of a treatment.
+a typically large number of predictor (or, explanatory) variables and the outcome of a treatment.
 % the variables and the outcome.
@@
 we often need to find a subset of 
-explanatory variables to initiate the treatment. However, current variable selection methods
+predictor variables to initiate the treatment. However, current variable selection methods
 simply tend to maximise the predictive performance of the outcome model. This can be problematic when information and data are limited,
@@
 robust Bayesian analysis, to allow for abstention when selecting
-explanatory variables.
-Our robust Bayesian model uses a set of spike and slab priors 
+predictor variables.
+%%% MT to TB: shortening
+% Our robust Bayesian model
+We
+use a set of spike and slab priors 
 through prior elicitation to obtain robust estimates for
@@
 in the sensitivity of the causal effect in the high dimensional causal inference
-as well as identifying confounder variables. However, indicator
-based confounder selection can be deceptive, especially
+%%% MT to TB: I've replaced "confounder variables" with "predictor variables that are causally linked"; check if ok (see also comments later; let us discuss on teams)
+as well as identifying predictor variables that are causally linked. However, indicator
+based variable selection can be deceptive, especially
 when the predictor is strongly associated with either the treatment or 
@@
 
+%%% MT to TB: I moved this sentence from abstract to intro (to make abstract a bit shorter)
+Causal inference using observational data is important in
+many fields, including epidemiology, social science, economics, and many more.
 Causal inference concerns estimating the causal
@@
 \small
-\begin{tabular}{l|ccccc|ccccc}
+\caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
+\begin{tabular}{c|ccccc|ccccc}
   \hline
@@
 \small
-\begin{tabular}{r|ccccc|ccccc}
+\caption{Comparison of different methods in estimating the causal effect for varying number of predictors.}
+\begin{tabular}{c|ccccc|ccccc}
   \hline
@@
   \hline
-25.00 & 3.06 & 4.18 &  &  & 3.98 & 3.61 & 5.12 &  &  & 3.69 \\ 
-  30.00 & 3.47 & 4.31 &  &  & 4.01 & 3.42 & 5.40 &  &  & 9.54 \\ 
-  35.00 & 3.24 & 3.53 &  &  & 3.99 & 3.69 & 4.93 &  &  & 9.86 \\ 
-  40.00 & 3.61 & 3.83 &  &  & 3.99 & 3.77 & 4.42 &  &  & 3.95 \\ 
-  45.00 & 3.80 & 3.87 &  &  & 3.95 & 3.67 & 3.96 &  &  & 3.95 \\ 
-  50.00 & 3.81 & 3.87 & 3.99 & 4.01 & 3.99 & 3.77 & 3.86 & 3.72 & 4.93 & 3.94 \\ 
-  55.00 & 3.88 & 3.95 & 3.97 & 4.00 & 3.98 & 3.79 & 3.92 & 3.96 & 3.95 & 3.97 \\ 
-  60.00 & 3.97 & 3.99 & 3.99 & 4.00 & 3.98 & 3.86 & 3.90 & 3.93 & 3.91 & 3.94 \\ 
-  65.00 & 3.96 & 4.00 & 4.00 & 4.02 & 4.00 & 3.91 & 3.94 & 3.95 & 3.94 & 3.94 \\ 
-  70.00 & 3.96 & 3.99 & 4.01 & 4.05 & 4.00 & 3.84 & 3.89 & 3.94 & 3.95 & 3.95 \\ 
-  75.00 & 3.98 & 4.00 & 4.02 & 4.03 & 4.02 & 3.84 & 3.87 & 3.97 & 3.97 & 3.97 \\ 
-  80.00 & 3.98 & 4.00 & 4.02 & 4.05 & 4.01 & 3.87 & 3.89 & 3.95 & 3.96 & 3.96 \\ 
-  85.00 & 3.97 & 4.00 & 4.03 & 4.04 & 4.03 & 3.91 & 3.93 & 3.96 & 3.94 & 3.96 \\ 
-  90.00 & 3.98 & 4.00 & 4.05 & 4.07 & 4.04 & 3.91 & 3.94 & 3.95 & 3.95 & 3.95 \\ 
-  95.00 & 3.97 & 3.99 & 4.02 & 4.05 & 4.04 & 3.92 & 3.93 & 3.97 & 3.97 & 3.97 \\ 
-  100.00 & 3.96 & 3.98 & 4.03 & 4.05 & 4.04 & 3.92 & 3.94 & 3.96 & 3.96 & 3.96 \\ 
-  105.00 & 3.98 & 3.99 & 4.03 & 4.05 & 4.03 & 3.92 & 3.93 & 3.95 & 3.95 & 3.95 \\ 
-  110.00 & 3.98 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.97 \\ 
-  115.00 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.93 & 3.94 & 3.97 & 3.98 & 3.98 \\ 
-  120.00 & 3.99 & 4.00 & 4.04 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
-  125.00 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
-  130.00 & 3.99 & 3.99 & 4.02 & 4.04 & 4.02 & 3.92 & 3.94 & 3.97 & 3.97 & 3.97 \\ 
-  135.00 & 3.99 & 4.00 & 4.02 & 4.04 & 4.02 & 3.93 & 3.94 & 3.98 & 3.97 & 3.98 \\ 
-  140.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
-  145.00 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.94 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
-  150.00 & 3.99 & 4.00 & 4.02 & 4.02 & 4.02 & 3.93 & 3.95 & 3.98 & 3.98 & 3.98 \\ 
-  155.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.98 & 3.98 & 3.99 \\ 
-  160.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
-  165.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.98 & 3.98 \\ 
-  170.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.99 & 3.99 \\ 
-  175.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.04 & 3.95 & 3.95 & 4.00 & 4.00 & 4.00 \\ 
-  180.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
-  185.00 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
-  190.00 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
-  195.00 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
-  200.00 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
+\hline
+30.00 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.89 & 3.91 & 3.99 & 3.99 & 3.99 \\ 
+  35.00 & 3.97 & 3.99 & 4.00 & 4.02 & 4.00 & 3.88 & 3.90 & 3.99 & 3.99 & 4.00 \\ 
+  40.00 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.88 & 3.90 & 3.99 & 4.00 & 3.99 \\ 
+  45.00 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.88 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
+  50.00 & 3.97 & 3.99 & 4.00 & 4.01 & 3.99 & 3.87 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
+  55.00 & 3.98 & 4.00 & 4.00 & 4.01 & 3.99 & 3.87 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
+  60.00 & 3.98 & 4.00 & 4.00 & 4.01 & 4.00 & 3.86 & 3.89 & 3.99 & 3.99 & 4.00 \\ 
+  65.00 & 3.98 & 4.01 & 3.99 & 4.02 & 4.00 & 3.85 & 3.89 & 3.99 & 3.99 & 3.99 \\ 
+  70.00 & 3.98 & 4.00 & 4.00 & 4.01 & 4.00 & 3.85 & 3.88 & 3.99 & 3.99 & 4.00 \\ 
+  75.00 & 3.98 & 4.00 & 4.00 & 4.00 & 4.00 & 3.84 & 3.89 & 3.99 & 4.00 & 3.99 \\ 
+  80.00 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.84 & 3.89 & 3.99 & 3.99 & 3.99 \\ 
+  85.00 & 3.99 & 4.01 & 4.00 & 4.01 & 4.00 & 3.82 & 3.88 & 4.00 & 3.99 & 3.99 \\ 
+  90.00 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.82 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
+  95.00 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.81 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
+  100.00 & 3.99 & 4.00 & 4.00 & 4.01 & 4.00 & 3.83 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
+  105.00 & 3.99 & 4.00 &  &  & 4.00 & 3.83 & 3.88 &  &  & 3.99 \\ 
+  110.00 & 3.99 & 4.00 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
+  115.00 & 3.98 & 4.01 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
+  120.00 & 3.99 & 4.00 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
+  125.00 & 3.99 & 4.01 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
+  130.00 & 3.99 & 4.01 &  &  & 4.00 & 3.82 & 3.87 &  &  & 3.99 \\ 
+  135.00 & 3.98 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
+  140.00 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.88 &  &  & 3.99 \\ 
+  145.00 & 3.99 & 4.01 &  &  & 4.00 & 3.80 & 3.88 &  &  & 3.99 \\ 
+  150.00 & 3.99 & 4.01 &  &  & 4.00 & 3.83 & 3.88 &  &  & 3.99 \\ 
+  155.00 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
+  160.00 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
+  165 & 3.98 & 4.01 &  &  & 4.00 & 3.81 & 3.88 &  &  & 3.99 \\ 
+  170 & 3.99 & 4.02 &  &  & 4.00 & 3.80 & 3.87 &  &  & 3.99 \\ 
+  175 & 3.99 & 4.01 &  &  & 4.00 & 3.79 & 3.87 &  &  & 3.99 \\ 
+  180 & 3.98 & 4.01 &  &  & 4.00 & 3.79 & 3.87 &  &  & 3.99 \\ 
+  185 & 3.99 & 4.01 &  &  & 4.00 & 3.79 & 3.88 &  &  & 3.99 \\ 
+  190 & 3.98 & 4.01 &  &  & 3.99 & 3.79 & 3.86 &  &  & 3.99 \\ 
+  195 & 3.99 & 4.01 &  &  & 4.00 & 3.80 & 3.86 &  &  & 3.99 \\ 
+  200 & 3.98 & 4.02 &  &  & 4.00 & 3.78 & 3.86 &  &  & 3.99 \\ 
    \hline
 \end{tabular}
-\end{table}
-\begin{figure}
+\end{table}\begin{figure}
     \centering
@@
 \begin{table}[ht]
-\caption{Loss based on misspecification of active variables in different
-models.}\label{tab:misspec}
+\caption{Loss based on misspecification of active variables for first scenario.}\label{tab:misspec}
 \centering
@@
 \begin{table}
-\caption{Second scenario: $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$}
+\small
+\caption{Loss based on misspecification of active variables for second scenario}
 \begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
@@
   \hline
-1 &   0 &   1 &  21 &  &  &  &  &   0 &   0 \\ 
-  2 &   0 &   0 &  44 &  &  &  &  &   0 &  13 \\ 
-  3 &   0 &   0 &  11 &  &  &  &  &   0 &  13 \\ 
-  4 &   0 &   0 &   4 &  &  &  &  &   0 &   0 \\ 
-  5 &   0 &   0 &   3 &  &  &  &  &   0 &   0 \\ 
-  6 &   0 &   0 &   2 &   0 &   0 &   0 &  15 &   0 &   0 \\ 
-  7 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  8 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  9 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  10 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  11 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  12 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  13 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  14 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  15 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  16 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  17 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  18 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  19 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  20 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  21 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  22 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  23 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  24 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  25 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  26 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  27 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  28 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  29 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  30 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  31 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  32 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  33 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  34 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  35 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  36 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
+25 &   0 &   1 &  21 & 5.2 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0\\ 
+  30 &   0 &   0 &  44 & 8.8 & -- &  --  &  -- &  --  &  -- &  --  &  0 &  13 &   13\\ 
+  35 &   0 &   0 &  11 & 2.2 & -- &  --  &  -- &  --  &  -- &  --  &  0 &  13 &   13\\ 
+  40 &   0 &   0 &   4 & .8 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0\\ 
+  45 &   0 &   0 &   3 & .6 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0\\ 
+  50 &   0 &   0 &   2 & .1 &  0 &   0 &   0 &   0 &  15 & 15 &   0 &   0 &   0\\ 
+  55 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  60 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  65 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  70 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  75 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  80 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  85 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  90 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  95 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  100 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  105 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  110 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  115 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  120 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  125 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  130 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  135 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  140 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  145 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  150 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  155 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  160 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  165 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  170 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  175 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  180 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  185 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  190 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  195 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+  200 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
    \hline

### 2024-03-25 JASA-template.tex
Small updates, use names style for elsevier citations.

@@
 by identifying causal links between
-%%% MT to TB: changed "the variables and the outcome" to "a typically large number of predictor variables and the outcome of a treatment"
+%%% MT to TB: changed "the variables and the outcome" to "a typically large number of predictor (or, explanatory) variables and the outcome of a treatment"
 %%% please check if you're happy with this
@@
 both the treatment and outcome model. We are specifically interested 
-in the sensitivity of the causal effect in the high dimensional causal inference
+in the sensitivity of the causal effect in high dimensional causal inference
 %%% MT to TB: I've replaced "confounder variables" with "predictor variables that are causally linked"; check if ok (see also comments later; let us discuss on teams)
@@
 which successfully removes negligible non-zero effects from the model,
-attaining a smaller set of confounders. Finally, we illustrate
+attaining a smaller set of 
+%%% MT to TB: using "predictors" again for consistency (and reduce confusion?)
+predictors.
+%confounders.
+Finally, we illustrate
 our method using a synthetic dataset.
@@
 In such cases, we must be extra cautious as we risk
-unwanted bias in the causal effect estimator \cite{rosenbaum83}.
+unwanted bias in the causal effect estimator \citep{rosenbaum83}.
 Several authors have tackled the presence of
 confounder variables. 
-Robins \cite{Robins1986ANA} used a graphical
+\Citet{Robins1986ANA} used a graphical
 approach to identify the causal parameters.
-Rosenbaum and Robin \cite{rosenbaum1985} suggested a link model to estimate
+\Citet{rosenbaum1985} suggested a link model to estimate
 the propensity scores for all individuals. Subsequently, several other
 methods have been proposed based on propensity score matching;
-see \cite{winship99,stuart10} for a brief review.
+see \citep{winship99,stuart10} for a brief review.
 
 One of the earlier Bayesian approaches to causal inference
-can be found in \cite{rubin1978}. More recently,
+can be found in \citep{rubin1978}. More recently,
 with the rise of high dimensional data,
 Bayesian methodologies have grown in popularity.
-Crainiceanu \text{et al.~}\cite{Crainiceanu2008} proposed a bi-level 
+\Citet{Crainiceanu2008} proposed a bi-level 
 Bayesian model averaging based method for estimating the causal 
-effect. Wang \text{et al.~}\cite{wang2015} suggested BAC (or, Bayesian adjustment for
+effect. \Citet{wang2015} suggested BAC (or, Bayesian adjustment for
 confounding),
@@
 proposed to tackle confounders from a Bayesian perspective,
-see for instance \cite{Zigler2014,Hahn2018} among others.
-
-In this paper we take inspiration from the approach of Koch \text{et al.~}\cite{koch2020}, who proposed a bi-level spike and slab prior for causal effect 
+see for instance \citep{Zigler2014,Hahn2018} among others.
+
+In this paper we take inspiration from the approach of \citet{koch2020}, who proposed a bi-level spike and slab prior for causal effect 
 estimation. They considered a data-driven adaptive approach to
@@
 sensitivity analysis, where instead of using a single prior, 
-we consider a set of priors \cite{BERGER1990303}. This is particularly 
+we consider a set of priors \citep{BERGER1990303}. This is particularly 
 interesting as in many cases, causal effect estimation can be performed 
 through a meta analysis where robust Bayesian analysis 
-can be beneficial under severe uncertainty \cite{raices_cruz22}.
+can be beneficial under severe uncertainty \citep{raices_cruz22}.
 Moreover, for some problems 
@@
 Our framework considers a set of continuous spike and slab priors 
-\cite{ishwaran2005} for confounder identification.
+\citep{ishwaran2005} for confounder identification.
 %%% MT to TB: check if you are happy with this next sentence
-We thereby construct a Bayesian group LASSO \cite{xu2015} type problem.
+We thereby construct a Bayesian group LASSO \citep{xu2015} type problem.
 To perform sensitivity analysis,
@@
 covariate selection probability for identifying the confounders. Finally, 
-we consider a post-hoc coefficient adjustment method \cite{hahn2015}
+we consider a post-hoc coefficient adjustment method \citep{hahn2015}
 to recover sparse estimates associated with either the outcome or the
@@
 correlation between the treatment indicator and the error term
-\cite{winship99,HECKMAN1985}.
+\citep{winship99,HECKMAN1985}.
 
@@
 % We rely on the important assumption that the treatment effect
-% on the $i$-th subject given that they received the treatment is the same as the (counterfactual) treatment effect when they remain as control \cite{winship99}.
+% on the $i$-th subject given that they received the treatment is the same as the (counterfactual) treatment effect when they remain as control \citep{winship99}.
 
@@
 of a standard normal distribution. To incorporate this probit
-link function, we model the $T_i$ as follows \cite{albert93}:
+link function, we model the $T_i$ as follows \citep{albert93}:
 \begin{align}
@@
 a foundation for a Bayesian group LASSO 
-\cite{xu2015} type model. This way, we can look into the posterior selection
+\citep{xu2015} type model. This way, we can look into the posterior selection
 probability of each predictor. There are several
@@
 variable selection. Here, we consider a continuous type
-\cite{ishwaran2005} prior for faster posterior
+\citep{ishwaran2005} prior for faster posterior
 computation.
@@
 the specific association with the treatment/outcome/both, we apply the 
-``decoupled shrinkage and selection'' method proposed by \cite{hahn2015}. 
-For that, we solve the following adaptive LASSO-type \cite{Zou2006}
+``decoupled shrinkage and selection'' method proposed by \citep{hahn2015}. 
+For that, we solve the following adaptive LASSO-type \citep{Zou2006}
 problems
@@
 robust Bayesian causal estimation (our method); SSCE for spike and
-slab causal estimation \cite{koch2020}; BSSCE for bi-level spike and slab causal
-estimation \cite{koch2020}; and BSSL for Bayesian spike and slab LASSO
-\cite{xu2015}. Note that since SSCE and BSSCE are formulated for problems
+slab causal estimation \citep{koch2020}; BSSCE for bi-level spike and slab causal
+estimation \citep{koch2020}; and BSSL for Bayesian spike and slab LASSO
+\citep{xu2015}. Note that since SSCE and BSSCE are formulated for problems
 where $p\le n$, we do not have any results for $n<50$ for these cases.
@@
 To implement our method, we use \texttt{rjags} and for the other three
-methods we use the code provided in the appendix of \cite{koch2020}.
+methods we use the code provided in the appendix of \citep{koch2020}.
 For our method, we set $\tau_0=10^{-6}$ and $\tau_1=1$ to construct the
@@
 \hline
-30.00 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.89 & 3.91 & 3.99 & 3.99 & 3.99 \\ 
-  35.00 & 3.97 & 3.99 & 4.00 & 4.02 & 4.00 & 3.88 & 3.90 & 3.99 & 3.99 & 4.00 \\ 
-  40.00 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.88 & 3.90 & 3.99 & 4.00 & 3.99 \\ 
-  45.00 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.88 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
-  50.00 & 3.97 & 3.99 & 4.00 & 4.01 & 3.99 & 3.87 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
-  55.00 & 3.98 & 4.00 & 4.00 & 4.01 & 3.99 & 3.87 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
-  60.00 & 3.98 & 4.00 & 4.00 & 4.01 & 4.00 & 3.86 & 3.89 & 3.99 & 3.99 & 4.00 \\ 
-  65.00 & 3.98 & 4.01 & 3.99 & 4.02 & 4.00 & 3.85 & 3.89 & 3.99 & 3.99 & 3.99 \\ 
-  70.00 & 3.98 & 4.00 & 4.00 & 4.01 & 4.00 & 3.85 & 3.88 & 3.99 & 3.99 & 4.00 \\ 
-  75.00 & 3.98 & 4.00 & 4.00 & 4.00 & 4.00 & 3.84 & 3.89 & 3.99 & 4.00 & 3.99 \\ 
-  80.00 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.84 & 3.89 & 3.99 & 3.99 & 3.99 \\ 
-  85.00 & 3.99 & 4.01 & 4.00 & 4.01 & 4.00 & 3.82 & 3.88 & 4.00 & 3.99 & 3.99 \\ 
-  90.00 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.82 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
-  95.00 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.81 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
-  100.00 & 3.99 & 4.00 & 4.00 & 4.01 & 4.00 & 3.83 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
-  105.00 & 3.99 & 4.00 &  &  & 4.00 & 3.83 & 3.88 &  &  & 3.99 \\ 
-  110.00 & 3.99 & 4.00 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
-  115.00 & 3.98 & 4.01 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
-  120.00 & 3.99 & 4.00 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
-  125.00 & 3.99 & 4.01 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
-  130.00 & 3.99 & 4.01 &  &  & 4.00 & 3.82 & 3.87 &  &  & 3.99 \\ 
-  135.00 & 3.98 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
-  140.00 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.88 &  &  & 3.99 \\ 
-  145.00 & 3.99 & 4.01 &  &  & 4.00 & 3.80 & 3.88 &  &  & 3.99 \\ 
-  150.00 & 3.99 & 4.01 &  &  & 4.00 & 3.83 & 3.88 &  &  & 3.99 \\ 
-  155.00 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
-  160.00 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
+30 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.89 & 3.91 & 3.99 & 3.99 & 3.99 \\ 
+  35 & 3.97 & 3.99 & 4.00 & 4.02 & 4.00 & 3.88 & 3.90 & 3.99 & 3.99 & 4.00 \\ 
+  40 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.88 & 3.90 & 3.99 & 4.00 & 3.99 \\ 
+  45 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.88 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
+  50 & 3.97 & 3.99 & 4.00 & 4.01 & 3.99 & 3.87 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
+  55 & 3.98 & 4.00 & 4.00 & 4.01 & 3.99 & 3.87 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
+  60 & 3.98 & 4.00 & 4.00 & 4.01 & 4.00 & 3.86 & 3.89 & 3.99 & 3.99 & 4.00 \\ 
+  65 & 3.98 & 4.01 & 3.99 & 4.02 & 4.00 & 3.85 & 3.89 & 3.99 & 3.99 & 3.99 \\ 
+  70 & 3.98 & 4.00 & 4.00 & 4.01 & 4.00 & 3.85 & 3.88 & 3.99 & 3.99 & 4.00 \\ 
+  75 & 3.98 & 4.00 & 4.00 & 4.00 & 4.00 & 3.84 & 3.89 & 3.99 & 4.00 & 3.99 \\ 
+  80 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.84 & 3.89 & 3.99 & 3.99 & 3.99 \\ 
+  85 & 3.99 & 4.01 & 4.00 & 4.01 & 4.00 & 3.82 & 3.88 & 4.00 & 3.99 & 3.99 \\ 
+  90 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.82 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
+  95 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.81 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
+  100 & 3.99 & 4.00 & 4.00 & 4.01 & 4.00 & 3.83 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
+  105 & 3.99 & 4.00 &  &  & 4.00 & 3.83 & 3.88 &  &  & 3.99 \\ 
+  110 & 3.99 & 4.00 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
+  115 & 3.98 & 4.01 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
+  120 & 3.99 & 4.00 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
+  125 & 3.99 & 4.01 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
+  130 & 3.99 & 4.01 &  &  & 4.00 & 3.82 & 3.87 &  &  & 3.99 \\ 
+  135 & 3.98 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
+  140 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.88 &  &  & 3.99 \\ 
+  145 & 3.99 & 4.01 &  &  & 4.00 & 3.80 & 3.88 &  &  & 3.99 \\ 
+  150 & 3.99 & 4.01 &  &  & 4.00 & 3.83 & 3.88 &  &  & 3.99 \\ 
+  155 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
+  160 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
   165 & 3.98 & 4.01 &  &  & 4.00 & 3.81 & 3.88 &  &  & 3.99 \\ 
@@
 Note that we could also choose more 
-sophisticated loss functions based on \cite{ZAFFALON20121282}.
+sophisticated loss functions based on \citep{ZAFFALON20121282}.
 We sum these losses together across all predictors
@@
 
-\bibliographystyle{elsarticle-num} 
+\bibliographystyle{elsarticle-num-names} 
 \bibliography{basu_causal}

### 2024-03-25 JASA-template.tex
Small changes (Matthias).

@@
 \begin{abstract}
-The goal of causal inference is to find the causal effect on subjects
+Causal inference aims to find the causal effect on subjects
 by identifying causal links between
-%%% MT to TB: changed "the variables and the outcome" to "a typically large number of predictor (or, explanatory) variables and the outcome of a treatment"
+%%% MT to TB: changed "the variables and the outcome" to "a number of predictor (or, explanatory) variables and the outcome of a treatment"
 %%% please check if you're happy with this
-a typically large number of predictor (or, explanatory) variables and the outcome of a treatment.
+a number of predictor (or, explanatory) variables and the outcome of a treatment.
 % the variables and the outcome.
@@
 %%% MT to TB: I added this, please check
-as well as identifying which predictors truly affect the outcome.
+as well as identifying which predictors are causally linked with the outcome.
 Ideally,
@@
 where data is collected though surveys or record keeping. But this
-can be problematic in the presence of confounders, which are variables associated with both the treatment and the outcome.
+can be problematic in the presence of confounders,
+%%% MT to TB: the definition on the next line sounds wrong (at least in the usual sense of "confounder"); a confounder in causal inference is a variable which causes both a predictor and the outcome, giving the false impression that this predictor causes the outcome
+which are variables associated with both the treatment and the outcome.
 In such cases, we must be extra cautious as we risk

### 2024-03-25 JASA-template.tex
Add figure and more details on confounding (Matthias).

@@
 \usepackage{tikz}
+\usetikzlibrary{arrows.meta}
+\tikzset{>={Stealth[length=3mm]}} % better arrow heads
 \usepackage{color}
@@
 \affiliation[1]{organization={Civil and Environmental Engineering, University of Strathclyde},
-            addressline={}, 
-            city={},
-            postcode={}, 
+            addressline={16 Richmond St }, 
+            city={Glasgow},
+            postcode={G1 1XQ}, 
             state={},
-            country={}}
+            country={United Kingdom}}
 \affiliation[2]{organization={Department of Mathematical Sciences, Durham University},
@@
 leaves us with observational studies
-where data is collected though surveys or record keeping. But this
-can be problematic in the presence of confounders,
-%%% MT to TB: the definition on the next line sounds wrong (at least in the usual sense of "confounder"); a confounder in causal inference is a variable which causes both a predictor and the outcome, giving the false impression that this predictor causes the outcome
-which are variables associated with both the treatment and the outcome.
+where data is collected though surveys or record keeping.
+
+But this
+can be problematic in the presence of confounding.
+%%% MT to TB: the definition on the next line sounds wrong (at least in the usual sense of "confounder"); I've added a definition and clarification as well as a figure; please check
+% Confounders are variables associated with both the treatment and the outcome.
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}[node distance=2cm, auto]
+  \node (confounder) at (0,0) [circle,draw,align=center] {biomarker \\(confounder)};
+  \node (predictor) at (4,2) [circle,draw,align=center] {treatment \\ decision \\ (predictor)};
+  \node (outcome) at (4,-2) [circle,draw,align=center] {treatment \\ outcome};
+  \draw[->] (confounder) to (predictor);
+  \draw[->] (confounder) to (outcome);
+  \draw[->,dashed] (predictor) to (outcome);
+\end{tikzpicture}
+\end{center}
+\caption{A biomarker influencing both the treatment decision and the treatment outcome, thereby acting as confounder.
+Solid arrows indicate causation, whilst the dashed arrow indicates correlation without causation.}
+\label{fig:confounding}
+\end{figure}
+A confounder is any variable which is causally linked with both a predictor and the outcome, giving the false impression that that predictor causes the outcome (see \cref{fig:confounding}).
+Confounding happens commonly in observational treatment studies because many predictors are often causally linked with the treatment decision (which is also a predictor), whilst simultaneously affecting the outcome of the treatment.
+Any such predictors act as a confounders between treatment decision (as one of the predictor variables) and treatment outcome.
 In such cases, we must be extra cautious as we risk
-unwanted bias in the causal effect estimator \citep{rosenbaum83}.
+unwanted bias in the causal effect estimator \citep{rosenbaum83},
+%%% MT to TB: I added next line for clarity
+if we ignore such correlations.
 Several authors have tackled the presence of
@@
 %%% MT to TB: check if this is correct; I hope I got this correctly from the code
-where $\epsilon_i\sim\mathcal{N}(0,0.01)$ (i.e.\ a standard deviation of $0.1$).
+where $\epsilon_i\sim\mathcal{N}(0,0.1^2)$.
 %%% MT to TB: added this sentence for clarity later when discussing tables
@@
 
-We present our analyses in \cref{tab:causal,tab:misspec}.
+We present our analyses in \cref{tab:causal1,tab:misspec1,tab:misspec2}.
 For the sake of clarity we use the following accronyms: RBCE for 
@@
 \paragraph{Results}
-\Cref{tab:causal} shows the results of estimating the causal effect $\beta_T$
+\Cref{tab:causal1} shows the results of estimating the causal effect $\beta_T$
+for the first and second scenarios.
 For reference, recall the true value is $\beta_T=4$. 
@@
 our method gives an interval estimate for the causal effect:
-the first row gives the lower bound
-and the second row gives the upper bound. We notice that our method is 
+the first(sixth) column gives the lower bound
+and the second(seventh) column gives the upper bound. We notice that our method is 
 somewhat in agreement with the other methods but is more consistent
-in terms of estimating the causal effect. However, this is not the
-case for other methods and sometimes those methods produce extreme 
-values. This can be observed in \cref{fig:comp:trt} as well. Here, the true 
-value is represented by the straight line for $\beta_T = 4$.
+in terms of estimating the causal effect in the first setting. However, this is not the
+case for the analysis with second dataset. We notice that our method tends to under
+estimate the causal effect. However, sometimes, other methods produce extreme 
+values which is not the case for our method. This can be observed in \cref{fig:comp:trt} as well. Here, the true 
+value is represented by the black straight line for $\beta_T = 4$.
 
@@
 %%% MT to TB: is the problem that it is "fixed"? this seems a bit misleading
-%TB to MT: I was thinking of a differernt value to get a flatter prior
+%TB to MT: I was thinking of a differernt value to get a flatter prior but that felt like manipulation so kept it fixed for each sample size or predicrtor size
 instead of a fixed value of $a=10$ for all of our analyses.
@@
 \end{tabular}
+\label{tab:causal1}
 \end{table}
@@
 
-% latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Mon Mar 25 10:08:22 2024
-\begin{table}[ht]
-\centering
-\small
-\caption{Comparison of different methods in estimating the causal effect for varying number of predictors.}
-\begin{tabular}{c|ccccc|ccccc}
-  \hline
- Case&  &  & 1 &  &  &  &  & 2 &  &  \\ 
-  \hline
- & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL \\ 
-  \hline
-\hline
-30 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.89 & 3.91 & 3.99 & 3.99 & 3.99 \\ 
-  35 & 3.97 & 3.99 & 4.00 & 4.02 & 4.00 & 3.88 & 3.90 & 3.99 & 3.99 & 4.00 \\ 
-  40 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.88 & 3.90 & 3.99 & 4.00 & 3.99 \\ 
-  45 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.88 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
-  50 & 3.97 & 3.99 & 4.00 & 4.01 & 3.99 & 3.87 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
-  55 & 3.98 & 4.00 & 4.00 & 4.01 & 3.99 & 3.87 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
-  60 & 3.98 & 4.00 & 4.00 & 4.01 & 4.00 & 3.86 & 3.89 & 3.99 & 3.99 & 4.00 \\ 
-  65 & 3.98 & 4.01 & 3.99 & 4.02 & 4.00 & 3.85 & 3.89 & 3.99 & 3.99 & 3.99 \\ 
-  70 & 3.98 & 4.00 & 4.00 & 4.01 & 4.00 & 3.85 & 3.88 & 3.99 & 3.99 & 4.00 \\ 
-  75 & 3.98 & 4.00 & 4.00 & 4.00 & 4.00 & 3.84 & 3.89 & 3.99 & 4.00 & 3.99 \\ 
-  80 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.84 & 3.89 & 3.99 & 3.99 & 3.99 \\ 
-  85 & 3.99 & 4.01 & 4.00 & 4.01 & 4.00 & 3.82 & 3.88 & 4.00 & 3.99 & 3.99 \\ 
-  90 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.82 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
-  95 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.81 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
-  100 & 3.99 & 4.00 & 4.00 & 4.01 & 4.00 & 3.83 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
-  105 & 3.99 & 4.00 &  &  & 4.00 & 3.83 & 3.88 &  &  & 3.99 \\ 
-  110 & 3.99 & 4.00 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
-  115 & 3.98 & 4.01 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
-  120 & 3.99 & 4.00 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
-  125 & 3.99 & 4.01 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
-  130 & 3.99 & 4.01 &  &  & 4.00 & 3.82 & 3.87 &  &  & 3.99 \\ 
-  135 & 3.98 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
-  140 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.88 &  &  & 3.99 \\ 
-  145 & 3.99 & 4.01 &  &  & 4.00 & 3.80 & 3.88 &  &  & 3.99 \\ 
-  150 & 3.99 & 4.01 &  &  & 4.00 & 3.83 & 3.88 &  &  & 3.99 \\ 
-  155 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
-  160 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
-  165 & 3.98 & 4.01 &  &  & 4.00 & 3.81 & 3.88 &  &  & 3.99 \\ 
-  170 & 3.99 & 4.02 &  &  & 4.00 & 3.80 & 3.87 &  &  & 3.99 \\ 
-  175 & 3.99 & 4.01 &  &  & 4.00 & 3.79 & 3.87 &  &  & 3.99 \\ 
-  180 & 3.98 & 4.01 &  &  & 4.00 & 3.79 & 3.87 &  &  & 3.99 \\ 
-  185 & 3.99 & 4.01 &  &  & 4.00 & 3.79 & 3.88 &  &  & 3.99 \\ 
-  190 & 3.98 & 4.01 &  &  & 3.99 & 3.79 & 3.86 &  &  & 3.99 \\ 
-  195 & 3.99 & 4.01 &  &  & 4.00 & 3.80 & 3.86 &  &  & 3.99 \\ 
-  200 & 3.98 & 4.02 &  &  & 4.00 & 3.78 & 3.86 &  &  & 3.99 \\ 
-   \hline
-\end{tabular}
-\end{table}\begin{figure}
-    \centering
-    \includegraphics[width = 0.9\linewidth]{treat_pred.pdf}
-    \caption{Comparison of different methods in estimating the causal effect for varying number of predictors.}
-    \label{fig:comp:trt:pred}
-\end{figure}
-
+We also provide tables for the performance of variable selection in \cref{tab:misspec1,tab:misspec2}.
 For variable selection, we use a loss function as described earlier.
@@
 We sum these losses together across all predictors
-to obtain the total loss, presented in \cref{tab:misspec}.
+to obtain the total loss, presented in \cref{tab:misspec1,tab:misspec2}.
 The table counts the number of
@@
 abstains from identifying some variables for 
-$n <50$. Especially for $n=25$, our method identifies 26 and 23 variables as indeterminate
+$n \le 50$. Especially for $n=25$, our method identifies 43 and 21 variables as indeterminate
 for the first setting and second setting respectively. However,
@@
 selection. We also notice that BSSL tends to perform poorly
-in terms of variable selection for $n=25$. This can be seen
-from the causal effect estimation as well.
-Moreover, we observe that for the second setting both SSCE
-and BSSCE underperform in identifying the active variables, which can 
-be explained from \cref{tab:causal} as well.
-
+in terms of variable selection in the second case giving away 13 FPs in both the cases. This can be seen in the bottom figure of \cref{fig:comp:trt}
+as well.
 % latex table generated in R 4.3.0 by xtable 1.8-4 package
@@
 \begin{table}[ht]
-\caption{Loss based on misspecification of active variables for first scenario.}\label{tab:misspec}
+\caption{Loss based on misspecification of active variables for first scenario.}\label{tab:misspec1}
 \centering
@@
 \caption{Loss based on misspecification of active variables for second scenario}
+\label{tab:misspec2}
 \begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
@@
 
+We show the result of our analyses with different number of predictors and
+fixed number of sample in \cref{fig:comp:trt:pred,tab:causal2}. Similar to
+the first two settings, we notice that our method is in good agreement with
+BSSL for the third setting. However, for the fourth setting, our method
+underestimate the treatment effect significantly (5\% in the worst case). This
+is somewhat in sync with the second setting and a possible reason behind this
+could be the fact that in both the cases, the number of active $\beta_j$ is
+higher than $\gamma_j$
+% latex table generated in R 4.3.2 by xtable 1.8-4 package
+% Mon Mar 25 10:08:22 2024
+\begin{table}[ht]
+\centering
+\small
+\caption{Comparison of different methods in estimating the causal effect for varying number of predictors.}
+\begin{tabular}{c|ccccc|ccccc}
+  \hline
+ Case&  &  & 1 &  &  &  &  & 2 &  &  \\ 
+  \hline
+ & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL \\ 
+  \hline
+\hline
+30 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.89 & 3.91 & 3.99 & 3.99 & 3.99 \\ 
+  35 & 3.97 & 3.99 & 4.00 & 4.02 & 4.00 & 3.88 & 3.90 & 3.99 & 3.99 & 4.00 \\ 
+  40 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.88 & 3.90 & 3.99 & 4.00 & 3.99 \\ 
+  45 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.88 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
+  50 & 3.97 & 3.99 & 4.00 & 4.01 & 3.99 & 3.87 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
+  55 & 3.98 & 4.00 & 4.00 & 4.01 & 3.99 & 3.87 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
+  60 & 3.98 & 4.00 & 4.00 & 4.01 & 4.00 & 3.86 & 3.89 & 3.99 & 3.99 & 4.00 \\ 
+  65 & 3.98 & 4.01 & 3.99 & 4.02 & 4.00 & 3.85 & 3.89 & 3.99 & 3.99 & 3.99 \\ 
+  70 & 3.98 & 4.00 & 4.00 & 4.01 & 4.00 & 3.85 & 3.88 & 3.99 & 3.99 & 4.00 \\ 
+  75 & 3.98 & 4.00 & 4.00 & 4.00 & 4.00 & 3.84 & 3.89 & 3.99 & 4.00 & 3.99 \\ 
+  80 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.84 & 3.89 & 3.99 & 3.99 & 3.99 \\ 
+  85 & 3.99 & 4.01 & 4.00 & 4.01 & 4.00 & 3.82 & 3.88 & 4.00 & 3.99 & 3.99 \\ 
+  90 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.82 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
+  95 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.81 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
+  100 & 3.99 & 4.00 & 4.00 & 4.01 & 4.00 & 3.83 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
+  105 & 3.99 & 4.00 &  &  & 4.00 & 3.83 & 3.88 &  &  & 3.99 \\ 
+  110 & 3.99 & 4.00 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
+  115 & 3.98 & 4.01 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
+  120 & 3.99 & 4.00 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
+  125 & 3.99 & 4.01 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
+  130 & 3.99 & 4.01 &  &  & 4.00 & 3.82 & 3.87 &  &  & 3.99 \\ 
+  135 & 3.98 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
+  140 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.88 &  &  & 3.99 \\ 
+  145 & 3.99 & 4.01 &  &  & 4.00 & 3.80 & 3.88 &  &  & 3.99 \\ 
+  150 & 3.99 & 4.01 &  &  & 4.00 & 3.83 & 3.88 &  &  & 3.99 \\ 
+  155 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
+  160 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
+  165 & 3.98 & 4.01 &  &  & 4.00 & 3.81 & 3.88 &  &  & 3.99 \\ 
+  170 & 3.99 & 4.02 &  &  & 4.00 & 3.80 & 3.87 &  &  & 3.99 \\ 
+  175 & 3.99 & 4.01 &  &  & 4.00 & 3.79 & 3.87 &  &  & 3.99 \\ 
+  180 & 3.98 & 4.01 &  &  & 4.00 & 3.79 & 3.87 &  &  & 3.99 \\ 
+  185 & 3.99 & 4.01 &  &  & 4.00 & 3.79 & 3.88 &  &  & 3.99 \\ 
+  190 & 3.98 & 4.01 &  &  & 3.99 & 3.79 & 3.86 &  &  & 3.99 \\ 
+  195 & 3.99 & 4.01 &  &  & 4.00 & 3.80 & 3.86 &  &  & 3.99 \\ 
+  200 & 3.98 & 4.02 &  &  & 4.00 & 3.78 & 3.86 &  &  & 3.99 \\ 
+   \hline
+\end{tabular}
+\label{tab:causal2}
+\end{table}
+
+\begin{figure}
+    \centering
+    \includegraphics[width = 0.9\linewidth]{treat_pred.pdf}
+    \caption{Comparison of different methods in estimating the causal effect for varying number of predictors.}
+    \label{fig:comp:trt:pred}
+\end{figure}
+
 \section{Conclusion}\label{sec:conc}

### 2024-03-25 JASA-template.tex
Small changes (Matthias).

@@
 % Confounders are variables associated with both the treatment and the outcome.
+%%% MT to TB: added text starts here
 \begin{figure}
@@
 Any such predictors act as a confounders between treatment decision (as one of the predictor variables) and treatment outcome.
+%%% MT to TB: added text ends here
 In such cases, we must be extra cautious as we risk
@@
 Moreover, for some problems 
-we have to rely on very limited data to perform our Bayesian analysis and 
-inference with a single prior may not be reliable.
+we have to rely on very limited data to perform our Bayesian analysis.
+In this case,
+inference with a single prior
+%%% MT to TB: I strenghtened this
+% may not be reliable.
+is unreliable.
 %%% MT to TB: I don't quite understand the heteroscedasticity argument;
@@
 based on empirical evidence. 
-This allows us to construct the problem of confounder identification 
+This allows us to construct the problem of 
+%%% MT to TB: changed "confounder identification" to "predictor selection"
+% confounder identification 
+predictor selection
 in a framework where abstention has a relatively positive gain i.e.~
@@
 Our framework considers a set of continuous spike and slab priors 
-\citep{ishwaran2005} for confounder identification.
+\citep{ishwaran2005} for
+%%% MT to TB: changed "confounder identification" to "predictor selection"
+% confounder identification.
+predictor selection.
 %%% MT to TB: check if you are happy with this next sentence
@@
 Let an observational study on $n$ individuals give us
-the outcomes $Y\coloneqq(Y_1, \dots, Y_n)$ along with 
-corresponding treatment indicators $T\coloneqq(T_1, \dots, T_n)$.
+\emph{treatment outcomes} $Y\coloneqq(Y_1, \dots, Y_n)$ with 
+corresponding \emph{treatment decisions} $T\coloneqq(T_1, \dots, T_n)$.
+%%% MT to TB: added this for clarity
+Here, we use an indicator to represent the treatment decision. That is, $T_i$ is $1$ if the $i$th patient was treated, and $0$ otherwise. Similarly,
+$Y_i$ is the treatment outcome of the $i$th patient, represented as some real-valued quantity.
+
 Regression methods are widely used in causal effect estimation. The
@@
 \citep{winship99,HECKMAN1985}.
-
-%%% MT to TB: not sure where this text needs to go, omitted for now...
-
-% In theory, both $\mathbb{E}(Y_i\mid T_i=1)$ and $\mathbb{E}(Y_i\mid T_i=0)$ exist.
-% However, we cannot observe them simultaneously, since we cannot `treat' and `not treat' the same individual at the same time.
-
-% We rely on the important assumption that the treatment effect
-% on the $i$-th subject given that they received the treatment is the same as the (counterfactual) treatment effect when they remain as control \citep{winship99}.
-
-To do so, we rely on $p$ different observed quantities
-or predictors denoted by $X\coloneqq$ $[X_1^T, \dots, X_n^T]^T$
+To do so, we rely on $p$ observed quantities, called
+\emph{predictors}, denoted by $X\coloneqq$ $[X_1^T, \dots, X_n^T]^T$
 where each $X_i\in\mathbb{R}^p$.
@@
 coefficients
-related to the predictors, and $\beta_T$ denote a regression coefficient related to the treatment.
+related to the predictors, and let $\beta_T$ denote a regression coefficient related to the
+%%% MT to TB: treatment -> treatment decision
+treatment decision.
 Then we can define a linear model for the outcome
@@
 \end{equation}
-where $\epsilon_i\sim \mathcal{N}(0, \sigma^2)$.
+where $\epsilon_i\sim \mathcal{N}(0, \sigma^2)$,
+%%% MT to TB: added independence statement as used later
+independent of $T_i$ and $X_i$.
+%%% MT to TB: added for clarity
+Note that both $T_i$ and $X_i$ are predictors for $Y_i$ in the above model.
+However, when we talk about predictors in this paper, we usually mean just the components of $X_i$.
 
@@
 That is, for another vector of regression coefficients 
-$\gamma\coloneqq(\gamma_1, \cdots, \gamma_p)^T$ we define
+$\gamma\coloneqq(\gamma_1, \cdots, \gamma_p)^T$ we
+%%% MT to TB: define -> assume
+assume
 \begin{align}
@@
 a foundation for a Bayesian group LASSO 
-\citep{xu2015} type model. This way, we can look into the posterior selection
+\citep{xu2015} type model. In this way, we can look into the posterior selection
 probability of each predictor. There are several
@@
 variable selection. Here, we consider a continuous type
-\citep{ishwaran2005} prior for faster posterior
+prior \citep{ishwaran2005} for faster posterior
 computation.
@@
 	\end{center}
-	\caption{Spike (left) and slab (right) components of a bi-variate distribution for $\tau_0 = 0.001$, $\tau_1$ = 5 and $\sigma=1$.}
+	\caption{Spike (left) and slab (right) components of a bivariate distribution for $\tau_0 = 0.001$, $\tau_1$ = 5 and $\sigma=1$.}
 	\label{fig:ssbl}
@@
 Alternatively, when $b=1$, we know that the interval
-$[0, 3a]$ contains the true value of the precision parameter with probability $0.95$.
+$[0, 3a]$ contains the true value of the precision parameter with probability close to $0.95$.
 So, we can also use a prior judgement on the 95\% quantile to set $a$.
@@
 the specific association with the treatment/outcome/both, we apply the 
-``decoupled shrinkage and selection'' method proposed by \citep{hahn2015}. 
+``decoupled shrinkage and selection'' (DSS) method proposed by \citep{hahn2015}. 
 For that, we solve the following adaptive LASSO-type \citep{Zou2006}
@@
 \centering
-\small
+\tiny
 \caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
@@
 is somewhat in sync with the second setting and a possible reason behind this
-could be the fact that in both the cases, the number of active $\beta_j$ is
-higher than $\gamma_j$
+could be the fact that in both the cases, the number of active $\beta_j$'s is
+higher than $\gamma_j$'s. This therefore, tends to reduce the value of treatment
+effect. A possible way to work around this issue can be using the `DSS' estimates
+of the regression coefficient and adjust the value of $\beta_T$.
+
+Besides this interesting result. We notice that all of the four methods performs
+perfectly in variable selection giving no misspecified variables. Therefore,
+we ommitt the table of variable selection for third and fourth scenarios.
+
 % latex table generated in R 4.3.2 by xtable 1.8-4 package
@@
 \centering
-\small
+\tiny
 \caption{Comparison of different methods in estimating the causal effect for varying number of predictors.}

### 2024-03-25 JASA-template.tex
Updates (Matthias).

@@
 
-%% Title, authors and addresses
+%%% MT to TB: what about "Robust Bayesian Analysis of Causal Inference in Medical Diagnosis and Treatment"
 \title{Robust Bayesian Analysis of Causal Inference Problems}
@@
 \affiliation[1]{organization={Civil and Environmental Engineering, University of Strathclyde},
-            addressline={16 Richmond St }, 
+            addressline={16 Richmond St}, 
             city={Glasgow},
             postcode={G1 1XQ}, 
-            state={},
+            %state={},
             country={United Kingdom}}
@@
 probability of the spike and slab priors. We use the posteriors of this
-covariate selection probability for identifying the confounders. Finally, 
+covariate selection probability for identifying the active predictors. Finally, 
 we consider a post-hoc coefficient adjustment method \citep{hahn2015}
@@
 motivation of a robust Bayesian analysis along with our proposed decision 
-theoretic framework for confounder (variable) selection. In \cref{sec:sim}, 
+theoretic framework for predictor selection. In \cref{sec:sim}, 
 we provide results of simulation studies under different scenarios 
@@
 cases, we consider different numbers of observations $n$ where
-$n=25+ 5k$ for $k=0,1,2,\dots,35$ and 50 ($p$)
+$n=25+ 5k$ for $k=0,1,2,\dots,35$ and $p=50$
 predictors. This way, we check the efficiency of our method with varying level of information.
@@
 cases, we consider different numbers of predictors $p$ where
-$p=25+ 5k$ for $k=1,2,\dots,35$ and 100 ($n$)
-predictors.
+$p=25+ 5k$ for $k=1,2,\dots,35$ and $n=100$
+subjects.
 
@@
 \paragraph{Elicitation}
-For the
-elicitation of $\mathcal{P}$, we use the marginal correlation between 
-$Y$ and $X$ to determine bounds on the number of active variables.
-%%% MT to BT: I think we need to clarify what is going on here... What
-%%% were the marginal correlations? How are these values 0.15 and 0.35
-%%% informed from the marginal correlations? Also, why are marginal
-%%% correlations the best way to do this? Ideally, one would set this
-%%% without reference to the data... (since it is prior elicitation)
-%%% TB to MT: To be honest it was just two random numbers I came up with, without any proper reason so that the this doesn't become an overfit
-
-We set the thresholds to be $0.15$ and $0.35$ for the correlations.
-We compute the
-number of variables with marginal correlation greater than 0.15
-(say $p_1$) and number of variables with  marginal 
-correlation greater than 0.35 (say $p_2$). 
-We use these numbers to obtain the bounds on the number of active
-variables so that $\mathcal{P}=[p_2/p , p_1/p]$.
+%%% MT to TB: I've edited this paragraph, see if you're happy with this
+One way to elicit $\mathcal{P}$
+is through a prior expected bound on the number of active predictors.
+Although we may do so directly,
+we may alternatively also use the empirically observed correlations from the data directly.
+This may give us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
+When doing so, we need a prior judgement instead on what is a reasonable correlation between active predictors and the outcome.
+
+So, say we judge, through expert elicitation, that
+an active predictor has a correlation with the outcome
+that is typically between $0.15$ and $0.35$.
+Let $p_1$ be the number of predictors with marginal correlation greater than $0.15$
+and let $p_2$ be number of predictors with marginal 
+correlation greater than $0.35$.
+Then $\mathcal{P}=[p_2/p , p_1/p]$ (note that $p_2\le p_1$) gives us a prior bound on the selection probability of each predictor, reflecting our prior expert judgement.
 
@@
   \hline
- & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL \\ 
+ & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL \\ 
   \hline
@@
 perfectly in variable selection giving no misspecified variables. Therefore,
-we ommitt the table of variable selection for third and fourth scenarios.
+we omit the table of variable selection for third and fourth scenarios.
 

### 2024-03-27 JASA-template.tex
updated text and loss fn

@@
 predictor variables.
-%%% MT to TB: shortening
-% Our robust Bayesian model
 We
@@
 in the sensitivity of the causal effect in high dimensional causal inference
-%%% MT to TB: I've replaced "confounder variables" with "predictor variables that are causally linked"; check if ok (see also comments later; let us discuss on teams)
 as well as identifying predictor variables that are causally linked. However, indicator
@@
 attaining a smaller set of 
-%%% MT to TB: using "predictors" again for consistency (and reduce confusion?)
 predictors.
-%confounders.
 Finally, we illustrate
@@
 
-%%% MT to TB: I moved this sentence from abstract to intro (to make abstract a bit shorter)
 Causal inference using observational data is important in
@@
 Causal inference concerns estimating the causal
-%%% MT to TB: I changed "dependent variable" to "outcome variable" (I think it's clearer for a general audience, and we talk a lot about the outcome later)
-%%% MT to TB: Why do we say "independent variables"? These need not be independent. I've changed this to "predictor variables", I hope that's ok.
 effect of predictor variables on an outcome variable,
-%%% MT to TB: I added this, please check
 as well as identifying which predictors are causally linked with the outcome.
@@
 can be problematic in the presence of confounding.
-%%% MT to TB: the definition on the next line sounds wrong (at least in the usual sense of "confounder"); I've added a definition and clarification as well as a figure; please check
-% Confounders are variables associated with both the treatment and the outcome.
-%%% MT to TB: added text starts here
 \begin{figure}
@@
 Any such predictors act as a confounders between treatment decision (as one of the predictor variables) and treatment outcome.
-%%% MT to TB: added text ends here
 In such cases, we must be extra cautious as we risk
 unwanted bias in the causal effect estimator \citep{rosenbaum83},
-%%% MT to TB: I added next line for clarity
 if we ignore such correlations.
@@
 confounding),
-%%% MT to TB: check next phrase
 where an informative prior obtained from
@@
 sensitivity analysis, where instead of using a single prior, 
-we consider a set of priors \citep{BERGER1990303}. This is particularly 
-interesting as in many cases, causal effect estimation can be performed 
+we consider a set of priors \citep{BERGER1990303}. %TB to MT: added zaffalon paper
+Some works have been done in this approach of
+prior sensitivity analysis. \citet{zaffalon20a} 
+used credal networks in structured causal models
+for causal inference; \citet{raices_cruz22} suggested
+that causal effect estimation can be performed 
 through a meta analysis where robust Bayesian analysis 
-can be beneficial under severe uncertainty \citep{raices_cruz22}.
-Moreover, for some problems 
-we have to rely on very limited data to perform our Bayesian analysis.
-In this case,
+can be beneficial under severe uncertainty. 
+This motivates us to extend prior sensitivity analysis for 
+regression models. This is particularly beneficial, as for high dimensional regression problems 
+we have to rely on very limited data to perform our Bayesian analysis and 
 inference with a single prior
-%%% MT to TB: I strenghtened this
-% may not be reliable.
 is unreliable.
-%%% MT to TB: I don't quite understand the heteroscedasticity argument;
-%%% I added "inference with a single prior" above instead
-% in presence of heteroscedasticity within the data.
-Instead, we use expert opinion to elicit a set of priors 
+To perform a prior sensitivity analysis, we use expert opinion to elicit a set of priors 
 based on empirical evidence. 
 This allows us to construct the problem of 
-%%% MT to TB: changed "confounder identification" to "predictor selection"
-% confounder identification 
 predictor selection
@@
 \citep{ishwaran2005} for
-%%% MT to TB: changed "confounder identification" to "predictor selection"
-% confounder identification.
 predictor selection.
-%%% MT to TB: check if you are happy with this next sentence
 We thereby construct a Bayesian group LASSO \citep{xu2015} type problem.
@@
 corresponding \emph{treatment decisions} $T\coloneqq(T_1, \dots, T_n)$.
-%%% MT to TB: added this for clarity
 Here, we use an indicator to represent the treatment decision. That is, $T_i$ is $1$ if the $i$th patient was treated, and $0$ otherwise. Similarly,
@@
 related to the predictors, and let $\beta_T$ denote a regression coefficient related to the
-%%% MT to TB: treatment -> treatment decision
 treatment decision.
@@
 where $\epsilon_i\sim \mathcal{N}(0, \sigma^2)$,
-%%% MT to TB: added independence statement as used later
 independent of $T_i$ and $X_i$.
-%%% MT to TB: added for clarity
 Note that both $T_i$ and $X_i$ are predictors for $Y_i$ in the above model.
@@
 
-%%% MT to TB: check if you're happy with this paragraph
 To decide whether or not to treat a new individual with given predictors,
@@
 $\gamma\coloneqq(\gamma_1, \cdots, \gamma_p)^T$ we
-%%% MT to TB: define -> assume
 assume
@@
 where $u_i\sim\mathcal{N}(0,1)$.
-%%% MT to TB: not entirely trivial so I added a quick derivation
 With this model, indeed
@@
 Practically, we model this by defining the following hierarchical model
-%%% MT to TB do you mean "from" instead of "for"? for now removed as confusing
-% for spike and  slab group LASSO
 so that,
@@
         \frac{1}{\sigma^2}&\sim \text{Gamma}(a, b)\\
-        %%% MT to TB: text referred to q_j so I changed q -> q_j here
 	\pi_{j} &\sim\text{Beta}\left(sq_j, s(1-q_j)\right).
@@
 fix $a$ so that it represents the prior mean of the precision.
-%%% MT to TB: check if you are happy with this
 Alternatively, when $b=1$, we know that the interval
@@
 we consider a utility based framework with three possible 
-%%% MT to TB: not sure what is meant, subsequent text does not consider "determining a variable"; replace with "scenarios"?
-% ways of determining a variable. 
 scenarios.
 
-In general, an unsuccessful treatment of a subject can have severe consequences 
-which cannot be associated with a suitable loss function. Instead, we
+%TB to MT: did some modification in the following text
+In particular through predictor selection, we also want 
+to check if a certain bio-marker should be considered
+for treatment decision. That is, in a very intuitive 
+situation, we can observe blood pressure with some
+other bio-markers and want to decide whether our
+treatment guideline should also consider the blood
+pressure of the subject before treating them. This is
+useful as an unnecessary treatment of a subject can have severe consequences because of the medicinal
+side effects. In general, this cannot be associated 
+with a suitable loss function. Instead, we
 assume that we can always revert any initial mistreatment by further treatments, 
@@
 So, we will associate two constant loss values $\ell_1$ and $\ell_2$ 
-with false positives and false negatives respectively. 
+with false positives (falsely selected predictor) and 
+false negatives (falsely rejected predictor) respectively. 
 Clearly, false positives will lead to unwanted side effects and
 false negatives will lead to mistreatment of the patient. Finally, we associate
-a loss value $\ell_3$ for abstention which can be interpreted as the cost of further tests.
+a loss value $\ell_3$ for abstention from selecting
+a variable which can be interpreted as the cost of further tests to determine whether that bio-marker
+is important for constructing the treatment guideline.
 Ideally, in most cases, $\ell_3\ll \ell_1,\ell_2$. However, in certain scenarios,
@@
 over time.
-\iffalse
-\begin{table}[h]
-    \caption{Losses with respect to different types of variable selection}
-    \label{tab:loss:vs}
-    \centering
-    \begin{tabular}{l||c|c|c}
-       &  False Positive & False Negative & Abstention \\
-       \hline
-       \hline
-       Value  &  $\ell_1$ & $\ell_2$ & $\ell_3$
-    \end{tabular}
-\end{table}
-\fi
-
-%%% MT to TB: text above talks about abstaining from treatment; this is quite different from abstaining from selecting a variable
+
 Now, based on this notion of abstaining from selecting a variable, we can perform
@@
 %%% MT to TB: should we add a subscript q to \mathbb{E} to emphasize the dependence?
+% TB to MT: I thought of it. But we are optimising over the set of $q$. So was thinking if should put it
 \begin{align}\label{eq:vs:remove}
@@
 In general, this framework is
-%%% MT to TB: self-sufficient sounds a bit strange here, do you mean "sufficient"? [changed]
 sufficient
@@
 \end{equation}
-%%% MT to TB: check if this is correct; I hope I got this correctly from the code
 where $\epsilon_i\sim\mathcal{N}(0,0.1^2)$.
-%%% MT to TB: added this sentence for clarity later when discussing tables
 Note that the simulated causal effect $\beta_T$ is equal to $4$.
@@
 %%% MT to TB: I've edited this paragraph, see if you're happy with this
+% TB to MYT: Thanks a lot. Couldn't be better, at least not by me. :D
 One way to elicit $\mathcal{P}$
@@
 %%% are all confounders and be consistent with our terminology)
-confounder selection
+predictor selection
 as well as causal effect estimation. We consider a spike and slab type
-prior for confounder selection and discuss the possible sources of uncertainty that
+prior for predictor selection and discuss the possible sources of uncertainty that
 need to be tackled carefully. We were particularly focused on the uncertainty associated
@@
 sensitivity analysis. We showed that the sensitivity analysis on the prior selection probability
-gives us a robust confounder selection scheme. In this way, we can abstain from selecting
-a confounder when the available data is not sufficient. We also propose a generalised
+gives us a robust predictor selection scheme. In this way, we can abstain from selecting
+a predictor when the available data is not sufficient. We also propose a generalised
 utility based framework, where we associate a loss for abstaining which can be interpreted 
@@
 for the posterior estimates to reduce the computational cost. Moreover, for the sake of
-illustration, we rely on simple loss functions and elicitation strategy. In future, we would
-like to investigate different elicitation strategies for the method and explore alternative 
-loss functions for formulating a decision theoretic framework. Last but not the least,
-we noticed that our method
+illustration, we rely on simple loss functions
+%TB to MT: edited the conclusion
+associated with the predictor selection. However,
+this paradigm can be used for a generalised
+decision theoretic framework as well where based on
+the predictor selection we can formulate the 
+problem as a decision support for treating a subject.
+
+We also notice with our simulation studies that our
+method tends to underestimate the causal effect
+when some predictors are only associated with the
+outcome model. This suggests that we might want
+to use a correction formula for the causal effect.
+Moreover, in future, we would
+like to investigate different elicitation strategies for different prior parameters and their importance in causal effect estimation.
+
+In general, we noticed that our method
 is in good agreement with other methods with an added level of robustness.
-This confirms that our method has good potential for real-life problems,
+This shows that our method has good potential for real-life problems,
 and we intend to apply it on a real dataset in future work.

### 2024-03-28 JASA-template.tex
Small fixes (Matthias).

@@
 %TB to MT: did some modification in the following text
-In particular through predictor selection, we also want 
+In particular, through predictor selection, we also want 
 to check if a certain bio-marker should be considered
-for treatment decision. That is, in a very intuitive 
-situation, we can observe blood pressure with some
+for the treatment decision. For example, say we can observe blood pressure with some
 other bio-markers and want to decide whether our
@@
 useful as an unnecessary treatment of a subject can have severe consequences because of the medicinal
-side effects. In general, this cannot be associated 
+side effects. In general, it is hard to associate such consequences 
 with a suitable loss function. Instead, we
@@
 false negatives (falsely rejected predictor) respectively. 
-Clearly, false positives will lead to unwanted side effects and
-false negatives will lead to mistreatment of the patient. Finally, we associate
+%%% MT to TB: not considering a predictor may or may not lead to mistreatment, it just means you'll have less information, not that the treatment is bad... I've chanted "will" to "may"
+Clearly, false positives may lead to unwanted side effects and
+false negatives may lead to mistreatment of the patient. Finally, we associate
 a loss value $\ell_3$ for abstention from selecting
@@
 
-Now, based on this notion of abstaining from selecting a variable, we can perform
+Now, based on this notion of abstaining from selecting a predictor, we can perform
 a sensitivity analysis over a set of priors on the prior selection probability.
@@
 
-The first two cases that we consider are:
+These four cases can be split in two categories. In one category we consider the
+case where we have increasing number of observations. In the first category we have two
+sub cases, in the first case we consider all active variables to be confounders
+and in the second case we consider some active variables which are only related to
+the outcome model. 
 \begin{description}
-    \item[Scenario 1] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
-    \item[Scenario 2] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
+    \item[Scenario 1a] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
+    \item[Scenario 1b] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
 \end{description}
 For both
-cases, we consider different numbers of observations $n$ where
+scenarios, we consider different numbers of observations $n$ where
 $n=25+ 5k$ for $k=0,1,2,\dots,35$ and $p=50$
@@
 
-For the next two cases, we check our method for varying number of predictors (and hence sparsity level, i.e.\ the percentage of active variables present in the model):
+For the second category, we check our method for varying number of predictors 
+(and hence sparsity level, i.e.\ the percentage of active variables present in the model).
+Similar to the first category we also have two sub cases:
 \begin{description}
-    \item[Scenario 3] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
-    \item[Scenario 4] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
+    \item[Scenario 2a] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
+    \item[Scenario 2b] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
 \end{description}
@@
 This suggests that
-we may want to have a different value of $a$ for these sets of observations
+we may want to have a different value of $a$ for these different simulated datasets
 %%% MT to TB: is the problem that it is "fixed"? this seems a bit misleading
@@
 We can also see that the lower bound tends to improve
-with increasing number of observations: as we accumulate
+with increased number of observations: as we accumulate
 more information, the interval becomes smaller and converges towards
-the true value.
+a single value.
 
@@
 fixed number of sample in \cref{fig:comp:trt:pred,tab:causal2}. Similar to
-the first two settings, we notice that our method is in good agreement with
+the first two settings, we notice that our method is somewhat in agreement with
 BSSL for the third setting. However, for the fourth setting, our method
-underestimate the treatment effect significantly (5\% in the worst case). This
-is somewhat in sync with the second setting and a possible reason behind this
+underestimates the treatment effect significantly (5\% in the worst case). This
+is somewhat in sync with the second setting, and a possible reason behind this
 could be the fact that in both the cases, the number of active $\beta_j$'s is
@@
 
-Besides this interesting result. We notice that all of the four methods performs
+Besides this interesting result, we notice that all of the four methods perform
 perfectly in variable selection giving no misspecified variables. Therefore,
@@
 the predictor selection we can formulate the 
-problem as a decision support for treating a subject.
+problem as a decision support problem for treating a subject.
 

### 2024-04-12 JASA-template.tex
Small edit (Matthias).

@@
 Moreover, with our variable selection we only determine whether the variable 
-is included in at least one of the models. But, we cannot determine a specific 
-association. Therefore, to adjust the sparsity of the estimates and understand
-the specific association with the treatment/outcome/both, we apply the 
+is included in at least one of the models.
+%%% MT to BT: I edited this paragraph for clarity; check
+%But, we cannot determine a specific 
+%association. Therefore, to adjust the sparsity of the estimates and understand
+%the specific association with the treatment/outcome/both, 
+To determine which predictors
+influence the outcome ($\beta_j\neq 0$),
+the treatment ($\gamma_j\neq 0$), or both,
+and to understand the degree of assocation
+(i.e.\ the magnitude of $\beta_j$ and/or $\gamma_j$),
+we apply the 
 ``decoupled shrinkage and selection'' (DSS) method proposed by \citep{hahn2015}. 
 For that, we solve the following adaptive LASSO-type \citep{Zou2006}
-problems
+problems:
 

### 2024-04-12 JASA-template.tex
Updates (Matthias).

@@
 \begin{align}\label{eq:vs:remove}
-	\uexp (\pi_j\mid W)\coloneqq \sup_{q\in \mathcal{P}} \mathbb{E}(\pi_j\mid W) < 1/2.
+	\uexp (\pi_j\mid W)\coloneqq \sup_{q\in \mathcal{P}} \mathbb{E}_q(\pi_j\mid W) < 1/2.
 \end{align}
@@
 \begin{align}\label{eq:vs:sel}
-	\lexp (\pi_j\mid W)\coloneqq \inf_{q\in \mathcal{P}} \mathbb{E}(\pi_j\mid W) \ge 1/2.
+	\lexp (\pi_j\mid W)\coloneqq \inf_{q\in \mathcal{P}} \mathbb{E}_q(\pi_j\mid W) \ge 1/2.
 \end{align}
@@
 	S(q)\coloneqq
-	\left\{j\colon \mathbb{E}(\pi_j\mid W) \ge 1/2\right\}.
+	\left\{j\colon \mathbb{E}_q(\pi_j\mid W) \ge 1/2\right\}.
 \end{equation}
@@
 
-Now, for each fixed value of $q$, let $\hat{\beta}_{S(q)}$ be the posterior means 
-of the regression coefficients of the outcome model with respect to
-the predictors that belong to $S(q)$. Similarly,
-let $\hat{\gamma}_{S(q)}$ be the posterior means of the regression
-coefficients for the causal effects. Since we use continuous 
-spike and slab priors, these regression coefficients are not sparse.
+We can derive bounds on the posterior means of the paramters as follows:
+\begin{align}
+\label{eq:beta:lower}
+\underline{\beta}_j&\coloneqq\lexp (\beta_j\mid W)= \inf_{q\in \mathcal{P}} \mathbb{E}_q(\beta_j\mid W) \\
+\label{eq:beta:upper}
+\overline{\beta}_j&\coloneqq\uexp (\beta_j\mid W)=\sup_{q\in \mathcal{P}} \mathbb{E}_q(\beta_j\mid W)
+\end{align}
+with similar expressions for 
+$\underline{\beta}_T$, $\overline{\beta}_T$,
+$\underline{\gamma}_j$ and $\overline{\gamma}_j$.
+If we take the posterior expectation interval $[0,0]=\{0\}$ on a regression coefficient to represent absence of a variable, then our bounds on the regression coefficients are generally not sparse, because we use continuous
+spike and slab priors.
+
 Moreover, with our variable selection we only determine whether the variable 
@@
 problems:
-
 \begin{align}
@@
 \end{align}
-where $q\in \mathcal{P}$.
+where $q\in \mathcal{P}$,
+where $\hat{\beta}_{S(q)}$ 
+and $\hat{\gamma}_{S(q)}$ are the posterior means 
+of the regression coefficients with respect to
+the predictors that belong to $S(q)$.
+
+To compute the posterior bounds (as in \cref{eq:vs:remove,eq:vs:sel,eq:beta:lower,eq:beta:upper}), unfortunately, we usually have to resort to brute force optimisation, due to the lack of tractable expressions for the posterior expectations.
+This is obviously a major drawback of this approach.
 
@@
 variable selection. In future, it will be interesting to derive inner approximation bounds
-for the posterior estimates to reduce the computational cost. Moreover, for the sake of
+for the posterior estimates to reduce the computational cost,
+or to find better ways than brute force optimisation, such as for instance iterative importance sampling \citep{cruz22_importance}. Moreover, for the sake of
 illustration, we rely on simple loss functions

### 2024-04-18 JASA-template.tex
Fix typo (Matthias).
just in case

@@
 
-We can derive bounds on the posterior means of the paramters as follows:
+We can derive bounds on the posterior means of the parameters as follows:
 \begin{align}
@@
 the predictors that belong to $S(q)$.
+By varying $q$, this gives us a set of point estimates for the model parameters $\beta$ and $\gamma$.
 
@@
 \fi
+
+\subsection{Refit}
+
+In our setting, the DSS method only gives us a set of point estimates for the final selection of variables: some coefficients may be always selected, some never, and some will be indeterminate.
+For the final inference model, the modeller will need to make a judgement about which of the indeterminate coefficients $\beta_j$ and $\gamma_j$ to include in the final model or not.
+Once done so, the model can be refitted to account for the effect of variable selection on the estimation of the model parameters.
+
+To do so, we can again use our Bayesian model without $\pi_j$ (i.e. there is no selection), and with
+\begin{align}
+\beta_j\sim\mathcal{N}(0,\tau_1\sigma^2)
+\end{align}
 

### 2024-04-18 causal (copy).R

@@ -15,11 +15,8 @@ source("other_causal.R")
 
 set.seed(1e8)
 
-ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 10, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
+ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 100, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
   MCMC = list()
-  x_scale = scale(x)
-  x_ctr = attr(x_scale,"scaled:center")
-  x_sd = attr(x_scale,"scaled:scale")
   
   string = "
   model {
@@ -110,11 +107,11 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 10, gam_b = 1,
   
   for (i in 1:length(alphas)) {
     
-    b_post[[i]] = as.matrix(MCMC[[i]][[1]])[,1:ncol(x)] / x_sd
+    b_post[[i]] = as.matrix(MCMC[[i]][[1]])[,1:ncol(x)] 
     
     b_T_post[[i]] = as.matrix(MCMC[[i]][[1]])[,(1+ncol(x))]
     
-    g_post[[i]] = as.matrix(MCMC[[i]][[1]])[,(ncol(x)+2):(2*ncol(x)+1)] / x_sd
+    g_post[[i]] = as.matrix(MCMC[[i]][[1]])[,(ncol(x)+2):(2*ncol(x)+1)] 
     
     w_post[[i]] = as.matrix(MCMC[[i]][[1]])[,(2*ncol(x)+3):(3*ncol(x)+2)]
     
@@ -130,315 +127,319 @@ coeff_adj = function(rbvs_obj){
 }
 
 ##############################################################################################
-# For inceasing observation
-n = 200
-p = 50
-
-sig1 = matrix(nrow=p,ncol = p)#diag(50)#
-
-for (i in 1:p) {
-  for (j in 1:p) {
-    sig1[i,j] = 0.3^abs(i-j)
-  }
-}
-
-# setting1 
-
-if(T){
-  x_all = rmvnorm(n, sigma = sig1)
-  
-  beta1 = c(runif(5, -4, -1), runif(5, 1, 4))
-  gamma1 = c(runif(5, -4, -1), runif(5, 1, 4))
-  
[…]

### 2024-04-18 causal_refit.R

@@ -1,0 +1,84 @@
+ISVS_d = function(x_b, x_g, y, a, gam_a = 100, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
+  MCMC = list()
+  
+  string = "
+  model {
+  
+    ## Likelihood
+    
+    for (i in 1:N) 
+    {
+      mean[i] = b_T * a[i] + inprod(x_b[i,], b)
+      y[i] ~ dnorm(mean[i], inv.var)
+      
+      a[i] ~ dinterval(a_dumm[i], 0)
+      
+      a_dumm[i] ~ dnorm(inprod(x_g[i,], g), 1)
+    }
+    
+    # Prior on the mean
+    
+    b_T ~ dnorm(0,inv.var)
+    
+    # prior on the precision
+    
+    inv.var ~ dgamma(gam_a, gam_b)
+    
+    sigma2 = 1 / inv.var
+    
+    ## Prior on the regression parameters 
+    
+    for (j in 1:p_b) 
+    {
+      
+      # Prior on beta
+      
+      b[j] ~ dnorm(0, inv.var)
+      
+    }
+    
+    for (j in 1:p_g) 
+    {
+      
+      # Prior on beta
+      
+      g[j] ~ dnorm(0, 1)
+      
+    }
+    
+  }
+  "
+  params = c("b","b_T", "g", "sigma2")
+  
+
+  MCMC =  {
+    
+    ISVS <- textConnection(string, open = "r")
+    
+    data = list(
+      y = as.vector(y),
+      x_g = x_g,
+      x_b = x_b,
+      a = a,
+      p_g = ncol(x_g),
+      p_b = ncol(x_b),
+      N = nrow(x),
+      gam_a = gam_a,
+      gam_b = gam_b
+    )
+    
+    model <- jags.model(data = data, file = ISVS, n.chains = 1, n.adapt = n.adapt)
+    update(model, n.iter)
+    coda.samples(model, params, n.sample)
+  }
+  
+
+  b_post = as.matrix(MCMC[[1]])[,1:ncol(x_b)]
+  b_T_post = as.matrix(MCMC[[1]])[,(1+ncol(x_b))]
+  g_post = as.matrix(MCMC[[1]])[,(ncol(x_b)+2):(ncol(x_b)+1+ncol(x_g))]
+  
+
[…]

### 2024-04-20 causal (copy).R
change

@@ -15,7 +15,7 @@ source("other_causal.R")
 
 set.seed(1e8)
 
-ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 100, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
+ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 50, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
   MCMC = list()
   
   string = "
@@ -28,9 +28,11 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 100, gam_b = 1
       mean[i] = b_T * a[i] + inprod(x[i,], b)
       y[i] ~ dnorm(mean[i], inv.var)
       
-      a[i] ~ dinterval(a_dumm[i], 0)
+      a[i] ~ dbern(a_prob[i])
       
-      a_dumm[i] ~ dnorm(inprod(x[i,], g), 1)
+      probit(a_prob[i]) = a_dumm[i]
+      
+      a_dumm[i] = inprod(x[i,], g)
     }
     
     # Prior on the mean
@@ -48,18 +50,21 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 100, gam_b = 1
     for (j in 1:p) 
     {
       # prior on the selection probability
-      w[j] ~ dbeta(2*alpha, 2*(1-alpha))I(0.001,0.999)
       
+      w[j] ~ dbeta(2*alpha, 2*(1-alpha))I(0.001,0.999)
       
       # Prior on beta
       
       spike[j] ~ dnorm(0, (inv.var / tau_0^2))
       slab[j] ~ dnorm(0, (inv.var / tau_1^2))
       
+      b[j] = w[j] * slab[j]  + (1 - w[j]) * spike[j]
+      
+      # Prior on gamma
+      
       spikeg[j] ~ dnorm(0, (1 / tau_0^2))
       slabg[j] ~ dnorm(0, (1 / tau_1^2))
       
-      b[j] = w[j] * slab[j]  + (1 - w[j]) * spike[j]
       g[j] = w[j] * slabg[j]  + (1 - w[j]) * spikeg[j]
     }
     
[…]

### 2024-04-20 causal_refit.R

@@ -1,4 +1,4 @@
-ISVS_d = function(x_b, x_g, y, a, gam_a = 100, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
+ISVS_d = function(x_b, x_g, y, a, tau_1 = 5, gam_a = 100, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
   MCMC = list()
   
   string = "
@@ -8,17 +8,21 @@ ISVS_d = function(x_b, x_g, y, a, gam_a = 100, gam_b = 1, n.iter = 2000, n.adapt
     
     for (i in 1:N) 
     {
-      mean[i] = b_T * a[i] + inprod(x_b[i,], b)
+      mean[i] = b_T * a[i] + inprod(x_b[i,], b) + b_int
       y[i] ~ dnorm(mean[i], inv.var)
       
-      a[i] ~ dinterval(a_dumm[i], 0)
+      a[i] ~ dbern(a_prob[i])
       
-      a_dumm[i] ~ dnorm(inprod(x_g[i,], g), 1)
+      probit(a_prob[i]) = a_dumm[i]
+      
+      a_dumm[i] = inprod(x_g[i,], g) + g_int
     }
     
     # Prior on the mean
     
     b_T ~ dnorm(0,inv.var)
+    b_int ~ dnorm(0,inv.var)
+    g_int ~ dnorm(0,1)
     
     # prior on the precision
     
@@ -33,7 +37,7 @@ ISVS_d = function(x_b, x_g, y, a, gam_a = 100, gam_b = 1, n.iter = 2000, n.adapt
       
       # Prior on beta
       
-      b[j] ~ dnorm(0, inv.var)
+      b[j] ~ dnorm(0, inv.var / tau_1^2)
       
     }
     
@@ -42,7 +46,7 @@ ISVS_d = function(x_b, x_g, y, a, gam_a = 100, gam_b = 1, n.iter = 2000, n.adapt
       
       # Prior on beta
       
-      g[j] ~ dnorm(0, 1)
+      g[j] ~ dnorm(0, 1 / tau_1^2)
       
     }
     
@@ -62,9 +66,10 @@ ISVS_d = function(x_b, x_g, y, a, gam_a = 100, gam_b = 1, n.iter = 2000, n.adapt
       a = a,
       p_g = ncol(x_g),
       p_b = ncol(x_b),
-      N = nrow(x),
[…]

### 2024-04-29 causal (copy).R
update plot

@@ -25,20 +25,24 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 50, gam_b = 1,
     
     for (i in 1:N) 
     {
-      mean[i] = b_T * a[i] + inprod(x[i,], b)
+      mean[i] = b_T * a[i] + inprod(x[i,], b) #+ b_int
       y[i] ~ dnorm(mean[i], inv.var)
       
       a[i] ~ dbern(a_prob[i])
       
       probit(a_prob[i]) = a_dumm[i]
       
-      a_dumm[i] = inprod(x[i,], g)
+      a_dumm[i] = inprod(x[i,], g) #+ g_int
     }
     
     # Prior on the mean
     
     b_T ~ dnorm(0,inv.var)
     
+    # b_int ~ dnorm(0,inv.var)
+    # 
+    # g_int ~ dnorm(0,1)
+    # 
     # prior on the precision
     
     inv.var ~ dgamma(gam_a, gam_b)
@@ -146,20 +150,136 @@ sparse_adjust = function(rbvs_obj){
 
 ##############################################################################################
 # For inceasing observation
-n = 200
-p = 50
-
-sig1 = matrix(nrow=p,ncol = p)#diag(50)#
-
-for (i in 1:p) {
-  for (j in 1:p) {
-    sig1[i,j] = 0.3^abs(i-j)
-  }
-}
+# n = 200
+# p = 50
+# 
+# sig1 = matrix(nrow=p,ncol = p)#diag(50)#
+# 
+# for (i in 1:p) {
+#   for (j in 1:p) {
+#     sig1[i,j] = 0.3^abs(i-j)
+#   }
+# }
 
 # setting1
 
-if(T){
+if(F){
+  x_all = rmvnorm(n, sigma = sig1)
+
+  beta1 = c(runif(5, -4, -1), runif(5, 1, 4))
+  gamma1 = c(runif(5, -4, -1), runif(5, 1, 4))
+
+  a1_dum_all = 1/(1 + exp(-x_all[,1:length(gamma1)] %*% gamma1))
+  a1_all = sapply(1:n, function(j)rbinom(1,1,a1_dum_all[j]))
+
+
+  y1_all = 4*a1_all + x_all[,1:length(beta1)] %*% beta1 + rnorm(n, sd = .1)
+  
+  val1 = sum(abs(cor(x_all,y1_all))>0.2)
+  val2 = sum(abs(cor(x_all,y1_all))>0.3)
+  
[…]

### 2024-04-29 JASA-template.tex

@@
 \begin{align}
-	(\beta_j,\gamma_j)^T \mid \pi_{j}, \sigma^2 &\sim 
+	\label{eq:spike:slab:prior:beta:gamma}(\beta_j,\gamma_j)^T \mid \pi_{j}, \sigma^2 &\sim 
 	\pi_{j}\normal\left( \begin{bmatrix}
@@
 the predictors that belong to $S(q)$.
-By varying $q$, this gives us a set of point estimates for the model parameters $\beta$ and $\gamma$.
+By varying $q$, this gives us a set of point estimates for the model parameters $\beta$ and $\gamma$, along with a more detailed selection of individual $\beta_j$ and $\gamma_j$.
 
@@
 
-To do so, we can again use our Bayesian model without $\pi_j$ (i.e. there is no selection), and with
-\begin{align}
-\beta_j\sim\mathcal{N}(0,\tau_1\sigma^2)
-\end{align}
+To do so, we can again use our Bayesian model without $\pi_j$ (as there is no selection anymore), and with priors
+\begin{align}
+\beta_j\mid\sigma^2&\sim\mathcal{N}(0,\tau_1^2\sigma^2) \\
+\gamma_j\mid\sigma^2&\sim\mathcal{N}(0,\tau_1^2)
+\end{align}
+for those $\beta_j$ and $\gamma_j$ that are selected in the model, with the remaining $\beta_j$ and $\gamma_j$ set to zero.
+This is similar to the spike and slab prior from \cref{eq:spike:slab:prior:beta:gamma} but without the spike component.
+
+We expect this to have only a small effect on the mean and variance of the estimated parameters.
+This refit is useful to validate the variable selection and to improve the estimating of the model parameters, including the causal effect $\beta_T$.
+Indeed, since there are fewer parameters for the same data, the estimates are expected to have less uncertainty.
+
+Note that here, we described a precise Bayesian refit model, but obviously this could be extended to robust Bayesian refit models too.
 
@@
   \hline
-25 & 3.06 & 4.18 & -- & -- & 3.98 & 3.61 & 5.12 &  &  & 3.69 \\ 
-  30 & 3.47 & 4.31 & -- & -- & 4.01 & 3.42 & 5.40 &  &  & 9.54 \\ 
-  35 & 3.24 & 3.53 & -- & -- & 3.99 & 3.69 & 4.93 &  &  & 9.86 \\ 
-  40 & 3.61 & 3.83 & -- & -- & 3.99 & 3.77 & 4.42 &  &  & 3.95 \\ 
-  45 & 3.80 & 3.87 & -- & -- & 3.95 & 3.67 & 3.96 &  &  & 3.95 \\ 
-  50 & 3.81 & 3.87 & 3.99 & 4.01 & 3.99 & 3.77 & 3.86 & 3.72 & 4.93 & 3.94 \\ 
-  55 & 3.88 & 3.95 & 3.97 & 4.00 & 3.98 & 3.79 & 3.92 & 3.96 & 3.95 & 3.97 \\ 
-  60 & 3.97 & 3.99 & 3.99 & 4.00 & 3.98 & 3.86 & 3.90 & 3.93 & 3.91 & 3.94 \\ 
-  65 & 3.96 & 4.00 & 4.00 & 4.02 & 4.00 & 3.91 & 3.94 & 3.95 & 3.94 & 3.94 \\ 
-  70 & 3.96 & 3.99 & 4.01 & 4.05 & 4.00 & 3.84 & 3.89 & 3.94 & 3.95 & 3.95 \\ 
-  75 & 3.98 & 4.00 & 4.02 & 4.03 & 4.02 & 3.84 & 3.87 & 3.97 & 3.97 & 3.97 \\ 
-  80 & 3.98 & 4.00 & 4.02 & 4.05 & 4.01 & 3.87 & 3.89 & 3.95 & 3.96 & 3.96 \\ 
-  85 & 3.97 & 4.00 & 4.03 & 4.04 & 4.03 & 3.91 & 3.93 & 3.96 & 3.94 & 3.96 \\ 
-  90 & 3.98 & 4.00 & 4.05 & 4.07 & 4.04 & 3.91 & 3.94 & 3.95 & 3.95 & 3.95 \\ 
-  95 & 3.97 & 3.99 & 4.02 & 4.05 & 4.04 & 3.92 & 3.93 & 3.97 & 3.97 & 3.97 \\ 
-  100 & 3.96 & 3.98 & 4.03 & 4.05 & 4.04 & 3.92 & 3.94 & 3.96 & 3.96 & 3.96 \\ 
-  105 & 3.98 & 3.99 & 4.03 & 4.05 & 4.03 & 3.92 & 3.93 & 3.95 & 3.95 & 3.95 \\ 
-  110 & 3.98 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.97 \\ 
-  115 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.93 & 3.94 & 3.97 & 3.98 & 3.98 \\ 
-  120 & 3.99 & 4.00 & 4.04 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
-  125 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
-  130 & 3.99 & 3.99 & 4.02 & 4.04 & 4.02 & 3.92 & 3.94 & 3.97 & 3.97 & 3.97 \\ 
-  135 & 3.99 & 4.00 & 4.02 & 4.04 & 4.02 & 3.93 & 3.94 & 3.98 & 3.97 & 3.98 \\ 
-  140 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
-  145 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.94 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
-  150 & 3.99 & 4.00 & 4.02 & 4.02 & 4.02 & 3.93 & 3.95 & 3.98 & 3.98 & 3.98 \\ 
-  155 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.98 & 3.98 & 3.99 \\ 
-  160 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
-  165 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.98 & 3.98 \\ 
-  170 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.99 & 3.99 \\ 
-  175 & 3.99 & 4.00 & 4.03 & 4.05 & 4.04 & 3.95 & 3.95 & 4.00 & 4.00 & 4.00 \\ 
-  180 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
-  185 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
-  190 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
-  195 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
-  200 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
+25 & 2.61 & 3.38 &  &  & 2.19 & 2.70 & 3.29 &  &  & 8.80 \\ 
+  30 & 3.14 & 3.56 &  &  & 3.99 & 3.01 & 3.54 &  &  & 9.02 \\ 
+  35 & 3.15 & 3.52 &  &  & 3.98 & 3.22 & 3.66 &  &  & 6.66 \\ 
+  40 & 3.60 & 3.75 &  &  & 3.98 & 3.20 & 3.70 &  &  & 4.42 \\ 
+  45 & 3.76 & 3.82 &  &  & 3.96 & 3.61 & 3.74 &  &  & 3.99 \\ 
+  50 & 3.79 & 3.84 & 3.99 & 4.01 & 3.99 & 3.75 & 3.79 & 9.04 & 9.36 & 4.01  \\ 
+  55 & 3.89 & 3.91 & 3.97 & 4.00 & 3.98 & 3.77 & 3.81 & 5.92 & 6.38 & 4.02 \\ 
+  60 & 3.93 & 3.95 & 3.99 & 4.00 & 3.98 & 3.76 & 3.77 & 3.89 & 3.50 & 4.03 \\ 
+  65 & 3.95 & 3.96 & 4.00 & 4.02 & 4.00 & 3.76 & 3.78 & 3.91 & 3.99 & 4.02 \\ 
+  70 & 3.94 & 3.96 & 4.01 & 4.05 & 4.00 & 3.77 & 3.79 & 4.01 & 3.96 & 4.03 \\ 
+  75 & 3.97 & 3.98 & 4.02 & 4.03 & 4.02  & 3.82 & 3.83 & 4.03 & 4.02 & 4.04 \\ 
+  80 & 3.96 & 3.98 & 4.02 & 4.05 & 4.01 & 3.83 & 3.85 & 4.04 & 4.05 & 4.05 \\ 
+  85 & 3.96 & 3.98 & 4.03 & 4.04 & 4.03 & 3.84 & 3.86 & 4.05 & 4.06 & 4.06 \\ 
+  90 & 3.97 & 3.99 & 4.05 & 4.07 & 4.04 & 3.87 & 3.88 & 4.06 & 4.04 & 4.05 \\ 
+  95 & 3.96 & 3.98 & 4.02 & 4.05 & 4.04 & 3.88 & 3.89 & 4.05 & 4.06 & 4.06 \\ 
+  100 & 3.95 & 3.98 & 4.03 & 4.05 & 4.04 & 3.88 & 3.89 & 4.07 & 4.06 & 4.07 \\ 
+  105 & 3.97 & 3.98 & 4.03 & 4.05 & 4.03 & 3.89 & 3.90 & 4.07 & 4.06 & 4.07 \\ 
+  110 & 3.97 & 3.99 & 4.03 & 4.05 & 4.03 & 3.90 & 3.91 & 4.07 & 4.05 & 4.07 \\ 
+  115 & 3.98 & 3.99 & 4.04 & 4.05 & 4.04 & 3.91 & 3.92 & 4.06 & 4.06 & 4.06 \\ 
+  120 & 3.98 & 3.99 & 4.04 & 4.05 & 4.03 & 3.91 & 3.92 & 4.04 & 4.05 & 4.04 \\ 
+  125 & 3.99 & 3.99 & 4.03 & 4.04 & 4.03 & 3.91 & 3.92 & 4.04 & 4.04 & 4.04 \\ 
+  130 & 3.98 & 3.99 & 4.02 & 4.04 & 4.02 & 3.92 & 3.93 & 4.03 & 4.04 & 4.04 \\ 
+  135 & 3.99 & 3.99 & 4.02 & 4.04 & 4.02 & 3.94 & 3.94 & 4.04 & 4.05 & 4.04 \\ 
+  140 &  3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 4.04 & 4.05 & 4.04 \\ 
+  145 & 3.99 & 3.99 & 4.03 & 4.04 & 4.03 & 3.95 & 3.95 & 4.05 & 4.05 & 4.05 \\ 
+  150 & 3.99 & 3.99 & 4.02 & 4.02 & 4.02 & 3.94 & 3.95 & 4.04 & 4.04 & 4.04 \\ 
    \hline
@@
   \cline{2-14}
- Samples & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
-  \hline
-25 &   0 &   0 &  43 & 8.6 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0&   0  \\ 
-  30 &   0 &   0 &   5 & 1 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0 \\ 
-  35 &   0 &   0 &   2 & .4 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0 \\ 
-  40 &   0 &   0 &   0 & 0 &  -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0 \\ 
-  45 &   0 &   0 &   0 & 0 & -- &  --  &  -- &  --  &  -- &  --  &    0 &   0 &   0 \\ 
+ Obs & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
+  \hline
+25 & 1 & 0 & 39 & 8.8 &  &  &  &  &  &  & 9 & 1 & 10 \\ 
+  30 & 0 & 0 & 3 & 0.6 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
+  35 & 0 & 0 & 3 & 0.6 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
+  40 & 0 & 0 & 0 & 0 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
+  45 & 0 & 0 & 0 & 0 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
   50 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
@@
   105 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  110 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0&   0 &   0 &   0  &   0 \\ 
+  110 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   115 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
@@
   150 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  155 &   0 &   0 &   0 &  0 &  1 &   0 & 1 &  0 &   0 &   0 &   0 &   0 &   0 \\ 
-  160 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  165 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  170 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  175 &   0 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  180 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  185 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  190 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  195 &   0 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
-  200 &   0 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
    \hline
@@
   \cline{2-14}
- Samples & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
-  \hline
-25 &   0 &   1 &  21 & 5.2 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0\\ 
-  30 &   0 &   0 &  44 & 8.8 & -- &  --  &  -- &  --  &  -- &  --  &  0 &  13 &   13\\ 
-  35 &   0 &   0 &  11 & 2.2 & -- &  --  &  -- &  --  &  -- &  --  &  0 &  13 &   13\\ 
-  40 &   0 &   0 &   4 & .8 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0\\ 
-  45 &   0 &   0 &   3 & .6 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0\\ 
-  50 &   0 &   0 &   2 & .1 &  0 &   0 &   0 &   0 &  15 & 15 &   0 &   0 &   0\\ 
-  55 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  60 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  65 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  70 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  75 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  80 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  85 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  90 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  95 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  100 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  105 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  110 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  115 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  120 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  125 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  130 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  135 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  140 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  145 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  150 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  155 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  160 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  165 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  170 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  175 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  180 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  185 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  190 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  195 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
-  200 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0&   0&   0\\ 
+ Obs & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
+  \hline
+25 &   5 & 0 & 35 & 12 &  &  &  &  &  &  & 0 & 15 & 15 \\ 
+  30 & 0 & 2 & 7 & 3.4 &  &  &  &  &  &  & 0 & 14 & 14 \\ 
+  35 & 0 & 1 & 9 & 2.8 &  &  &  &  &  &  & 0 & 14 & 14 \\ 
+  40 & 0 & 0 & 21 & 4.2 &  &  &  &  &  &  & 0 & 10 & 10 \\ 
+  45 & 0 & 0 & 1 & 0.2 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
+  50 & 0 & 0 & 0 & 0 & 0 & 15 & 15 & 0 & 15 & 15 & 0 & 0 & 0 \\ 
+  55 & 0 & 0 & 0 & 0 & 0 & 14 & 14 & 0 & 14 & 14 & 0 & 0 & 0 \\ 
+  60 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  65 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  70 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  75 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  80 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  85 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  90 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  95 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  100 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  105 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  110 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  115 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  120 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  125 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  130 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  135 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  140 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  145 & 0 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+  150 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline

### 2024-04-30 JASA-template.tex
sync

@@
 %%% MT to TB: what about "Robust Bayesian Analysis of Causal Inference in Medical Diagnosis and Treatment"
-\title{Robust Bayesian Analysis of Causal Inference Problems}
+%%% TB to MT: changed it
+\title{Robust Bayesian Analysis of Causal Inference in Medical Diagnosis and Treatment}
 \author[1]{Tathagata Basu\corref{cor1}}
@@
 by identifying causal links between
-%%% MT to TB: changed "the variables and the outcome" to "a number of predictor (or, explanatory) variables and the outcome of a treatment"
-%%% please check if you're happy with this
 a number of predictor (or, explanatory) variables and the outcome of a treatment.
-% the variables and the outcome.
 However, estimation of such causal links is extremely 
@@
 
-%TB to MT: did some modification in the following text
 In particular, through predictor selection, we also want 
@@
 false negatives (falsely rejected predictor) respectively. 
-%%% MT to TB: not considering a predictor may or may not lead to mistreatment, it just means you'll have less information, not that the treatment is bad... I've chanted "will" to "may"
 Clearly, false positives may lead to unwanted side effects and
@@
 treatment and outcome model, if
-%%% MT to TB: should we add a subscript q to \mathbb{E} to emphasize the dependence?
-% TB to MT: I thought of it. But we are optimising over the set of $q$. So was thinking if should put it
 \begin{align}\label{eq:vs:remove}
@@
 is included in at least one of the models.
-%%% MT to BT: I edited this paragraph for clarity; check
-%But, we cannot determine a specific 
-%association. Therefore, to adjust the sparsity of the estimates and understand
-%the specific association with the treatment/outcome/both, 
 To determine which predictors
@@
 \paragraph{Elicitation}
-%%% MT to TB: I've edited this paragraph, see if you're happy with this
-% TB to MYT: Thanks a lot. Couldn't be better, at least not by me. :D
 One way to elicit $\mathcal{P}$
@@
 %%% MT to TB: where does a=10 come from? can we say something about that?
-For the noise term, we set $a=10$ and $b=1$.
+For the noise term, we set $a=50$ and $b=1$.
 To perform 
@@
 estimate the causal effect. However, sometimes, other methods produce extreme 
-values which is not the case for our method. This can be observed in \cref{fig:comp:trt} as well. Here, the true 
-value is represented by the black straight line for $\beta_T = 4$.
+values which is not the case for our method. This can be observed in \cref{fig:comp:trt} as well. %Here, the true 
+%value is represented by the black straight line for $\beta_T = 4$.
 
@@
 to underestimate the causal effect.
-%%% MT to TB: why is the problem with a? can you explain a bit more?
 This suggests that
 we may want to have a different value of $a$ for these different simulated datasets
-%%% MT to TB: is the problem that it is "fixed"? this seems a bit misleading
-%TB to MT: I was thinking of a differernt value to get a flatter prior but that felt like manipulation so kept it fixed for each sample size or predicrtor size
-instead of a fixed value of $a=10$ for all of our analyses.
+instead of a single value of $a=50$ for all of our analyses.
 We can also see that the lower bound tends to improve
@@
 abstains from identifying some variables for 
-$n \le 50$. Especially for $n=25$, our method identifies 43 and 21 variables as indeterminate
+$n \le 50$. Especially for $n=25$, our method identifies 39 and 35 variables as indeterminate
 for the first setting and second setting respectively. However,
 later on our method gives more precise results in terms of variable
-selection. We also notice that BSSL tends to perform poorly
-in terms of variable selection in the second case giving away 13 FPs in both the cases. This can be seen in the bottom figure of \cref{fig:comp:trt}
+selection. We also notice that the other methods tend to perform poorly
+in terms of variable selection in the second case giving away many FNs. 
+This can be seen in the bottom figure of \cref{fig:comp:trt}
 as well.
@@
 \hline
-30 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.89 & 3.91 & 3.99 & 3.99 & 3.99 \\ 
-  35 & 3.97 & 3.99 & 4.00 & 4.02 & 4.00 & 3.88 & 3.90 & 3.99 & 3.99 & 4.00 \\ 
-  40 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.88 & 3.90 & 3.99 & 4.00 & 3.99 \\ 
-  45 & 3.97 & 3.99 & 4.00 & 4.01 & 4.00 & 3.88 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
-  50 & 3.97 & 3.99 & 4.00 & 4.01 & 3.99 & 3.87 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
-  55 & 3.98 & 4.00 & 4.00 & 4.01 & 3.99 & 3.87 & 3.90 & 3.99 & 3.99 & 3.99 \\ 
-  60 & 3.98 & 4.00 & 4.00 & 4.01 & 4.00 & 3.86 & 3.89 & 3.99 & 3.99 & 4.00 \\ 
-  65 & 3.98 & 4.01 & 3.99 & 4.02 & 4.00 & 3.85 & 3.89 & 3.99 & 3.99 & 3.99 \\ 
-  70 & 3.98 & 4.00 & 4.00 & 4.01 & 4.00 & 3.85 & 3.88 & 3.99 & 3.99 & 4.00 \\ 
-  75 & 3.98 & 4.00 & 4.00 & 4.00 & 4.00 & 3.84 & 3.89 & 3.99 & 4.00 & 3.99 \\ 
-  80 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.84 & 3.89 & 3.99 & 3.99 & 3.99 \\ 
-  85 & 3.99 & 4.01 & 4.00 & 4.01 & 4.00 & 3.82 & 3.88 & 4.00 & 3.99 & 3.99 \\ 
-  90 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.82 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
-  95 & 3.99 & 4.00 & 4.00 & 4.02 & 4.00 & 3.81 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
-  100 & 3.99 & 4.00 & 4.00 & 4.01 & 4.00 & 3.83 & 3.88 & 3.99 & 4.00 & 3.99 \\ 
-  105 & 3.99 & 4.00 &  &  & 4.00 & 3.83 & 3.88 &  &  & 3.99 \\ 
-  110 & 3.99 & 4.00 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
-  115 & 3.98 & 4.01 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
-  120 & 3.99 & 4.00 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
-  125 & 3.99 & 4.01 &  &  & 4.00 & 3.82 & 3.88 &  &  & 3.99 \\ 
-  130 & 3.99 & 4.01 &  &  & 4.00 & 3.82 & 3.87 &  &  & 3.99 \\ 
-  135 & 3.98 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
-  140 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.88 &  &  & 3.99 \\ 
-  145 & 3.99 & 4.01 &  &  & 4.00 & 3.80 & 3.88 &  &  & 3.99 \\ 
-  150 & 3.99 & 4.01 &  &  & 4.00 & 3.83 & 3.88 &  &  & 3.99 \\ 
-  155 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
-  160 & 3.99 & 4.01 &  &  & 4.00 & 3.81 & 3.87 &  &  & 3.99 \\ 
-  165 & 3.98 & 4.01 &  &  & 4.00 & 3.81 & 3.88 &  &  & 3.99 \\ 
-  170 & 3.99 & 4.02 &  &  & 4.00 & 3.80 & 3.87 &  &  & 3.99 \\ 
-  175 & 3.99 & 4.01 &  &  & 4.00 & 3.79 & 3.87 &  &  & 3.99 \\ 
-  180 & 3.98 & 4.01 &  &  & 4.00 & 3.79 & 3.87 &  &  & 3.99 \\ 
-  185 & 3.99 & 4.01 &  &  & 4.00 & 3.79 & 3.88 &  &  & 3.99 \\ 
-  190 & 3.98 & 4.01 &  &  & 3.99 & 3.79 & 3.86 &  &  & 3.99 \\ 
-  195 & 3.99 & 4.01 &  &  & 4.00 & 3.80 & 3.86 &  &  & 3.99 \\ 
-  200 & 3.98 & 4.02 &  &  & 4.00 & 3.78 & 3.86 &  &  & 3.99 \\ 
+30 & 3.93 & 3.95 & 3.99 & 4.00 & 3.99 & 3.89 & 3.90 & 4.02 & 4.02 & 4.01 \\ 
+  35 & 3.93 & 3.94 & 3.99 & 3.99 & 3.99 & 3.88 & 3.91 & 4.02 & 4.01 & 4.02 \\ 
+  40 & 3.93 & 3.95 & 3.99 & 4.01 & 3.99 & 3.89 & 3.91 & 4.01 & 4.03 & 4.01 \\ 
+  45 & 3.93 & 3.95 & 3.99 & 4.01 & 3.99 & 3.89 & 3.91 & 4.02 & 4.02 & 4.02 \\ 
+  50 & 3.94 & 3.95 & 3.99 & 4.00 & 3.99 & 3.89 & 3.91 & 4.01 & 4.02 & 4.02 \\ 
+  55 & 3.94 & 3.95 & 3.99 & 4.00 & 3.98 & 3.89 & 3.91 & 4.02 & 4.02 & 4.02 \\ 
+  60 & 3.94 & 3.95 & 3.99 & 4.01 & 3.99 & 3.89 & 3.91 & 4.02 & 4.02 & 4.02 \\ 
+  65 & 3.94 & 3.94 & 3.99 & 4.00 & 3.98 & 3.89 & 3.91 & 4.02 & 4.03 & 4.02 \\ 
+  70 & 3.93 & 3.95 & 3.99 & 4.00 & 3.99 & 3.89 & 3.90 & 4.02 & 4.02 & 4.02 \\ 
+  75 & 3.92 & 3.94 & 3.99 & 4.00 & 3.99 & 3.89 & 3.90 & 4.01 & 4.02 & 4.02 \\ 
+  80 & 3.92 & 3.94 & 3.99 & 3.99 & 3.99 & 3.89 & 3.90 & 4.01 & 4.01 & 4.02 \\ 
+  85 & 3.92 & 3.94 & 3.99 & 4.00 & 3.98 & 3.88 & 3.90 & 4.02 & 4.02 & 4.02 \\ 
+  90 & 3.92 & 3.93 & 3.99 & 4.00 & 3.99 & 3.88 & 3.90 & 4.02 & 4.01 & 4.02 \\ 
+  95 & 3.92 & 3.94 & 3.99 & 4.00 & 3.98 & 3.87 & 3.90 & 4.02 & 4.01 & 4.02 \\ 
+  100 & 3.92 & 3.94 & 3.99 & 3.99 & 3.98 & 3.88 & 3.90 & 4.02 & 4.02 & 4.01 \\ 
+  105 & 3.92 & 3.94 &  &  & 3.98 & 3.86 & 3.90 &  &  & 4.02 \\ 
+  110 & 3.92 & 3.94 &  &  & 3.99 & 3.87 & 3.90 &  &  & 4.01 \\ 
+  115 & 3.91 & 3.94 &  &  & 3.98 & 3.87 & 3.90 &  &  & 4.02 \\ 
+  120 & 3.91 & 3.94 &  &  & 3.99 & 3.87 & 3.91 &  &  & 4.02 \\ 
+  125 & 3.91 & 3.94 &  &  & 3.99 & 3.87 & 3.89 &  &  & 4.02 \\ 
+  130 & 3.92 & 3.94 &  &  & 3.99 & 3.86 & 3.90 &  &  & 4.01 \\ 
+  135 & 3.90 & 3.93 &  &  & 3.98 & 3.86 & 3.90 &  &  & 4.01 \\ 
+  140 & 3.91 & 3.93 &  &  & 3.99 & 3.85 & 3.89 &  &  & 4.01 \\ 
+  145 & 3.90 & 3.94 &  &  & 3.98 & 3.84 & 3.89 &  &  & 4.01 \\ 
+  150 & 3.90 & 3.93 &  &  & 3.99 & 3.85 & 3.88 &  &  & 4.02 \\ 
    \hline

### 2024-04-30 causal (copy).R

@@ -736,78 +736,92 @@ xtable::xtable(cbind(set2_sum_loss[,1:3], (set2_sum_loss[,1]+set2_sum_loss[,2] +
 ######################################################################################
 
 # tables
-# RBVS3_list = list()
-# RBVS4_list = list()
-# 
-# for (k in 1:15) {
-#   RBVS3_list[[k]] = get(paste0("set3_rbvs_obj_", k))
-#   RBVS4_list[[k]] = get(paste0("set4_rbvs_obj_", k))
-# }
-# 
-# set3_sum_beta_trt = c()
-# for (k in 1:15) {
-#   set3_sum_beta_trt = cbind(set3_sum_beta_trt, rbind(min(range(get(paste0("set3_casual_", k)))), max(range(get(paste0("set3_casual_", k)))), get(paste0("set3_SSCE_", k))$mean.trt.effect, get(paste0("set3_BSSCE_", k))$mean.trt.effect, get(paste0("set3_BSSL_", k))$means[(25 + 5*k +2)]))
-# }
-# 
-# # for (k in 16:35) {
-# #   set3_sum_beta_trt = cbind(set3_sum_beta_trt, rbind(min(range(get(paste0("set3_casual_", k)))), max(range(get(paste0("set3_casual_", k)))), NA, NA, get(paste0("set3_BSSL_", k))$means[(25 + 5*k +2)]))
-# # }
-# 
-# set4_sum_beta_trt = c()
-# for (k in 1:15) {
-#   set4_sum_beta_trt = cbind(set4_sum_beta_trt, rbind(min(range(get(paste0("set4_casual_", k)))), max(range(get(paste0("set4_casual_", k)))), get(paste0("set4_SSCE_", k))$mean.trt.effect, get(paste0("set4_BSSCE_", k))$mean.trt.effect, get(paste0("set4_BSSL_", k))$means[(25 + 5*k +2)]))
-# }
-# 
-# # for (k in 16:35) {
-# #   set4_sum_beta_trt = cbind(set4_sum_beta_trt, rbind(min(range(get(paste0("set4_casual_", k)))), max(range(get(paste0("set4_casual_", k)))), NA, NA, get(paste0("set4_BSSL_", k))$means[(25 + 5*k +2)]))
-# # }
-# 
-# set3_sum_loss = c()
-# 
-# for (k in 1:15) {
[…]

### 2024-07-30 JASA-template.tex
Update from Matthias on overleaf.

@@
 \begin{highlights}
-\item *** TODO ***
-\item *** TODO ***
+\item Earlier a version of this paper was presented in ECSQARU 2023 conference. 
+Since then we have changed the following contents of the paper for this extended version. 
+\item A thorough introduction with additional image to express our problem
+formulation in a better way as well as discussion of previous works.
+\item Introduction of additional equations to justify and explain the
+causal inference model under confounding.
+\item We have put additional text for better explanation of Bayesian causal
+estimation model as well as the importance of a robust Bayesian analysis. These
+are accompanied by a new subsection discussing refit model, which can be
+used for better understanding and selection of a single model from set of causal models.
+\item A larger simulation study with more number of observations. Additionally
+we have introduced a new simulation setting where we vary the number of predictors
+for better understanding of the performance of our approach.
 \end{highlights}
@@
 To do so, we rely on $p$ observed quantities, called
-\emph{predictors}, denoted by $X\coloneqq$ $[X_1^T, \dots, X_n^T]^T$
+\emph{predictors}, denoted by $X\coloneqq$ $[X_1^{\top}, \dots, X_n^{\top}]^{\top}$
 where each $X_i\in\mathbb{R}^p$.
@@
 Now, let
-$\beta \coloneqq (\beta_1$, \dots, $\beta_p)^T$ denote the vector of regression
+$\beta \coloneqq (\beta_1$, \dots, $\beta_p)^{\top}$ denote the vector of regression
 coefficients
@@
 \begin{align}
+  &\delta(x_{n+1})\nonumber\\
+  &\coloneqq\mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) - \mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1}=0)
+\end{align}
+For our model, due to linearity of expectation, we have that
+\begin{align}
   \delta(x_{n+1})
-  &\coloneqq\mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) - \mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1}=0)
-\end{align}
-For our model, due to linearity of expectation, we have that
+  =\beta_T+&x_{n+1}\beta+\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) \nonumber\\
+  - &x_{n+1}\beta-\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =0)
+  \end{align}
+  {and because $\epsilon_{n+1}$ is independent from $X_{n+1}$ and $T_{n+1}$,}
   \begin{align}
   \delta(x_{n+1})
-  &=\beta_T+x_{n+1}\beta+\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) \\
-  &\quad - x_{n+1}\beta-\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =0)\\
-  \intertext{and because $\epsilon_{n+1}$ is independent from $X_{n+1}$ and $T_{n+1}$,}
   &=\beta_{T}.
@@
 That is, for another vector of regression coefficients 
-$\gamma\coloneqq(\gamma_1, \cdots, \gamma_p)^T$ we
+$\gamma\coloneqq(\gamma_1, \cdots, \gamma_p)^{\top}$ we
 assume
@@
   &=P(T_i^*>0)=P(u_i>-X_i\gamma)=1-P(u_i\le -X_i\gamma) \\
-  &=1-\Phi(-X_i\gamma)=\Phi(X_i\gamma)
+  &=1-\Phi(-X_i\gamma)=\Phi(X_i\gamma).
 \end{align}
@@
 \end{align}
-where $\nu \coloneqq (\beta_T, \beta^T, \gamma^T)^T$ and
+where $\nu \coloneqq (\beta_T, \beta^{\top}, \gamma^{\top})^{\top}$ and
 \begin{align}
@@
 \begin{align}
-	\label{eq:spike:slab:prior:beta:gamma}(\beta_j,\gamma_j)^T \mid \pi_{j}, \sigma^2 &\sim 
+	\label{eq:spike:slab:prior:beta:gamma}(\beta_j,\gamma_j)^{\top} \mid \pi_{j}, \sigma^2 &\sim 
 	\pi_{j}\normal\left( \begin{bmatrix}
@@
 	\end{bmatrix}\right)\\
-	\beta_T\mid \sigma^2 &\sim \normal\left(0, \sigma^2\right)\\
+	\beta_T\mid \sigma^2 &\sim \normal\left(0, \sigma^2\right)\label{eq:prior:causal}\\
         \frac{1}{\sigma^2}&\sim \text{Gamma}(a, b)\\
@@
 a concentration parameter.
-For the causal effect, we want to use a Gaussian distribution that 
+For the causal effect (\cref{eq:prior:causal}), we want to use a Gaussian distribution that 
 matches the scale of the noise term. Therefore, we consider $\beta_T\sim \normal(0,\sigma^2)$.
@@
 \begin{equation}
-    \beta_{T}^D(q) = \left(\left(\hat{T}^D\right)^T \hat{T}^D\right)^{-1}
-    \left(\hat{T}^D\right)^T \left[\hat{\beta}_{T}(q)\hat{T} 
+    \beta_{T}^D(q) = \left(\left(\hat{T}^D\right)^{\top} \hat{T}^D\right)^{-1}
+    \left(\hat{T}^D\right)^{\top} \left[\hat{\beta}_{T}(q)\hat{T} 
     + X_{S(q)}\left(\hat{\beta}_{S(q)} - \hat{\beta}^D_{S(q)}\right) 
@@
 scenarios, we consider different numbers of observations $n$ where
-$n=25+ 5k$ for $k=0,1,2,\dots,35$ and $p=50$
+$n=25+ 5k$ for $k=0,1,2,\dots,25$ and $p=50$
 predictors. This way, we check the efficiency of our method with varying level of information.
@@
 cases, we consider different numbers of predictors $p$ where
-$p=25+ 5k$ for $k=1,2,\dots,35$ and $n=100$
+$p=25+ 5k$ for $k=1,2,\dots,25$ and $n=100$
 subjects.
@@
 This may give us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
-When doing so, we need a prior judgement instead on what is a reasonable correlation between active predictors and the outcome.
+When doing so, we need a prior judgement on what is a reasonable correlation between active predictors and the outcome.
 
@@
 our method gives an interval estimate for the causal effect:
-the first(sixth) column gives the lower bound
-and the second(seventh) column gives the upper bound. We notice that our method is 
+column RBCE-l gives the lower bound
+and column RBCE-u gives the upper bound. We notice that our method is 
 somewhat in agreement with the other methods but is more consistent
@@
 In these simulations, our method tends
-to underestimate the causal effect.
+to underestimate the causal effect by a very short amount.
 This suggests that
-we may want to have a different value of $a$ for these different simulated datasets
-instead of a single value of $a=50$ for all of our analyses.
+we may want to seek for a different value of $a$ based on the sample size
+instead of a fixing $a=50$ for all of our analyses irrespective of the
+sample size.
 We can also see that the lower bound tends to improve
@@
 more information, the interval becomes smaller and converges towards
-a single value.
+a single value. Note that in some cases lower and upper bound for 
+RBCE is same. However, this is only due to approximation upto the
+second decimal place.
 
@@
 fixed number of sample in \cref{fig:comp:trt:pred,tab:causal2}. Similar to
-the first two settings, we notice that our method is somewhat in agreement with
-BSSL for the third setting. However, for the fourth setting, our method
-underestimates the treatment effect significantly (5\% in the worst case). This
-is somewhat in sync with the second setting, and a possible reason behind this
-could be the fact that in both the cases, the number of active $\beta_j$'s is
-higher than $\gamma_j$'s. This therefore, tends to reduce the value of treatment
-effect. A possible way to work around this issue can be using the `DSS' estimates
-of the regression coefficient and adjust the value of $\beta_T$.
-
-Besides this interesting result, we notice that all of the four methods perform
-perfectly in variable selection giving no misspecified variables. Therefore,
+our analyses with increasing number of observations, we notice that our method 
+is overall in agreement with
+other methods. However, our method slightly
+underestimates the treatment effect (5\% in the worst case). 
+This result is also similar to our
+analyses with increasing number of observations in \cref{tab:causal1}.
+Specifically, this can be understood from the result when $n=100$ and 
+$p=50$ in \cref{tab:causal1,tab:causal2}. In general this is not of great
+concern. But we can improve this estimation by using the refit method
+as described before.
+
+Besides this, we notice that all of the four methods perform
+perfectly in variable selection giving no misspecified variables this
+can also be understood from \cref{fig:comp:trt:pred} because
+in case of misspecified variables we get a very different value
+of the treatment effect. Therefore,
 we omit the table of variable selection for third and fourth scenarios.
@@
 Especially in risk-sensitive situations, such as medicine, it needs to
-be performed with utmost care as in many cases poor estimation can have severe adverse consequences.
+be performed with the utmost care as in many cases poor estimation can have severe adverse consequences.
 In this paper, we tackle this issue by proposing a robust Bayesian analysis of the causal 
@@
 we rely on sampling strategies to obtain the posterior bounds as well as performing 
-variable selection. In future, it will be interesting to derive inner approximation bounds
+variable selection. In the future, it will be interesting to derive inner approximation bounds
 for the posterior estimates to reduce the computational cost,

### 2024-07-30 JASA-template.tex
Reviewer 1: explain choice of linear model.
Note importance of having no interaction terms in the model to the reviewer, and make comment in paper.

@@
 treatment decision.
-Then we can define a linear model for the outcome
-so that
+Following the usual approach in the literature
+(see for instance \citep{winship99,HECKMAN1985}),
+we model the outcome using a linear model
 \begin{equation}
@@
 So, to find the causal effect, we simply need to estimate $\beta_T$.
+Note that, if interaction terms between $X$ and $T$ were present in
+the model (for example a term of the form, say, $\eta XT$ for some
+parameter vector $\eta$), that would result in a dependence of the
+causal effect on $x_{n+1}$.
 

### 2024-07-30 JASA-template.tex
Discuss limitations of link function.

--- 2024-07-30 JASA-template.tex
@@
 \linenumbers
+
+\newcommand{\added}[1]{\textcolor{blue}{#1}}
 
@@
 treatment decision.
-Then we can define a linear model for the outcome
-so that
+\added{%
+Following the usual approach in the literature
+(see for instance \citep{winship99,HECKMAN1985}),
+we model the outcome using a linear model%
+}
 \begin{equation}
@@
 So, to find the causal effect, we simply need to estimate $\beta_T$.
+\added{%
+Note that, if interaction terms between $X_i$ and $T_i$ were present in
+the model (for example a term of the form, say, $\eta X_iT_i$ for some
+parameter vector $\eta$), that would result in a dependence of the
+causal effect on $x_{n+1}$.%
+}
 
@@
 association between the treatment indicators $T$ and the predictors $X$.
-A common choice in the literature is to use a probit link function.
+A common choice in the literature is to use a probit link function
+\citep{winship99},
+\added{%
+though other link functions, such as the logit, can also be used
+\citep{HECKMAN1985}.%
+}
 In this way, we can

### 2024-07-30 JASA-template.tex
Add missing data reference in conclusion.

@@
 
+\added{%
+Another topic of interest pertinent to medical diagnosis is missing data.
+It has been shown that using bounded probability is particularly suitable
+for dealing with instances where data cannot be assumed missing at random
+\citep{decoomanzaffalon2004}.
+Incorporating robustness against missing data could lead to an interesting
+extension of the model in this paper.%
+}
 We also notice with our simulation studies that our

### 2024-07-30 JASA-template.tex
Paragraph.

--- 2024-07-30 JASA-template.tex
@@
 
+\added{%
+Another topic of interest pertinent to medical diagnosis is missing data.
+It has been shown that using bounded probability is particularly suitable
+for dealing with instances where data cannot be assumed missing at random
+\citep{decoomanzaffalon2004}.
+Incorporating robustness against missing data could lead to an interesting
+extension of the model in this paper.%
+}
+
 We also notice with our simulation studies that our

### 2024-07-30 JASA-template.tex
Use split for clean splitting of overfull hboxes.

@@
 \begin{align}
-  &\delta(x_{n+1})\nonumber\\
-  &\coloneqq\mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) - \mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1}=0)
-\end{align}
-For our model, due to linearity of expectation, we have that
-\begin{align}
+  \begin{split}
   \delta(x_{n+1})
-  =\beta_T+&x_{n+1}\beta+\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) \nonumber\\
-  - &x_{n+1}\beta-\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =0)
-  \end{align}
-  {and because $\epsilon_{n+1}$ is independent from $X_{n+1}$ and $T_{n+1}$,}
-  \begin{align}
+    &\coloneqq\mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) \\
+    &\qquad - \mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1}=0)
+  \end{split}
+  \intertext{For our model, due to linearity of expectation, we have that}
+  \begin{split}
   \delta(x_{n+1})
+    &=\beta_T
+      +x_{n+1}\beta+\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) \\
+    &\qquad\,\,\, %%% for alignment
+      -x_{n+1}\beta-\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =0)
+  \end{split}
+\intertext{and because $\epsilon_{n+1}$ is independent from $X_{n+1}$ and $T_{n+1}$,}
   &=\beta_{T}.

### 2024-07-30 JASA-template.tex
Note things fixed already by Tatha.
Indicate another fix from Tatha.

@@
 a concentration parameter.
-For the causal effect (\cref{eq:prior:causal}), we want to use a Gaussian distribution that 
-matches the scale of the noise term. Therefore, we consider $\beta_T\sim \normal(0,\sigma^2)$.
+For the causal effect \added{in \cref{eq:prior:causal}}, we want to use a Gaussian distribution that 
+matches the scale of the noise term. Therefore, we consider $\beta_T\added{\mid\sigma^2}\sim \normal(0,\sigma^2)$.
 
@@
 This may give us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
-When doing so, we need a prior judgement on what is a reasonable correlation between active predictors and the outcome.
+When doing so, we need \added{a prior judgement on what is a reasonable} correlation between active predictors and the outcome.
 

### 2024-07-30 JASA-template.tex
Final changes in response to reviewer 1 indicated.

@@
 our method gives an interval estimate for the causal effect:
-column RBCE-l gives the lower bound
-and column RBCE-u gives the upper bound. We notice that our method is 
+\added{column RBCE-l gives the lower bound
+and column RBCE-u gives the upper bound}. We notice that our method is 
 somewhat in agreement with the other methods but is more consistent
@@
 Especially in risk-sensitive situations, such as medicine, it needs to
-be performed with the utmost care as in many cases poor estimation can have severe adverse consequences.
+be performed \added{with the utmost care} as in many cases poor estimation can have severe adverse consequences.
 In this paper, we tackle this issue by proposing a robust Bayesian analysis of the causal 
@@
 we rely on sampling strategies to obtain the posterior bounds as well as performing 
-variable selection. In the future, it will be interesting to derive inner approximation bounds
+variable selection. \added{In the future,} it will be interesting to derive inner approximation bounds
 for the posterior estimates to reduce the computational cost,

### 2024-07-31 JASA-template.tex
Fix notation, add sentence to clarify strength of probit assumption.

@@
 Note that, if interaction terms between $X_i$ and $T_i$ were present in
-the model (for example a term of the form, say, $\eta X_iT_i$ for some
+the model (for example a term of the form, say, $T_iX_i\eta$ for some
 parameter vector $\eta$), that would result in a dependence of the
@@
 where $\Phi$ denotes the cumulative distribution function
-of a standard normal distribution. To incorporate this probit
+of a standard normal distribution.
+\added{%
+The key assumption made here is that
+there is a monotone relationship between
+the predictors and the probability of treatment.
+Here too, interaction terms between the $X_i$ could be added
+to form more complex models if so desired.%
+}
+
+To incorporate this probit
 link function, we model the $T_i$ as follows \citep{albert93}:

### 2024-07-31 JASA-template.tex
Add response to computational comment.
Add disclaimer around causal inference for reviewer #5.

@@
 
-But this
-can be problematic in the presence of confounding.
+\added{%
+Unfortunately, without fully controlled randomised trials and full
+knowledge of potential confounders, it is well understood that
+statistical models are unable to infer causality, as correlation
+does not imply causation especially in the presence of confounders.
+Still, it is highly desirable to try to adjust for confounding in
+our statistical models to the best of our ability. This is termed
+(perhaps somewhat unfortunately) \emph{causal inference} in the
+literature
+\citep{rubin1978,rosenbaum83,Robins1986ANA,winship99,stuart10,Zigler2014,wang2015,koch2018,Hahn2018,koch2020}.
+This is also the approach that we will follow here, under the
+disclaimer that whether actual causality can be inferred
+remains a subject of interpretation and conjecture specific to the
+sitation being studied.%
+}
+
+%%% MT to TB: removed this phrase for now to make text flow better
+% But this
+% can be problematic in the presence of confounding.
 \begin{figure}
@@
 we rely on sampling strategies to obtain the posterior bounds as well as performing 
-variable selection. \added{In the future,} it will be interesting to derive inner approximation bounds
+variable selection.
+\added{%
+A weakness of our approach is simulation efficiency,
+as we resorted to brute force optimisation.
+However, there is ample opportunity to improve computational aspects.%
+}
+\added{In the future,} it will be interesting to derive inner approximation bounds
 for the posterior estimates to reduce the computational cost,

### 2024-07-31 JASA-template.tex
Fix.

@@
 Unfortunately, without fully controlled randomised trials and full
-knowledge of potential confounders, it is well understood that
+knowledge of confounders, it is well understood that
 statistical models are unable to infer causality, as correlation

### 2024-07-31 JASA-template.tex
Response to elicitation of P.

@@
 not practical. Instead, we incorporate expert elicitation to define our model.
-For instance, we can consider $q\in \left[\underline{q}, \overline{q}\right]$
-where $p\underline{q}$ and $p\overline{q}$ represent the bounds of the prior expectation on the
-total number of variables present in either of the models.
+
+\added{%
+For instance, assume $\underline{k}$ and $\overline{k}$ represent the expert's bounds of the prior expectation on the
+total number of variables present in either of the models. We can then consider $q\in \left[\underline{k}/p, \overline{k}/p\right]$.%
+}
+
+\added{%
+We may also use the empirically observed correlations from the data directly.
+This may give us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
+When doing so, we need
+% \added{
+a prior judgement on what is a reasonable
+%}
+correlation between active predictors and the outcome.
+Say the expert judges that
+an active predictor has a correlation with the outcome
+that is typically between $\underline{c}$ and $\overline{c}$.
+Let $\overline{k}$ be the number of predictors with marginal correlation greater than $\underline{c}$
+and $\underline{k}$ be number of predictors with marginal 
+correlation greater than $\overline{c}$.
+%%% MT to TB: in retrospect, using \underline{k} to lower bound the
+%%% number of active variables is a bit strange... it seems like we're
+%%% treating variables with "too high" correlations as inactive;
+%%% should we simply set \underline{k} directly (e.g. 0, 1, or higher
+%%% if suitable) instead of using the correlations?
+As before, we can then consider $q\in \left[\underline{k}/p, \overline{k}/p\right]$.%
+}
 
@@
 \paragraph{Elicitation}
-One way to elicit $\mathcal{P}$
-is through a prior expected bound on the number of active predictors.
-Although we may do so directly,
-we may alternatively also use the empirically observed correlations from the data directly.
-This may give us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
-When doing so, we need \added{a prior judgement on what is a reasonable} correlation between active predictors and the outcome.
-
-So, say we judge, through expert elicitation, that
+
+\added{%
+To elicit $\mathcal{P}$,
+as discussed earlier,
+we use the empirically observed correlations from the data directly.
+We assume that, through expert elicitation,
 an active predictor has a correlation with the outcome
 that is typically between $0.15$ and $0.35$.
-Let $p_1$ be the number of predictors with marginal correlation greater than $0.15$
-and let $p_2$ be number of predictors with marginal 
+Let $\overline{k}$ be the number of predictors with marginal correlation greater than $0.15$
+and let $\underline{k}$ be number of predictors with marginal 
 correlation greater than $0.35$.
-Then $\mathcal{P}=[p_2/p , p_1/p]$ (note that $p_2\le p_1$) gives us a prior bound on the selection probability of each predictor, reflecting our prior expert judgement.
+Then $\mathcal{P}=[\underline{k}/p , \overline{k}/p]$ gives us a prior bound on the selection probability of each predictor, reflecting our prior expert judgement.%
+}
 

### 2024-07-31 JASA-template.tex
Eliminate redundant subsection.
Add rjags citation.

@@
 
-\subsection{Regression Model}
-
 Let an observational study on $n$ individuals give us
@@
 \paragraph{Initialisation} 
-To implement our method, we use \texttt{rjags} and for the other three
+To implement our method, we use \texttt{rjags} \added{\citep{rjags2023}} and for the other three
 methods we use the code provided in the appendix of \citep{koch2020}.

### 2024-07-31 JASA-template.tex
Small fix in caption.
Update figure for spike and slab (uses tikz now).

@@
 \tikzset{>={Stealth[length=3mm]}} % better arrow heads
+\usepackage{pgfplots}
 \usepackage{color}
@@
 
-\begin{figure}[h]
+\begin{figure}
 	\begin{center}
-		\includegraphics[width = 0.95\linewidth]{spike_slab_bi.pdf}
+\begin{tikzpicture}[scale=0.6]
+    \begin{axis}[
+        width=10cm,
+        view={60}{30},
+        xlabel={$x_1$},
+        ylabel={$x_2$},
+        ]
+        \addplot3[
+            surf,
+            samples=51,
+            domain=-7:7,
+            y domain=-7:7,
+        ] 
+        {exp(-0.5*(x^2 + y^2)/0.09) / (2*pi*0.09)};
+
+    \end{axis}
+\end{tikzpicture}
+\qquad
+\begin{tikzpicture}[scale=0.6]
+    \begin{axis}[
+        width=10cm,
+        view={60}{30},
+        xlabel={$x_1$},
+        ylabel={$x_2$},
+        ]
+        \addplot3[
+            surf,
+            samples=26,
+            domain=-7:7,
+            y domain=-7:7,
+        ] 
+        {exp(-0.5*(x^2 + y^2)/25) / (2*pi*25)};
+
+    \end{axis}
+\end{tikzpicture}
+          %\includegraphics[width = 0.95\linewidth]{spike_slab_bi.pdf}
 	\end{center}
-	\caption{Spike (left) and slab (right) components of a bivariate distribution for $\tau_0 = 0.001$, $\tau_1$ = 5 and $\sigma=1$.}
+	\caption{Spike (left) and slab (right) components of a bivariate distribution for $\tau_0 = 0.3$, $\tau_1 = 5$ and $\sigma=1$.}
 	\label{fig:ssbl}
@@
 	\end{tikzpicture}
-	\caption{Probabilistic graphical representation for causal inference with Bayesian hierarchical model.}
+	\caption{Probabilistic graphical representation for causal inference with \added{our} Bayesian hierarchical model.}
 	\label{fig:regress}

### 2024-07-31 JASA-template.tex
Reduce samples to make overleaf happy.

@@
             surf,
-            samples=51,
+            samples=11,
             domain=-7:7,
@@
             surf,
-            samples=26,
+            samples=11,
             domain=-7:7,

### 2024-08-02 JASA-template.tex
Update (Matthias).

@@
 \subsection{Robust Bayesian Analysis}
+\label{sec:robustbayesanalysis}
 
@@
 For instance, assume $\underline{k}$ and $\overline{k}$ represent the expert's bounds of the prior expectation on the
-total number of variables present in either of the models. We can then consider $q\in \left[\underline{k}/p, \overline{k}/p\right]$.%
+total number of variables present in either of the models. We can then consider $q\in \left[\underline{k}/p, \overline{k}/p\right]$.
+Using an interval for the prior expectation on the total number of active variables
+gives us a more cautious approach to specifying the prior distribution on variable selection,
+and thus more robust inferences.%
 }
 
+%%% TODO MT: add in review.txt
 \added{%
-We may also use the empirically observed correlations from the data directly.
+Alternatively, we may also use the empirically observed correlations from the data directly.
 This may give us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
@@
 an active predictor has a correlation with the outcome
-that is typically between $\underline{c}$ and $\overline{c}$.
-Let $\overline{k}$ be the number of predictors with marginal correlation greater than $\underline{c}$
-and $\underline{k}$ be number of predictors with marginal 
-correlation greater than $\overline{c}$.
-%%% MT to TB: in retrospect, using \underline{k} to lower bound the
-%%% number of active variables is a bit strange... it seems like we're
-%%% treating variables with "too high" correlations as inactive;
-%%% should we simply set \underline{k} directly (e.g. 0, 1, or higher
-%%% if suitable) instead of using the correlations?
-As before, we can then consider $q\in \left[\underline{k}/p, \overline{k}/p\right]$.%
+that lies typically in $[-1,-c]\cup[c,1]$, i.e.
+an absolute correlation larger than $c$.
+Let $k_c$ be the number of predictors with absolute marginal correlation greater than $c$.
+We could then consider $q=k_c/p$ for the prior, as it gives a prior estimate on the selection probability that is consistent with a prior predictive expectation of $k_c$ active variables.
+Now, it is in general quite difficult to specify an exact value for $c$ a priori.
+Therefore, we consider an interval $[\underline{c},\overline{c}]$ for $c$, leading to
+$q\in \left[k_{\overline{c}}/p, k_{\underline{c}}/p\right]$
+(note that $k_c$ is monotonically non-increasing in $c$).
 }
@@
 To elicit $\mathcal{P}$,
-as discussed earlier,
+as discussed earlier in \cref{sec:robustbayesanalysis},
 we use the empirically observed correlations from the data directly.
 We assume that, through expert elicitation,
-an active predictor has a correlation with the outcome
-that is typically between $0.15$ and $0.35$.
-Let $\overline{k}$ be the number of predictors with marginal correlation greater than $0.15$
-and let $\underline{k}$ be number of predictors with marginal 
-correlation greater than $0.35$.
+an active predictor has an absolute correlation with the outcome
+that is typically larger than a value lying in the interval $[0.15,0.35]$
+*** TODO TB cite some papers with values consistent with this ***.
+Let $\overline{k}$ be the number of predictors with absolute marginal correlation greater than $0.15$
+and let $\underline{k}$ be number of predictors with absolute marginal correlation greater than $0.35$.
 Then $\mathcal{P}=[\underline{k}/p , \overline{k}/p]$ gives us a prior bound on the selection probability of each predictor, reflecting our prior expert judgement.%

### 2024-08-02 JASA-template.tex
Sync reviews.txt with article on elicitation of P.
Answer to loss function idea for reviewer #5.

@@
 
-%%% TODO MT: add in review.txt
 \added{%
@@
 for the posterior estimates to reduce the computational cost,
-or to find better ways than brute force optimisation, such as for instance iterative importance sampling \citep{cruz22_importance}. Moreover, for the sake of
-illustration, we rely on simple loss functions
-%TB to MT: edited the conclusion
+or to find better ways than brute force optimisation, such as for instance iterative importance sampling \citep{cruz22_importance}.
+
+\added{To compare the different methods, we rely on simple loss functions
 associated with the predictor selection. However,
-this paradigm can be used for a generalised
-decision theoretic framework as well where based on
-the predictor selection we can formulate the 
-problem as a decision support problem for treating a subject.
+loss functions could be used for a generalised
+decision theoretic framework as well.
+For instance,
+the selection problem itself could be formulated as a decision problem,
+potentially leading to different selection thresholds or even selection systems that are directly based on a loss function.
+Additionally, we could formulate the 
+problem of whether or not to treat a subject as a decision support problem
+based on predictor selection.%
+}
 

### 2024-08-02 JASA-template.tex
Thank reviewers.
Respond to confusing terminology.

@@
 
-%%% MT to TB: what about "Robust Bayesian Analysis of Causal Inference in Medical Diagnosis and Treatment"
-%%% TB to MT: changed it
+%%% MT what about using "Robust Bayesian causal estimation" (name for our method) in the title, e.g. "Robust Bayesian causal estimation for causal inference in medical diagnosis"
 \title{Robust Bayesian Analysis of Causal Inference in Medical Diagnosis and Treatment}
@@
 \item A larger simulation study with more number of observations. Additionally
-we have introduced a new simulation setting where we vary the number of predictors
+we have introduced a new simulation where we vary the number of predictors
 for better understanding of the performance of our approach.
@@
 can have the option to ask for more data before reaching any conclusion. To achieve this,
-we consider a utility based framework with three possible 
-scenarios.
+we consider a utility based framework with three possible \added{outcomes}.
 
@@
 
-For the simulation studies, we consider 4 different settings. In each
-case, we generate the design matrix $X$ such that $X_i\sim\mathcal{N}(0, \Sigma)$
+For the simulation studies, we consider \added{2 different cases each with 2 sub-cases, amounting to 4 studies in total}. In each
+\alert{of these 4 studies}, we generate the design matrix $X$ such that $X_i\sim\mathcal{N}(0, \Sigma)$
 for $1\le i\le n$ where $\Sigma_{ij} = 0.3^{|i-j|}$. In this way, we 
@@
 
-These four cases can be split in two categories. In one category we consider the
-case where we have increasing number of observations. In the first category we have two
-sub cases, in the first case we consider all active variables to be confounders
-and in the second case we consider some active variables which are only related to
+\added{In case 1, we consider an} increasing number of observations. \added{We} have two
+sub-cases: in \alert{case 1a} we consider all active variables to be confounders
+and in the second \alert{case 1b} we consider some active variables which are only related to
 the outcome model. 
 \begin{description}
-    \item[Scenario 1a] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
-    \item[Scenario 1b] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
+    \item[\added{Case} 1a] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
+    \item[\added{Case} 1b] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
+\end{description}
+For both \added{case 1a and 1b}, we consider different numbers of observations $n$ where
+$n=25+ 5k$ for $k=0,1,2,\dots,25$ and $p=50$
+predictors. This way, we check the efficiency of our method with varying level of information.
+
+For \added{case 2}, we check our method for varying number of predictors 
+(and hence sparsity level, i.e.\ the percentage of active variables present in the model).
+Similar to \added{case 1} we also have two \added{sub-cases}:
+\begin{description}
+    \item[\added{Case} 2a] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
+    \item[\added{Case} 2b] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
 \end{description}
 For both
-scenarios, we consider different numbers of observations $n$ where
-$n=25+ 5k$ for $k=0,1,2,\dots,25$ and $p=50$
-predictors. This way, we check the efficiency of our method with varying level of information.
-
-For the second category, we check our method for varying number of predictors 
-(and hence sparsity level, i.e.\ the percentage of active variables present in the model).
-Similar to the first category we also have two sub cases:
-\begin{description}
-    \item[Scenario 2a] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
-    \item[Scenario 2b] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
-\end{description}
-For both
-cases, we consider different numbers of predictors $p$ where
+\added{case 2a and 2b}, we consider different numbers of predictors $p$ where
 $p=25+ 5k$ for $k=1,2,\dots,25$ and $n=100$
@@
 \Cref{tab:causal1} shows the results of estimating the causal effect $\beta_T$
-for the first and second scenarios.
+for \added{case 1a and 1b}.
 For reference, recall the true value is $\beta_T=4$. 
@@
 somewhat in agreement with the other methods but is more consistent
-in terms of estimating the causal effect in the first setting. However, this is not the
-case for the analysis with second dataset. We notice that our method tends to under
+in terms of estimating the causal effect in \added{case 1a}. However, this is not the
+case for the analysis with \added{case 1b}. We notice that our method tends to under
 estimate the causal effect. However, sometimes, other methods produce extreme 
@@
 % Mon Mar 25 09:52:08 2024
-\begin{table}[ht]
+\begin{table}
 \centering
@@
   \hline
- Case&  &  & 1 &  &  &  &  & 2 &  &  \\ 
-  \hline
- & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL \\ 
+ Case&  &  & \added{1a} &  &  &  &  & \added{1b} &  &  \\ 
+  \hline
+\added{Obs} & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL \\ 
   \hline
@@
 which counts the number of indeterminate predictors.
-From the table it can be seen that for the first scenario, our method
+From the table it can be seen that for \added{case 1}, our method
 abstains from identifying some variables for 
 $n \le 50$. Especially for $n=25$, our method identifies 39 and 35 variables as indeterminate
-for the first setting and second setting respectively. However,
+for \added{cases 1a and 1b} respectively. However,
 later on our method gives more precise results in terms of variable
@@
 \begin{table}[ht]
-\caption{Loss based on misspecification of active variables for first scenario.}\label{tab:misspec1}
+\caption{Loss based on misspecification of active variables for \added{case 1a}.}\label{tab:misspec1}
 \centering
@@
 \small
-\caption{Loss based on misspecification of active variables for second scenario}
+\caption{Loss based on misspecification of active variables for \added{case 1b}}
 \label{tab:misspec2}
@@
 of the treatment effect. Therefore,
-we omit the table of variable selection for third and fourth scenarios.
+we omit the table of variable selection for \added{cases 2a and 2b}.
 
@@
 We sincerely thank Jochen Einbeck for his contributions to an earlier version of this paper.
+We also thank all reviewers for their kind and constructive comments which helped improve the paper.
 

### 2024-08-02 JASA-template.tex
Fix typo.

@@
 For the simulation studies, we consider \added{2 different cases each with 2 sub-cases, amounting to 4 studies in total}. In each
-\alert{of these 4 studies}, we generate the design matrix $X$ such that $X_i\sim\mathcal{N}(0, \Sigma)$
+\added{of these 4 studies}, we generate the design matrix $X$ such that $X_i\sim\mathcal{N}(0, \Sigma)$
 for $1\le i\le n$ where $\Sigma_{ij} = 0.3^{|i-j|}$. In this way, we 
@@
 \added{In case 1, we consider an} increasing number of observations. \added{We} have two
-sub-cases: in \alert{case 1a} we consider all active variables to be confounders
-and in the second \alert{case 1b} we consider some active variables which are only related to
+sub-cases: in \added{case 1a} we consider all active variables to be confounders
+and in the second \added{case 1b} we consider some active variables which are only related to
 the outcome model. 

### 2024-08-02 JASA-template.tex
Fix.

@@
 sub-cases: in \added{case 1a} we consider all active variables to be confounders
-and in the second \added{case 1b} we consider some active variables which are only related to
+and in \added{case 1b} we consider some active variables which are only related to
 the outcome model. 

### 2024-08-02 JASA-template.tex
Resolve notational inconsistency with q and P.

@@
 For instance, assume $\underline{k}$ and $\overline{k}$ represent the expert's bounds of the prior expectation on the
-total number of variables present in either of the models. We can then consider $q\in \left[\underline{k}/p, \overline{k}/p\right]$.
+total number of variables present in either of the models. We can then consider $\mathcal{P}=\left[\underline{k}/p, \overline{k}/p\right]^p$.
 Using an interval for the prior expectation on the total number of active variables
@@
 Therefore, we consider an interval $[\underline{c},\overline{c}]$ for $c$, leading to
-$q\in \left[k_{\overline{c}}/p, k_{\underline{c}}/p\right]$
+$\mathcal{P}=\left[k_{\overline{c}}/p, k_{\underline{c}}/p\right]^p$
 (note that $k_c$ is monotonically non-increasing in $c$).
@@
 and let $\underline{k}$ be number of predictors with absolute marginal correlation greater than $0.35$.
-Then $\mathcal{P}=[\underline{k}/p , \overline{k}/p]$ gives us a prior bound on the selection probability of each predictor, reflecting our prior expert judgement.%
+Then $\mathcal{P}=[\underline{k}/p , \overline{k}/p]^p$ gives us a prior bound on the selection probability of each predictor, reflecting our prior expert judgement.%
 }

### 2024-08-23 basu_IJAR.tex
updated
submission version

--- 2024-08-02 JASA-template.tex
@@
 \usepackage{pgfplots}
+\pgfplotsset{compat=1.16}
 \usepackage{color}
-
+\usepackage{arydshln}
 \usepackage{hyperref}
@@
 %%% MT what about using "Robust Bayesian causal estimation" (name for our method) in the title, e.g. "Robust Bayesian causal estimation for causal inference in medical diagnosis"
-\title{Robust Bayesian Analysis of Causal Inference in Medical Diagnosis and Treatment}
+\title{\added{Robust Bayesian causal estimation for causal inference in medical diagnosis}}
 \author[1]{Tathagata Basu\corref{cor1}}
@@
 \begin{abstract}
-Causal inference aims to find the causal effect on subjects
+\added{Causal effect estimation is a critical task in statistical learning} that aims to find the causal effect on subjects
 by identifying causal links between
-a number of predictor (or, explanatory) variables and the outcome of a treatment.
-However, estimation of such causal links is extremely 
-difficult because the causal effects may vary from subject 
-to subject. Unfortunately, modelling the underlying heterogeneity explicitly makes the 
-problem practically unsolvable. Additionally, for high dimensional problems,
-we often need to find a subset of 
-predictor variables to initiate the treatment. However, current variable selection methods
-simply tend to maximise the predictive performance of the outcome model. This can be problematic when information and data are limited,
-as the consequence of mistreatment can be harmful. 
-So, in this paper, we develop a model for causal inference using
-robust Bayesian analysis, to allow for abstention when selecting
-predictor variables.
-We
-use a set of spike and slab priors 
-through prior elicitation to obtain robust estimates for
-both the treatment and outcome model. We are specifically interested 
-in the sensitivity of the causal effect in high dimensional causal inference
-as well as identifying predictor variables that are causally linked. However, indicator
-based variable selection can be deceptive, especially
-when the predictor is strongly associated with either the treatment or 
-the outcome, as this increases the posterior expectation of the selection
-indicators. To avoid that, we apply a post-hoc selection scheme
-which successfully removes negligible non-zero effects from the model,
-attaining a smaller set of 
-predictors.
-Finally, we illustrate
-our method using a synthetic dataset.
+a number of predictor (or, explanatory) variables and the outcome of a treatment. \added{In a regressional
+framework, we assign a treatment and outcome model to
+estimate the average causal effect.} Additionally, for high dimensional \added{regression problems, variable selection methods are also used} to find a subset of 
+predictor variables \added{that} maximises the predictive performance of the \added{underlying model for better estimation of the causal effect.}  In this paper, we \added{propose a different approach.
+We focus on the variable selection aspects of
+high dimensional causal estimation problem. We suggest a cautious
+Bayesian group LASSO framework for variable selection using prior sensitivity analysis.
+We  argue that in some cases, abstaining from selecting (or, rejecting) a predictor is beneficial and we should gather more information to obtain a more decisive result.
+We also show that for problems with very limited information, expert elicited variable selection can give us a more stable causal effect estimation as it avoids overfitting.
+Lastly, we carry a comparative study with
+synthetic dataset and show the applicability of our method in
+real-life situations.}
+
 \end{abstract}
@@
 \begin{keyword}
-  high dimensional data\sep variable selection\sep Bayesian analysis\sep imprecise probability
+  high dimensional \added{regresssion}\sep variable selection\sep Bayesian analysis\sep imprecise probability
 \end{keyword}
@@
 \begin{highlights}
-\item Earlier a version of this paper was presented in ECSQARU 2023 conference. 
-Since then we have changed the following contents of the paper for this extended version. 
-\item A thorough introduction with additional image to express our problem
-formulation in a better way as well as discussion of previous works.
-\item Introduction of additional equations to justify and explain the
-causal inference model under confounding.
-\item We have put additional text for better explanation of Bayesian causal
-estimation model as well as the importance of a robust Bayesian analysis. These
-are accompanied by a new subsection discussing refit model, which can be
-used for better understanding and selection of a single model from set of causal models.
-\item A larger simulation study with more number of observations. Additionally
-we have introduced a new simulation where we vary the number of predictors
-for better understanding of the performance of our approach.
+\item \added{A robust variable selection method for high dimensional causal estimation}
+
+\item \added{Prior sensitivity analysis of spike and slab group-LASSO.}
+
+\item \added{We show importance of elicitation in variable
+selection problem}
+
+\item \added{We show empirical behaviour of our method and
+its usefulness in medical diagnosis.}
+
 \end{highlights}
@@
 \end{frontmatter}
-
 \section{Introduction}\label{sec:intro}
@@
 remains a subject of interpretation and conjecture specific to the
-sitation being studied.%
+sitation being studied. In this regard, we also refer to \citep{imbiens_2022}
+where a detailed discussion on different interpretations of `causality'
+in statistics and econometrics can be found 
 }
@@
 estimating the causal effect. Several other methods were
-proposed to tackle confounders from a Bayesian perspective,
-see for instance \citep{Zigler2014,Hahn2018} among others.
-
-In this paper we take inspiration from the approach of \citet{koch2020}, who proposed a bi-level spike and slab prior for causal effect 
-estimation. They considered a data-driven adaptive approach to
+proposed to tackle confounders,
+see for instance \citep{Zigler2014,Hahn2018} among others \added{for
+	a Bayesian perspective and
+	\citep{zhang_2018} for a survey of methods for addressing unmeasured confounding.}
+
+In this paper, we take inspiration from the approach of \citet{koch2020}, who proposed a bi-level spike and slab prior for causal effect estimation \added{in high dimensional problems (i.e.~when number of predictors
+	is larger than the number of observation)}. 
+	They considered a data-driven adaptive approach to
 propose their prior which reduces the variance of the causal estimate. 
-Our approach is based on
+Our approach \added{however focuses on the other aspect of high
+dimensional causal inference problem, ie.~variable selection. To achieve that we rely} on \added{prior}
 sensitivity analysis, where instead of using a single prior, 
-we consider a set of priors \citep{BERGER1990303}. %TB to MT: added zaffalon paper
-Some works have been done in this approach of
-prior sensitivity analysis. \citet{zaffalon20a} 
+we consider a set of priors \citep{BERGER1990303}. 
+\added{Prior sensitivity analysis for causal inference has
+been a topic of interest lately.} \citet{zaffalon20a} 
 used credal networks in structured causal models
-for causal inference; \citet{raices_cruz22} suggested
-that causal effect estimation can be performed 
-through a meta analysis where robust Bayesian analysis 
-can be beneficial under severe uncertainty. 
-This motivates us to extend prior sensitivity analysis for 
-regression models. This is particularly beneficial, as for high dimensional regression problems 
-we have to rely on very limited data to perform our Bayesian analysis and 
-inference with a single prior
-is unreliable.
-To perform a prior sensitivity analysis, we use expert opinion to elicit a set of priors 
+for causal inference; \citet{raices_cruz22} \added{performed 
+	a meta analysis in a robust Bayesian framework for causal effect estimation. However, variable selection in causal estimation
+	problem has not been investigated in robust Bayesian framework.} 
+This motivates us to \added{investigate the role and applicability of} prior sensitivity analysis in high dimensional \added{causal estimation} problems. This is particularly beneficial, as
+in high dimensional problems,
+we have to rely on very limited \added{observations} to perform our Bayesian analysis and
+\added{as a result variable selection} with a single prior
+can be unreliable \citep{basu2023robust} \added{in many cases, Moreover, in causal effect estimation, failing to correctly identify a relation between the treatment effect and predictor can lead to
+harmful side-effects. Therefore, it
+is extremely important to adopt a cautious approach in selecting
+or rejecting a variable.}
+To \added{achieve this cautious paradigm and to} perform a prior sensitivity analysis, we rely on expert opinion to elicit a set of priors 
 based on empirical evidence. 
@@
 predictor selection
-in a framework where abstention has a relatively positive gain i.e.~
-when the cost of further tests/data collection is cheaper than
-mistreating a subject.
+in a framework where abstention has a relatively positive gain i.e.~when the cost of further tests/data collection is cheaper than
+\added{incorrect treatment} a subject.
 
@@
 predictor selection.
-We thereby construct a Bayesian group LASSO \citep{xu2015} type problem.
+We thereby construct a Bayesian group LASSO \added{(least absolute shrinkage and selection operator)} \citep{xu2015} type problem.
 To perform sensitivity analysis,
@@
 
-\section{Bayesian Causal Estimation}\label{sec:bayes}
+\section{\added{Robust} Bayesian Causal Estimation}\label{sec:bayes}
 
@@
 \citep{xu2015} type model. In this way, we can look into the posterior selection
-probability of each predictor. There are several
+probability of each predictor. \added{In this section, we formally introduce our
+	proposed methodology for causal estimation and we call it as
+	`robust Bayesian causal estimation' as we perform a robust
+	Bayesian analysis \citep{BERGER1990303} to achieve a cautious
+	variable selection paradigm. There are several
 ways to construct spike and slab priors for
-variable selection. Here, we consider a continuous type
-prior \citep{ishwaran2005} for faster posterior
+variable selection. In our method}, we consider a continuous type
+prior \citep{basu2023robust,ishwaran2005} for faster posterior
 computation.
@@
         ] 
-        {exp(-0.5*(x^2 + y^2)/0.09) / (2*pi*0.09)};
+        {exp(-0.5*(x^2 + y^2)/0.01) / (2*pi*0.01)};
 
@@
 	\end{center}
-	\caption{Spike (left) and slab (right) components of a bivariate distribution for $\tau_0 = 0.3$, $\tau_1 = 5$ and $\sigma=1$.}
+	\caption{\added{Spike (left) and slab (right) components of a bivariate distribution for $\tau_0 = 0.1$, $\tau_1 = 5$ and $\sigma=1$.}}
 	\label{fig:ssbl}
@@
 variable selection and performs well when we have sufficient data. 
-However, especially in the case of causal inference, we do not always have sufficient data. Moreover, 
+However, especially in many situations, we do not always have sufficient data. Moreover, 
 we also must be cautious about the side effects of a treatment.
@@
 with a suitable loss function. Instead, we
-assume that we can always revert any initial mistreatment by further treatments, 
+assume that we can always revert any initial incorrect treatment by further treatments, 
 and we can associate a loss function with the cost of further treatments.
@@
 Clearly, false positives may lead to unwanted side effects and
-false negatives may lead to mistreatment of the patient. Finally, we associate
+false negatives may lead to incorrect treatment of the patient. Finally, we associate
 a loss value $\ell_3$ for abstention from selecting
@@
 \added{%
-Alternatively, we may also use the empirically observed correlations from the data directly.
-This may give us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
+Alternatively, we may also use the empirically observed correlations from the data directly. This is particularly common in ultra high
+dimensional problems (when $p\gg n$) for reducing the dimensionality
+of the problem \citep{fan2008}. We can also use this approach
+to have us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
 When doing so, we need
@@
 
-\subsection{Variable selection and coefficient adjustment}
-For the co-variate selection, we look into the posterior expectation of $\pi_j$. 
-We consider the $j$-th predictor to be removed from both the
+\paragraph{Variable selection}
+\added{Ideally, we should check the joint posterior probability of $\pi_j$'s to select the most probable model.
+However, this means we have to search a space of dimension $2^p$, which is practically impossible when $p$ is very large.
+Instead, we can use the posterior of individual $\pi_j$ as \citet{barbieri2004} showed that median probability model gives the optimal model.
+That is we can set a threshold of $1/2$ to select a variable.
+Therefore,}
+we consider the $j$-th predictor to be removed from both the
 treatment and outcome model, if
@@
 
-In general, this framework is
-sufficient
-for variable selection. However, for
-model fitting and prediction, we need to evaluate the values 
-of the regression coefficients. For that we first need to find the set of active
+\subsection{\added{Coefficient Adjustment and Refit}}
+In general, \added{our} framework is
+intended
+for \added{robust} variable selection \added{in causal effect estimation problem}. However, \added{one might also be interested in}
+model fitting and prediction, \added{for that} we need to evaluate the values 
+of the regression coefficients. To do so, we first need to find the set of active
 predictors with respect to our prior expectation of the selection probability $q$.
@@
 
-\iffalse
-The DSS method explained
-above give us adjusted coefficient estimates for the treatment
-and outcome model. However, as result the causal effect estimate
-remains the same and modelling with such adjusted sparse effect 
-will contribute to the prediction error. Therefore, we need to 
-adjust the causal effect estimate as well. Let
-\begin{equation}
-    \hat{T}^D = \mathbb{I}\left(X_{S(q)}\hat{\gamma}^D_{S(q)} >0\right)
-    \quad\text{and}\quad
-    \hat{T} = \mathbb{I}\left(X\hat{\gamma}^q >0\right).
-\end{equation}
-and let $\beta_{T}^D(q)$
-be the causal effect after applying `DSS' and $\hat{\beta}_{T}(q)$ be the
-posterior estimate of the causal effect for any fixed $q\in\mathcal{P}$. Then
-the adjusted estimate is given by:
-\begin{equation}
-    \beta_{T}^D(q) = \left(\left(\hat{T}^D\right)^{\top} \hat{T}^D\right)^{-1}
-    \left(\hat{T}^D\right)^{\top} \left[\hat{\beta}_{T}(q)\hat{T} 
-    + X_{S(q)}\left(\hat{\beta}_{S(q)} - \hat{\beta}^D_{S(q)}\right) 
-    +X_{S^C(q)}\hat{\beta}_{S^C(q)}\right]
-\end{equation}
-where
-\begin{equation}
-    S^C(q)\coloneqq \left\{1,2,\cdots, p\right\} \neg S(q).
-\end{equation}
-\fi
-
-\subsection{Refit}
+\paragraph{Refit}
 
@@
 For both \added{case 1a and 1b}, we consider different numbers of observations $n$ where
-$n=25+ 5k$ for $k=0,1,2,\dots,25$ and $p=50$
+\added{$n=20+ 5k$ for $k=1,2,\dots,11$ and $p=50$}
 predictors. This way, we check the efficiency of our method with varying level of information.
@@
 \added{case 2a and 2b}, we consider different numbers of predictors $p$ where
-$p=25+ 5k$ for $k=1,2,\dots,25$ and $n=100$
+\added{$p=20+ 5k$ for $k=1,2,\dots,11$ and $n=40$}
 subjects.
 
-We present our analyses in \cref{tab:causal1,tab:misspec1,tab:misspec2}.
-For the sake of clarity we use the following accronyms: RBCE for 
+\begin{figure}
+	\begin{center}
+		\begin{tikzpicture}[node distance=2cm, auto]
+			\node (1) at (0,2) [circle,draw,align=center] {increasing \\ observation};
+			\node (2) at (4,2) [circle,draw,align=center] {increasing \\ predictor \\ (predictor)};
+			\node (a) at (0,-2) [circle,draw,align=center] {only \\ confounders};
+			\node (b) at (4,-2) [circle,draw,align=center] {outcome \& \\ confounders};
+			\draw[->] (1) to (a);
+			\draw[->] (1) to (b);
+			\draw[->] (2) to (a);
+			\draw[->] (2) to (b);
+			%\draw[->,dashed] (predictor) to (outcome);
+		\end{tikzpicture}
+	\end{center}
+	\caption{\added{Diagram of the simulation setup for comparative study.}}
+	\label{fig:experiment}
+\end{figure}
+
+\added{We use these studies to compare our method with three other approaches. From now on, for the sake of illustration,}
+we use the following acronyms: RBCE for 
 robust Bayesian causal estimation (our method); SSCE for spike and
@@
 estimation \citep{koch2020}; and BSSL for Bayesian spike and slab LASSO
-\citep{xu2015}. Note that since SSCE and BSSCE are formulated for problems
-where $p\le n$, we do not have any results for $n<50$ for these cases.
+\citep{xu2015}.
 
@@
 we use the empirically observed correlations from the data directly.
-We assume that, through expert elicitation,
-an active predictor has an absolute correlation with the outcome
-that is typically larger than a value lying in the interval $[0.15,0.35]$
-*** TODO TB cite some papers with values consistent with this ***.
+For expert elicitation, we follow the correlation guidelines mentioned in \citep{AKOGLU201891}
+where the authors provide \cref{tab:corr}.}
+
+\begin{table}
+	\centering
+	\caption{\added{Interpretation of the Pearson's and Spearman's correlation coefficients in absolute values}}
+	\begin{tabular}{|c|l|l|l|}
+		\hline
+		Absolute & Dancey \& Reidy\citep{dancey2007statistics} & Chan YH\citep{chan2003biostatistics} & Quinnipiac University \\
+		Correlation & (Psychology)& (Medicine) & (Politics)\\
+		\hline
+		1.0 & Perfect & Perfect & Perfect \\
+		0.9 & Strong & Very strong & Very strong \\
+		0.8 & Strong & Very Strong & Very strong \\
+		0.7 & Strong & Moderate & Very strong \\
+		0.6 & Moderate & Moderate & Strong \\
+		0.5 & Moderate & Fair & Strong \\
+		0.4 & Moderate & Fair & Strong \\
+		\cdashline{2-2}
+		0.3 & Weak & Fair & Moderate \\
+		0.2 & Weak & Poor & Weak \\
+		\cdashline{4-4}
+		0.1 & Weak & Poor & Negligible\\
+		0.0 & Zero & Zero & Zero \\
+		\hline
+	\end{tabular}
+	\label{tab:corr}
+\end{table}
+
+\added{From \cref{tab:corr}, we notice that the number of
+	labelled relations is different for different columns. As
+	a result it is difficult to obtain a single value for $c$
+	as mentioned in \cref{sec:robustbayesanalysis}. Instead,
+	we can disregard the last labelled relation (other than zero)
+	and assume that $c$ is typically larger than a value lying in the interval $[0.15,0.35]$
 	Let $\overline{k}$ be the number of predictors with absolute marginal correlation greater than $0.15$
@@
 methods we use the code provided in the appendix of \citep{koch2020}.
+\added{However, we modify to accommodate analysis with `high dimensional'
+	data.}
 For our method, we set $\tau_0=10^{-6}$ and $\tau_1=1$ to construct the
@@
 posterior estimates. For the other methods we use the in-built settings 
-to initiate the analyses.
+to initiate the analyses. \added{We also transform the data so that the data is centred around $0$
+for the outcome model to avoid having an intercept term.}
 
@@
 \added{column RBCE-l gives the lower bound
-and column RBCE-u gives the upper bound}. We notice that our method is 
-somewhat in agreement with the other methods but is more consistent
+and column RBCE-u gives the upper bound}. We notice that 
+\added{as we increase the number of observation our approach provides more precise estimates which shows that our set of priors is able to learn from the data.
+We also observe that our method gives an estimate close to the true value} and is more consistent
 in terms of estimating the causal effect in \added{case 1a}. However, this is not the
 case for the analysis with \added{case 1b}. We notice that our method tends to under
-estimate the causal effect. However, sometimes, other methods produce extreme 
-values which is not the case for our method. This can be observed in \cref{fig:comp:trt} as well. %Here, the true 
-%value is represented by the black straight line for $\beta_T = 4$.
-
-In these simulations, our method tends
-to underestimate the causal effect by a very short amount.
+estimate the causal effect \added{observations fewer than $55$}. However, sometimes, other methods produce extreme 
+values which is not the case for our method. This can be observed in \cref{fig:comp:trt} as well. \added{In the figure, the top row
+illustrates the case 1a where the left image shows the estimated
+causal effect with respect to observations and the right image
+shows the same within the range of $[3.8,4.2]$. Similarly, the
+bottom row represents the causal effect estimation for case 1b.
+In the figure, RBCE bounds are given by red lines; SSCE estimates by blue lines; BSSCE estimates by green lines; BSSL estimates by purple line; and true value by black lines.
+}
+
+\added{We see that for case 1b}, our method tends
+to underestimate the causal effect \added{for fewer number of observations.}
 This suggests that
 we may want to seek for a different value of $a$ based on the sample size
-instead of a fixing $a=50$ for all of our analyses irrespective of the
-sample size.
-We can also see that the lower bound tends to improve
-with increased number of observations: as we accumulate
-more information, the interval becomes smaller and converges towards
-a single value. Note that in some cases lower and upper bound for 
-RBCE is same. However, this is only due to approximation upto the
-second decimal place.
-
-% latex table generated in R 4.3.0 by xtable 1.8-4 package
-% Tue May 23 18:29:20 2023
-% latex table generated in R 4.3.2 by xtable 1.8-4 package
-% Mon Mar 25 09:52:08 2024
+instead of a fixing $a=50$ for all of our analyses. \added{We also provide the posterior distributions of the causal effect in \cref{fig:post:trt:obs} for different observations. Since we perform
+a prior sensitivity analysis therefore it is not possible to obtain a single value for percentiles.
+Instead we provide the maximum taken over all $q\in\mathcal{P}$ for 5 (green dotted line) and 25(green solid line) percentile whereas the minimum taken over all $q\in\mathcal{P}$ is provided for 95 (red dotted line) and 75 (red solid line) percentile.
+We notice that the true value of the causal effect is contained within the 25 and 75 percentile in all the cases except one.
+We can also see that we have different variability in the posteriors, this can be explained from the fact that we have different number of observations for our analyses.}
+
 \begin{table}
@@
 \tiny
-\caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
+\caption{\added{Comparison of different methods in estimating the causal effect for varying number of observations.
+On the left section (1a), we illustrate the results when all the active variables are confounders.
+On the right section (1b), we present the results when some variables are also related to the outcome model.}}
 \begin{tabular}{c|ccccc|ccccc}
@@
   \hline
-25 & 2.61 & 3.38 &  &  & 2.19 & 2.70 & 3.29 &  &  & 8.80 \\ 
-  30 & 3.14 & 3.56 &  &  & 3.99 & 3.01 & 3.54 &  &  & 9.02 \\ 
-  35 & 3.15 & 3.52 &  &  & 3.98 & 3.22 & 3.66 &  &  & 6.66 \\ 
-  40 & 3.60 & 3.75 &  &  & 3.98 & 3.20 & 3.70 &  &  & 4.42 \\ 
-  45 & 3.76 & 3.82 &  &  & 3.96 & 3.61 & 3.74 &  &  & 3.99 \\ 
-  50 & 3.79 & 3.84 & 3.99 & 4.01 & 3.99 & 3.75 & 3.79 & 9.04 & 9.36 & 4.01  \\ 
-  55 & 3.89 & 3.91 & 3.97 & 4.00 & 3.98 & 3.77 & 3.81 & 5.92 & 6.38 & 4.02 \\ 
-  60 & 3.93 & 3.95 & 3.99 & 4.00 & 3.98 & 3.76 & 3.77 & 3.89 & 3.50 & 4.03 \\ 
-  65 & 3.95 & 3.96 & 4.00 & 4.02 & 4.00 & 3.76 & 3.78 & 3.91 & 3.99 & 4.02 \\ 
-  70 & 3.94 & 3.96 & 4.01 & 4.05 & 4.00 & 3.77 & 3.79 & 4.01 & 3.96 & 4.03 \\ 
-  75 & 3.97 & 3.98 & 4.02 & 4.03 & 4.02  & 3.82 & 3.83 & 4.03 & 4.02 & 4.04 \\ 
-  80 & 3.96 & 3.98 & 4.02 & 4.05 & 4.01 & 3.83 & 3.85 & 4.04 & 4.05 & 4.05 \\ 
-  85 & 3.96 & 3.98 & 4.03 & 4.04 & 4.03 & 3.84 & 3.86 & 4.05 & 4.06 & 4.06 \\ 
-  90 & 3.97 & 3.99 & 4.05 & 4.07 & 4.04 & 3.87 & 3.88 & 4.06 & 4.04 & 4.05 \\ 
-  95 & 3.96 & 3.98 & 4.02 & 4.05 & 4.04 & 3.88 & 3.89 & 4.05 & 4.06 & 4.06 \\ 
-  100 & 3.95 & 3.98 & 4.03 & 4.05 & 4.04 & 3.88 & 3.89 & 4.07 & 4.06 & 4.07 \\ 
-  105 & 3.97 & 3.98 & 4.03 & 4.05 & 4.03 & 3.89 & 3.90 & 4.07 & 4.06 & 4.07 \\ 
-  110 & 3.97 & 3.99 & 4.03 & 4.05 & 4.03 & 3.90 & 3.91 & 4.07 & 4.05 & 4.07 \\ 
-  115 & 3.98 & 3.99 & 4.04 & 4.05 & 4.04 & 3.91 & 3.92 & 4.06 & 4.06 & 4.06 \\ 
-  120 & 3.98 & 3.99 & 4.04 & 4.05 & 4.03 & 3.91 & 3.92 & 4.04 & 4.05 & 4.04 \\ 
-  125 & 3.99 & 3.99 & 4.03 & 4.04 & 4.03 & 3.91 & 3.92 & 4.04 & 4.04 & 4.04 \\ 
-  130 & 3.98 & 3.99 & 4.02 & 4.04 & 4.02 & 3.92 & 3.93 & 4.03 & 4.04 & 4.04 \\ 
-  135 & 3.99 & 3.99 & 4.02 & 4.04 & 4.02 & 3.94 & 3.94 & 4.04 & 4.05 & 4.04 \\ 
-  140 &  3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 4.04 & 4.05 & 4.04 \\ 
-  145 & 3.99 & 3.99 & 4.03 & 4.04 & 4.03 & 3.95 & 3.95 & 4.05 & 4.05 & 4.05 \\ 
-  150 & 3.99 & 3.99 & 4.02 & 4.02 & 4.02 & 3.94 & 3.95 & 4.04 & 4.04 & 4.04 \\ 
+25 & 3.74 & 4.13 & 28.71 & 28.78 & 3.82 & 3.66 & 3.96 & 1.04 & 20.38 & 3.10 \\ 
+30 & 3.72 & 4.06 & 3.90 & 28.56 & 3.90 & 3.05 & 3.34 & 20.61 & 20.29 & -2.41 \\ 
+35 & 3.95 & 4.04 & 12.35 & 25.11 & 3.97 & 3.67 & 3.71 & 22.82 & 22.93 & 3.90 \\ 
+40 & 3.98 & 4.02 & 3.97 & 29.78 & 3.98 & 3.72 & 3.77 & 4.75 & 22.83 & 3.93 \\ 
+45 & 4.03 & 4.06 & 4.03 & 28.52 & 4.03 & 3.78 & 3.82 & 4.41 & 4.13 & 3.95 \\ 
+50 & 4.02 & 4.05 & 4.02 & 4.04 & 4.02 & 3.83 & 3.89 & 3.97 & 4.33 & 3.94 \\ 
+55 & 4.03 & 4.05 & 4.04 & 4.19 & 4.04 & 3.99 & 4.01 & 4.15 & 4.09 & 3.93 \\ 
+60 & 4.04 & 4.07 & 4.02 & 4.03 & 4.02 & 3.99 & 4.02 & 3.94 & 3.97 & 3.93 \\ 
+65 & 4.03 & 4.06 & 4.02 & 4.06 & 4.02 & 4.00 & 4.05 & 3.96 & 3.96 & 3.96 \\ 
+70 & 4.04 & 4.06 & 4.01 & 4.06 & 4.01 & 4.00 & 4.03 & 3.95 & 3.97 & 3.95 \\ 
+75 & 4.06 & 4.08 & 4.01 & 4.07 & 4.01 & 4.01 & 4.03 & 3.98 & 3.99 & 3.98 \\ 
 \hline
@@
     \centering
-    \includegraphics[width = 0.9\linewidth]{treat_obs.pdf}
-    \caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
+    \includegraphics[width = 0.95\linewidth]{treat_obs_rev.pdf}
+    \caption{\added{Comparison of different methods in estimating the causal effect for varying number of observations. The top (bottom) row
+    represents case 1a (case 1b). The left images show the estimated causal effects and right images show the same within $[3.8,4.2]$ to compare with true value. }}
     \label{fig:comp:trt}
 \end{figure}
-
-We also provide tables for the performance of variable selection in \cref{tab:misspec1,tab:misspec2}.
+\begin{figure}
+	\centering
+	\includegraphics[width = 0.95\linewidth]{treat_post_obs.png}
+	\caption{\added{Posterior of the causal effect for varying number of observations. The top (bottom) row
+			represents the posteriors for case 1a (case 1b).
+The green dotted (solid) lines represent the maximum of 5 (25) percentile taken over all $q$ and red dotted (solid) lines represent the minimum of 95 (75) percentile taken over all $q$.
+}}
+	\label{fig:post:trt:obs}
+\end{figure}
+
+We also provide tables for the performance of variable selection in \cref{fig:comp:loss:obs}.
 For variable selection, we use a loss function as described earlier.
@@
 We sum these losses together across all predictors
-to obtain the total loss, presented in \cref{tab:misspec1,tab:misspec2}.
-The table counts the number of
-false positives (FP) and false negatives (FN). For RBCE, we have an
-additional column (ID)
-which counts the number of indeterminate predictors.
-From the table it can be seen that for \added{case 1}, our method
+\added{and divide by the total number of predictors} to obtain the total \added{relative} loss.
+From the \added{figure} it can be seen that for \added{case 1}, our method
 abstains from identifying some variables for 
-$n \le 50$. Especially for $n=25$, our method identifies 39 and 35 variables as indeterminate
-for \added{cases 1a and 1b} respectively. However,
+$n \le 35$. However,
 later on our method gives more precise results in terms of variable
-selection. We also notice that the other methods tend to perform poorly
-in terms of variable selection in the second case giving away many FNs. 
-This can be seen in the bottom figure of \cref{fig:comp:trt}
-as well.
-% latex table generated in R 4.3.0 by xtable 1.8-4 package
-% Wed May 24 00:50:53 2023
-\begin{table}[ht]
-\caption{Loss based on misspecification of active variables for \added{case 1a}.}\label{tab:misspec1}
+selection. We also notice that the SSCE and BSSCE tend to perform poorly
+in terms of variable selection \added{case 1a}. \added{For} case 
+\added{1b, even BSSL performs poorly for fewer number of observation leading to a higher relative loss, unlike case 1a.}
+
+\begin{figure}
 	\centering
-\small
-\begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
-  \hline
-  &\multicolumn{4}{c||}{RBCE}&\multicolumn{3}{c||}{SSCE}
-  &\multicolumn{3}{c||}{BSSCE}&\multicolumn{3}{c|}{BSSL}\\
-  \cline{2-14}
- Obs & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
-  \hline
-25 & 1 & 0 & 39 & 8.8 &  &  &  &  &  &  & 9 & 1 & 10 \\ 
-  30 & 0 & 0 & 3 & 0.6 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
-  35 & 0 & 0 & 3 & 0.6 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
-  40 & 0 & 0 & 0 & 0 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
-  45 & 0 & 0 & 0 & 0 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
-  50 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  55 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  60 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  65 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  70 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  75 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  80 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  85 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  90 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  95 & 0 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  100 & 0 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  105 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  110 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  115 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  120 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  125 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  130 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  135 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  140 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  145 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  150 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-   \hline
-\end{tabular}
-\end{table}
-\begin{table}
-\small
-\caption{Loss based on misspecification of active variables for \added{case 1b}}
-\label{tab:misspec2}
-\begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
-  \hline
-  &\multicolumn{4}{c||}{RBCE}&\multicolumn{3}{c||}{SSCE}
-  &\multicolumn{3}{c||}{BSSCE}&\multicolumn{3}{c|}{BSSL}\\
-  \cline{2-14}
- Obs & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
-  \hline
-25 &   5 & 0 & 35 & 12 &  &  &  &  &  &  & 0 & 15 & 15 \\ 
-  30 & 0 & 2 & 7 & 3.4 &  &  &  &  &  &  & 0 & 14 & 14 \\ 
-  35 & 0 & 1 & 9 & 2.8 &  &  &  &  &  &  & 0 & 14 & 14 \\ 
-  40 & 0 & 0 & 21 & 4.2 &  &  &  &  &  &  & 0 & 10 & 10 \\ 
-  45 & 0 & 0 & 1 & 0.2 &  &  &  &  &  &  & 0 & 0 & 0 \\ 
-  50 & 0 & 0 & 0 & 0 & 0 & 15 & 15 & 0 & 15 & 15 & 0 & 0 & 0 \\ 
-  55 & 0 & 0 & 0 & 0 & 0 & 14 & 14 & 0 & 14 & 14 & 0 & 0 & 0 \\ 
-  60 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  65 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  70 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  75 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  80 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  85 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  90 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  95 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  100 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  105 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  110 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  115 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  120 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  125 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  130 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  135 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  140 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  145 & 0 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  150 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
-  \hline
-\end{tabular}
-\end{table}
+	\includegraphics[width = 0.95\linewidth]{loss_obs.pdf}
+	\caption{\added{Comparison of different methods in identifying the confounders for varying number of observations.
+One the left (right) we present case 1a (1b).
+The red line presents RBCE; blue line presents SSCE; green line presents BSSCE; and purple line
+	presents BSSL}}
+	\label{fig:comp:loss:obs}
+\end{figure}
 
 We show the result of our analyses with different number of predictors and
-fixed number of sample in \cref{fig:comp:trt:pred,tab:causal2}. Similar to
+fixed number of sample in \cref{tab:causal2,fig:comp:trt:pred}. Similar to
 our analyses with increasing number of observations, we notice that our method 
 is overall in agreement with
-other methods. However, our method slightly
-underestimates the treatment effect (5\% in the worst case). 
+\added{BSSL for case 2a}. However, our method tends to
+underestimate the treatment effect (approximately 8\% in the worst case) for \added{case 2b}. 
 This result is also similar to our
-analyses with increasing number of observations in \cref{tab:causal1}.
-Specifically, this can be understood from the result when $n=100$ and 
-$p=50$ in \cref{tab:causal1,tab:causal2}. In general this is not of great
-concern. But we can improve this estimation by using the refit method
-as described before.
-
-Besides this, we notice that all of the four methods perform
-perfectly in variable selection giving no misspecified variables this
-can also be understood from \cref{fig:comp:trt:pred} because
-in case of misspecified variables we get a very different value
-of the treatment effect. Therefore,
-we omit the table of variable selection for \added{cases 2a and 2b}.
+analyses with increasing number of observations in \cref{tab:causal1}
+\added{especially, for 1b with fewer observations than the predictors}.
+In general, \added{this can be explained from the fact that our prior sensitivity analysis gives us indeterminate variables in some cases and as a result the regression coefficients may not be shrinked close to zero leading to some deviations in the causal effect estimation.
+Similar to our analyses with varying observations, we also provide the posteriors of the causal effect in \cref{fig:post:trt:pred}.
+We notice that for case 2a the true value is always contained within 25 to 75 percentiles.
+However, for case 2b, the true values is not contained within 25 to 75 percentiles in 4 different cases, though they were inside 5 and 95 percentiles bound}.
+
+\added{Besides these, we also provide the performance in variable selection for case 2a and 2b in \cref{fig:comp:loss:pred}.
+We notice that our method performs extremely good and outperforms all the other methods in most cases.
+Only SSCE and BSSCE is able to match our accuracy in variable selection in few cases.
+}
 
@@
 \tiny
-\caption{Comparison of different methods in estimating the causal effect for varying number of predictors.}
+\caption{\added{Comparison of different methods in estimating the causal effect for varying number of predictors.
+On the left section (2a), we illustrate the results when all the active variables are confounders.
+On the right section (2b), we present the results when some variables are also related to the outcome model.}}
 \begin{tabular}{c|ccccc|ccccc}
   \hline
- Case&  &  & 1 &  &  &  &  & 2 &  &  \\ 
-  \hline
- & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL \\ 
-  \hline
-\hline
-30 & 3.93 & 3.95 & 3.99 & 4.00 & 3.99 & 3.89 & 3.90 & 4.02 & 4.02 & 4.01 \\ 
-  35 & 3.93 & 3.94 & 3.99 & 3.99 & 3.99 & 3.88 & 3.91 & 4.02 & 4.01 & 4.02 \\ 
-  40 & 3.93 & 3.95 & 3.99 & 4.01 & 3.99 & 3.89 & 3.91 & 4.01 & 4.03 & 4.01 \\ 
-  45 & 3.93 & 3.95 & 3.99 & 4.01 & 3.99 & 3.89 & 3.91 & 4.02 & 4.02 & 4.02 \\ 
-  50 & 3.94 & 3.95 & 3.99 & 4.00 & 3.99 & 3.89 & 3.91 & 4.01 & 4.02 & 4.02 \\ 
-  55 & 3.94 & 3.95 & 3.99 & 4.00 & 3.98 & 3.89 & 3.91 & 4.02 & 4.02 & 4.02 \\ 
-  60 & 3.94 & 3.95 & 3.99 & 4.01 & 3.99 & 3.89 & 3.91 & 4.02 & 4.02 & 4.02 \\ 
-  65 & 3.94 & 3.94 & 3.99 & 4.00 & 3.98 & 3.89 & 3.91 & 4.02 & 4.03 & 4.02 \\ 
-  70 & 3.93 & 3.95 & 3.99 & 4.00 & 3.99 & 3.89 & 3.90 & 4.02 & 4.02 & 4.02 \\ 
-  75 & 3.92 & 3.94 & 3.99 & 4.00 & 3.99 & 3.89 & 3.90 & 4.01 & 4.02 & 4.02 \\ 
-  80 & 3.92 & 3.94 & 3.99 & 3.99 & 3.99 & 3.89 & 3.90 & 4.01 & 4.01 & 4.02 \\ 
-  85 & 3.92 & 3.94 & 3.99 & 4.00 & 3.98 & 3.88 & 3.90 & 4.02 & 4.02 & 4.02 \\ 
-  90 & 3.92 & 3.93 & 3.99 & 4.00 & 3.99 & 3.88 & 3.90 & 4.02 & 4.01 & 4.02 \\ 
-  95 & 3.92 & 3.94 & 3.99 & 4.00 & 3.98 & 3.87 & 3.90 & 4.02 & 4.01 & 4.02 \\ 
-  100 & 3.92 & 3.94 & 3.99 & 3.99 & 3.98 & 3.88 & 3.90 & 4.02 & 4.02 & 4.01 \\ 
-  105 & 3.92 & 3.94 &  &  & 3.98 & 3.86 & 3.90 &  &  & 4.02 \\ 
-  110 & 3.92 & 3.94 &  &  & 3.99 & 3.87 & 3.90 &  &  & 4.01 \\ 
-  115 & 3.91 & 3.94 &  &  & 3.98 & 3.87 & 3.90 &  &  & 4.02 \\ 
-  120 & 3.91 & 3.94 &  &  & 3.99 & 3.87 & 3.91 &  &  & 4.02 \\ 
-  125 & 3.91 & 3.94 &  &  & 3.99 & 3.87 & 3.89 &  &  & 4.02 \\ 
-  130 & 3.92 & 3.94 &  &  & 3.99 & 3.86 & 3.90 &  &  & 4.01 \\ 
-  135 & 3.90 & 3.93 &  &  & 3.98 & 3.86 & 3.90 &  &  & 4.01 \\ 
-  140 & 3.91 & 3.93 &  &  & 3.99 & 3.85 & 3.89 &  &  & 4.01 \\ 
-  145 & 3.90 & 3.94 &  &  & 3.98 & 3.84 & 3.89 &  &  & 4.01 \\ 
-  150 & 3.90 & 3.93 &  &  & 3.99 & 3.85 & 3.88 &  &  & 4.02 \\ 
+ Case&  &  & \added{2a} &  &  &  &  & \added{2b} &  &  \\ 
+  \hline
+ \added{Pred} & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL \\ 
+  \hline
+ 25 & 3.90 & 3.94 & 29.44 & 4.07 & 3.98 & 3.61 & 3.70 & 3.98 & 4.07 & 3.94 \\ 
+ 30 & 3.89 & 3.96 & 3.97 & 4.04 & 3.98 & 3.61 & 3.69 & 4.03 & 4.19 & 3.94 \\ 
+ 35 & 3.96 & 4.00 & 4.75 & 4.15 & 3.98 & 3.62 & 3.73 & 3.95 & 6.77 & 3.92 \\ 
+ 40 & 3.96 & 4.01 & 3.98 & 4.55 & 3.97 & 3.56 & 3.71 & 3.98 & 22.76 & 3.92 \\ 
+ 45 & 3.98 & 4.01 & 3.98 & 4.28 & 3.98 & 3.72 & 3.75 & 17.81 & 21.77 & 3.93 \\ 
+ 50 & 3.98 & 4.05 & 10.55 & 29.61 & 3.98 & 3.65 & 3.77 & 22.70 & 22.43 & 3.95 \\ 
+ 55 & 3.98 & 4.02 & 29.61 & 29.56 & 3.97 & 3.74 & 3.81 & 4.60 & 14.69 & 3.94 \\ 
+ 60 & 3.99 & 4.07 & 3.97 & 29.72 & 3.98 & 3.77 & 3.83 & 6.88 & 21.84 & 3.94 \\ 
+ 65 & 4.02 & 4.11 & 3.97 & 29.67 & 3.97 & 3.77 & 3.88 & 3.94 & 22.23 & 3.92 \\ 
+ 70 & 4.01 & 4.12 & 5.70 & 28.93 & 3.98 & 3.74 & 3.86 & 4.34 & 22.54 & 3.91 \\ 
+ 75 & 4.00 & 4.11 & 3.97 & 29.96 & 3.98 & 3.73 & 3.84 & 6.46 & 18.41 & 3.93 \\ 
  \hline
@@
     \centering
-    \includegraphics[width = 0.9\linewidth]{treat_pred.pdf}
-    \caption{Comparison of different methods in estimating the causal effect for varying number of predictors.}
+    \includegraphics[width = 0.9\linewidth]{treat_pred_rev.pdf}
+    \caption{\added{Comparison of different methods in estimating the causal effect for varying number of predictors.}}
     \label{fig:comp:trt:pred}
 \end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width = 0.95\linewidth]{treat_post_pred.png}
+	\caption{\added{Posterior of the causal effect for varying number of predictors. The top (bottom) row
+			represents the posteriors for case 2a (case 2b).
+The green dotted (solid) lines represent the maximum of 5 (25) percentile taken over all $q$ and red dotted (solid) lines represent the minimum of 95 (75) percentile taken over all $q$.
+}}
+	\label{fig:post:trt:pred}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width = 0.9\linewidth]{loss_pred.pdf}
+	\caption{\added{Comparison of different methods in identifying the confounders for varying number of predictors.}}
+	\label{fig:comp:loss:pred}
+\end{figure}
+
+\paragraph{\added{Importance of prior elicitation}}\label{sec:importance:elicit}
+\added{Our method relies on expert elicitation and prior sensitivity analysis.
+So we also explore the effect of prior elicitation in identifying the active variables in our model.
+As mentioned earlier,
+	we consider $c$ is expected to be lying in the interval $[0.15,0.35]$
+	based on \cref{tab:corr}. However, we might want to choose a different
+	value for $c$.
+To compare the effect of having different value for $c$, we use the case 2b and set $c\in[0.2,0.4]$.
+That is we set a higher threshold for the correlation so that $\overline{k}$ becomes smaller and hence the prior expectation of the inclusion probability.
+We show our results in \cref{tab:comp:elict}.
+In the left hand side we elicit the expected number of active variables by setting the marginal correlation threshold $c\in[0.15,0.35]$ and the right we set $c\in[0.2,0.4]$.
+On the left hand side, we see our method tends to give higher number of indeterminate variables for fewer observations than the right hand side.
+As we increase the observation the higher threshold of marginal correlation plays an important role and we see more cases of false negative variables on the right hand side.
+}
+
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{c|ccc|ccc}
+		\hline
+		$[\underline{c},\overline{c}]$ &  &   $[0.15,0.35]$ &    &  & $[0.2,0.4]$ &    \\
+		\hline
+		Pred & FP & FN & ID & FP & FN & ID  \\ 
+		\hline
+		25 & 0 & 0 & 1 & 0 & 0 & 1  \\ 
+		30 & 0 & 0 & 3 & 0 & 0 & 1  \\ 
+		35 & 0 & 0 & 2 & 0 & 0 & 1  \\ 
+		40 & 0 & 0 & 2 & 0 & 0 & 1  \\ 
+		45 & 0 & 0 & 1 & 0 & 1 & 0  \\ 
+		50 & 0 & 0 & 1 & 0 & 1 & 0  \\ 
+		55 & 0 & 0 & 1 & 0 & 1 & 0  \\ 
+		60 & 0 & 0 & 1 & 0 & 1 & 0  \\ 
+		65 & 0 & 1 & 0 & 0 & 1 & 0  \\ 
+		70 & 0 & 1 & 0 & 0 & 1 & 0  \\ 
+		75 & 0 & 1 & 1 & 0 & 1 & 1  \\ 
+		\hline
+	\end{tabular}
+	\caption{\added{Effect of elicitation of the inclusion probability of the variables where FP stands for false positive, FN stands for false negative and ID stands for indeterminate. }}
+	\label{tab:comp:elict}
+\end{table}
 
@@
 framework is focused on the effect of prior elicitation on
-%%% MT to TB: I don't understand "confounder selection" - do you mean
-%%% "predictor selection" or "variable selection"? (also see later,
-%%% "confounder selection" is repeated a few times; I'm not sure
-%%% "confounder" is the correct term here, some variables may be
-%%% confounding but some may not; if it is appropriate then earlier in
-%%% the paper we should talk a bit more to explain why these variables
-%%% are all confounders and be consistent with our terminology)
 predictor selection
@@
 gives us a robust predictor selection scheme. In this way, we can abstain from selecting
-a predictor when the available data is not sufficient. We also propose a generalised
+a predictor when the available data is not sufficient. We also propose a more relaxed
 utility based framework, where we associate a loss for abstaining which can be interpreted 
-as the cost of further data collection. Finally, we illustrate our method with synthetic dataset
+as the cost of further data collection. We illustrate our method with synthetic dataset
 and compare with other state of the art Bayesian methods.
+\added{We could see that our elicitation based approach helps to have a more consistent causal effect estimation for very limited number of observations and avoids producing extreme values for the causal effect.
+Moreover, we also notice correct elicitation of the inclusion probability plays a crucial role in identifying the active variables and therefore can be extremely useful in cases where we need to design a treatment guideline with multiple bio-markers.
+}
 

### 2024-08-23 causal (copy).R

@@ -1,547 +1,0 @@
-library(mvtnorm)
-library(rjags)
-library(SSLASSO)
-library(monomvn)
-library(spikeslab)
-library(horseshoe)
-library(glmnet)
-library(ncvreg)
-library(xtable)
-library(foreach)
-library(doParallel)
-
-source("other_causal.R")
-
-
-set.seed(1e8)
-
-ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 50, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
-  MCMC = list()
-  
-  string = "
-  model {
-  
-    ## Likelihood
-    
-    for (i in 1:N) 
-    {
-      mean[i] = b_T * a[i] + inprod(x[i,], b) #+ b_int
-      y[i] ~ dnorm(mean[i], inv.var)
-      
-      a[i] ~ dbern(a_prob[i])
-      
-      probit(a_prob[i]) = a_dumm[i]
-      
-      a_dumm[i] = inprod(x[i,], g) #+ g_int
-    }
-    
-    # Prior on the mean
-    
-    b_T ~ dnorm(0,inv.var)
-    
-    # b_int ~ dnorm(0,inv.var)
-    # 
-    # g_int ~ dnorm(0,1)
-    # 
-    # prior on the precision
-    
-    inv.var ~ dgamma(gam_a, gam_b)
-    
-    sigma2 = 1 / inv.var
-    
-    ## Prior on the regression parameters 
-    
-    for (j in 1:p) 
-    {
-      # prior on the selection probability
-      
-      w[j] ~ dbeta(2*alpha, 2*(1-alpha))I(0.001,0.999)
-      
-      # Prior on beta
-      
-      spike[j] ~ dnorm(0, (inv.var / tau_0^2))
-      slab[j] ~ dnorm(0, (inv.var / tau_1^2))
-      
-      b[j] = w[j] * slab[j]  + (1 - w[j]) * spike[j]
-      
-      # Prior on gamma
-      
-      spikeg[j] ~ dnorm(0, (1 / tau_0^2))
-      slabg[j] ~ dnorm(0, (1 / tau_1^2))
-      
-      g[j] = w[j] * slabg[j]  + (1 - w[j]) * spikeg[j]
-    }
-    
-  }
-  "
-  params = c("b","b_T", "g", "sigma2", "w")
-  
-  if(n.cores>detectCores()){
[…]

### 2024-08-23 causal.R

@@ -10,24 +10,8 @@ library(xtable)
 library(foreach)
 library(doParallel)
 
-source("other_causal.R")
-
-
-set.seed(1e8)
-
-sig1 = matrix(nrow=50,ncol = 50)#diag(50)#
-
-for (i in 1:50) {
-  for (j in 1:50) {
-    sig1[i,j] = 0.3^abs(i-j)
-  }
-}
-
-ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 10, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
+ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 50, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
   MCMC = list()
-  x_scale = scale(x)
-  x_ctr = attr(x_scale,"scaled:center")
-  x_sd = attr(x_scale,"scaled:scale")
   
   string = "
   model {
@@ -36,18 +20,24 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 10, gam_b = 1,
     
     for (i in 1:N) 
     {
-      mean[i] = b_T * a[i] + inprod(x[i,], b)
+      mean[i] = b_T * a[i] + inprod(x[i,], b) #+ b_int
       y[i] ~ dnorm(mean[i], inv.var)
       
-      a[i] ~ dinterval(a_dumm[i], 0)
+      a_us[i] ~ dbern(a_prob[i])
       
-      a_dumm[i] ~ dnorm(inprod(x[i,], g), 1)
+      probit(a_prob[i]) = a_dumm[i]
+      
+      a_dumm[i] = inprod(x[i,], g) #+ g_int
     }
     
     # Prior on the mean
     
     b_T ~ dnorm(0,inv.var)
     
+    # b_int ~ dnorm(0,inv.var)
+    # 
+    # g_int ~ dnorm(0,1)
+    # 
     # prior on the precision
     
     inv.var ~ dgamma(gam_a, gam_b)
@@ -59,18 +49,21 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 10, gam_b = 1,
     for (j in 1:p) 
     {
       # prior on the selection probability
[…]

### 2024-08-23 causal_refit.R

@@ -1,89 +1,0 @@
-ISVS_d = function(x_b, x_g, y, a, tau_1 = 5, gam_a = 100, gam_b = 1, n.iter = 2000, n.adapt = 2000, n.sample = 5000, n.cores = 1){
-  MCMC = list()
-  
-  string = "
-  model {
-  
-    ## Likelihood
-    
-    for (i in 1:N) 
-    {
-      mean[i] = b_T * a[i] + inprod(x_b[i,], b) + b_int
-      y[i] ~ dnorm(mean[i], inv.var)
-      
-      a[i] ~ dbern(a_prob[i])
-      
-      probit(a_prob[i]) = a_dumm[i]
-      
-      a_dumm[i] = inprod(x_g[i,], g) + g_int
-    }
-    
-    # Prior on the mean
-    
-    b_T ~ dnorm(0,inv.var)
-    b_int ~ dnorm(0,inv.var)
-    g_int ~ dnorm(0,1)
-    
-    # prior on the precision
-    
-    inv.var ~ dgamma(gam_a, gam_b)
-    
-    sigma2 = 1 / inv.var
-    
-    ## Prior on the regression parameters 
-    
-    for (j in 1:p_b) 
-    {
-      
-      # Prior on beta
-      
-      b[j] ~ dnorm(0, inv.var / tau_1^2)
-      
-    }
-    
-    for (j in 1:p_g) 
-    {
-      
-      # Prior on beta
-      
-      g[j] ~ dnorm(0, 1 / tau_1^2)
-      
-    }
-    
-  }
-  "
-  params = c("b","b_T", "g", "sigma2")
-  
-
-  MCMC =  {
-    
-    ISVS <- textConnection(string, open = "r")
-    
-    data = list(
-      y = as.vector(y),
-      x_g = x_g,
-      x_b = x_b,
-      a = a,
-      p_g = ncol(x_g),
-      p_b = ncol(x_b),
-      N = nrow(x_g),
-      gam_a = gam_a,
-      gam_b = gam_b,
-      tau_1 = tau_1
-    )
-    
-    model <- jags.model(data = data, file = ISVS, n.chains = 1, n.adapt = n.adapt)
-    update(model, n.iter)
-    coda.samples(model, params, n.sample)
-  }
-  
-
-  b_post = as.matrix(MCMC[[1]])[,1:ncol(x_b)]
[…]

### 2024-08-23 causal_sims.R

@@ -1,0 +1,582 @@
+source("other_causal.R")
+source("causal.R")
+
+set.seed(1e8)
+
+##############################################################################################
+# data generation
+
+n = 100
+p = 75
+
+sig = matrix(nrow=p,ncol = p)
+
+for (i in 1:p) {
+  for (j in 1:p) {
+    sig[i,j] = 0.3^abs(i-j)
+  }
+}
+
+x_all = rmvnorm(n, sigma = sig)
+
+# data with setting 1
+
+beta1 = c(runif(5,-5,-1), runif(5,1,5))
+gamma1 = c(runif(5,-5,-1), runif(5,1,5))
+
+a1_dum_all = 1/(1 + exp(-x_all[,1:length(gamma1)] %*% gamma1))
+a1_all = sapply(1:n, function(j)rbinom(1,1,a1_dum_all[j]))
+
+y1_all = 4*a1_all + x_all[,1:length(beta1)] %*% beta1 + rnorm(n, sd = .1)
+
+# data with setting 2
+
+beta2 = c(runif(5,-5,-1), runif(10,1,5))
+
+a2_dum_all = 1/(1 + exp(-x_all[,1:length(gamma1)] %*% gamma1))
+a2_all = sapply(1:n, function(j)rbinom(1,1,a2_dum_all[j]))
+
+y2_all = 4*a2_all + x_all[,1:length(beta2)] %*% beta2 + rnorm(n, sd = .1)
+
+##############################################################################################
+# For increasing observation
+
+# setting1
+
+if(F){
+  
+  for (k in 1:11) { #
+    N = 20 + 5*k
+
+    x = x_all[1:N,1:50]
+    y1 = y1_all[1:N]
+    a1 = a1_all[1:N]
+
+    val1 = sum(abs(cor(x,y1))>0.15)
+    val2 = sum(abs(cor(x,y1))>0.35)
+
+    alph_min = min(val1, val2) /p
+    alph_max = max(val1, val2) /p
+
+    rbvs_obj = ISVS(x, y1, a1, alphas = seq(alph_min,alph_max, length.out = 11), tau_1 = 1, n.cores = 11)
+
+    prob_exp = matrix(unlist(lapply(rbvs_obj$probs, function(x)colMeans(as.matrix(x)))), nrow = length(rbvs_obj$Causal_post), byrow = T)
+
+    active = t(sapply(1:length(rbvs_obj$Causal_post), function(i) (prob_exp[i,] >= 0.5)))
+
[…]

### 2024-08-23 causal.R
cleaning

@@ -20,24 +20,20 @@ ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 50, gam_b = 1,
     
     for (i in 1:N) 
     {
-      mean[i] = b_T * a[i] + inprod(x[i,], b) #+ b_int
+      mean[i] = b_T * a[i] + inprod(x[i,], b) 
       y[i] ~ dnorm(mean[i], inv.var)
       
       a_us[i] ~ dbern(a_prob[i])
       
       probit(a_prob[i]) = a_dumm[i]
       
-      a_dumm[i] = inprod(x[i,], g) #+ g_int
+      a_dumm[i] = inprod(x[i,], g)
     }
     
     # Prior on the mean
     
     b_T ~ dnorm(0,inv.var)
     
-    # b_int ~ dnorm(0,inv.var)
-    # 
-    # g_int ~ dnorm(0,1)
-    # 
     # prior on the precision
     
     inv.var ~ dgamma(gam_a, gam_b)

### 2024-08-23 causal_sims.R

@@ -43,7 +43,7 @@ y2_all = 4*a2_all + x_all[,1:length(beta2)] %*% beta2 + rnorm(n, sd = .1)
 
 # setting1
 
-if(F){
+if(T){
   
   for (k in 1:11) { #
     N = 20 + 5*k
@@ -186,7 +186,7 @@ if(T){
 # setting2
 
 
-if(F){
+if(T){
   
   for (k in 1:11) {
     P = 20 + 5*k

### 2024-09-30 basu_IJAR.tex
second review

@@
 remains a subject of interpretation and conjecture specific to the
-sitation being studied. In this regard, we also refer to \citep{imbiens_2022}
+situation being studied. In this regard, we also refer to \citep{imbiens_2022}
 where a detailed discussion on different interpretations of `causality'
@@
 
-%%% MT to TB: removed this phrase for now to make text flow better
-% But this
-% can be problematic in the presence of confounding.
-\begin{figure}
+\begin{figure}[h]
 \begin{center}
@@
 In this paper, we take inspiration from the approach of \citet{koch2020}, who proposed a bi-level spike and slab prior for causal effect estimation \added{in high dimensional problems (i.e.~when number of predictors
-	is larger than the number of observation)}. 
+	is larger than the number of observations)}. 
 	They considered a data-driven adaptive approach to
@@
 predictor selection
-in a framework where abstention has a relatively positive gain i.e.~when the cost of further tests/data collection is cheaper than
-\added{incorrect treatment} a subject.
+in a framework where abstention has a relatively positive gain i.e.~when the cost of further tests/data collection is
+\added{lower than that of incorrectly treating} a subject.
 
@@
 \begin{equation}
-	Y_i =  T_i \beta_{T} + X_i\beta + \epsilon_i
+	Y_i =  T_i \beta_{T} + X_i\beta \added{+ \beta_0} + \epsilon_i
 \end{equation}
@@
 \begin{align}
-	P(T_i=1\mid X_i) = \Phi(X_i\gamma)
+	P(T_i=1\mid X_i) = \Phi(X_i\gamma\added{+\gamma_0})
 \end{align}
@@
 \begin{align}
-    T_i^* &= X_i\gamma +u_i \\
+    T_i^* &= X_i\gamma\added{+\gamma_0} +u_i \\
     T_i   &= \mathbb{I}(T_i^*>0)
@@
   P(T_i=1\mid X_i)
-  &=P(T_i^*>0)=P(u_i>-X_i\gamma)=1-P(u_i\le -X_i\gamma) \\
-  &=1-\Phi(-X_i\gamma)=\Phi(X_i\gamma).
+  &=P(T_i^*>0)=P(u_i>-X_i\gamma\added{-\gamma_0})=1-P(u_i\le -X_i\gamma\added{-\gamma_0}) \\
+  &=1-\Phi(-X_i\gamma\added{-\gamma_0})=\Phi(X_i\gamma\added{+\gamma_0}).
 \end{align}
@@
 $W\coloneqq\left(\begin{smallmatrix}Y \\ T^*\end{smallmatrix}\right)$
-and corresponding $2n\times(2p+1)$ dimensional design matrix
+and corresponding $2n\times(2p+\added{3})$ dimensional design matrix
 \begin{align}
@@
         \begin{bmatrix}
-           T_1 & X_1 & 0 \\
-           \vdots & \vdots & 0 \\
-           T_n & X_n & 0 \\
-           0 & 0 & X_1 \\
-           \vdots & \vdots & \vdots \\
-           0 & 0 & X_n
+           T_1 & X_1 & \added{1} & 0 & \added{0} \\
+           \vdots & \vdots & \added{\vdots} & 0 & \added{0} \\
+           T_n & X_n & \added{1} & 0 & \added{0} \\
+           0 & 0 & \added{0} & X_1 & \added{1} \\
+           \vdots & \vdots & \added{\vdots} & \vdots & \added{\vdots} \\
+           0 & 0 & \added{0} & X_n & \added{1}
         \end{bmatrix}
@@
 \end{align}
-where, $X_O \coloneqq [T, X]$ and $X_T \coloneqq X$. Then, considering the assumption of
+where, $X_O \coloneqq [T, X, \added{\mathbf{1}_n}]$ and $X_T \coloneqq [X, \added{\mathbf{1}_n}]$. Then, considering the assumption of
 Gaussian error terms, we have the following likelihood distribution
 \begin{align}
-	W\mid Z, \beta_T, \beta, \gamma, \sigma^2 \sim\normal\left(Z\nu, \Sigma\right)\label{eq:like:group},
+	W\mid Z, \beta_T, \beta, \added{\beta_0,} \gamma, \added{\gamma_0,} \sigma^2 \sim\normal\left(Z\nu, \Sigma\right)\label{eq:like:group},
 \end{align}
-where $\nu \coloneqq (\beta_T, \beta^{\top}, \gamma^{\top})^{\top}$ and
+where $\nu \coloneqq (\beta_T, \beta^{\top}, \added{\beta_0,} \gamma^{\top}\added{, \gamma_0})^{\top}$ and
 \begin{align}
@@
 	\beta_T\mid \sigma^2 &\sim \normal\left(0, \sigma^2\right)\label{eq:prior:causal}\\
+        \beta_0\mid \sigma^2 &\sim \normal\left(0, \sigma^2\right)\label{eq:prior:int:out}\\
+        \gamma_0 &\sim \normal\left(0, 1\right)\label{eq:prior:int:trt}\\
         \frac{1}{\sigma^2}&\sim \text{Gamma}(a, b)\\
@@
 \cref{fig:ssbl} (with fixed $\sigma=1$). We generate the spike component 
-with $\tau_0=0.001$ and the slab component with $\tau_1=5$.
-
-\begin{figure}
+with $\tau_0=0.1$ and the slab component with $\tau_1=5$.
+
+\begin{figure}[h]
 	\begin{center}
@@
         ylabel={$x_2$},
+        zlabel={pdf},
         ]
@@
 a concentration parameter.
-For the causal effect \added{in \cref{eq:prior:causal}}, we want to use a Gaussian distribution that 
-matches the scale of the noise term. Therefore, we consider $\beta_T\added{\mid\sigma^2}\sim \normal(0,\sigma^2)$.
+For the causal effect \added{in \cref{eq:prior:causal} and intercept term of the outcome model in \cref{eq:prior:int:out}}, we want to use a Gaussian distribution that 
+matches the scale of the noise term.
+Therefore, we consider $\beta_T\added{, \beta_0\mid\sigma^2}\sim \normal(0,\sigma^2)$.
+\added{Similarly, for the intercept of the treatment model we match the scale of the probit model and consider $\gamma_0\sim \mathcal{N}(0,1)$}.
 
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
@@
 		\node[params] (4) at (1.5,1.5) {$\gamma$};
+		\node[params] (15) at (1.5,0) {$\gamma_0$};
 		\node[latent] (5) at (4.5,1.5) {$T^*$};
 		\node[params] (6) at (1.5,-1.5) {$\beta$};
+		\node[params] (16) at (1.5,-3) {$\beta_0$};
 		\node[data] (7) at (3.5,-1.5) {$Y$};
@@
 		\path (14) edge[->]  (8);
+		\path (15) edge[->]  (5);
+		\path (16) edge[->]  (7);
 
@@
 of the problem \citep{fan2008}. We can also use this approach
-to have us a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
+to have a better prior judgement since any predictors that are correlated with the outcome are good candidates to be active.
 When doing so, we need
@@
 
+\added{For all four cases, we consider 20 replicates for an empirical statistical analysis to check the consistency and robustness of our approach.}
+
 \begin{figure}
@@
 		\begin{tikzpicture}[node distance=2cm, auto]
-			\node (1) at (0,2) [circle,draw,align=center] {increasing \\ observation};
-			\node (2) at (4,2) [circle,draw,align=center] {increasing \\ predictor \\ (predictor)};
-			\node (a) at (0,-2) [circle,draw,align=center] {only \\ confounders};
-			\node (b) at (4,-2) [circle,draw,align=center] {outcome \& \\ confounders};
+			\node (1) at (0,2) [circle,draw,align=center] {Case:\textbf{1}\\increasing \\ observation};
+			\node (2) at (4,2) [circle,draw,align=center] {Case:\textbf{2}\\increasing \\ predictor};
+			\node (a) at (0,-2) [circle,draw,align=center] {Subcase:\textbf{a}\\only \\ confounders};
+			\node (b) at (4,-2) [circle,draw,align=center] {Subcase:\textbf{b}\\outcome \& \\ confounders};
 			\draw[->] (1) to (a);
@@
 \citep{xu2015}.
+
+\paragraph{Metrics}
+
+\added{ 
+	As mentioned earlier, to perform our statistical analyses we use 20
+	replications. To evaluate the accuracy of estimation, we consider
+	mean and median values obtained from these 20 samples. Similarly, to check the
+	dispersion, we use standard deviation (denoted by sd), mean squared 
+	error with respect to the true value (denoted by MSE) and coverage (percentage) of the true value within the
+	95\% posterior credible interval (denoted by CI\%). Finally, 
+	to check the accuracy of variable selection, we evaluate false average positive numbers (denoted by FP), average false negative numbers (denoted
+	by FN) and average number of indeterminate variables (denoted by ID). Clearly
+	for other classical methods ID is equal to zero and therefore 
+	is not presented in the tables. We also define a misspecification loss
+	in the following way for illustration :
+	\begin{equation}
+		\text{Misspecification Loss} = \frac{FP}{TN} + \frac{FN}{TP} + 0.2* \frac{ID}{\text{Total no of predictors}}.
+	\end{equation}
+}
+
+\added{Note that since RBCE gives interval estimates, CI\% is calculated using the minimum of the lower bounds of credible intervals and the maximum of the upper bounds of credible intervals.}
 
@@
 To perform 
-our Bayesian analysis with \texttt{rjags}, we first consider an adaptive 
-stage with 2000 iterations followed by discarding of 2000 burn in samples 
-to refine the posteriors. We consider 5000 MCMC samples to compute the
+our Bayesian analysis with \texttt{rjags}, \added{we discard 500 burn in samples and consider 2500 MCMC samples} to compute the
 posterior estimates. For the other methods we use the in-built settings 
@@
 
+\begin{table}[ht]
+	\tiny
+	\centering
+	\caption{\added{Comparison of different methods for varying number of observations where all the active variables are confounders.}}
+	\label{tab:causal1a}
+	\subcaption{Accuracy in estimation of causal effect}
+	\begin{tabular}{l|cccc|cc|cc|cc}
+		\hline
+		\multicolumn{1}{l|}{}&
+		\multicolumn{4}{c|}{RBCE}&
+		\multicolumn{2}{c|}{SCCE}&
+		\multicolumn{2}{c|}{BSSCE}&
+		\multicolumn{2}{c}{BSSL}\\
+		\hline
+		\multicolumn{1}{l|}{Obs}&
+		\multicolumn{2}{c}{Mean}&
+		\multicolumn{2}{c|}{Median}&
+		\multicolumn{1}{c}{Mean}&
+		\multicolumn{1}{c|}{Median}&
+		\multicolumn{1}{c}{Mean}&
+		\multicolumn{1}{c|}{Median}&
+		\multicolumn{1}{c}{Mean}&
+		\multicolumn{1}{c}{Median}\\
+		\hline
+		25 & 2.6 & 3.5 & 2.5 & 3.6 & 20.4 & 20.4 & 20.9 & 20.7 & 15.6 & 19.0 \\ 
+		30 & 3.0 & 3.7 & 2.9 & 3.7 & 18.4 & 19.9 & 20.9 & 21.2 & 10.3 & 4.1 \\ 
+		35 & 3.3 & 3.8 & 3.3 & 3.8 & 15.8 & 18.5 & 19.6 & 19.8 & 7.2 & 4.1 \\ 
+		40 & 3.4 & 3.8 & 3.4 & 3.8 & 11.8 & 10.4 & 16.4 & 18.3 & 4.2 & 4.0 \\ 
+		45 & 3.6 & 3.8 & 3.6 & 3.8 & 8.1 & 4.1 & 11.0 & 11.3 & 4.1 & 4.0 \\ 
+		50 & 3.7 & 3.8 & 3.6 & 3.8 & 7.5 & 4.1 & 7.8 & 4.2 & 4.0 & 4.0 \\ 
+		55 & 3.7 & 3.9 & 3.7 & 3.9 & 4.5 & 4.0 & 4.4 & 4.0 & 4.0 & 4.0 \\ 
+		60 & 3.8 & 3.9 & 3.8 & 3.9 & 4.2 & 4.0 & 4.0 & 4.0 & 4.0 & 4.0 \\ 
+		65 & 3.8 & 3.9 & 3.8 & 3.9 & 4.1 & 4.0 & 4.0 & 4.0 & 4.0 & 4.0 \\ 
+		70 & 3.8 & 3.9 & 3.8 & 3.9 & 4.0 & 4.0 & 4.0 & 4.0 & 4.0 & 4.0 \\ 
+		75 & 3.8 & 3.9 & 3.8 & 3.9 & 4.0 & 4.0 & 4.0 & 4.0 & 4.0 & 4.0 \\ 
+		\hline
+	\end{tabular}
+	\subcaption{Dispersion of estimated causal effect: values less than 0.05 are replaced with *}
+	\begin{tabular}{l|rrrrr|rrr|rrr|rrr}
+		\hline
+		\multicolumn{1}{l|}{}&
+		\multicolumn{5}{c|}{RBCE}&
+		\multicolumn{3}{c|}{SCCE}&
+		\multicolumn{3}{c|}{BSSCE}&
+		\multicolumn{3}{c}{BSSL}\\
+		\hline
+		\multicolumn{1}{l|}{Obs}&
+		\multicolumn{2}{c}{sd}&
+		\multicolumn{2}{c}{MSE}&
+		\multicolumn{1}{c|}{CI\%}&
+		\multicolumn{1}{c}{sd}&
+		\multicolumn{1}{c}{MSE}&
+		\multicolumn{1}{c|}{CI\%}&
+		\multicolumn{1}{c}{sd}&
+		\multicolumn{1}{c}{MSE}&
+		\multicolumn{1}{c|}{CI\%}&
+		\multicolumn{1}{c}{sd}&
+		\multicolumn{1}{c}{MSE}&
+		\multicolumn{1}{c}{CI\%}
+		\\
+		\hline
+		25 & 0.4 & 0.5 & 0.5 & 2.1 & 100 & 3.1 & 277.4 & 0 & 3.0 & 295.1 & 0 & 9.3 & 217.6 & 20 \\ 
+		30 & 0.4 & 0.5 & 0.2 & 1.3 & 100 & 5.9 & 239.9 & 15 & 2.7 & 291.9 & 0 & 8.4 & 107.2 & 60 \\ 
+		35 & 0.3 & 0.4 & 0.1 & 0.7 & 100 & 7.2 & 187.0 & 25 & 4.3 & 261.4 & 10 & 6.7 & 53.7 & 80 \\ 
+		40 & 0.2 & 0.3 & 0.1 & 0.4 & 100 & 7.8 & 118.7 & 45 & 6.4 & 191.7 & 20 & 0.9 & 0.7 & 95 \\ 
+		45 & 0.2 & 0.2 & 0.1 & 0.2 & 100 & 6.0 & 50.7 & 60 & 6.6 & 90.5 & 45 & 0.5 & 0.3 & 95 \\ 
+		50 & 0.1 & 0.2 & * & 0.1 & 100 & 5.3 & 39.6 & 65 & 5.5 & 43.0 & 65 & 0.1 & * & 100 \\ 
+		55 & 0.1 & 0.1 & * & 0.1 & 100 & 1.6 & 2.6 & 95 & 1.6 & 2.5 & 95 & 0.1 & * & 95 \\ 
+		60 & 0.1 & 0.1 & * & 0.1 & 100 & 0.9 & 0.9 & 90 & 0.1 & * & 100 & * & * & 95 \\ 
+		65 & 0.1 & 0.1 & * & * & 100 & 0.5 & 0.3 & 95 & 0.1 & * & 95 & * & * & 95 \\ 
+		70 & 0.1 & 0.1 & * & * & 100 & * & * & 95 & * & * & 95 & * & * & 95 \\ 
+		75 & 0.1 & 0.1 & * & * & 100 & * & * & 95 & * & * & 95 & * & * & 95 \\ 
+		\hline
+	\end{tabular}
+	\subcaption{Accuracy of variable selection: all the values are averaged over 20 replications}
+	\begin{tabular}{l|rrr|rr|rr|rr}
+		\hline
+		\multicolumn{1}{l|}{}&
+		\multicolumn{3}{c|}{RBCE}&
+		\multicolumn{2}{c|}{SCCE}&
+		\multicolumn{2}{c|}{BSSCE}&
+		\multicolumn{2}{c}{BSSL}\\
+		\hline
+		\multicolumn{1}{l|}{Obs}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c}{FN}&
+		\multicolumn{1}{c|}{ID}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c|}{FN}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c|}{FN}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c}{FN}
+		\\
+		\hline
+		25 & 0.7 & 0.2 & 30.4 & 0 & 9.8 & 0 & 10 & 1.4 & 7.1 \\ 
+		30 & 0 & 0 & 19.2 & 0 & 8.8 & 0 & 10 & 0 & 3.8 \\ 
+		35 & 0 & 0 & 8.1 & 0 & 7.3 & 0 & 9.4 & 0 & 2.0 \\ 
+		40 & 0 & 0 & 3.0 & 0 & 5.1 & 0 & 8.2 & 0 & 0.2 \\ 
+		45 & 0 & 0 & 0.6 & 0 & 2.9 & 0 & 5.0 & 0 & 0 \\ 
+		50 & 0 & 0 & 0.4 & 0 & 2.9 & 0 & 3.0 & 0 & 0 \\ 
+		55 & 0 & 0 & 0 & 0 & 0.6 & 0 & 0.4 & 0 & 0 \\ 
+		60 & 0 & 0 & 0 & 0 & 0.2 & 0 & 0 & 0 & 0 \\ 
+		65 & 0 & 0 & 0 & 0 & 0.2 & 0 & 0 & 0 & 0 \\ 
+		70 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+		75 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+		\hline
+	\end{tabular}
+\end{table}
+
 \paragraph{Results}
-\Cref{tab:causal1} shows the results of estimating the causal effect $\beta_T$
-for \added{case 1a and 1b}.
+\Cref{tab:causal1a} shows the results of estimating the causal effect $\beta_T$
+for \added{case 1a}.
 For reference, recall the true value is $\beta_T=4$. 
 As we perform a sensitivity analysis,
-our method gives an interval estimate for the causal effect:
-\added{column RBCE-l gives the lower bound
-and column RBCE-u gives the upper bound}. We notice that 
+our method gives an interval estimate for the causal effect.
+\added{So we present mean, median, sd and MSE for RBCE using two columns where the left columns give the lower bounds
+and the right columns give the upper bounds}. We notice that 
 \added{as we increase the number of observation our approach provides more precise estimates which shows that our set of priors is able to learn from the data.
-We also observe that our method gives an estimate close to the true value} and is more consistent
-in terms of estimating the causal effect in \added{case 1a}. However, this is not the
-case for the analysis with \added{case 1b}. We notice that our method tends to under
-estimate the causal effect \added{observations fewer than $55$}. However, sometimes, other methods produce extreme 
-values which is not the case for our method. This can be observed in \cref{fig:comp:trt} as well. \added{In the figure, the top row
-illustrates the case 1a where the left image shows the estimated
-causal effect with respect to observations and the right image
-shows the same within the range of $[3.8,4.2]$. Similarly, the
-bottom row represents the causal effect estimation for case 1b.
-In the figure, RBCE bounds are given by red lines; SSCE estimates by blue lines; BSSCE estimates by green lines; BSSL estimates by purple line; and true value by black lines.
-}
-
-\added{We see that for case 1b}, our method tends
-to underestimate the causal effect \added{for fewer number of observations.}
-This suggests that
-we may want to seek for a different value of $a$ based on the sample size
-instead of a fixing $a=50$ for all of our analyses. \added{We also provide the posterior distributions of the causal effect in \cref{fig:post:trt:obs} for different observations. Since we perform
-a prior sensitivity analysis therefore it is not possible to obtain a single value for percentiles.
-Instead we provide the maximum taken over all $q\in\mathcal{P}$ for 5 (green dotted line) and 25(green solid line) percentile whereas the minimum taken over all $q\in\mathcal{P}$ is provided for 95 (red dotted line) and 75 (red solid line) percentile.
-We notice that the true value of the causal effect is contained within the 25 and 75 percentile in all the cases except one.
-We can also see that we have different variability in the posteriors, this can be explained from the fact that we have different number of observations for our analyses.}
-
-\begin{table}
+We also observe that our method tends to under estimate the causal effect.
+However, our approach does not produce any extreme values} and is more consistent
+in terms of estimating the causal effect, \added{especially for fewer number of observations which is not the case for SSCE and BSSCE.
+For BSSL we notice that median value is close to the true value for fewer number of observations but mean value is higher which shows that for some experiments BSSL tend to produce extreme values.
+This can also be from the table for dispersion in estimation where BSSL tends to have a high MSE and lower CI\% for fewer number of observations.}
+
+\added{We also provide the performance in variable selection in \cref{tab:causal1a}. We notice that for fewer number of observations
+our method tends to give many indeterminate variables but this number gradually decreases as we increase the number of observations.
+However, our elicitation based approach ensures that we have very few false negative and false positive variables which is not the case for other approaches.}
+
+\begin{table}[ht]
+	\tiny
 	\centering
-\tiny
+	\caption{\added{Comparison of different methods in estimating the causal effect for varying number of observations where some variables are only related to the outcome model.}}
+	\label{tab:causal1b}
+	\subcaption{Accuracy in estimation of causal effect}
+	\begin{tabular}{c|cccc|cc|cc|cc}
+		\hline
+		\multicolumn{1}{c|}{}&
+		\multicolumn{4}{c|}{RBCE}&
+		\multicolumn{2}{c|}{SCCE}&
+		\multicolumn{2}{c|}{BSSCE}&
+		\multicolumn{2}{c}{BSSL}\\
+		\hline
+		\multicolumn{1}{c|}{Obs}&
+		\multicolumn{2}{c}{Mean}&
+		\multicolumn{2}{c|}{Median}&
+		\multicolumn{1}{c}{Mean}&
+		\multicolumn{1}{c|}{Median}&
+		\multicolumn{1}{c}{Mean}&
+		\multicolumn{1}{c|}{Median}&
+		\multicolumn{1}{c}{Mean}&
+		\multicolumn{1}{c}{Median}\\
+		\hline
+		25 & 2.8 & 3.7 & 2.8 & 3.8 & 25.5 & 25.0 & 26.2 & 25.5 & 20.5 & 24.1 \\ 
+		30 & 3.2 & 4.1 & 3.1 & 4.1 & 25.4 & 25.1 & 26.4 & 26.2 & 15.8 & 10.8 \\ 
+		35 & 3.7 & 4.3 & 3.7 & 4.3 & 22.3 & 25.1 & 26.2 & 26.0 & 10.9 & 4.0 \\ 
+		40 & 3.9 & 4.3 & 3.9 & 4.4 & 21.4 & 24.6 & 26.0 & 25.4 & 4.7 & 4.0 \\ 
+		45 & 3.9 & 4.2 & 3.9 & 4.2 & 18.7 & 23.9 & 22.5 & 25.2 & 4.0 & 4.0 \\ 
+		50 & 3.9 & 4.2 & 3.9 & 4.2 & 9.6 & 4.0 & 13.2 & 6.2 & 4.0 & 4.0 \\ 
+		55 & 4.0 & 4.1 & 3.9 & 4.2 & 7.1 & 4.0 & 9.3 & 4.1 & 4.0 & 4.0 \\ 
+		60 & 4.0 & 4.1 & 4.0 & 4.1 & 4.0 & 4.0 & 4.0 & 4.0 & 4.0 & 4.0 \\ 
+		65 & 4.0 & 4.1 & 4.0 & 4.1 & 4.6 & 4.0 & 4.5 & 4.0 & 4.0 & 4.0 \\ 
+		70 & 4.0 & 4.1 & 4.0 & 4.1 & 4.0 & 4.0 & 4.0 & 4.0 & 4.0 & 4.0 \\ 
+		75 & 4.0 & 4.1 & 4.0 & 4.1 & 4.0 & 4.0 & 4.0 & 4.0 & 4.0 & 4.0 \\ 
+		\hline
+	\end{tabular}
+	\subcaption{Dispersion of estimated causal effect: values less than 0.05 are replaced with *}
+	\begin{tabular}{c|rrrrr|rrr|rrr|rrr}
+		\hline
+		\multicolumn{1}{c|}{}&
+		\multicolumn{5}{c|}{RBCE}&
+		\multicolumn{3}{c|}{SCCE}&
+		\multicolumn{3}{c|}{BSSCE}&
+		\multicolumn{3}{c}{BSSL}\\
+		\hline
+		\multicolumn{1}{c|}{Obs}&
+		\multicolumn{2}{c}{sd}&
+		\multicolumn{2}{c}{MSE}&
+		\multicolumn{1}{c|}{CI\%}&
+		\multicolumn{1}{c}{sd}&
+		\multicolumn{1}{c}{MSE}&
+		\multicolumn{1}{c|}{CI\%}&
+		\multicolumn{1}{c}{sd}&
+		\multicolumn{1}{c}{MSE}&
+		\multicolumn{1}{c|}{CI\%}&
+		\multicolumn{1}{c}{sd}&
+		\multicolumn{1}{c}{MSE}&
+		\multicolumn{1}{c}{CI\%}
+		\\
+		\hline
+		25 & 0.4 & 0.6 & 0.4 & 1.6 & 100 & 5.6 & 492.2 & 10 & 5.2 & 517.1 & 0 & 10.4 & 375.8 & 10 \\ 
+		30 & 0.6 & 0.6 & 0.3 & 0.9 & 100 & 5.8 & 488.8 & 5 & 5.0 & 525.3 & 0 & 12.2 & 280.9 & 50 \\ 
+		35 & 0.6 & 0.6 & 0.3 & 0.5 & 100 & 8.5 & 405.3 & 20 & 4.7 & 514.7 & 0 & 9.4 & 130.9 & 60 \\ 
+		40 & 0.4 & 0.5 & 0.2 & 0.3 & 100 & 9.6 & 390.6 & 20 & 4.4 & 500.1 & 0 & 3.4 & 11.3 & 95 \\ 
+		45 & 0.3 & 0.3 & 0.1 & 0.1 & 100 & 11.0 & 330.5 & 30 & 8.5 & 413.2 & 15 & * & * & 100 \\ 
+		50 & 0.3 & 0.3 & 0.1 & 0.1 & 100 & 9.8 & 123.0 & 70 & 11.0 & 199.1 & 50 & * & * & 100 \\ 
+		55 & 0.2 & 0.3 & * & 0.1 & 100 & 7.5 & 63.4 & 85 & 9.4 & 110.9 & 75 & * & * & 100 \\ 
+		60 & 0.2 & 0.2 & * & 0.1 & 100 & * & * & 100 & * & * & 100 & * & * & 100 \\ 
+		65 & 0.1 & 0.2 & * & * & 100 & 2.4 & 6.0 & 95 & 2.1 & 4.3 & 95 & * & * & 100 \\ 
+		70 & 0.1 & 0.1 & * & * & 100 & * & * & 100 & * & * & 100 & * & * & 100 \\ 
+		75 & 0.1 & 0.1 & * & * & 100 & * & * & 100 & * & * & 100 & * & * & 100 \\ 
+		\hline
+	\end{tabular}
+	\subcaption{Accuracy of variable selection: all the values are averaged over 20 replications}
+	\begin{tabular}{c|rrr|rr|rr|rr}
+		\hline
+		\multicolumn{1}{l|}{}&
+		\multicolumn{3}{c|}{RBCE}&
+		\multicolumn{2}{c|}{SCCE}&
+		\multicolumn{2}{c|}{BSSCE}&
+		\multicolumn{2}{c}{BSSL}\\
+		\hline
+		\multicolumn{1}{c|}{Obs}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c}{FN}&
+		\multicolumn{1}{c|}{ID}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c|}{FN}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c|}{FN}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c}{FN}
+		\\
+		\hline
+		25 & 1.8 & 0.6 & 31.8 & 0 & 14.7 & 0 & 14.9 & 2.0 & 11.6 \\ 
+		30 & 0.6 & 0.4 & 27.2 & 0 & 14.8 & 0 & 14.9 & 1.0 & 7.7 \\ 
+		35 & 0.2 & 0.5 & 16.9 & 0 & 13.1 & 0 & 15.0 & 0 & 5.2 \\ 
+		40 & 0 & 0.2 & 10 & 0 & 12.8 & 0 & 15.0 & 0 & 0.6 \\ 
+		45 & 0 & 0 & 2.9 & 0 & 10.2 & 0 & 12.9 & 0 & 0 \\ 
+		50 & 0 & 0 & 0.9 & 0 & 3.9 & 0 & 6.6 & 0 & 0 \\ 
+		55 & 0 & 0 & 0.4 & 0 & 2.0 & 0 & 3.5 & 0 & 0 \\ 
+		60 & 0 & 0 & 0.3 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+		65 & 0 & 0 & 0.3 & 0 & 0.6 & 0 & 0.6 & 0 & 0 \\ 
+		70 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+		75 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
+		\hline
+	\end{tabular}
+\end{table}
+
+\added{We present our analysis for case 1b in \cref{tab:causal1b}.
+Similar to our analyses for case 1a, we notice that as we obtain more observations the imprecision in the estimation reduces.
+However, unlike case 1a, our approach tends to over estimate the causal effect for higher number of observations.
+This also shows an overall increasing trend of the estimated causal effect similar to case 1a.
+We also notice that for case 1b number of indeterminate variables is higher than that of case 1a.
+This happens as some of the variables are only related to the outcome model.
+This also contributes to higher number of false negative variables in for other methods.
+We also observe that similar to the previous case, other methods often produces extreme values for the causal effect increasing the sd and MSE of the estimated causal effect.}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width = 0.9\linewidth]{treat_obs_rev.pdf}
 	\caption{\added{Comparison of different methods in estimating the causal effect for varying number of observations.
-On the left section (1a), we illustrate the results when all the active variables are confounders.
-On the right section (1b), we present the results when some variables are also related to the outcome model.}}
-\begin{tabular}{c|ccccc|ccccc}
-  \hline
- Case&  &  & \added{1a} &  &  &  &  & \added{1b} &  &  \\ 
-  \hline
-\added{Obs} & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL \\ 
-  \hline
-25 & 3.74 & 4.13 & 28.71 & 28.78 & 3.82 & 3.66 & 3.96 & 1.04 & 20.38 & 3.10 \\ 
-30 & 3.72 & 4.06 & 3.90 & 28.56 & 3.90 & 3.05 & 3.34 & 20.61 & 20.29 & -2.41 \\ 
-35 & 3.95 & 4.04 & 12.35 & 25.11 & 3.97 & 3.67 & 3.71 & 22.82 & 22.93 & 3.90 \\ 
-40 & 3.98 & 4.02 & 3.97 & 29.78 & 3.98 & 3.72 & 3.77 & 4.75 & 22.83 & 3.93 \\ 
-45 & 4.03 & 4.06 & 4.03 & 28.52 & 4.03 & 3.78 & 3.82 & 4.41 & 4.13 & 3.95 \\ 
-50 & 4.02 & 4.05 & 4.02 & 4.04 & 4.02 & 3.83 & 3.89 & 3.97 & 4.33 & 3.94 \\ 
-55 & 4.03 & 4.05 & 4.04 & 4.19 & 4.04 & 3.99 & 4.01 & 4.15 & 4.09 & 3.93 \\ 
-60 & 4.04 & 4.07 & 4.02 & 4.03 & 4.02 & 3.99 & 4.02 & 3.94 & 3.97 & 3.93 \\ 
-65 & 4.03 & 4.06 & 4.02 & 4.06 & 4.02 & 4.00 & 4.05 & 3.96 & 3.96 & 3.96 \\ 
-70 & 4.04 & 4.06 & 4.01 & 4.06 & 4.01 & 4.00 & 4.03 & 3.95 & 3.97 & 3.95 \\ 
-75 & 4.06 & 4.08 & 4.01 & 4.07 & 4.01 & 4.01 & 4.03 & 3.98 & 3.99 & 3.98 \\ 
-\hline
-\end{tabular}
-\label{tab:causal1}
-\end{table}
-\begin{figure}
-    \centering
-    \includegraphics[width = 0.95\linewidth]{treat_obs_rev.pdf}
-    \caption{\added{Comparison of different methods in estimating the causal effect for varying number of observations. The top (bottom) row
-    represents case 1a (case 1b). The left images show the estimated causal effects and right images show the same within $[3.8,4.2]$ to compare with true value. }}
+The top (bottom) row represents case 1a (case 1b).
+The left(right) images show the average(median) causal effects obtained from 20 replications.
+}}
 	\label{fig:comp:trt}
 \end{figure}
-\begin{figure}
-	\centering
-	\includegraphics[width = 0.95\linewidth]{treat_post_obs.png}
-	\caption{\added{Posterior of the causal effect for varying number of observations. The top (bottom) row
-			represents the posteriors for case 1a (case 1b).
-The green dotted (solid) lines represent the maximum of 5 (25) percentile taken over all $q$ and red dotted (solid) lines represent the minimum of 95 (75) percentile taken over all $q$.
-}}
-	\label{fig:post:trt:obs}
-\end{figure}
-
-We also provide tables for the performance of variable selection in \cref{fig:comp:loss:obs}.
-For variable selection, we use a loss function as described earlier.
-Here, we consider
-$\ell_1=\ell_2=1$ and $\ell_3= 0.2$,
-i.e. we associate a loss of $1$ with false positive and false negative selections,
-and a loss of $0.2$ with indeterminate selections.
-Note that we could also choose more 
-sophisticated loss functions based on \citep{ZAFFALON20121282}.
-We sum these losses together across all predictors
-\added{and divide by the total number of predictors} to obtain the total \added{relative} loss.
-From the \added{figure} it can be seen that for \added{case 1}, our method
-abstains from identifying some variables for 
-$n \le 35$. However,
-later on our method gives more precise results in terms of variable
-selection. We also notice that the SSCE and BSSCE tend to perform poorly
-in terms of variable selection \added{case 1a}. \added{For} case 
-\added{1b, even BSSL performs poorly for fewer number of observation leading to a higher relative loss, unlike case 1a.}
-
-\begin{figure}
+
+\added{We illustrate the estimated causal effect} in \cref{fig:comp:trt} as well. \added{In the figure, the top row
+illustrates the case 1a where the left image shows the average value of the estimated
+causal effect with respect to observations and the right image
+shows the median value. Similarly, the
+bottom row represents the same for case 1b.
+In the figure, RBCE bounds are given by red lines; SSCE estimates by blue lines; BSSCE estimates by green lines; BSSL estimates by purple line; and true value by black lines.
+In the figure, we can also notice the increase trend of the estimated causal effect as we obtain more observations and also the estimation becomes more precise.}
+
+\begin{figure}[h]
 	\centering
@@
 
-We show the result of our analyses with different number of predictors and
-fixed number of sample in \cref{tab:causal2,fig:comp:trt:pred}. Similar to
+We also illustrate the performance of variable selection in \cref{fig:comp:loss:obs}.
+For variable selection, we use a loss function as described earlier.
+Here, we consider
+$\ell_1=\ell_2=1$ and $\ell_3= 0.2$,
+i.e. we associate a loss of $1$ with false positive and false negative selections,
+and a loss of $0.2$ with indeterminate selections. 
+Note that we could also choose more 
+sophisticated loss functions based on \citep{ZAFFALON20121282}.
+We \added{evaluate the misspecification} loss \added{using the equation that we described before}.
+From the \added{figure} it can be seen that for \added{case 1}, our method
+abstains from identifying some variables for 
+$n \le 40$. However,
+later on our method gives more precise results in terms of variable
+selection. We also notice that the SSCE, BSSCE and BSSL tend to perform poorly
+in terms of variable selection. 
+\added{However, BSSL performs better than the rest for higher number of observations}
+
+\begin{table}[ht]
+	\tiny
+	\centering
+	\caption{\added{Comparison of different methods in estimating the causal effect for varying number of predictors where all the active variables are confounders.}}
+	\label{tab:causal2a}
+	\subcaption{Accuracy in estimation of causal effect}
+	\begin{tabular}{c|cccc|cc|cc|cc}
+		\hline
+		\multicolumn{1}{l|}{}&
+		\multicolumn{4}{c|}{RBCE}&
+		\multicolumn{2}{c|}{SCCE}&
+		\multicolumn{2}{c|}{BSSCE}&
+		\multicolumn{2}{c}{BSSL}\\
+		\hline
+		\multicolumn{1}{c|}{Pred}&
+		\multicolumn{2}{c}{Mean}&
+		\multicolumn{2}{c|}{Median}&
+		\multicolumn{1}{c}{Mean}&
+		\multicolumn{1}{c|}{Median}&
+		\multicolumn{1}{c}{Mean}&
+		\multicolumn{1}{c|}{Median}&
+		\multicolumn{1}{c}{Mean}&
+		\multicolumn{1}{c}{Median}\\
+		\hline
+		1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
+		\hline
+		25 & 3.6 & 3.8 & 3.7 & 3.8 & 9.5 & 4.6 & 11.8 & 14.0 & 4.0 & 4.0 \\ 
+		30 & 3.6 & 3.8 & 3.6 & 3.8 & 8.8 & 4.1 & 9.7 & 4.7 & 4.5 & 4.0 \\ 
+		35 & 3.6 & 3.8 & 3.6 & 3.8 & 12.8 & 17.4 & 12.8 & 14.9 & 4.9 & 4.0 \\ 
+		40 & 3.5 & 3.8 & 3.5 & 3.8 & 12.3 & 15.2 & 14.9 & 17.6 & 4.0 & 4.0 \\ 
+		45 & 3.5 & 3.8 & 3.4 & 3.8 & 10.7 & 4.1 & 16.6 & 18.3 & 4.0 & 4.0 \\ 
+		50 & 3.4 & 3.8 & 3.5 & 3.8 & 11.8 & 10.4 & 16.4 & 18.3 & 4.2 & 4.0 \\ 
+		55 & 3.4 & 3.8 & 3.4 & 3.8 & 12.4 & 15.6 & 16.6 & 18.8 & 4.5 & 4.0 \\ 
+		60 & 3.3 & 3.8 & 3.3 & 3.8 & 14.2 & 18.7 & 17.3 & 19.1 & 4.1 & 4.0 \\ 
+		65 & 3.2 & 3.8 & 3.3 & 3.8 & 12.6 & 15.5 & 19.4 & 19.2 & 5.0 & 4.0 \\ 
+		70 & 3.1 & 3.8 & 3.2 & 3.8 & 11.1 & 4.1 & 16.7 & 19.1 & 4.0 & 4.0 \\ 
+		75 & 3.1 & 3.8 & 3.1 & 3.8 & 11.7 & 9.3 & 18.4 & 19.2 & 4.5 & 4.0 \\ 
+		\hline
+	\end{tabular}
+	\subcaption{Dispersion of estimated causal effect: values less than 0.05 are replaced with *}
+	\begin{tabular}{c|rrrrr|rrr|rrr|rrr}
+		\hline
+		\multicolumn{1}{l|}{}&
+		\multicolumn{5}{c|}{RBCE}&
+		\multicolumn{3}{c|}{SCCE}&
+		\multicolumn{3}{c|}{BSSCE}&
+		\multicolumn{3}{c}{BSSL}\\
+		\hline
+		\multicolumn{1}{c|}{Pred}&
+		\multicolumn{2}{c}{sd}&
+		\multicolumn{2}{c}{MSE}&
+		\multicolumn{1}{c|}{CI\%}&
+		\multicolumn{1}{c}{sd}&
+		\multicolumn{1}{c}{MSE}&
+		\multicolumn{1}{c|}{CI\%}&
+		\multicolumn{1}{c}{sd}&
+		\multicolumn{1}{c}{MSE}&
+		\multicolumn{1}{c|}{CI\%}&
+		\multicolumn{1}{c}{sd}&
+		\multicolumn{1}{c}{MSE}&
+		\multicolumn{1}{c}{CI\%}
+		\\
+		\hline
+		25 & 0.2 & 0.2 & 0.1 & 0.2 & 100 & 6.6 & 72.1 & 50 & 7.1 & 109.3 & 45 & 0.1 & * & 100 \\ 
+		30 & 0.2 & 0.2 & 0.1 & 0.2 & 100 & 6.6 & 64.4 & 65 & 6.8 & 76.7 & 60 & 2.0 & 3.9 & 95 \\ 
+		35 & 0.2 & 0.2 & 0.1 & 0.2 & 100 & 7.4 & 129.2 & 35 & 7.4 & 130.1 & 40 & 4.1 & 16.6 & 90 \\ 
+		40 & 0.2 & 0.2 & 0.1 & 0.2 & 100 & 7.9 & 129.0 & 45 & 6.7 & 162.0 & 30 & 0.1 & * & 95 \\ 
+		45 & 0.2 & 0.2 & 0.1 & 0.3 & 100 & 7.8 & 102.5 & 55 & 5.7 & 190.4 & 20 & 0.1 & * & 100 \\ 
+		50 & 0.2 & 0.3 & 0.1 & 0.4 & 100 & 7.8 & 118.7 & 45 & 6.4 & 191.7 & 20 & 0.9 & 0.7 & 95 \\ 
+		55 & 0.2 & 0.3 & 0.1 & 0.5 & 100 & 8.0 & 132.4 & 45 & 6.8 & 201.9 & 25 & 2.3 & 5.2 & 95 \\ 
+		60 & 0.2 & 0.3 & 0.1 & 0.6 & 100 & 8.1 & 165.8 & 30 & 6.2 & 214.7 & 15 & 0.6 & 0.4 & 100 \\ 
+		65 & 0.2 & 0.4 & 0.1 & 0.8 & 100 & 8.3 & 139.2 & 40 & 2.8 & 244.0 & 0 & 4.4 & 19.1 & 95 \\ 
+		70 & 0.2 & 0.4 & 0.1 & 0.9 & 100 & 8.2 & 114.9 & 55 & 6.6 & 202.1 & 25 & 0.1 & * & 95 \\ 
+		75 & 0.2 & 0.4 & 0.1 & 1.0 & 100 & 8.0 & 120.2 & 50 & 4.8 & 228.7 & 10 & 3.5 & 11.9 & 85 \\ 
+		\hline
+	\end{tabular}
+	\subcaption{Accuracy of variable selection: all the values are averaged over 20 replications}
+	\begin{tabular}{c|rrr|rr|rr|rr}
+		\hline
+		\multicolumn{1}{l|}{}&
+		\multicolumn{3}{c|}{RBCE}&
+		\multicolumn{2}{c|}{SCCE}&
+		\multicolumn{2}{c|}{BSSCE}&
+		\multicolumn{2}{c}{BSSL}\\
+		\hline
+		\multicolumn{1}{c|}{Pred}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c}{FN}&
+		\multicolumn{1}{c|}{ID}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c|}{FN}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c|}{FN}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c}{FN}
+		\\
+		\hline
+		25 & 0 & 0 & 5.2 & 0 & 4.0 & 0 & 5.5 & 0 & 0 \\ 
+		30 & 0 & 0 & 2.4 & 0 & 3.5 & 0 & 4.1 & 0 & 0.4 \\ 
+		35 & 0 & 0 & 2.0 & 0 & 6.0 & 0 & 6.0 & 0 & 0.5 \\ 
+		40 & 0 & 0 & 2.1 & 0 & 5.4 & 0 & 7.3 & 0 & 0 \\ 
+		45 & 0 & 0 & 2.6 & 0 & 4.4 & 0 & 8.4 & 0 & 0 \\ 
+		50 & 0 & 0 & 3.0 & 0 & 5.1 & 0 & 8.2 & 0 & 0.2 \\ 
+		55 & 0 & 0 & 3.8 & 0 & 5.4 & 0 & 7.9 & 0 & 0.4 \\ 
+		60 & 0 & 0 & 5.0 & 0 & 6.4 & 0 & 8.4 & 0 & 0 \\ 
+		65 & 0 & 0 & 4.4 & 0 & 5.4 & 0 & 9.9 & 0 & 0.5 \\ 
+		70 & 0 & 0 & 4.8 & 0 & 4.4 & 0 & 8.0 & 0 & 0 \\ 
+		75 & 0 & 0 & 6.2 & 0 & 4.9 & 0 & 9.2 & 2.4 & 0.6 \\ 
+		\hline
+	\end{tabular}
+\end{table}
+
+We show the result of our analyses \added{case 2a} in \cref{tab:causal2a}. Similar to
 our analyses with increasing number of observations, we notice that our method 
 is overall in agreement with
-\added{BSSL for case 2a}. However, our method tends to
-underestimate the treatment effect (approximately 8\% in the worst case) for \added{case 2b}. 
-This result is also similar to our
-analyses with increasing number of observations in \cref{tab:causal1}
-\added{especially, for 1b with fewer observations than the predictors}.
-In general, \added{this can be explained from the fact that our prior sensitivity analysis gives us indeterminate variables in some cases and as a result the regression coefficients may not be shrinked close to zero leading to some deviations in the causal effect estimation.
-Similar to our analyses with varying observations, we also provide the posteriors of the causal effect in \cref{fig:post:trt:pred}.
-We notice that for case 2a the true value is always contained within 25 to 75 percentiles.
-However, for case 2b, the true values is not contained within 25 to 75 percentiles in 4 different cases, though they were inside 5 and 95 percentiles bound}.
-
-\added{Besides these, we also provide the performance in variable selection for case 2a and 2b in \cref{fig:comp:loss:pred}.
-We notice that our method performs extremely good and outperforms all the other methods in most cases.
-Only SSCE and BSSCE is able to match our accuracy in variable selection in few cases.
-}
+\added{BSSL}. However, \added{similar to case 1a} our method tends to
+underestimate the treatment effect (approximately 5\%) for \added{case 2b}.
+\added{We also notice that the imprecision in estimation increases as we increase the number of predictors.
+This happens as observation per predictor reduces.
+We also notice that BSSL outperforms RBCE in terms of median value of estimated causal effect over 20 replications.
+However, in very few cases BSSL provides extreme values which can be understood from mean and CI\% as well as MSE.
+Moreover, for 75 predictors BSSL gives higher number of false positives which is not the case for RBCE.
+Unlike the case 1a and 1b, SSCE and BSSCE performs poorly for every value of predictors.}
+
+\begin{table}[h]
+	\tiny
+	\centering
+	\caption{\added{Comparison of different methods in estimating the causal effect for varying number of predictors where some variables are only to the outcome model.}}
+	\label{tab:causal2b}
+	\subcaption{Accuracy in estimation of causal effect}
+	\begin{tabular}{c|cccc|cc|cc|cc}
+		\hline
+		\multicolumn{1}{c|}{}&
+		\multicolumn{4}{c|}{RBCE}&
+		\multicolumn{2}{c|}{SCCE}&
+		\multicolumn{2}{c|}{BSSCE}&
+		\multicolumn{2}{c}{BSSL}\\
+		\hline
+		\multicolumn{1}{c|}{Pred}&
+		\multicolumn{2}{c}{Mean}&
+		\multicolumn{2}{c|}{Median}&
+		\multicolumn{1}{c}{Mean}&
+		\multicolumn{1}{c|}{Median}&
+		\multicolumn{1}{c}{Mean}&
+		\multicolumn{1}{c|}{Median}&
+		\multicolumn{1}{c}{Mean}&
+		\multicolumn{1}{c}{Median}\\
+		\hline
+		1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
+		\hline
+		25 & 3.8 & 4.1 & 3.8 & 4.1 & 19.0 & 22.3 & 24.0 & 25.3 & 4.0 & 4.0 \\ 
+		30 & 3.9 & 4.2 & 3.9 & 4.1 & 20.6 & 24.6 & 20.9 & 24.5 & 7.4 & 4.0 \\ 
+		35 & 3.9 & 4.3 & 3.9 & 4.2 & 21.9 & 24.7 & 23.7 & 24.8 & 7.3 & 4.0 \\ 
+		40 & 3.9 & 4.3 & 3.9 & 4.3 & 20.9 & 24.4 & 24.7 & 25.5 & 5.1 & 4.0 \\ 
+		45 & 3.8 & 4.3 & 3.9 & 4.3 & 20.2 & 23.9 & 26.1 & 25.4 & 4.8 & 4.0 \\ 
+		50 & 3.9 & 4.3 & 3.9 & 4.3 & 21.4 & 24.6 & 26.0 & 25.4 & 4.7 & 4.0 \\ 
+		55 & 3.8 & 4.4 & 3.9 & 4.4 & 21.8 & 24.8 & 26.0 & 25.1 & 9.5 & 4.0 \\ 
+		60 & 3.8 & 4.4 & 3.9 & 4.4 & 16.6 & 19.7 & 25.1 & 25.5 & 8.4 & 4.0 \\ 
+		65 & 3.7 & 4.4 & 3.8 & 4.4 & 18.7 & 22.8 & 26.2 & 25.6 & 5.4 & 4.0 \\ 
+		70 & 3.7 & 4.5 & 3.8 & 4.4 & 20.4 & 23.9 & 25.5 & 25.2 & 8.5 & 4.0 \\ 
+		75 & 3.7 & 4.5 & 3.7 & 4.4 & 17.7 & 22.8 & 26.0 & 25.2 & 5.0 & 4.0 \\ 
+		\hline
+	\end{tabular}
+	\subcaption{Dispersion of estimated causal effect: values less than 0.05 are replaced with *}
+	\begin{tabular}{c|rrrrr|rrr|rrr|rrr}
+		\hline
+		\multicolumn{1}{c|}{}&
+		\multicolumn{5}{c|}{RBCE}&
+		\multicolumn{3}{c|}{SCCE}&
+		\multicolumn{3}{c|}{BSSCE}&
+		\multicolumn{3}{c}{BSSL}\\
+		\hline
+		\multicolumn{1}{c|}{Pred}&
+		\multicolumn{2}{c}{sd}&
+		\multicolumn{2}{c}{MSE}&
+		\multicolumn{1}{c|}{CI\%}&
+		\multicolumn{1}{c}{sd}&
+		\multicolumn{1}{c}{MSE}&
+		\multicolumn{1}{c|}{CI\%}&
+		\multicolumn{1}{c}{sd}&
+		\multicolumn{1}{c}{MSE}&
+		\multicolumn{1}{c|}{CI\%}&
+		\multicolumn{1}{c}{sd}&
+		\multicolumn{1}{c}{MSE}&
+		\multicolumn{1}{c}{CI\%}
+		\\
+		\hline
+		25 & 0.2 & 0.3 & 0.1 & 0.1 & 100 & 11.2 & 343.7 & 35 & 8.0 & 459.5 & 10 & 0.1 & * & 100 \\ 
+		30 & 0.3 & 0.4 & 0.1 & 0.1 & 100 & 10.4 & 377.0 & 25 & 10.8 & 397.7 & 25 & 8.3 & 77.9 & 85 \\ 
+		35 & 0.3 & 0.4 & 0.1 & 0.2 & 100 & 9.9 & 412.9 & 20 & 7.4 & 438.6 & 10 & 8.0 & 71.7 & 85 \\ 
+		40 & 0.4 & 0.4 & 0.1 & 0.3 & 100 & 9.3 & 366.8 & 15 & 7.0 & 475.8 & 10 & 4.8 & 23.1 & 95 \\ 
+		45 & 0.4 & 0.4 & 0.2 & 0.3 & 100 & 10.4 & 365.5 & 25 & 4.4 & 504.8 & 0 & 3.4 & 11.3 & 95 \\ 
+		50 & 0.4 & 0.5 & 0.2 & 0.3 & 100 & 9.6 & 390.6 & 20 & 4.4 & 500.1 & 0 & 3.4 & 11.3 & 95 \\ 
+		55 & 0.4 & 0.5 & 0.2 & 0.3 & 100 & 9.9 & 410.6 & 20 & 4.5 & 503.9 & 0 & 9.9 & 123.1 & 75 \\ 
+		60 & 0.5 & 0.5 & 0.2 & 0.4 & 100 & 11.7 & 288.5 & 40 & 6.4 & 484.0 & 5 & 9.3 & 102.4 & 80 \\ 
+		65 & 0.4 & 0.5 & 0.2 & 0.4 & 100 & 11.2 & 334.4 & 30 & 4.5 & 510.0 & 0 & 6.4 & 40.5 & 95 \\ 
+		70 & 0.5 & 0.5 & 0.2 & 0.5 & 100 & 11.1 & 385.3 & 25 & 5.2 & 488.8 & 5 & 9.3 & 102.1 & 80 \\ 
+		75 & 0.5 & 0.5 & 0.2 & 0.5 & 100 & 11.8 & 318.1 & 40 & 4.5 & 502.1 & 0 & 4.0 & 16.3 & 95 \\ 
+		\hline
+	\end{tabular}
+	\subcaption{Accuracy of variable selection: all the values are averaged over 20 replications}
+	\begin{tabular}{c|rrr|rr|rr|rr}
+		\hline
+		\multicolumn{1}{c|}{}&
+		\multicolumn{3}{c|}{RBCE}&
+		\multicolumn{2}{c|}{SCCE}&
+		\multicolumn{2}{c|}{BSSCE}&
+		\multicolumn{2}{c}{BSSL}\\
+		\hline
+		\multicolumn{1}{c|}{Pred}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c}{FN}&
+		\multicolumn{1}{c|}{ID}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c|}{FN}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c|}{FN}&
+		\multicolumn{1}{c}{FP}&
+		\multicolumn{1}{c}{FN}
+		\\
+		\hline
+		25 & 0 & 0 & 7.8 & 0 & 10.2 & 0 & 13.5 & 0 & 0 \\ 
+		30 & 0 & 0 & 8.2 & 0 & 11.6 & 0 & 11.2 & 0 & 2.0 \\ 
+		35 & 0 & 0 & 9.2 & 0 & 12.6 & 0 & 14.0 & 0 & 2.2 \\ 
+		40 & 0 & 0 & 10.1 & 0 & 11.9 & 0 & 13.8 & 0 & 0.8 \\ 
+		45 & 0 & 0.1 & 10.8 & 0 & 11.8 & 0 & 15.0 & 0 & 0.6 \\ 
+		50 & 0 & 0.2 & 10.1 & 0 & 12.8 & 0 & 15.0 & 0 & 0.6 \\ 
+		55 & 0 & 0.3 & 8.9 & 0 & 12.0 & 0 & 15.0 & 0 & 3.5 \\ 
+		60 & 0 & 0.4 & 11.1 & 0 & 9.2 & 0 & 14.4 & 0.5 & 2.9 \\ 
+		65 & 0 & 0.8 & 11.9 & 0 & 10.6 & 0 & 15.0 & 0.4 & 0.8 \\ 
+		70 & 0 & 0.8 & 12.8 & 0 & 10.9 & 0 & 14.8 & 0 & 2.8 \\ 
+		75 & 0 & 1.0 & 12.3 & 0.1 & 9.6 & 0 & 15.0 & 0 & 0.9 \\ 
+		\hline
+	\end{tabular}
+\end{table}
+
+\added{The result for case 2b is presented in \cref{tab:causal2b}.
+We notice that for this case the true causal effect is always contained within the estimated bounds unlike the previous cases.
+For this case, the imprecision in the estimated causal effect increases with respect to predictors similar to case 2a as the observation per predictor reduces.
+We also see that SSCE and BSSCE performs poorly similar to case 2a and BSSL is mostly consistent in estimation but produces extreme values for some experiments giving a significant differences between mean and median of the estimated causal treatments.}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width = 0.85\linewidth]{treat_pred_rev.pdf}
+	\caption{\added{Comparison of different methods in estimating the causal effect for varying number of predictors.
+The top (bottom) row represents case 2a (case 2b).
+The left(right) images show the average(median) causal effects obtained from 20 replications.
+}}
+	\label{fig:comp:trt:pred}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width = 0.9\linewidth]{loss_pred.pdf}
+	\caption{\added{Comparison of different methods in identifying the confounders for varying number of predictors.
+One the left (right) we present case 1a (1b).
+The red line presents RBCE; blue line presents SSCE; green line presents BSSCE; and purple line
+			presents BSSL}}
+	\label{fig:comp:loss:pred}
+\end{figure}
+
+\added{We also show the causal effect estimation and performance in variable selection in \cref{fig:comp:trt:pred,fig:comp:loss:pred}.
+From \cref{fig:comp:trt:pred} we can see the increase in imprecision as we increase then number of predictors.
+We also see that RBCE performs more consistently than other methods in terms of estimating the causal effect.
+We also notice that BSSL outperforms RBCE in terms of estimating the causal effect and performs at per in terms of variable selection for case 2a.
+However, for case 2b, BSSL appears to be less consistent in terms of variable selection.
+From these two figures we can also see that SSCE and BSSCE performs poorly as we increase the number of predictors and is particularly unstable for case 2a.}
 
@@
 % Mon Mar 25 10:08:22 2024
-\begin{table}[ht]
-\centering
-\tiny
-\caption{\added{Comparison of different methods in estimating the causal effect for varying number of predictors.
-On the left section (2a), we illustrate the results when all the active variables are confounders.
-On the right section (2b), we present the results when some variables are also related to the outcome model.}}
-\begin{tabular}{c|ccccc|ccccc}
-  \hline
- Case&  &  & \added{2a} &  &  &  &  & \added{2b} &  &  \\ 
-  \hline
- \added{Pred} & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL & RBCE-l & RBCE-u & SSCE & BSSCE & BSSL \\ 
-  \hline
- 25 & 3.90 & 3.94 & 29.44 & 4.07 & 3.98 & 3.61 & 3.70 & 3.98 & 4.07 & 3.94 \\ 
- 30 & 3.89 & 3.96 & 3.97 & 4.04 & 3.98 & 3.61 & 3.69 & 4.03 & 4.19 & 3.94 \\ 
- 35 & 3.96 & 4.00 & 4.75 & 4.15 & 3.98 & 3.62 & 3.73 & 3.95 & 6.77 & 3.92 \\ 
- 40 & 3.96 & 4.01 & 3.98 & 4.55 & 3.97 & 3.56 & 3.71 & 3.98 & 22.76 & 3.92 \\ 
- 45 & 3.98 & 4.01 & 3.98 & 4.28 & 3.98 & 3.72 & 3.75 & 17.81 & 21.77 & 3.93 \\ 
- 50 & 3.98 & 4.05 & 10.55 & 29.61 & 3.98 & 3.65 & 3.77 & 22.70 & 22.43 & 3.95 \\ 
- 55 & 3.98 & 4.02 & 29.61 & 29.56 & 3.97 & 3.74 & 3.81 & 4.60 & 14.69 & 3.94 \\ 
- 60 & 3.99 & 4.07 & 3.97 & 29.72 & 3.98 & 3.77 & 3.83 & 6.88 & 21.84 & 3.94 \\ 
- 65 & 4.02 & 4.11 & 3.97 & 29.67 & 3.97 & 3.77 & 3.88 & 3.94 & 22.23 & 3.92 \\ 
- 70 & 4.01 & 4.12 & 5.70 & 28.93 & 3.98 & 3.74 & 3.86 & 4.34 & 22.54 & 3.91 \\ 
- 75 & 4.00 & 4.11 & 3.97 & 29.96 & 3.98 & 3.73 & 3.84 & 6.46 & 18.41 & 3.93 \\ 
+
+\begin{table}[h]
+	\caption{\added{Effect of elicitation of the inclusion probability of the variables where FP stands for false positive, FN stands for false negative and ID stands for indeterminate. }}
+	\label{tab:comp:elict}\centering
+	\begin{tabular}{c|rrrrr|rrrrr}
+		\hline
+		\multicolumn{1}{c|}{$[\underline{c},\overline{c}]$}&
+		\multicolumn{5}{c|}{$[0.15,0.35]$}&
+		\multicolumn{5}{c}{$[0.2,0.4]$}\\
+		\hline
+		\multicolumn{1}{c|}{Pred}&
+		\multicolumn{2}{c}{Mean} &
+		\multicolumn{1}{c}{FP} &
+		\multicolumn{1}{c}{FN} &
+		\multicolumn{1}{c|}{IDR} &
+		\multicolumn{2}{c}{Mean} &
+		\multicolumn{1}{c}{FP} &
+		\multicolumn{1}{c}{FN} &
+		\multicolumn{1}{c}{IDR}\\
+		\hline
+		25 & 3.8 & 4.1 & 0 & 0 & 7.8 & 3.9 & 4.2 & 0 & 0 & 4.9 \\ 
+		30 & 3.9 & 4.2 & 0 & 0 & 8.2 & 3.9 & 4.3 & 0 & 0 & 4.2 \\ 
+		35 & 3.9 & 4.3 & 0 & 0 & 9.2 & 4.0 & 4.3 & 0 & 0.2 & 3.5 \\ 
+		40 & 3.9 & 4.3 & 0 & 0 & 10.1 & 4.0 & 4.4 & 0 & 0.3 & 3.4 \\ 
+		45 & 3.8 & 4.3 & 0 & 0.1 & 10.8 & 4.0 & 4.4 & 0 & 0.4 & 3.5 \\ 
+		50 & 3.9 & 4.3 & 0 & 0.2 & 10.1 & 4.0 & 4.4 & 0 & 0.6 & 3.0 \\ 
+		55 & 3.8 & 4.4 & 0 & 0.3 & 8.9 & 4.0 & 4.4 & 0 & 0.6 & 3.0 \\ 
+		60 & 3.8 & 4.4 & 0 & 0.4 & 11.1 & 4.0 & 4.5 & 0 & 0.8 & 3.4 \\ 
+		65 & 3.7 & 4.4 & 0 & 0.8 & 11.9 & 4.0 & 4.5 & 0 & 1.0 & 3.8 \\ 
+		70 & 3.7 & 4.5 & 0 & 0.8 & 12.8 & 4.0 & 4.5 & 0 & 1.3 & 3.0 \\ 
+		75 & 3.7 & 4.5 & 0 & 1.0 & 12.3 & 4.0 & 4.5 & 0 & 1.4 & 3.1 \\ 
 		\hline
 	\end{tabular}
-\label{tab:causal2}
 \end{table}
-
-\begin{figure}
-    \centering
-    \includegraphics[width = 0.9\linewidth]{treat_pred_rev.pdf}
-    \caption{\added{Comparison of different methods in estimating the causal effect for varying number of predictors.}}
-    \label{fig:comp:trt:pred}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width = 0.95\linewidth]{treat_post_pred.png}
-	\caption{\added{Posterior of the causal effect for varying number of predictors. The top (bottom) row
-			represents the posteriors for case 2a (case 2b).
-The green dotted (solid) lines represent the maximum of 5 (25) percentile taken over all $q$ and red dotted (solid) lines represent the minimum of 95 (75) percentile taken over all $q$.
-}}
-	\label{fig:post:trt:pred}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width = 0.9\linewidth]{loss_pred.pdf}
-	\caption{\added{Comparison of different methods in identifying the confounders for varying number of predictors.}}
-	\label{fig:comp:loss:pred}
-\end{figure}
 
@@
 On the left hand side, we see our method tends to give higher number of indeterminate variables for fewer observations than the right hand side.
-As we increase the observation the higher threshold of marginal correlation plays an important role and we see more cases of false negative variables on the right hand side.
-}
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{c|ccc|ccc}
-		\hline
-		$[\underline{c},\overline{c}]$ &  &   $[0.15,0.35]$ &    &  & $[0.2,0.4]$ &    \\
-		\hline
-		Pred & FP & FN & ID & FP & FN & ID  \\ 
-		\hline
-		25 & 0 & 0 & 1 & 0 & 0 & 1  \\ 
-		30 & 0 & 0 & 3 & 0 & 0 & 1  \\ 
-		35 & 0 & 0 & 2 & 0 & 0 & 1  \\ 
-		40 & 0 & 0 & 2 & 0 & 0 & 1  \\ 
-		45 & 0 & 0 & 1 & 0 & 1 & 0  \\ 
-		50 & 0 & 0 & 1 & 0 & 1 & 0  \\ 
-		55 & 0 & 0 & 1 & 0 & 1 & 0  \\ 
-		60 & 0 & 0 & 1 & 0 & 1 & 0  \\ 
-		65 & 0 & 1 & 0 & 0 & 1 & 0  \\ 
-		70 & 0 & 1 & 0 & 0 & 1 & 0  \\ 
-		75 & 0 & 1 & 1 & 0 & 1 & 1  \\ 
-		\hline
-	\end{tabular}
-	\caption{\added{Effect of elicitation of the inclusion probability of the variables where FP stands for false positive, FN stands for false negative and ID stands for indeterminate. }}
-	\label{tab:comp:elict}
-\end{table}
+As we increase the predictors the higher threshold of marginal correlation plays an important role and we see more cases of false negative variables on the right hand side.
+This also results to over estimation of the causal effect as many true active variables are shrinked towards zero.
+As a result the lower bound of the averaged causal effect is more than four on the right hand side.}
+
+The analyses and simulation studies can be investigated using the code from \url{https://github.com/tathagatabasu/Causal-Inference}.
 
@@
 method tends to underestimate the causal effect
-when some predictors are only associated with the
-outcome model. This suggests that we might want
+when \added{only confounders are present in the}
+model. This suggests that we might want
 to use a correction formula for the causal effect.

### 2024-09-30 causal.R

@@ -1,147 +1,0 @@
-library(mvtnorm)
-library(rjags)
-library(SSLASSO)
-library(monomvn)
-library(spikeslab)
-library(horseshoe)
-library(glmnet)
-library(ncvreg)
-library(xtable)
-library(foreach)
-library(doParallel)
-
-ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 50, gam_b = 1, n.burn = 500, n.sample = 2500){
-  MCMC = list()
-  
-  string = "
-  model {
-  
-    ## Likelihood
-    
-    for (i in 1:N) 
-    {
-      mean[i] = b_T * a[i] + inprod(x[i,], b) + b_int
-      y[i] ~ dnorm(mean[i], inv.var)
-      
-      a[i] ~ dbern(a_prob[i])
-      
-      probit(a_prob[i]) = a_dumm[i]
-      
-      a_dumm[i] = inprod(x[i,], g) + g_int
-    }
-    
-    # Prior on the mean
-    
-    b_T ~ dnorm(0,inv.var)
-    
-    b_int ~ dnorm(0,inv.var)
-
-    g_int ~ dnorm(0,1)
-
-    # prior on the precision
-    
-    inv.var ~ dgamma(gam_a, gam_b)
-    
-    sigma2 = 1 / inv.var
-    
-    ## Prior on the regression parameters 
-    
-    for (j in 1:p) 
-    {
-      # prior on the selection probability
-      
-      w[j] ~ dbeta(2*alpha, 2*(1-alpha))I(0.001,0.999)
-      
-      # Prior on beta
-      
-      spike[j] ~ dnorm(0, (inv.var / tau_0^2))
-      slab[j] ~ dnorm(0, (inv.var / tau_1^2))
-      
-      b[j] = w[j] * slab[j]  + (1 - w[j]) * spike[j]
-      
-      # Prior on gamma
-      
-      spikeg[j] ~ dnorm(0, (1 / tau_0^2))
-      slabg[j] ~ dnorm(0, (1 / tau_1^2))
-      
-      g[j] = w[j] * slabg[j]  + (1 - w[j]) * spikeg[j]
-    }
-    
-  }
-  "
-  params = c("b","b_int", "b_T", "g", "g_int", "sigma2", "w")
-  
-  for (i in 1:length(alphas)) {
-    
-    alpha = as.vector(alphas[i])
-    
-    ISVS <- textConnection(string, open = "r")
-    
[…]

### 2024-09-30 causal_sims.R

@@ -1,444 +1,0 @@
-source("other_causal.R")
-source("causal.R")
-source("mclapply.R")
-
-set.seed(1e8)
-
-##############################################################################################
-# data generation
-
-n = 100
-M = 20
-p = 75
-no.of.cores = 10
-
-sig = matrix(nrow=p,ncol = p)
-
-for (i in 1:p) {
-  for (j in 1:p) {
-    sig[i,j] = 0.3^abs(i-j)
-  }
-}
-
-x_all = lapply(1:M, function(i)rmvnorm(n, sigma = sig))
-
-# data with setting 1
-
-beta1 = c(runif(5,-5,-1), runif(5,1,5))
-gamma1 = c(runif(5,-5,-1), runif(5,1,5))
-
-a1_dum_all = lapply(1:M, function(i) (1/(1 + exp(-x_all[[i]][,1:length(gamma1)] %*% gamma1))))
-a1_all = lapply(1:M, function(i) (sapply(1:n, function(j)rbinom(1,1,a1_dum_all[[i]][j]))))
-
-y1_all = lapply(1:M, function(i) (4*a1_all[[i]] + x_all[[i]][,1:length(beta1)] %*% beta1 + rnorm(n, sd = .1)))
-
-# data with setting 2
-
-beta2 = c(runif(5,-5,-1), runif(10,1,5))
-
-a2_dum_all = lapply(1:M, function(i) (1/(1 + exp(-x_all[[i]][,1:length(gamma1)] %*% gamma1))))
-a2_all = lapply(1:M, function(i) (sapply(1:n, function(j)rbinom(1,1,a2_dum_all[[i]][j]))))
-
-y2_all = lapply(1:M, function(i) (4*a2_all[[i]] + x_all[[i]][,1:length(beta2)] %*% beta2 + rnorm(n, sd = .1)))
-
-##############################################################################################
-# For increasing observation
-
-# setting1
-
-if(F){
-  
-  for (k in 1:11) { #
-    N = 20 + 5*k
-    
-    assign(paste0("set1_RBCE_",k), mclapply.hack(1:M, function(i) rbce_wrapper_sim(x_all[[i]][1:N,1:50], y1_all[[i]][1:N], a1_all[[i]][1:N]), mc.cores = no.of.cores))
[…]

### 2024-09-30 codes/causal.R

@@ -1,0 +1,148 @@
+library(mvtnorm)
+library(rjags)
+library(SSLASSO)
+library(monomvn)
+library(spikeslab)
+library(horseshoe)
+library(glmnet)
+library(ncvreg)
+library(xtable)
+library(foreach)
+library(doParallel)
+
+ISVS = function(x, y, a, alphas, tau_0 = 1e-6, tau_1 = 5, gam_a = 50, gam_b = 1, n.burn = 500, n.sample = 2500){
+  MCMC = list()
+  
+  string = "
+  model {
+  
+    ## Likelihood
+    
+    for (i in 1:N) 
+    {
+      mean[i] = b_T * a[i] + inprod(x[i,], b) + b_int
+      y[i] ~ dnorm(mean[i], inv.var)
+      
+       a_us[i] ~ dbern(a_prob[i])
+      
+      probit(a_prob[i]) = a_dumm[i]
+      
+      a_dumm[i] = inprod(x[i,], g) + g_int
+    }
+    
+    # Prior on the mean
+    
+    b_T ~ dnorm(0,inv.var)
+    
+    b_int ~ dnorm(0,inv.var)
+
+    g_int ~ dnorm(0,1)
+
+    # prior on the precision
+    
+    inv.var ~ dgamma(gam_a, gam_b)
+    
+    sigma2 = 1 / inv.var
+    
+    ## Prior on the regression parameters 
+    
+    for (j in 1:p) 
+    {
+      # prior on the selection probability
+      
+      w[j] ~ dbeta(2*alpha, 2*(1-alpha))I(0.001,0.999)
+      
+      # Prior on beta
+      
+      spike[j] ~ dnorm(0, (inv.var / tau_0^2))
+      slab[j] ~ dnorm(0, (inv.var / tau_1^2))
+      
+      b[j] = w[j] * slab[j]  + (1 - w[j]) * spike[j]
+      
+      # Prior on gamma
+      
+      spikeg[j] ~ dnorm(0, (1 / tau_0^2))
+      slabg[j] ~ dnorm(0, (1 / tau_1^2))
+      
+      g[j] = w[j] * slabg[j]  + (1 - w[j]) * spikeg[j]
+    }
+    
+  }
+  "
+  params = c("b","b_int", "b_T", "g", "g_int", "sigma2", "w")
+  
+  for (i in 1:length(alphas)) {
+    
+    alpha = as.vector(alphas[i])
+    
+    ISVS <- textConnection(string, open = "r")
[…]

### 2024-09-30 codes/causal_sims.R

@@ -1,0 +1,549 @@
+source("other_causal.R")
+source("causal.R")
+source("mclapply.R")
+
+set.seed(1e8)
+
+##############################################################################################
+# data generation
+
+if(F){
+  n = 100
+  M = 20
+  p = 75
+  no.of.cores = 15
+  
+  sig = matrix(nrow=p,ncol = p)
+  
+  for (i in 1:p) {
+    for (j in 1:p) {
+      sig[i,j] = 0.3^abs(i-j)
+    }
+  }
+  
+  x_all = lapply(1:M, function(i)rmvnorm(n, sigma = sig))
+  
+  # data with setting 1
+  
+  beta1 = c(runif(5,-5,-1), runif(5,1,5))
+  gamma1 = c(runif(5,-5,-1), runif(5,1,5))
+  
+  a1_dum_all = lapply(1:M, function(i) (1/(1 + exp(-x_all[[i]][,1:length(gamma1)] %*% gamma1))))
+  a1_all = lapply(1:M, function(i) (sapply(1:n, function(j)rbinom(1,1,a1_dum_all[[i]][j]))))
+  
+  y1_all = lapply(1:M, function(i) (4*a1_all[[i]] + x_all[[i]][,1:length(beta1)] %*% beta1 + rnorm(n, sd = .1)))
+  
+  # data with setting 2
+  
+  beta2 = c(runif(5,-5,-1), runif(10,1,5))
+  
+  a2_dum_all = lapply(1:M, function(i) (1/(1 + exp(-x_all[[i]][,1:length(gamma1)] %*% gamma1))))
+  a2_all = lapply(1:M, function(i) (sapply(1:n, function(j)rbinom(1,1,a2_dum_all[[i]][j]))))
+  
+  y2_all = lapply(1:M, function(i) (4*a2_all[[i]] + x_all[[i]][,1:length(beta2)] %*% beta2 + rnorm(n, sd = .1)))
+}
+
+##############################################################################################
+# For increasing observation
+
+# setting1
+
+if(F){
+  
+  for (k in 1:11) { #
+    N = 20 + 5*k
+    
[…]
